### 2023-01-07 manuscript.Rmd
Set-up of manuscript and associated files

---
title: "Binocular integration of chromatic information"
author: |
   | Daniel H. Baker, Kirralise J. Hansford, Federico G. Segala, Rowan J. Huxley,   
   | Joel T. Martin, Lauren E. Welbourne & Alex R. Wade
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document: default
  pdf_document:
    toc: no
  html_document: default
bibliography: references.bib
csl: elife.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

# Introduction

# Materials & Methods

## Participants

All four experiments were completed by the first author (DHB) and two other participants, who differed for each experiment. Written informed consent was provided before data collection began, and all procedures were approved by the ethics committee of the Department of Psychology at the University of York.

## Apparatus & stimuli

In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg. The gratings were windowed by a raised cosine envelope with a diameter of 3 degrees. Spatial phase, relative to a central fixation cross, was randomised on each trial across the four cardinal phases. In the achromatic conditions, the sine-wave modulated all three colour channels equally. In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant. In the (L+M)-S condition, the isoluminant stimuli maximised S-cone contrast. Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals [@Stockman2000].

The stimuli in Experiments 3 and 4 were temporal modulations of luminance and colour, using the same raised cosine envelope as described above, but with no further spatial modulation. The stimuli counterphase flickered sinusoidally at 4Hz, along the same axes of luminance and colour as described for Experiments 1 and 2.

In all experiments, we displayed a binocular fusion lock, consisting of three concentric rings of small square elements with random colour. A black central fixation cross was also displayed throughout.

All stimuli were presented on an Iiyama VisionMaster Pro 510 CRT monitor, with a refresh rate of 100Hz, and a resolution of 1024 x 768 pixels. The display was driven by a ViSaGe MkII stimulus generator (Cambridge Research Systems Ltd., Kent, UK) running in 42-bit colour mode (14 bits per colour channel). We presented stimuli to the left and right eyes independently using a four-mirror stereoscope with front-silvered mirrors. The display was luminance calibrated using a ColourCal photometer (Cambridge Research Systems), and gamma corrected by fitting a four-parameter gamma function to the output of each CRT gun. The maximum luminance was 87 cd/m$^2$. We also measured the spectral output of each phosphor using a Jaz spectroradiometer (Ocean Insight, Florida), and used these measurements to convert between LMS (cone) space and the monitor RGB coordinates.

## Procedure

All experiments took place in a darkened room. Participants placed their heads in a chin rest mounted on a height-adjustable table, to which the stereoscope was also attached. The total optical viewing distance (including the light path through the mirrors) was XXcm, at which distance 1 degree of visual angle encompassed 48 pixels on the monitor.

Before beginning primary data collection, each participant completed an isoluminance adjustment task. Stimuli were presented that counterphase flickered at 10Hz, defined about either the L-M or (L+M)-S plane in cone space. Participants used a trackball to dynamically adjust the angle of the stimulus to minimise the percept of flicker. Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli for the main experiment for that participant. Settings were very similar across participants for the (L+M)-S direction, and varied somewhat more for the L-M direction (Figure?).

*Figure here summarising the isoluminant data*

In Experiments 1 and 3, participants completed a two-interval-forced-choice (2IFC) contrast discrimination task.

In Experiments 2 and 3, participants completed a 2IFC dichoptic masking task.

## Data analysis and computational modelling

Psychometric functions from each experiment were fit with \emph{psignifit} 4 to estimate full posterior distributions for threshold and slope parameters via a Bayesian numerical integration method [@Schutt2016]. We also implemented a Bayesian hierarchical version of the two stage model of @Meese2006 using the Stan language [@Carpenter2017]. This used a Bernoulli distribution to model the trial-by-trial response data, and was fit separately to each chromatic condition of Experiments 1 and 3 (i.e. 6 model fits in total). The modelling primarily focuses on comparing posterior parameter distributions across conditions and experiments, rather than a model comparison approach. We generated over 1 million posterior samples for each model, and retained 10% of them for plotting.

## Data and code availability

All experimental code, raw data and analysis scripts are available at: https://osf.io/3vdga/

# Results

## Experiment 1

## Experiment 2

## Experiment 3

## Experiment 4

# Discussion

# Conclusions

# Acknowledgements

Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW.

# References

### 2023-01-07 manuscript.tex
Set-up of manuscript and associated files

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Binocular integration of chromatic information},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Binocular integration of chromatic information}
\author{Daniel H. Baker, Kirralise J. Hansford, Federico G. Segala, Rowan J. Huxley,\\
Joel T. Martin, Lauren E. Welbourne \& Alex R. Wade}
\date{2023-01-07}

\begin{document}
\maketitle

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{materials-methods}{%
\section{Materials \& Methods}\label{materials-methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

All four experiments were completed by the first author (DHB) and two other participants, who differed for each experiment. Written informed consent was provided before data collection began, and all procedures were approved by the ethics committee of the Department of Psychology at the University of York.

\hypertarget{apparatus-stimuli}{%
\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}

In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg. The gratings were windowed by a raised cosine envelope with a diameter of 3 degrees. Spatial phase, relative to a central fixation cross, was randomised on each trial across the four cardinal phases. In the achromatic conditions, the sine-wave modulated all three colour channels equally. In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant. In the (L+M)-S condition, the isoluminant stimuli maximised S-cone contrast. Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals (Stockman and Sharpe, 2000).

The stimuli in Experiments 3 and 4 were temporal modulations of luminance and colour, using the same raised cosine envelope as described above, but with no further spatial modulation. The stimuli counterphase flickered sinusoidally at 4Hz, along the same axes of luminance and colour as described for Experiments 1 and 2.

In all experiments, we displayed a binocular fusion lock, consisting of three concentric rings of small square elements with random colour. A black central fixation cross was also displayed throughout.

All stimuli were presented on an Iiyama VisionMaster Pro 510 CRT monitor, with a refresh rate of 100Hz, and a resolution of 1024 x 768 pixels. The display was driven by a ViSaGe MkII stimulus generator (Cambridge Research Systems Ltd., Kent, UK) running in 42-bit colour mode (14 bits per colour channel). We presented stimuli to the left and right eyes independently using a four-mirror stereoscope with front-silvered mirrors. The display was luminance calibrated using a ColourCal photometer (Cambridge Research Systems), and gamma corrected by fitting a four-parameter gamma function to the output of each CRT gun. The maximum luminance was 87 cd/m\(^2\). We also measured the spectral output of each phosphor using a Jaz spectroradiometer (Ocean Insight, Florida), and used these measurements to convert between LMS (cone) space and the monitor RGB coordinates.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

All experiments took place in a darkened room. Participants placed their heads in a chin rest mounted on a height-adjustable table, to which the stereoscope was also attached. The total optical viewing distance (including the light path through the mirrors) was XXcm, at which distance 1 degree of visual angle encompassed 48 pixels on the monitor.

Before beginning primary data collection, each participant completed an isoluminance adjustment task. Stimuli were presented that counterphase flickered at 10Hz, defined about either the L-M or (L+M)-S plane in cone space. Participants used a trackball to dynamically adjust the angle of the stimulus to minimise the percept of flicker. Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli for the main experiment for that participant. Settings were very similar across participants for the (L+M)-S direction, and varied somewhat more for the L-M direction (Figure?).

\emph{Figure here summarising the isoluminant data}

\hypertarget{data-analysis-and-computational-modelling}{%
\subsection{Data analysis and computational modelling}\label{data-analysis-and-computational-modelling}}

Psychometric functions from each experiment were fit with \emph{psignifit} 4 to estimate full posterior distributions for threshold and slope parameters via a Bayesian numerical integration method (Schütt et al., 2016). We also implemented a Bayesian hierarchical version of the two stage model of Meese et al. (2006) using the Stan language (Carpenter et al., 2017). This used a Bernoulli distribution to model the trial-by-trial response data, and was fit separately to each chromatic condition of Experiments 1 and 3 (i.e.~6 model fits in total). The modelling primarily focuses on comparing posterior parameter distributions across conditions and experiments, rather than a model comparison approach. We generated over 1 million posterior samples for each model, and retained 10\% of them for plotting.

\hypertarget{data-and-code-availability}{%
\subsection{Data and code availability}\label{data-and-code-availability}}

All experimental code, raw data and analysis scripts are available at: \url{https://osf.io/3vdga/}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{experiment-1}{%
\subsection{Experiment 1}\label{experiment-1}}

\hypertarget{experiment-2}{%
\subsection{Experiment 2}\label{experiment-2}}

\hypertarget{experiment-3}{%
\subsection{Experiment 3}\label{experiment-3}}

\hypertarget{experiment-4}{%
\subsection{Experiment 4}\label{experiment-4}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker M, Guo J, Li P, Riddell A. 2017. Stan: A probabilistic programming language. \emph{Journal of Statistical Software} \textbf{76}:1--32. doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}

\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}

\leavevmode\vadjust pre{\hypertarget{ref-Schutt2016}{}}%
Schütt HH, Harmeling S, Macke JH, Wichmann FA. 2016. Painfree and accurate bayesian estimation of psychometric functions for (potentially) overdispersed data. \emph{Vision Res} \textbf{122}:105--123. doi:\href{https://doi.org/10.1016/j.visres.2016.02.002}{10.1016/j.visres.2016.02.002}

\leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
Stockman A, Sharpe LT. 2000. The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype. \emph{Vision Res} \textbf{40}:1711--37. doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}

\end{CSLReferences}

\end{document}

### 2024-03-09 manuscript.Rmd
Started writing manuscript

@@
 ---
-title: "Binocular integration of chromatic information"
+title: "Binocular integration of chromatic and luminance signals"
 author: |
-   | Daniel H. Baker, Kirralise J. Hansford, Federico G. Segala, Rowan J. Huxley,   
-   | Joel T. Martin, Lauren E. Welbourne & Alex R. Wade
+   | Daniel H. Baker, Kirralise J. Hansford, Federico G. Segala, Annie Y. Morsi,
+   | Rowan J. Huxley, Joel T. Martin, Maya Rockman & Alex R. Wade
 date: "`r Sys.Date()`"
@@
   word_document: default
-  pdf_document:
-    toc: no
   html_document: default
 bibliography: references.bib
-csl: elife.csl
+csl: journal-of-vision.csl
+header-includes: 
+  \usepackage{float} \floatplacement{figure}{H} 
+  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
 ---
@@
 ```{r setup, include=FALSE}
+
+processdata <- 0
+# the processdata flag has three settings:
+# 0: do no analysis, just produce the pdf of the manuscript
+# 1: fit psychometric functions and plot graphs
+# 2: do Stan modelling (takes N hours)
+
+nsamples <- 10000    # number of Stan samples for modelling
+
+# reasonably compact code to check which packages are installed, install the missing ones, and activate all
+packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','doParallel','R.matlab') # list of CRAN packages
+missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
+if (length(missingpackages)>0){install.packages(missingpackages)}
+toinstall <- packagelist[which(!packagelist %in% (.packages()))]
+invisible(lapply(toinstall,library,character.only=TRUE))
+
+# helper function to make colours transparent
+addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}
+
+lms2rgb <- function(phosphors,fundamentals,lms){
+  rgbTOlms <- t(as.matrix(fundamentals)) %*% as.matrix(phosphors)
+  lmsTOrgb <- solve(rgbTOlms)
+  rgb <- lmsTOrgb %*% lms
+return(rgb)}
+
+getmodelresp <- function(p,L,R){
+  Lresp <- (L^p[3])/(p[4] + L + p[6]*R)
+  Rresp <- (R^p[3])/(p[4] + R + p[6]*L)
+  bs <- Lresp + Rresp
+  resp <- (bs^p[1])/(p[5] + bs^p[2])
+return(resp)}
+
+discriminate <- function(p,pedC,cond) {
+
+  if (cond==1){baseline <- getmodelresp(p,pedC,0)}
+  if (cond==2){baseline <- getmodelresp(p,pedC,pedC)}
+  if (cond==3){baseline <- getmodelresp(p,pedC,pedC)}
+  if (cond==4){baseline <- getmodelresp(p,pedC,0)}
+
+  modelresp <- -10
+  contrastinc <- 0
+  if (baseline>-999){
+    while (((modelresp-baseline) < p[7])){
+      contrastinc <- contrastinc + 0.1
+  if (cond==1){modelresp <- getmodelresp(p,pedC+contrastinc,0)}
+  if (cond==2){modelresp <- getmodelresp(p,pedC+contrastinc,pedC+contrastinc)}
+  if (cond==3){modelresp <- getmodelresp(p,pedC+contrastinc,pedC)}
+  if (cond==4){modelresp <- getmodelresp(p,pedC,contrastinc)}
+    }
+    while (((modelresp-baseline) > p[7])){
+      contrastinc <- contrastinc - 0.001
+  if (cond==1){modelresp <- getmodelresp(p,pedC+contrastinc,0)}
+  if (cond==2){modelresp <- getmodelresp(p,pedC+contrastinc,pedC+contrastinc)}
+  if (cond==3){modelresp <- getmodelresp(p,pedC+contrastinc,pedC)}
+  if (cond==4){modelresp <- getmodelresp(p,pedC,contrastinc)}
+    }    
+    }
+  else{contrastinc <- 99}
+return(contrastinc) }
+
+use_miniconda('r-reticulate')
+# install psignifit in the terminal with:
+# sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
+ps <- import('psignifit')
+
+# calculate constant to scale the slope parameter to the Gaussian SD
+C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
+
+if (!dir.exists('local/fits')){dir.create('local/fits')}
+
 knitr::opts_chunk$set(echo = TRUE)
+
+```
+
+```{r plotisoluminance, include=FALSE}
+
+if (processdata>0){
+
+fundamentals <- read.csv('local/fundamentals.csv')
+phosphors <- read.csv('local/phosphors.csv')
+thetalist <- (0:360)*pi/180
+
+pdf('Figures/isosettings.pdf',width=11,height=6)
+
+isodata <- read.csv('local/isosettings.csv')
+isomeans <- colMeans(isodata)
+
+collist <- brewer.set1(9)
+
+par(mfrow=c(1,2))
+
+ticklocs <- seq(-1,1,0.5)
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-1,1), ylim=c(-1,1))  
+axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocs, side = 1, at=ticklocs, line=0.3)    
+mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
+title(xlab="L", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='L-M gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+text(-0.95,0.9,'(a)',cex=2)
+
+lines(c(0,0),c(-1,1),lty=2)
+lines(c(-1,1),c(0,0),lty=2)
+
+rgbvals <- matrix(0,nrow=length(thetalist),ncol=3)
+for (n in 1:length(thetalist)){
+    theta <- thetalist[n]
+    stimLMS <- c(cos(theta), sin(theta), 0)
+    rgbvals[n,] <- lms2rgb(phosphors,fundamentals,stimLMS)
+}
+
+rgbvals <- (rgbvals/(2*max(abs(rgbvals)))) + 0.5
+for (n in 1:length(thetalist)){    points(cos(thetalist[n]),sin(thetalist[n]),pch=16,col=rgb(rgbvals[n,1],rgbvals[n,2],rgbvals[n,3]),cex=2)}
+
+arctheta <- seq(60,179,0.5)*pi/180
+lines(cos(arctheta)*0.45,sin(arctheta)*0.5,lwd=2);
+lines(-cos(arctheta)*0.45,-sin(arctheta)*0.5,lwd=2);
+
+for (s in 1:5){
+    a <- isomeans[s]*pi/180
+    lines(cos(a)*c(-0.9, 0.9),sin(a)*c(-0.9,0.9),lwd=2,col=collist[s]);
+}
+
+legend(-1,-0.25,c('P1','P2','P3','P4','P5'),lwd=2,col=collist[1:5],box.lwd=2,cex=1.2,bg='white')
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-1,1), ylim=c(-1,1))  
+axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocs, side = 1, at=ticklocs, line=0.3)    
+mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
+title(xlab="L+M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="S", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='S-(L+M) gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+text(-0.95,0.9,'(b)',cex=2)
+
+lines(c(0,0),c(-1,1),lty=2)
+lines(c(-1,1),c(0,0),lty=2)
+
+rgbvals <- matrix(0,nrow=length(thetalist),ncol=3)
+for (n in 1:length(thetalist)){
+    theta <- thetalist[n]
+    stimLMS <- c(cos(theta), cos(theta), sin(theta))
+    rgbvals[n,] <- lms2rgb(phosphors,fundamentals,stimLMS)
+}
+
+rgbvals <- (rgbvals/(2*max(abs(rgbvals)))) + 0.5
+for (n in 1:length(thetalist)){    points(cos(thetalist[n]),sin(thetalist[n]),pch=16,col=rgb(rgbvals[n,1],rgbvals[n,2],rgbvals[n,3]),cex=2)}
+
+arctheta <- seq(45,135,0.5)*pi/180
+lines(cos(arctheta)*0.45,sin(arctheta)*0.5,lwd=2);
+lines(-cos(arctheta)*0.45,-sin(arctheta)*0.5,lwd=2);
+
+for (s in 1:5){
+    a <- isomeans[s+5]*pi/180
+    lines(cos(a)*c(-0.9, 0.9),sin(a)*c(-0.9,0.9),lwd=2,col=collist[s]);
+}
+
+dev.off()
+
+}
+
+```
+
+```{r loaddata, include=FALSE}
+
+ex1data <- read.csv('local/Experiment1.csv')
+ex2data <- read.csv('local/Experiment2.csv')
+
+if (processdata>0){
+
+sublist <- unique(ex1data$Subject)
+explist <- unique(ex1data$Experiment)
+
+options <- NULL
+options$sigmoidName <- 'norm'   # choose a cumulative Gauss as the sigmoid
+options$expType <- '2AFC'   # choose 2-AFC as the paradigm of the experiment
+
+allthresh <- array(0,dim=c(3,3,4,8))
+allslope <- array(0,dim=c(3,3,4,8))
+for (subj in 1:3){
+  subdata <- subset(ex1data,Subject==sublist[subj])
+for (expt in 1:3){
+  expdata <- subset(subdata,Experiment==explist[expt])
+for (cond in 1:4){
+  conddata <- subset(expdata,Condition==(2*cond)|Condition==((2*cond)-1))
+  pedlevs <- unique(conddata$PedestalContrast)
+for (pedlevel in 1:8){
+
+blockdata <- subset(conddata,PedestalContrast==pedlevs[pedlevel])
+
+if (nrow(blockdata)>0){
+targetcontrasts <- sort(unique(blockdata$TargetContrast))
+ntrials <- rep(0,length(targetcontrasts))
+ncorrect <- rep(0,length(targetcontrasts))
+for (lev in 1:length(targetcontrasts)){
+  temp <- subset(blockdata,TargetContrast==targetcontrasts[lev])
+  ntrials[lev] <- nrow(temp)
+  ncorrect[lev] <- sum(temp$IsCorrect)
+}
+
+tofit <- as.matrix(data.frame(20*log10(targetcontrasts),ncorrect,ntrials))
+
+res <- ps$psignifit(tofit,options)
+
+allthresh[subj,expt,cond,pedlevel] <- res$Fit[1]
+allslope[subj,expt,cond,pedlevel] <- res$Fit[2]/C
+}
+
+}}}}
+
+# shift hbin and dich conditions up one
+allthresh[,,3,2:8] <- allthresh[,,3,1:7]
+allthresh[,,4,2:8] <- allthresh[,,4,1:7]
+allslope[,,3,2:8] <- allslope[,,3,1:7]
+allslope[,,4,2:8] <- allslope[,,4,1:7]
+# duplicate the mon threshold conditions for hbin and dich
+allthresh[,,3,1] <- allthresh[,,1,1]
+allthresh[,,4,1] <- allthresh[,,1,1]
+allslope[,,3,1] <- allslope[,,1,1]
+allslope[,,4,1] <- allslope[,,1,1]
+
+meanthresh <- apply(allthresh,2:4,mean)
+meanslope <- apply(allslope,2:4,mean)
+
+SEthresh <- apply(allthresh,2:4,sd)/sqrt(3)
+SEslope <- apply(allslope,2:4,sd)/sqrt(3)
+
+save(file='local/thresholddata.RData',list=c('allthresh','allslope','meanthresh','meanslope','SEthresh','SEslope'))
+
+pedlist <- c('DET','AC','RG','BY')
+tarlist <- c('AC','RG','BY')
+sublist <- unique(ex2data$Subject)
+
+ntrials <- array(0,dim=c(length(sublist),12,10))
+ncorrect <- ntrials
+contrastsC <- ntrials
+counter <- 0
+for (ped in 1:length(pedlist)){
+  for (tar in 1:length(tarlist)){
+    counter <- counter + 1
+    for (subj in 1:length(sublist)){
+    thiscond <- subset(ex2data,Subject==sublist[subj] & TargetType==tarlist[tar] & PedestalType==pedlist[ped])
+    targetcontrasts <- sort(as.numeric(unique(thiscond$TargetContrast)))
+    for (tlevel in 1:length(targetcontrasts)){
+      thislevel <- subset(thiscond, TargetContrast==targetcontrasts[tlevel])
+      ntrials[subj,counter,tlevel] <- nrow(thislevel)
+      ncorrect[subj,counter,tlevel] <- sum(thislevel$IsCorrect)
+      contrastsC[subj,counter,tlevel] <- targetcontrasts[tlevel]
+    }
+  }
+}
+}
+
+MCSpropcorr <- 100*ncorrect/ntrials
+contrastsdB <- round(20*log10(contrastsC))
+
+MCSthresh <- matrix(0,nrow=length(sublist),ncol=12)
+MCSslope <- MCSthresh
+for (subj in 1:length(sublist)){
+for (cond in 1:12){
+  datatofit <- data.frame(contrastsdB[subj,cond,],ncorrect[subj,cond,],ntrials[subj,cond,])
+  colnames(datatofit) <- c('CdB','Ncorrect','Ntrials')
+
+  res <- ps$psignifit(as.matrix(datatofit),options)
+
+  MCSthresh[subj,cond] <- res$Fit[1]
+  MCSslope[subj,cond] <- res$Fit[2]/C
+
+}}
+
+thdelev <- array(0,dim=c(3,3,3))
+slopematrix <- array(0,dim=c(3,3,3))
+
+for (subj in 1:length(sublist)){
+thdelev[subj,1,] <- MCSthresh[subj,c(4,7,10)] - MCSthresh[subj,1]
+thdelev[subj,2,] <- MCSthresh[subj,c(5,8,11)] - MCSthresh[subj,2]
+thdelev[subj,3,] <- MCSthresh[subj,c(6,9,12)] - MCSthresh[subj,3]
+
+slopematrix[subj,1,] <- 10.3/MCSslope[subj,c(4,7,10)]
+slopematrix[subj,2,] <- 10.3/MCSslope[subj,c(5,8,11)]
+slopematrix[subj,3,] <- 10.3/MCSslope[subj,c(6,9,12)]
+}
+detslopes <- 10.3/MCSslope[,1:3]
+
+save(file='local/MCSdata.RData',list=c('MCSthresh','MCSslope','thdelev','slopematrix','detslopes','MCSpropcorr','contrastsdB'))
+
+}
+
+```
+
+```{r domodellingsimplex, include=FALSE}
+
+load('local/thresholddata.RData')
+
+getmodelresp <- function(p,L,R){
+  Lresp <- (L^p[3])/(p[4] + L + p[6]*R)
+  Rresp <- (R^p[3])/(p[4] + R + p[6]*L)
+  bs <- Lresp + Rresp
+  resp <- (bs^p[1])/(p[5] + bs^p[2])
+return(resp)}
+
+discriminate <- function(p,pedC,cond) {
+
+  if (cond==1){baseline <- getmodelresp(p,pedC,0)}
+  if (cond==2){baseline <- getmodelresp(p,pedC,pedC)}
+  if (cond==3){baseline <- getmodelresp(p,pedC,pedC)}
+  if (cond==4){baseline <- getmodelresp(p,pedC,0)}
+
+  modelresp <- -10
+  contrastinc <- 0
+  if (baseline>-999){
+
+    while (((modelresp-baseline) < p[7])){
+      contrastinc <- contrastinc + 0.1
+  if (cond==1){modelresp <- getmodelresp(p,pedC+contrastinc,0)}
+  if (cond==2){modelresp <- getmodelresp(p,pedC+contrastinc,pedC+contrastinc)}
+  if (cond==3){modelresp <- getmodelresp(p,pedC+contrastinc,pedC)}
+  if (cond==4){modelresp <- getmodelresp(p,pedC,contrastinc)}
+    }
+    while (((modelresp-baseline) > p[7])){
+      contrastinc <- contrastinc - 0.001
+  if (cond==1){modelresp <- getmodelresp(p,pedC+contrastinc,0)}
+  if (cond==2){modelresp <- getmodelresp(p,pedC+contrastinc,pedC+contrastinc)}
+  if (cond==3){modelresp <- getmodelresp(p,pedC+contrastinc,pedC)}
+  if (cond==4){modelresp <- getmodelresp(p,pedC,contrastinc)}
+    }    
+    }
+  else{contrastinc <- 99}
+return(contrastinc) }
+
+errorfit <- function(p){
+
+p <- 10^p
+p[2] <- p[2] + 1
+p[2] <- min(p[2],10)
+p[1] <- 1 + p[1] + p[2]
+p[3] <- 1 + p[3]
+
+pedlevelsC <- 10^(pedlist/20)
+pedlevelsC[1] <- 0
+allpred <- array(0,dim=c(4,length(pedlist)))
+
+  for (cond in 1:4){
+    for (pedlev in 1:length(pedlist)){
+      allpred[cond,pedlev] <- discriminate(p,pedlevelsC[pedlev],cond)
+    }
+  }
+
+allpreddB <- 20*log10(allpred)
+rms <- sqrt(mean((allpreddB - datatofit)^2))
+if (is.na(rms)){rms <- 999}
+return(rms)}
+
+if (processdata==2){
+
+ntotalsimplexfits <- 100
+
+cluster <- makeCluster(8)
+registerDoParallel(cluster)
+
+pedlist <<- seq(-12,30,6)
+allp <- matrix(0,nrow=3,ncol=7)
+allparams <- array(0,dim=c(3,ntotalsimplexfits,8))
+allrms <- NULL
+ for (cond in 1:3){
+   print(cond)
+   datatofit <<- meanthresh[cond,,]
+
+   nfits <- ntotalsimplexfits
+   for (n in 1:ntotalsimplexfits){
+     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){nfits <- nfits-1}
+   }
+
+   if (nfits > 0){
+   foreach(i = 1:nfits, .combine=rbind) %dopar% {
+   sout <- pracma::nelder_mead(errorfit,rnorm(7,sd=0.1)+log10(c(0.5,5.5,0.3,1,0.01,1,0.2)))
+   allout <- c(errorfit(sout$xmin),sout$xmin)
+
+   hassaved <- 0
+   filecount <- 0
+   while (!hassaved){
+     filecount <- filecount + 1
+     if (!file.exists(paste0('local/fits/E',cond,'f',filecount,'.RData'))){
+       save(file=paste0('local/fits/E',cond,'f',filecount,'.RData'),list='allout')
+       hassaved <- 1}
+   }
+   allout <- c(errorfit(sout$xmin),sout$xmin)
+   }
+   }
+
+   finalout <- matrix(0,nrow=ntotalsimplexfits,ncol=8)
+   for (n in 1:ntotalsimplexfits){
+     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){
+       load(file=paste0('local/fits/E',cond,'f',n,'.RData'))
+       finalout[n,] <- allout
+     }
+   }
+   i <- which(finalout[,1]==min(finalout[,1]))
+   p <- 10^finalout[i[1],2:8]
+   allrms[cond] <- finalout[i[1],1]
+   p[2] <- p[2] + 1
+   p[2] <- min(p[2],10)
+   p[1] <- 1 + p[1] + p[2]
+   p[3] <- 1 + p[3]
+   allp[cond,] <- p
+   pedlist <<- seq(-6,36,6)
+
+   allparams[cond,,] <- finalout
+ }
+
+save(file='local/simplexfits.RData',list=c('allp','allrms','allparams','ntotalsimplexfits'))
+
+stopCluster(cluster)
+
+}
+
+```
+
+```{r plotmodellingsimplex, include=FALSE}
+
+if (processdata>0){
+
+load('local/simplexfits.RData')
+
+pedlist <- -12:39
+pedlevelsC <- 10^(pedlist/20)
+pedlevelsC[1] <- 0
+allpred <- array(0,dim=c(3,4,length(pedlist)))
+
+for (expt in 1:3){
+  for (cond in 1:4){
+    for (pedlev in 1:length(pedlist)){
+      allpred[expt,cond,pedlev] <- discriminate(allp[expt,],pedlevelsC[pedlev],cond)
+    }
+  }
+}
+allpreddB <- 20*log10(allpred)
+
+pdf('Figures/dipperssimplex.pdf',width=12,height=5)
+
+collist <- c('red','blue','orange','darkgreen')
+
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
+ticklocsy <- seq(-12,36,6)
+ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
+
+par(pty="s",mfcol=c(1,3))  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='Achromatic')
+
+pedcontrasts <- seq(-12,30,6)
+
+for (cond in 1:4){
+  arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]+SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]-SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
+  lines(pedlist,allpreddB[1,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanthresh[1,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+text(24,-9,paste0('RMS = ',round(allrms[1],digits=2),'dB'),cex=2)
+legend(-12,36,c('Monocular','Binocular','Half-bin','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='Red/Green')
+
+pedcontrasts <- c(-12,seq(0,36,6))
+
+for (cond in 1:4){
+  arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]+SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]-SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+ # lines(pedcontrasts,meanthresh[3,cond,],col=collist[cond],lwd=2)
+  lines(pedlist,allpreddB[3,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanthresh[3,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+text(24,-9,paste0('RMS = ',round(allrms[2],digits=2),'dB'),cex=2)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='Blue/Yellow')
+
+for (cond in 1:4){
+  arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]+SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]-SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+ # lines(pedcontrasts,meanthresh[2,cond,],col=collist[cond],lwd=2)
+  lines(pedlist,allpreddB[2,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanthresh[2,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+text(24,-9,paste0('RMS = ',round(allrms[3],digits=2),'dB'),cex=2)
+
+dev.off()
+
+}
+
+```
+
+```{r domodelling, include=FALSE}
+
+if (processdata==2){
+
+  numSavedSteps <- nsamples    # total number of MCMC steps
+  adaptSteps = 200  # Number of steps to "tune" the samplers
+  burnInSteps = 200 
+  thinSteps <- 1
+  nChains = 24
+  options(mc.cores=8)
+
+modelString = "
+  data {
+    int<lower=1> Nsubj ;
+    int<lower=1> Ntotal ;
+    int correct[Ntotal] ;
+    real PedestalContrast[Ntotal] ;
+    real TargetContrast[Ntotal] ;
+    int<lower=1> c[Ntotal] ;
+    int<lower=1> s[Ntotal] ;
+  }
+  parameters {
+    real<lower=0> p[Nsubj] ;
+    real<lower=0> q[Nsubj] ;    
+    real<lower=0> m[Nsubj] ;
+    real<lower=0> S[Nsubj] ;  
+    real<lower=0> Z[Nsubj] ;
+    real<lower=0> w[Nsubj] ;
+    real<lower=0> k[Nsubj] ;
+
+    real<lower=0> sigma ;
+    real<lower=0> pmu ; 
+    real<lower=0> qmu ; 
+    real<lower=0> mmu ;
+    real<lower=0> Smu ;
+    real<lower=0> Zmu ; 
+    real<lower=0> wmu ; 
+    real<lower=0> kmu ;
+
+    real<lower=0> psigma ;
+    real<lower=0> qsigma ;
+    real<lower=0> msigma ;
+    real<lower=0> Ssigma ;
+    real<lower=0> Zsigma ;    
+    real<lower=0> wsigma ;
+    real<lower=0> ksigma ;    
+  }
+  model {
+
+    pmu ~ normal( 1.4 , 1.4/3 ) ;
+    qmu ~ normal( 6.59 , 6.59/3 ) ;
+    mmu ~ normal( 1.28 , 1.28/3 ) ;
+    Smu ~ normal( 0.985 , 0.985/3 ) ;
+    Zmu ~ uniform( 0.001 , 100 ) ;
+    wmu ~ normal( 1 , 0.3333 ) ;
+    kmu ~ normal( 0.194 , 0.194/2 ) ;
+    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    msigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    Ssigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
+    wsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+
+    p ~ normal( pmu , psigma ) ; // vectorized
+    q ~ normal( qmu , qsigma ) ; // vectorized
+    m ~ normal( mmu , msigma ) ; // vectorized
+    S ~ normal( Smu , Ssigma ) ; // vectorized
+    Z ~ normal( Zmu , Zsigma ) ; // vectorized
+    w ~ normal( wmu , wsigma ) ; // vectorized
+    k ~ normal( kmu , ksigma ) ; // vectorized
+
+    for ( i in 1:Ntotal ) {
+
+    real Lt ;
+    real Rt ;
+    real Ln ;
+    real Rn ;
+    real targresp ;
+    real nullresp ;
+
+    if (c[i]==1) { // monocular condition
+    Lt = pow(PedestalContrast[i]+TargetContrast[i],m[s[i]]) / (S[s[i]] + (PedestalContrast[i]+TargetContrast[i])) ;
+    Rt = 0 ;
+    Ln = pow(PedestalContrast[i],m[s[i]]) / (S[s[i]] + PedestalContrast[i]) ;
+    Rn = 0 ; 
+    }
+
+    if (c[i]==2) { // binocular condition 
+      Lt = pow(PedestalContrast[i]+TargetContrast[i],m[s[i]]) / (S[s[i]] + (PedestalContrast[i]+TargetContrast[i]) + w[s[i]]*(PedestalContrast[i]+TargetContrast[i])) ;
+      Rt = pow(PedestalContrast[i]+TargetContrast[i],m[s[i]]) / (S[s[i]] + (PedestalContrast[i]+TargetContrast[i]) + w[s[i]]*(PedestalContrast[i]+TargetContrast[i])) ;
+      Ln = pow(PedestalContrast[i],m[s[i]]) / (S[s[i]] + PedestalContrast[i] + w[s[i]]*PedestalContrast[i]) ;
+      Rn = pow(PedestalContrast[i],m[s[i]]) / (S[s[i]] + PedestalContrast[i] + w[s[i]]*PedestalContrast[i]) ;
+    }
+
+    if (c[i]==3) { // half-binocular condition 
+      Lt = pow(PedestalContrast[i]+TargetContrast[i],m[s[i]]) / (S[s[i]] + (PedestalContrast[i]+TargetContrast[i]) + w[s[i]]*PedestalContrast[i]) ;
+      Rt = pow(PedestalContrast[i],m[s[i]]) / (S[s[i]] + PedestalContrast[i] + w[s[i]]*(PedestalContrast[i]+TargetContrast[i])) ;
+      Ln = pow(PedestalContrast[i],m[s[i]]) / (S[s[i]] + PedestalContrast[i] + w[s[i]]*PedestalContrast[i]) ;
+      Rn = pow(PedestalContrast[i],m[s[i]]) / (S[s[i]] + PedestalContrast[i] + w[s[i]]*PedestalContrast[i]) ;  
+    }
+
+    if (c[i]==4) { // dichoptic condition 
+      Lt = pow(TargetContrast[i],m[s[i]]) / (S[s[i]] + TargetContrast[i] + w[s[i]]*PedestalContrast[i]) ;
+      Rt = pow(PedestalContrast[i],m[s[i]]) / (S[s[i]] + PedestalContrast[i] + w[s[i]]*TargetContrast[i]) ;
+      Ln = 0 ;
+      Rn = pow(PedestalContrast[i],m[s[i]]) / (S[s[i]] + PedestalContrast[i]) ;      
+    }
+
+    targresp = pow((Lt + Rt), (p[s[i]]+q[s[i]])) / (Z[s[i]] + pow((Lt + Rt), q[s[i]])) ;
+    nullresp = pow((Ln + Rn), (p[s[i]]+q[s[i]])) / (Z[s[i]] + pow((Ln + Rn), q[s[i]])) ;     
+    correct[i] ~ bernoulli((1 + erf((targresp - nullresp)/k[s[i]]))/2) ;
+
+    }
+  }  
+  " # close quote for modelString
+
+  # Translate to C++ and compile to DSO:
+    dipmodel <- stan_model(model_code=modelString)
+
+  ex1data <- read.csv('local/Experiment1.csv')
+  explist <- unique(ex1data$Experiment)
+
+for (mod in 1:1){
+  expdata <- subset(ex1data,Experiment==explist[mod])
+  expdata$Participant <- as.numeric(gsub('\\D','',expdata$Subject))
+  expdata$Condition <- ceiling(expdata$Condition/2)
+
+  dataList = list(correct = expdata$IsCorrect, PedestalContrast = expdata$PedestalContrast, TargetContrast = expdata$TargetContrast, c = expdata$Condition, s = expdata$Participant, Nsubj = max(expdata$Participant), Ntotal = nrow(expdata))
+
+  # Get MC sample of posterior:
+    stanFit <- sampling(object=dipmodel, 
+                        data = dataList, 
+                        chains = nChains,
+                        iter = (ceiling(numSavedSteps/nChains)*thinSteps
+                                +burnInSteps), 
+                        warmup = burnInSteps, 
+                        thin = thinSteps,
+                        cores = getOption("mc.cores", 1L))
+
+    # convert stan format to coda format:jkn9
+    mcmcCoda2 = mcmc.list(lapply( 1:ncol(stanFit), function(x){mcmc(as.array(stanFit)[,x,])}))
+
+    save(file=paste0('local/E1mod',mod,'.RData'),list=c('stanFit','mcmcCoda2'))
+
+}
+
+}
+
+```
+
+```{r plotdata, include=FALSE}
+
+load('local/thresholddata.RData')
+
+if (processdata>0){
+
+  paramorder <- c('p','q','m','S','Z','w','k')
+  allsamples <- array(0,dim=c(3,7,10008))
+  for (expt in 1:3){
+    load(file=paste0('local/E1mod',expt,'.RData'))
+    p <- NULL
+    q <- NULL
+    m <- NULL
+    S <- NULL
+    Z <- NULL
+    w <- NULL
+    k <- NULL
+    for (i in 1:length(mcmcCoda2)){
+      p <- c(p,mcmcCoda2[[i]][,23])  
+      q <- c(q,mcmcCoda2[[i]][,24])  
+      m <- c(m,mcmcCoda2[[i]][,25])  
+      S <- c(S,mcmcCoda2[[i]][,26])  
+      Z <- c(Z,mcmcCoda2[[i]][,27])  
+      w <- c(w,mcmcCoda2[[i]][,28])  
+      k <- c(k,mcmcCoda2[[i]][,29])  
+    }        
+    p <- p + q
+allsamples[expt,1,] <- p
+allsamples[expt,2,] <- q
+allsamples[expt,3,] <- m
+allsamples[expt,4,] <- S
+allsamples[expt,5,] <- Z
+allsamples[expt,6,] <- w
+allsamples[expt,7,] <- k
+
+  }
+# meanparams <- 10^apply(log10(allsamples),1:2,mlv,method='meanshift')
+meanparams <- 10^apply(log10(allsamples),1:2,mean)
+# meanparams[2:3,5] <- meanparams[2:3,5]*100
+
+pdf('Figures/modelparams.pdf',width=12,height=8)
+
+collist <- c('black','cornflowerblue','darkred')
+
+par(pty="s",mfcol=c(2,4))
+
+ticklocsx <- seq(-18,18,6)
+ticklabelsx <- c('1/8','1/4','1/2',1,2,4,8)
+ticklocsy <- seq(0,1,0.2)
+ticklabelsy <- ticklocsy
+
+for (param in 1:7){
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,18), ylim=c(0,1))  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab=paramorder[param], col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  for (expt in 1:3){
+
+    svals <- 20*log10(allsamples[expt,param,])
+    a <- density(svals)
+    a$y <- a$y/max(a$y)
+    lines(a$x,a$y,col=collist[expt])
+
+    lines(20*log10(meanparams[expt,c(param,param)]),c(0,1),col=collist[expt])
+  }
+
+}
+
+dev.off()
+
+pedlist <- -12:39
+pedlevelsC <- 10^(pedlist/20)
+pedlevelsC[1] <- 0
+allpred <- array(0,dim=c(3,4,length(pedlist)))
+
+for (expt in 1:3){
+  for (cond in 1:4){
+    for (pedlev in 1:length(pedlist)){
+      allpred[expt,cond,pedlev] <- discriminate(meanparams[expt,],pedlevelsC[pedlev],cond)
+    }
+  }
+}
+allpreddB <- 20*log10(allpred)
+
+pdf('Figures/dippers.pdf',width=12,height=5)
+
+collist <- c('red','blue','orange','darkgreen')
+
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
+ticklocsy <- seq(-12,36,6)
+ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
+
+par(pty="s",mfcol=c(1,3))  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='Achromatic')
+
+pedcontrasts <- seq(-12,30,6)
+
+for (cond in 1:4){
+  arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]+SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]-SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
+  lines(pedlist,allpreddB[1,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanthresh[1,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+legend(-12,36,c('Monocular','Binocular','Half-bin','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='Red/Green')
+
+pedcontrasts <- c(-12,seq(0,36,6))
+
+for (cond in 1:4){
+  arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]+SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]-SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+ # lines(pedcontrasts,meanthresh[3,cond,],col=collist[cond],lwd=2)
+  lines(pedlist,allpreddB[3,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanthresh[3,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='Blue/Yellow')
+
+for (cond in 1:4){
+  arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]+SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]-SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+ # lines(pedcontrasts,meanthresh[2,cond,],col=collist[cond],lwd=2)
+  lines(pedlist,allpreddB[2,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanthresh[2,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+
+dev.off()
+
+}
+
+summation <- meanthresh[,1,1] - meanthresh[,2,1]
+
+```
+
+```{r plotexampledips, include=FALSE}
+
+if (processdata>0){
+
+mkgrating <- function(regionsize, f, o, p, c){
+# ported from the Matlab function, originally by Tim Meese
+# generates a single component sine wave grating using the following inputs:
+  # regionsize is the width of the stimulus
+  # f is spatial frequency in cycles per image
+  # o is orientation in degrees
+  # p is phase in degrees relative to the centre of the image
+  # c is contrast
+
+p <- p*(pi/180)   # convert phase from degrees to radians
+o <- o*(pi/180)   # convert orientation from degrees to radians
+f <- f/regionsize # scale frequency by image size
+x0 <- (regionsize+1)/2  # locate centre of image
+y0 <- x0
+
+u <- f * cos(o) * 2*pi
+v <- f * sin(o) * 2*pi
+
+gridout <- meshgrid(1:regionsize,1:regionsize)   # generate x and y coordinate systems, requires the pracma package
+xx <- gridout$X
+yy <- gridout$Y
+
+output <- matrix(0,nrow=regionsize,ncol=regionsize)
+output <- (c * sin(u * (xx-x0) + v*(yy-y0) + p))
+
+return(output)}
+make_soft_window <- function(W,H,D=0.9){
+  # Mark's function to make sine-wave gratings, ported from Matlab
+  # W is width (in pixels), H is height (in pixels)
+  # D is the diameter of the soft window at half height as a proportion of the width
+
+  radius <- min(W*D/2,H*D/2)     # radius in pixels
+  L <- 2*(min(W/2,H/2) - radius) # blur half-cycle
+  X1 <- seq(-L/2,L/2)
+
+  X <- (1:W) - (W/2)
+  Y <- (1:H) - (H/2)
+  xx <- matrix(rep(X,H),nrow=H,ncol=W,byrow=TRUE)
+  yy <- t(matrix(rep(Y,W),nrow=W,ncol=H,byrow=TRUE))
+
+  mask <- (xx^2 + yy^2)
+  mask[mask<=(radius^2)] <- 1
+  mask[mask>(radius^2)] <- 0
+
+  WinKernel <- cos(X1*pi/L)  # half-cycle cosine
+  convkernW <- (1:W)*0
+  convkernW[(1+(W/2)-length(X1)/2):((W/2)+length(X1)/2)] <- WinKernel
+  convkernH <- (1:H)*0
+  convkernH[(1+(H/2)-length(X1)/2):((H/2)+length(X1)/2)] <- WinKernel
+  cH <- t(apply(mask,2,convolve,convkernH))
+  cH <- cH[,c((1+H/2):H,1:(H/2))]
+  cW <- apply(mask,1,convolve,convkernW)
+  cW <- cW[c((1+W/2):W,1:(W/2)),]
+  mask <- cH * cW
+
+  mask <- mask/max(mask)
+
+  return(mask)}
+
+  window <- make_soft_window(256,256)
+  grating <- mkgrating(256,3,90,0,1)
+  stim1 <- (1+(0.5*window*grating))/2
+  stim2 <- (1+(0.25*window*grating))/2
+  stim3 <- (1+(0.75*window*grating))/2
+
+      pdf(paste0('Figures/exampledips.pdf'),width=12,height=6.5)
+
+par(mfrow=c(1,2))
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,4), ylim=c(0,4))
+
+ticklocsx <- seq(0.5,3.5,1)
+ticklabelsx <- c('Left eye','Right eye','Left eye','Right eye')
+ticklocsy <- c(0.5,1.38,1.62,2.5,3.5)
+ticklabelsy <- c('Dichoptic','binocular','Half-','Binocular','Monocular')
+
+  mtext(text = c('Pedestal only','Pedestal + Target'), cex=1.5, side = 3, at=c(1,3), line=0)  
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0)   
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0, las=1)
+
+  polygon(c(0,4,4,0),c(0,0,4,4),border=NA,col=rgb(0.5,0.5,0.5))
+
+  rasterImage(stim1,0.2,3.2,0.8,3.8)
+  rasterImage(stim1,0.2,2.2,0.8,2.8)
+  rasterImage(stim1,1.2,2.2,1.8,2.8)
+  rasterImage(stim1,0.2,1.2,0.8,1.8)
+  rasterImage(stim1,1.2,1.2,1.8,1.8)
+  rasterImage(stim1,1.2,0.2,1.8,0.8)
+
+  rasterImage(stim3,2.2,3.2,2.8,3.8)
+  rasterImage(stim3,2.2,2.2,2.8,2.8)
+  rasterImage(stim3,3.2,2.2,3.8,2.8)
+  rasterImage(stim3,2.2,1.2,2.8,1.8)
+  rasterImage(stim1,3.2,1.2,3.8,1.8)
+  rasterImage(stim2,2.2,0.2,2.8,0.8)
+  rasterImage(stim1,3.2,0.2,3.8,0.8)
+
+  lines(c(0,4),c(0,0),lwd=3)
+  lines(c(0,4),c(4,4),lwd=3)
+  lines(c(0,0),c(0,4),lwd=3)
+  lines(c(4,4),c(0,4),lwd=3)
+
+  lines(c(0,4),c(1,1),lwd=1.5)
+  lines(c(0,4),c(2,2),lwd=1.5)
+  lines(c(0,4),c(3,3),lwd=1.5)
+
+  lines(c(1,1),c(0,4),lwd=1.5)
+  lines(c(2,2),c(0,4),lwd=3)
+  lines(c(3,3),c(0,4),lwd=1.5)
+
+collist <- c('red','blue','orange','darkgreen')
+
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c('0','1/2','1','2','4','8','16','32','64')
+ticklocsy <- seq(-12,36,6)
+ticklabelsy <- c('1/4','1/2','1','2','4','8','16','32','64')
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,36))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+pedlist <- -12:36
+pedlevelsC <- 10^(pedlist/20)
+pedlevelsC[1] <- 0
+exampledip <- array(0,dim=c(4,length(pedlist)))
+  for (cond in 1:4){
+    for (pedlev in 1:length(pedlist)){
+      exampledip[cond,pedlev] <- discriminate(c(7.8,6.5,1.3,1,0.1,1,0.2),pedlevelsC[pedlev],cond)
+    }
+  }
+
+exampledipdB <- 20*log10(exampledip)
+
+for (cond in 1:4){
+  lines(pedlist,exampledipdB[cond,],col=collist[cond],lwd=3)
+}
+
+legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),lwd=3,col=collist,box.lwd=2,cex=1.5)
+
+}
+
+```
+
+```{r plotMCS, include=FALSE}
+
+  load('local/MCSdata.RData')
+slopematrix <- 10^(apply(log10(slopematrix),c(2,3),mean))
+slopematrix <- round(slopematrix,digits=2)
+
+if (processdata>0){
+
+  propcorr <- apply(MCSpropcorr,2:3,mean)
+  contrastsdB <- contrastsdB[1,,]
+
+ticklocsx <- seq(-12,42,6)
+ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64','128')
+ticklocsy <- seq(0,100,25)
+ticklabelsy <- ticklocsy
+
+titlelist <- c('(a) Achromatic target','(b) R/G target','(c) B/Y target','(d) Threshold elevation','(e) Psychometric slope')
+
+    pdf(paste0('Figures/MCSdata.pdf'),width=12,height=8)
+
+    layout(matrix(c(1,1,2,2,3,3,0,4,4,5,5,0),2,6,byrow=TRUE))
+
+  for (cond in 1:3){
+
+  par(pty="s")
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,42), ylim=c(0,100))  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5)     # add the tick labels
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+  title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+  title(ylab="Percent correct", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+  title(main=titlelist[cond],cex.main=2)
+
+  lines(c(-12,42),c(50,50),lty=2)
+
+  lines(contrastsdB[cond,],propcorr[cond,],lwd=3)
+  points(contrastsdB[cond,],propcorr[cond,],pch=21,lwd=3,cex=2,bg='black')
+
+  lines(contrastsdB[cond+3,],propcorr[cond+3,],lwd=3)
+  points(contrastsdB[cond+3,],propcorr[cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
+
+  lines(contrastsdB[cond+6,],propcorr[cond+6,],lwd=3)
+  points(contrastsdB[cond+6,],propcorr[cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
+
+  lines(contrastsdB[cond+9,],propcorr[cond+9,],lwd=3)
+  points(contrastsdB[cond+9,],propcorr[cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
+
+  # text(18,10,paste(ntrials[1],'trials/level'),pos=4)
+
+  legend(-2,40,c('Target only','Achromatic mask','R/G mask','B/Y mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)
+
+}
+
+  par(pty="s")
+
+plotlims <- c(0.5,3.5,0.5,3.5)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocs <- seq(1,3)    # locations of tick marks on x axis
+ticklabels <- c('ACH','R/G','B/Y')
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabels, side = 1, at=ticklocs,line=0.5) 
+mtext(text = ticklabels, side = 2, at=ticklocs, line=0.2, las=1) 
+title(xlab="Target", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Mask", col.lab=rgb(0,0,0), line=2.5, cex.lab=1.5)
+title(main=titlelist[4],cex.main=2)
+
+thdelev <- apply(thdelev,c(2,3),mean)
+
+ramp2 <- colorRamp(c("white","cornflowerblue"))  # create a ramp from one colour to another
+colmatrix2 <- rgb(ramp2(seq(0, 1, length = 101)), max = 255)
+image(1:3,1:3,thdelev,zlim=c(0,30),col=colmatrix2,add=TRUE,useRaster=FALSE)
+
+thdfactor <- round(10^(thdelev/20),digits=2)
+counter <- 0
+for (x in 1:3){
+  for (y in 1:3){
+    text(x,y,thdfactor[x,y],cex=1.6)
+  }
+}
+
+par(pty="s")
+
+plotlims <- c(0.5,3.5,0.5,3.5)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocs <- seq(1,3)    # locations of tick marks on x axis
+ticklabels <- c('ACH','R/G','B/Y')
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabels, side = 1, at=ticklocs,line=0.5) 
+mtext(text = ticklabels, side = 2, at=ticklocs, line=0.2, las=1) 
+title(xlab="Target", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Mask", col.lab=rgb(0,0,0), line=2.5, cex.lab=1.5)
+title(main=titlelist[5],cex.main=2)
+
+ramp2 <- colorRamp(c("white","darkgreen"))  # create a ramp from one colour to another
+colmatrix2 <- rgb(ramp2(seq(0, 1, length = 101)), max = 255)
+image(1:3,1:3,slopematrix,zlim=c(0,8),col=colmatrix2,add=TRUE,useRaster=FALSE)
+
+counter <- 0
+for (x in 1:3){
+  for (y in 1:3){
+    text(x,y,slopematrix[x,y],cex=1.6)
+  }
+}
+
+  dev.off()
+
+}
+
+```
+
+```{r plotindividual, include=FALSE}
+
+# plot individual participant data for appendices
+
+if (processdata>0){
+
+load('local/thresholddata.RData')
+
+pdf('Figures/individualdippers.pdf',width=12,height=12)
+par(mfrow=c(3,3))
+
+collist <- c('red','blue','orange','darkgreen')
+
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
+ticklocsy <- seq(-12,36,6)
+ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
+
+for (p in 1:3){
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main=paste0('(',letters[(3*(p-1)+1)],')  P',p,': Achromatic'),cex.main=2)
+
+pedcontrasts <- seq(-12,30,6)
+
+for (cond in 1:4){
+  lines(pedcontrasts,allthresh[p,1,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,allthresh[p,1,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+
+if (p==1){legend(-12,36,c('Monocular','Binocular','Half-bin','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main=paste0('(',letters[(3*(p-1)+2)],')  P',p,': Red/Green'),cex.main=2)
+
+pedcontrasts <- c(-12,seq(0,36,6))
+
+for (cond in 1:4){
+  lines(pedcontrasts,allthresh[p,3,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,allthresh[p,3,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main=paste0('(',letters[(3*(p-1)+3)],')  P',p,': Blue/Yellow'),cex.main=2)
+
+for (cond in 1:4){
+  lines(pedcontrasts,allthresh[p,2,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,allthresh[p,2,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+
+}
+
+dev.off()
+
+load('local/MCSdata.RData')
+slopematrix <- 10^(apply(log10(slopematrix),c(2,3),mean))
+slopematrix <- round(slopematrix,digits=2)
+contrastsdB <- contrastsdB[1,,]
+
+titlelist <- c('(a)  P1: Achromatic target','(b)  P1: R/G target','(c)  P1: B/Y target','(d)  P4: Achromatic target','(e)  P4: R/G target','(f)  P4: B/Y target','(g)  P5: Achromatic target','(h)  P5: R/G target','(i)  P5: B/Y target')
+
+ticklocsx <- seq(-12,42,6)
+ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64','128')
+ticklocsy <- seq(0,100,25)
+ticklabelsy <- ticklocsy
+
+pdf('Figures/individualMCS.pdf',width=12,height=12)
+par(mfrow=c(3,3))
+
+for (p in 1:3){
+  for (cond in 1:3){
+
+  par(pty="s")
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,42), ylim=c(0,100))  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5)     # add the tick labels
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+  title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+  title(ylab="Percent correct", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+  title(main=titlelist[3*(p-1)+cond],cex.main=2)
+
+  lines(c(-12,42),c(50,50),lty=2)
+
+  lines(contrastsdB[cond,],MCSpropcorr[p,cond,],lwd=3)
+  points(contrastsdB[cond,],MCSpropcorr[p,cond,],pch=21,lwd=3,cex=2,bg='black')
+
+  lines(contrastsdB[cond+3,],MCSpropcorr[p,cond+3,],lwd=3)
+  points(contrastsdB[cond+3,],MCSpropcorr[p,cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
+
+  lines(contrastsdB[cond+6,],MCSpropcorr[p,cond+6,],lwd=3)
+  points(contrastsdB[cond+6,],MCSpropcorr[p,cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
+
+  lines(contrastsdB[cond+9,],MCSpropcorr[p,cond+9,],lwd=3)
+  points(contrastsdB[cond+9,],MCSpropcorr[p,cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
+
+if (p==1 & cond==1){legend(-2,40,c('Target only','Achromatic mask','R/G mask','B/Y mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)}
+
+  }}
+
+}
+
 ```
@@
 
+The process by which the brain combines independent inputs is of fundamental importance for understanding sensory perception.
+Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains combine the inputs from the left and right eyes to provide binocular single vision.
+In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data across multiple techniques, including psychophysics [@Meese2006], EEG [@Baker2017], fMRI [@Moradi2009] and pupillometry [@Segala2023].
+However, the majority of this work has used achromatic (black and white) stimuli; we know comparatively little about how chromatic signals are combined binocularly, or about how signals in different ocular and chromatic channels interact.
+In this study we use psychophysical detection and discrimination paradigms to explore binocular interactions in the chromatic pathways.
+
+A useful framework for understanding binocular signal processing is the two-stage gain control model of binocular combination introduced by @Meese2006.
+This model features interocular suppression between monocular channels, followed by binocular summation.
+The model accounts well for the pattern of contrast discrimination ('dipper') functions for four distinct ocular configurations [see also @Georgeson2016], illustrated in Figure \@ref(fig:exampledips).
+In the monocular condition, participants must discriminate between stimuli of two contrasts (a 'pedestal', and a 'pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance.
+In the binocular condition, the same stimuli are shown to both eyes.
+In the half-binocular condition the pedestal is shown to both eyes, but the target increment shown only to one eye.
+Finally, the dichoptic condition involves presenting the pedestal to one eye, and the target increment to the other eye.
+
+```{r exampledips, fig.cap="Illustration of stimulus conditions (left) and example dipper functions (right).", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/exampledips.pdf')
+
+```
+
+The detailed pattern of results across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
+At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition owing to binocular summation [@Baker2018; @Campbell1965].
+However at high pedestal contrasts the 'handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation [@Legge1984; @Maehara2005].
+The half-binocular condition avoids confounding the number of eyes seeing the target with the number of eyes seeing the pedestal [@Meese2006].
+The pedestal is always binocular in this condition, whereas the target increment is monocular, and thresholds are consistently higher than in the binocular condition across the full range of pedestal contrasts.
+This demonstrates that binocular summation occurs across the full contrast range, when the pedestal ocularity is appropriately controlled.
+Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast in order to be detectable [@Legge1979; @Maehara2005; @Baker2007b].
+
+At the output of the human retina, visual signals are split into three chromatic pathways.
+The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information, and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
+The difference of long- and medium-wavelength cone outputs (L-M) is responsive to chromatic stimuli modulating along a red/green axis in colour space.
+Finally the short wavelength cone outputs (S-(L+M)) code chromatic stimuli modulating along a blue/yellow axis.
+There has not yet been a detailed investigation of binocular contrast discrimination in either of these chromatic pathways, however there is reason to believe they may differ from the achromatic pathway.
+At detection threshold, binocular summation is greater for chromatic versus achromatic stimuli [@Simmons2005], implying a more linear initial stage of processing.
+For cross-orientation masking, there are differences in the magnitude of masking between chromatic (red/green) and achromatic stimuli [@Kim2013; @Medina2009], as well as differences in their temporal dynamics [@Kim2015].
+There are also interactions between chromatic and achromatic pathways both within [@Chen2000] and between [@Mullen2014; @Kingdom2015] the eyes, yet these have not been fully explored for arrangements where the target and mask have the same orientation.
+Finally, the neurophysiological underpinnings of colour vision are distinct from the achromatic system.
+In primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981].
+The blob regions appear to be largely monocular [@Livingstone1984], suggesting that binocular combination for chromatic stimuli might occur later than for achromatic stimuli and be subject to different constraints.
+
+Strong interocular normalization is well-established when using DC-balanced periodic stimuli such as sine-wave gratings [@Meese2006; @Baker2017; @Moradi2009].
+However there is some evidence that binocular combination is more linear for luminance increments [@Levelt1965; @Anstis1998], particularly against a dark background [@Baker2012].
+Our recent work has extended this finding to flickering discs of luminance, which are DC-balanced across time [@Segala2023].
+Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement, indicating that binocular combination rules may differ for temporal contrast.
+
+The main aim of the present study is to characterise binocular signal combination for chromatic stimuli, and for temporal modulations of luminance.
+We also aimed to investigate interocular suppression between chromatic and achromatic pathways.
+We therefore preregistered a series of psychophysical experiments (see: [https://osf.io/3vdga/](https://osf.io/3vdga/)).
+In Experiment 1 we replicate the four key pedestal masking conditions of @Meese2006 described above for achromatic grating stimuli, and extend this to both red/green and blue/yellow isoluminant chromatic stimuli.
+In Experiment 2 we explore dichoptic masking within and between these stimuli.
+Experiment 3 repeats the achromatic condition from the first experiment, but using a temporally modulated disc rather than sine-wave gratings.
+We take a Bayesian approach to data analysis and modelling; by fitting a hierarchical version of the two-stage gain control model [@Meese2006] we compare posterior parameter distributions to understand how model parameters such as the weight of interocular suppression vary across visual pathways.
+
 # Materials & Methods
@@
 
-All four experiments were completed by the first author (DHB) and two other participants, who differed for each experiment.
-Written informed consent was provided before data collection began, and all procedures were approved by the ethics committee of the Department of Psychology at the University of York.
+All experiments were completed by the first author (DHB) and two other participants, who differed for each experiment.
+Written informed consent was obtained before data collection began, and all procedures were approved by the ethics committee of the Department of Psychology at the University of York (ID number 2202).
 
@@
 In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant.
-In the (L+M)-S condition, the isoluminant stimuli maximised S-cone contrast.
+In the S-(L+M) condition, the isoluminant stimuli maximised S-cone contrast.
 Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals [@Stockman2000].
-
-The stimuli in Experiments 3 and 4 were temporal modulations of luminance and colour, using the same raised cosine envelope as described above, but with no further spatial modulation.
-The stimuli counterphase flickered sinusoidally at 4Hz, along the same axes of luminance and colour as described for Experiments 1 and 2.
-
+The stimuli in Experiment 3 were temporal modulations of luminance, using the same raised cosine envelope as described above, but with no further spatial modulation.
+The stimuli counterphase flickered sinusoidally at 4Hz.
 In all experiments, we displayed a binocular fusion lock, consisting of three concentric rings of small square elements with random colour.
@@
 
+For convenience, we express stimulus contrast as a percentage of the maximum possible contrast that could be displayed on our system.
+For achromatic stimuli, the maximum contrast is 1, so this is equivalent to the standard Michelson contrast expressed as a percentage.
+For the isoluminant chromatic stimuli, the maximum displayable L-M (red/green) cone contrast was 0.1, and the maximum displayable S-(L+M) (blue/yellow) cone contrast was 0.88.
+So an L-M threshold of 50\% is a cone contrast of $0.5\times0.1 = 0.05$, and an S-(L+M) threshold of 50\% is a cone contrast of $0.5\times0.88 = 0.44$.
+The threshold values reported throughout can therefore be converted to cone contrast by a straightforward multiplicative transform.
+
 ## Procedure
@@
 
-Before beginning primary data collection, each participant completed an isoluminance adjustment task.
-Stimuli were presented that counterphase flickered at 10Hz, defined about either the L-M or (L+M)-S plane in cone space.
+Before beginning primary data collection, each participant in Experiments 1 and 2 completed an isoluminance adjustment task.
+Stimuli were presented that counterphase flickered at 5Hz, defined about either the L-M or S-(L+M) plane in cone space.
 Participants used a trackball to dynamically adjust the angle of the stimulus to minimise the percept of flicker.
 Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli for the main experiment for that participant.
-Settings were very similar across participants for the (L+M)-S direction, and varied somewhat more for the L-M direction (Figure?).
+Settings were very similar across participants for the S-(L+M) direction, and  somewhat more heterogeneous for the L-M direction (see Figure \@ref(fig:isofig)).
 
-*Figure here summarising the isoluminant data*
+```{r isofig, fig.cap="Isoluminance settings from all participants in Experiments 1 and 2.
+Panel (a) shows red/green and panel (b) shows blue/yellow settings that were subsequently used to generate stimuli in the main experiments.
+Within each panel, solid lines show the mean settings for each participant, and black curves show the range of possible stimuli displayed during the adjustment task.", fig.align="center", echo=FALSE}
 
-In Experiments 1 and 3, participants completed a two-interval-forced-choice (2IFC) contrast discrimination task.
+knitr::include_graphics('Figures/isosettings.pdf')
 
-In Experiments 2 and 3, participants completed a 2IFC dichoptic masking task.
+```
+
+In Experiment 1, participants completed a two-interval-forced-choice (2IFC) contrast discrimination task.
+Stimuli were presented for 200ms, with an interstimulus interval of 400ms.
+Each interval was indicated by an auditory beep, and participants made their responses using a two-button trackball.
+Correct trials were indicated by a high pitched tone, and incorrect trials by a low pitched tone.
+Each block of the experiment tested a single pedestal contrast level, and lasted around 12 minutes.
+On each trial the target contrast level was determined by a 3-down-1-up staircase procedure.
+There were 8 interleaved staircases in total; four stimulus arrangements (see Figure \@ref(fig:exampledips)) by two target eye assignments.
+Each pedestal contrast was repeated 3 times by each participant, and the block order was randomised.
+The experiment lasted around 4 hours per participant for each chromatic condition, which took place over the course of several weeks.
+In total, the experiment consisted of `r nrow(ex1data)` trials (pooled across participants).
+
+In Experiment 2, participants completed a 2IFC dichoptic masking task.
+The stimuli and trial protocol were the same as for Experiment 1, except that the target contrast was chosen from a set of 10 possible values, determined in advance based on the data of Experiment 1.
+There were 12 possible conditions: baseline detection thresholds for achromatic, red/green and blue/yellow stimuli, and the nine possible factorial pairings obtained by assigning these conditions to be target and dichoptic mask stimuli.
+Mask contrasts were chosen to be approximately 16 times their (monocular) detection threshold, based on the data from Experiment 1.
+Each block of the experiment tested a single condition, and consisted of 200 trials.
+A high contrast example of the target stimulus was displayed at the foot of the screen throughout, so that there was no ambiguity about the target identity on a given block.
+Participants completed 10 repetitions of each condition (120 blocks of ~6 minutes each), lasting around 12 hours, for a total of `r nrow(ex2data)` trials (pooled across participants).
+
+In Experiment 3, the achromatic conditions from Experiment 1 were repeated using a flickering disc stimulus.
+The stimulus counterphase flickered at 4Hz, and was presented for 500ms (i.e.
+2 full cycles of the temporal modulation).
+All other procedures were the same as for Experiment 1, and the experiment comprised a total of X trials (pooled across participants).
 
@@
 
-Psychometric functions from each experiment were fit with \emph{psignifit} 4 to estimate full posterior distributions for threshold and slope parameters via a Bayesian numerical integration method [@Schutt2016].
+Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate full posterior distributions for threshold and slope parameters via a Bayesian numerical integration method [@Schutt2016], fitting a cumulative Gaussian.
 We also implemented a Bayesian hierarchical version of the two stage model of @Meese2006 using the Stan language [@Carpenter2017].
-This used a Bernoulli distribution to model the trial-by-trial response data, and was fit separately to each chromatic condition of Experiments 1 and 3 (i.e.
-6 model fits in total).
+This used a binomial generator function to model the proportion correct data at each target level, and was fit separately to each chromatic condition of Experiment 1, and the data of Experiment 3 (i.e.
+4 model fits in total).
 The modelling primarily focuses on comparing posterior parameter distributions across conditions and experiments, rather than a model comparison approach.
-We generated over 1 million posterior samples for each model, and retained 10% of them for plotting.
+We generated over 1 million posterior samples for each model, and retained 10\% of them for plotting.
 
-## Data and code availability
+## Open science practices
 
-All experimental code, raw data and analysis scripts are available at: https://osf.io/3vdga/
+All experimental code, raw data and analysis scripts are available at: https://osf.io/3vdga/.
+The linked GitHub repository also contains a fully reproducible version of the manuscript.
+Note that we deviated slightly from the planned preregistration, in that we did not collect data for chromatic flickering discs, or for the cross-pathway dichoptic experiment using disc stimuli.
+This is because the grating data from Experiments 1 and 2, and the achromatic disc data from Experiment 3, were sufficient to address the questions we had wanted to answer from these experiments.
 
@@
 
+```{r dipregressions, echo=FALSE}
+
+regdata <- NULL
+regdata$thd <- meanthresh[1,2,5:8]
+regdata$ped <- seq(12,30,6)
+regdata <- as.data.frame(regdata)
+binregACH <- lm(thd ~ ped, data=regdata)
+
+regdata <- NULL
+regdata$thd <- meanthresh[3,2,5:8]
+regdata$ped <- seq(12,30,6)
+regdata <- as.data.frame(regdata)
+binregRG <- lm(thd ~ ped, data=regdata)
+
+regdata <- NULL
+regdata$thd <- meanthresh[2,2,5:8]
+regdata$ped <- seq(12,30,6)
+regdata <- as.data.frame(regdata)
+binregBY <- lm(thd ~ ped, data=regdata)
+
+regdata <- NULL
+regdata$thd <- meanthresh[1,4,5:8]
+regdata$ped <- seq(12,30,6)
+regdata <- as.data.frame(regdata)
+dichregACH <- lm(thd ~ ped, data=regdata)
+
+regdata <- NULL
+regdata$thd <- meanthresh[3,4,5:8]
+regdata$ped <- seq(12,30,6)
+regdata <- as.data.frame(regdata)
+dichregRG <- lm(thd ~ ped, data=regdata)
+
+regdata <- NULL
+regdata$thd <- meanthresh[2,4,5:8]
+regdata$ped <- seq(12,30,6)
+regdata <- as.data.frame(regdata)
+dichregBY <- lm(thd ~ ped, data=regdata)
+
+```
+
+Dipper functions from Experiment 1 are displayed in Figure \@ref(fig:dipperfig).
+Panel (a) shows the achromatic results, which replicate the key features from previous work.
+At detection threshold, binocular summation was a factor of `r round(10^(summation[1]/20),digits=2)` (`r round(summation[1],digits=2)`dB), consistent with previous reports.
+Pedestal masking functions follow the typical 'dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
+The monocular and binocular dipper handles converge at high contrasts, whereas the half-binocular thresholds remain above the binocular thresholds across the full range of pedestal contrasts.
+The dichoptic condition produced very high thresholds, with the rising portion of the dipper having a slope around 1 (regression slope of `r round(dichregACH$coefficients[2], digits=2)` across the highest 4 pedestal contrasts in log (dB) units).
+
+```{r dipperfig, fig.cap="Dipper functions from Experiment 1, averaged across three participants.
+Error bars show ±1SE across participants.
+Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/dipperssimplex.pdf')
+
+```
+
+A similar pattern of results was observed for both the red/green and blue/yellow isoluminant stimuli (see Figure \@ref(fig:dipperfig)b,c).
+Summation at threshold was a factor of `r round(10^(summation[3]/20),digits=2)` (`r round(summation[3],digits=2)`dB) for the red/green targets, and a factor of `r round(10^(summation[2]/20),digits=2)` (`r round(summation[2],digits=2)`dB) for the blue/yellow targets, and so was marginally higher than for achromatic stimuli.
+The general character of the dipper functions was largely consistent with the achromatic results, though we observed shallower facilitation and weaker masking, especially for the blue/yellow stimuli.
+For example, the strongest facilitation in the binocular condition for achromatic stimuli was a factor of `r round(10^((meanthresh[1,2,1]-meanthresh[1,2,3])/20),digits=2)`, whereas it reduced to a factor of `r round(10^((meanthresh[3,2,1]-meanthresh[3,2,3])/20),digits=2)` for red/green stimuli and `r round(10^((meanthresh[2,2,1]-meanthresh[2,2,3])/20),digits=2)` for blue/yellow stimuli.
+The slope of the binocular dipper handle was `r round(binregACH$coefficients[2], digits=2)` for achromatic stimuli, `r round(binregRG$coefficients[2], digits=2)` for red/green stimuli, and `r round(binregBY$coefficients[2], digits=2)` for blue/yellow stimuli.
+Dichoptic masking remained as strong for the chromatic conditions as for the achromatic stimuli (regression slopes of `r round(dichregRG$coefficients[2], digits=2)` for red/green and `r round(dichregBY$coefficients[2], digits=2)` for blue/yellow).
+The pattern of results for individual participants was consistent with the averages, as shown in Figure \@ref(fig:individualdips).
+
+Modelling
+
+```{r params, fig.cap="Model parameters", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/modelparams.pdf')
+
+```
+
 ## Experiment 2
+
+In Experiment 2 we focussed on the dichoptic condition at a single mask contrast, and measured full psychometric functions using the method of constant stimuli for all factorial pairings of target and mask chromaticity.
+The pooled results across three participants are shown in Figure \@ref(fig:MCSfig), and results for individual participants are available in Figure \@ref(fig:individualMCS).
+All conditions produced monotonically increasing psychometric functions (panels a-c), but the extent of masking was highly dependent on the relationship between the target and mask chromaticity.
+
+```{r MCSfig, fig.cap="Summary of data from Experiment 2.
+Panels (a-c) show psychometric functions for each condition, pooled across participants (600 trials per target contrast level).
+Panel (d) shows the average threshold elevation factor for each combination of target and mask stimulus.
+Panel (e) shows the geometric mean psychometric slope value for each masking condition in Weibull beta units.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/MCSdata.pdf')
+
+```
+
+Threshold elevation was greatest when the target and mask had the same chromaticity - notice that the psychometric function is shifted furthest to the right for the achromatic target with an achromatic mask (white and black circles in Figure \@ref(fig:MCSfig)a), for the red/green target with a red/green mask (red and green circles in Figure \@ref(fig:MCSfig)b), and for the blue/yellow target with a blue/yellow mask (blue and yellow circles in Figure \@ref(fig:MCSfig)c).
+Masking was weakest between achromatic masks/targets and chromatic masks/targets.
+Finally there was an intermediate level of masking between red/green and blue/yellow stimuli.
+This is summarised in Figure \@ref(fig:MCSfig)d, which represents threshold elevation for each combination of target and mask chromaticity.
+Note that the positive diagonal exhibits the highest values, and represents threshold elevation between targets and masks of the same chromaticity.
+
+We also calculated the slope of the psychometric function for each condition, converted to equivalent Weibull $\beta$ values.
+In the absence of a mask, the average slope was $\beta$ = `r round(10^(mean(log10(detslopes))),digits=2)`, which is typical for contrast detection tasks.
+Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average $\beta$ = `r round(10^(mean(log10(c(slopematrix[1,1],slopematrix[2,2],slopematrix[3,3])))),digits=2)`).
+These 'super-steep' psychometric functions for dichoptic pedestal masking have been reported previously [@Meese2006; @Baker2013], and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \@ref(fig:MCSfig)e).
+However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average $\beta$ = `r round(10^(mean(log10(c(slopematrix[1,2],slopematrix[1,3],slopematrix[2,1],slopematrix[2,3],slopematrix[3,1],slopematrix[3,2])))),digits=2)` for the off-diagonal values).
 
@@
 
-## Experiment 4
+In our final experiment, we again measured dipper functions, but this time for a temporally modulating luminance disc.
+This was motivated by our recent work [@Segala2023] that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
+The pattern of dipper functions for a 4Hz flickering disc (see Figure X) was very similar to that observed for achromatic gratings (see Figure \@ref(fig:dipperfig)a), and the binocular summation ratio at threshold was also similar (a factor of).
+Fitting the same computational model to the disc data also generated an estimated weight of interocular suppression around 1.
+Data for individual participants are shown in Figure AX.
 
 # Discussion
+
+Across three psychophysical experiments, we have demonstrated that:
+
+- Binocular combination of isoluminant chromatic stimuli is similar to that for achromatic stimuli
+- Interocular suppression is strongest within a chromatic pathway, and weakest between achromatic and chromatic pathways
+- Binocular combination occurs similarly for temporal and temporal luminance modulations
+
+We now discuss the relationship to previous work, consider the likely physiological substrates of these effects and .
+
+Recent evidence indicates that the physiological substrate of interocular suppression may be neurons in layer 4 of primary visual cortex [@Dougherty2019].
+Most cells in this layer are monocularly exciteable, in that their responses increase only by stimulation of their preferred eye.
+However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed by the two-stage model.
+In terms of perception, the consequence of this early suppression is to achieve 'ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes [@Baker2007].
+Similar processes of invariance have also been reported using fMRI [@Moradi2009] and steady-state EEG [@Baker2017].
 
@@
 # References
+
+<div id='refs'> </div>
+
+# Appendices
+
+\beginsupplement
+
+```{r individualdips, fig.cap="Individual participant data from Experiment 1.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/individualdippers.pdf')
+
+```
+
+```{r individualMCS, fig.cap="Individual participant data from Experiment 2.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/individualMCS.pdf')
+
+```

### 2024-03-09 manuscript.tex
Started writing manuscript

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{float} \floatplacement{figure}{H} \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
 \ifLuaTeX
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
-  pdftitle={Binocular integration of chromatic information},
+  pdftitle={Binocular integration of chromatic and luminance signals},
   hidelinks,
@@
 
-\title{Binocular integration of chromatic information}
-\author{Daniel H. Baker, Kirralise J. Hansford, Federico G. Segala, Rowan J. Huxley,\\
-Joel T. Martin, Lauren E. Welbourne \& Alex R. Wade}
-\date{2023-01-07}
+\title{Binocular integration of chromatic and luminance signals}
+\author{Daniel H. Baker, Kirralise J. Hansford, Federico G. Segala, Annie Y. Morsi,\\
+Rowan J. Huxley, Joel T. Martin, Maya Rockman \& Alex R. Wade}
+\date{2024-03-09}
 
@@
 
+The process by which the brain combines independent inputs is of fundamental importance for understanding sensory perception.
+Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains combine the inputs from the left and right eyes to provide binocular single vision.
+In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data across multiple techniques, including psychophysics (Meese et al., 2006), EEG (Baker \& Wade, 2017), fMRI (Moradi \& Heeger, 2009) and pupillometry (Segala et al., 2023).
+However, the majority of this work has used achromatic (black and white) stimuli; we know comparatively little about how chromatic signals are combined binocularly, or about how signals in different ocular and chromatic channels interact.
+In this study we use psychophysical detection and discrimination paradigms to explore binocular interactions in the chromatic pathways.
+
+A useful framework for understanding binocular signal processing is the two-stage gain control model of binocular combination introduced by Meese et al.
+(2006).
+This model features interocular suppression between monocular channels, followed by binocular summation.
+The model accounts well for the pattern of contrast discrimination (`dipper') functions for four distinct ocular configurations (see also Georgeson et al., 2016), illustrated in Figure \ref{fig:exampledips}.
+In the monocular condition, participants must discriminate between stimuli of two contrasts (a `pedestal', and a `pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance.
+In the binocular condition, the same stimuli are shown to both eyes.
+In the half-binocular condition the pedestal is shown to both eyes, but the target increment shown only to one eye.
+Finally, the dichoptic condition involves presenting the pedestal to one eye, and the target increment to the other eye.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/exampledips}
+
+}
+
+\caption{Illustration of stimulus conditions (left) and example dipper functions (right).}\label{fig:exampledips}
+\end{figure}
+
+The detailed pattern of results across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
+At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition owing to binocular summation (Baker et al., 2018; Campbell \& Green, 1965).
+However at high pedestal contrasts the `handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation (Legge, 1984; Maehara \& Goryo, 2005).
+The half-binocular condition avoids confounding the number of eyes seeing the target with the number of eyes seeing the pedestal (Meese et al., 2006).
+The pedestal is always binocular in this condition, whereas the target increment is monocular, and thresholds are consistently higher than in the binocular condition across the full range of pedestal contrasts.
+This demonstrates that binocular summation occurs across the full contrast range, when the pedestal ocularity is appropriately controlled.
+Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast in order to be detectable (Baker \& Meese, 2007; Legge, 1979; Maehara \& Goryo, 2005).
+
+At the output of the human retina, visual signals are split into three chromatic pathways.
+The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information, and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
+The difference of long- and medium-wavelength cone outputs (L-M) is responsive to chromatic stimuli modulating along a red/green axis in colour space.
+Finally the short wavelength cone outputs (S-(L+M)) code chromatic stimuli modulating along a blue/yellow axis.
+There has not yet been a detailed investigation of binocular contrast discrimination in either of these chromatic pathways, however there is reason to believe they may differ from the achromatic pathway.
+At detection threshold, binocular summation is greater for chromatic versus achromatic stimuli (Simmons, 2005), implying a more linear initial stage of processing.
+For cross-orientation masking, there are differences in the magnitude of masking between chromatic (red/green) and achromatic stimuli (Kim et al., 2013; Medina \& Mullen, 2009), as well as differences in their temporal dynamics (Kim \& Mullen, 2015).
+There are also interactions between chromatic and achromatic pathways both within (Chen et al., 2000) and between (Kingdom \& Libenson, 2015; Mullen et al., 2014) the eyes, yet these have not been fully explored for arrangements where the target and mask have the same orientation.
+Finally, the neurophysiological underpinnings of colour vision are distinct from the achromatic system.
+In primary visual cortex (V1), chromatic signals are processed in `blob' regions that are revealed by cytochrome oxidase staining (Horton \& Hubel, 1981).
+The blob regions appear to be largely monocular (Livingstone \& Hubel, 1984), suggesting that binocular combination for chromatic stimuli might occur later than for achromatic stimuli and be subject to different constraints.
+
+Strong interocular normalization is well-established when using DC-balanced periodic stimuli such as sine-wave gratings (Baker \& Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009).
+However there is some evidence that binocular combination is more linear for luminance increments (Anstis \& Ho, 1998; Levelt, 1965), particularly against a dark background (Baker et al., 2012).
+Our recent work has extended this finding to flickering discs of luminance, which are DC-balanced across time (Segala et al., 2023).
+Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement, indicating that binocular combination rules may differ for temporal contrast.
+
+The main aim of the present study is to characterise binocular signal combination for chromatic stimuli, and for temporal modulations of luminance.
+We also aimed to investigate interocular suppression between chromatic and achromatic pathways.
+We therefore preregistered a series of psychophysical experiments (see: \url{https://osf.io/3vdga/}).
+In Experiment 1 we replicate the four key pedestal masking conditions of Meese et al.
+(2006) described above for achromatic grating stimuli, and extend this to both red/green and blue/yellow isoluminant chromatic stimuli.
+In Experiment 2 we explore dichoptic masking within and between these stimuli.
+Experiment 3 repeats the achromatic condition from the first experiment, but using a temporally modulated disc rather than sine-wave gratings.
+We take a Bayesian approach to data analysis and modelling; by fitting a hierarchical version of the two-stage gain control model (Meese et al., 2006) we compare posterior parameter distributions to understand how model parameters such as the weight of interocular suppression vary across visual pathways.
+
 \hypertarget{materials-methods}{%
@@
 In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant.
-In the (L+M)-S condition, the isoluminant stimuli maximised S-cone contrast.
-Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals (Stockman and Sharpe, 2000).
-
-The stimuli in Experiments 3 and 4 were temporal modulations of luminance and colour, using the same raised cosine envelope as described above, but with no further spatial modulation.
-The stimuli counterphase flickered sinusoidally at 4Hz, along the same axes of luminance and colour as described for Experiments 1 and 2.
-
+In the S-(L+M) condition, the isoluminant stimuli maximised S-cone contrast.
+Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals (Stockman \& Sharpe, 2000).
+The stimuli in Experiment 3 were temporal modulations of luminance, using the same raised cosine envelope as described above, but with no further spatial modulation.
+The stimuli counterphase flickered sinusoidally at 4Hz.
 In all experiments, we displayed a binocular fusion lock, consisting of three concentric rings of small square elements with random colour.
@@
 
+For convenience, we express stimulus contrast as a percentage of the maximum possible contrast that could be displayed on our system.
+For achromatic stimuli, the maximum contrast is 1, so this is equivalent to the standard Michelson contrast expressed as a percentage.
+For the isoluminant chromatic stimuli, the maximum displayable L-M (red/green) cone contrast was 0.1, and the maximum displayable S-(L+M) (blue/yellow) cone contrast was 0.88.
+So an L-M threshold of 50\% is a cone contrast of \(0.5\times0.1 = 0.05\), and an S-(L+M) threshold of 50\% is a cone contrast of \(0.5\times0.88 = 0.44\).
+The threshold values reported throughout can therefore be converted to cone contrast by a straightforward multiplicative transform.
+
 \hypertarget{procedure}{%
@@
 
-Before beginning primary data collection, each participant completed an isoluminance adjustment task.
-Stimuli were presented that counterphase flickered at 10Hz, defined about either the L-M or (L+M)-S plane in cone space.
+Before beginning primary data collection, each participant in Experiments 1 and 2 completed an isoluminance adjustment task.
+Stimuli were presented that counterphase flickered at 5Hz, defined about either the L-M or S-(L+M) plane in cone space.
 Participants used a trackball to dynamically adjust the angle of the stimulus to minimise the percept of flicker.
 Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli for the main experiment for that participant.
-Settings were very similar across participants for the (L+M)-S direction, and varied somewhat more for the L-M direction (Figure?).
+Settings were very similar across participants for the S-(L+M) direction, and somewhat more heterogeneous for the L-M direction (see Figure \ref{fig:isofig}).
 
-\emph{Figure here summarising the isoluminant data}
+\begin{figure}
+
+{\centering \includegraphics{Figures/isosettings}
+
+}
+
+\caption{Isoluminance settings from all participants in Experiments 1 and 2.
+Panel (a) shows red/green and panel (b) shows blue/yellow settings that were subsequently used to generate stimuli in the main experiments.
+Within each panel, solid lines show the mean settings for each participant, and black curves show the range of possible stimuli displayed during the adjustment task.}\label{fig:isofig}
+\end{figure}
+
+In Experiment 1, participants completed a two-interval-forced-choice (2IFC) contrast discrimination task.
+Stimuli were presented for 200ms, with an interstimulus interval of 400ms.
+Each interval was indicated by an auditory beep, and participants made their responses using a two-button trackball.
+Correct trials were indicated by a high pitched tone, and incorrect trials by a low pitched tone.
+Each block of the experiment tested a single pedestal contrast level, and lasted around 12 minutes.
+On each trial the target contrast level was determined by a 3-down-1-up staircase procedure.
+There were 8 interleaved staircases in total; four stimulus arrangements (see Figure \ref{fig:exampledips}) by two target eye assignments.
+Each pedestal contrast was repeated 3 times by each participant, and the block order was randomised.
+The experiment lasted around 4 hours per participant for each chromatic condition, which took place over the course of several weeks.
+In total, the experiment consisted of 67978 trials (pooled across participants).
+
+In Experiment 2, participants completed a 2IFC dichoptic masking task.
+The stimuli and trial protocol were the same as for Experiment 1, except that the target contrast was chosen from a set of 10 possible values, determined in advance based on the data of Experiment 1.
+There were 12 possible conditions: baseline detection thresholds for achromatic, red/green and blue/yellow stimuli, and the nine possible factorial pairings obtained by assigning these conditions to be target and dichoptic mask stimuli.
+Mask contrasts were chosen to be approximately 16 times their (monocular) detection threshold, based on the data from Experiment 1.
+Each block of the experiment tested a single condition, and consisted of 200 trials.
+A high contrast example of the target stimulus was displayed at the foot of the screen throughout, so that there was no ambiguity about the target identity on a given block.
+Participants completed 10 repetitions of each condition (120 blocks of \textasciitilde6 minutes each), lasting around 12 hours, for a total of 72000 trials (pooled across participants).
+
+In Experiment 3, the achromatic conditions from Experiment 1 were repeated using a flickering disc stimulus.
+The stimulus counterphase flickered at 4Hz, and was presented for 500ms (i.e.~2 full cycles of the temporal modulation).
+All other procedures were the same as for Experiment 1, and the experiment comprised a total of X trials (pooled across participants).
 
@@
 
-Psychometric functions from each experiment were fit with \emph{psignifit} 4 to estimate full posterior distributions for threshold and slope parameters via a Bayesian numerical integration method (Schütt et al., 2016).
+Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate full posterior distributions for threshold and slope parameters via a Bayesian numerical integration method (Schütt et al., 2016), fitting a cumulative Gaussian.
 We also implemented a Bayesian hierarchical version of the two stage model of Meese et al.
 (2006) using the Stan language (Carpenter et al., 2017).
-This used a Bernoulli distribution to model the trial-by-trial response data, and was fit separately to each chromatic condition of Experiments 1 and 3 (i.e.~6 model fits in total).
+This used a binomial generator function to model the proportion correct data at each target level, and was fit separately to each chromatic condition of Experiment 1, and the data of Experiment 3 (i.e.~4 model fits in total).
 The modelling primarily focuses on comparing posterior parameter distributions across conditions and experiments, rather than a model comparison approach.
@@
 
-\hypertarget{data-and-code-availability}{%
-\subsection{Data and code availability}\label{data-and-code-availability}}
+\hypertarget{open-science-practices}{%
+\subsection{Open science practices}\label{open-science-practices}}
 
-All experimental code, raw data and analysis scripts are available at: \url{https://osf.io/3vdga/}
+All experimental code, raw data and analysis scripts are available at: \url{https://osf.io/3vdga/}.
+The linked GitHub repository also contains a fully reproducible version of the manuscript.
+Note that we deviated slightly from the planned preregistration, in that we did not collect data for chromatic flickering discs, or for the cross-pathway dichoptic experiment using disc stimuli.
+This is because the grating data from Experiments 1 and 2, and the achromatic disc data from Experiment 3, were sufficient to address the questions we had wanted to answer from these experiments.
 
@@
 
+Dipper functions from Experiment 1 are displayed in Figure \ref{fig:dipperfig}.
+Panel (a) shows the achromatic results, which replicate the key features from previous work.
+At detection threshold, binocular summation was a factor of 1.67 (4.47dB), consistent with previous reports.
+Pedestal masking functions follow the typical `dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
+The monocular and binocular dipper handles converge at high contrasts, whereas the half-binocular thresholds remain above the binocular thresholds across the full range of pedestal contrasts.
+The dichoptic condition produced very high thresholds, with the rising portion of the dipper having a slope around 1 (regression slope of 1.06 across the highest 4 pedestal contrasts in log (dB) units).
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/dipperssimplex}
+
+}
+
+\caption{Dipper functions from Experiment 1, averaged across three participants.
+Error bars show ±1SE across participants.
+Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).}\label{fig:dipperfig}
+\end{figure}
+
+A similar pattern of results was observed for both the red/green and blue/yellow isoluminant stimuli (see Figure \ref{fig:dipperfig}b,c).
+Summation at threshold was a factor of 1.71 (4.66dB) for the red/green targets, and a factor of 1.73 (4.77dB) for the blue/yellow targets, and so was marginally higher than for achromatic stimuli.
+The general character of the dipper functions was largely consistent with the achromatic results, though we observed shallower facilitation and weaker masking, especially for the blue/yellow stimuli.
+For example, the strongest facilitation in the binocular condition for achromatic stimuli was a factor of 2.63, whereas it reduced to a factor of 2.35 for red/green stimuli and 1.57 for blue/yellow stimuli.
+The slope of the binocular dipper handle was 0.52 for achromatic stimuli, 0.58 for red/green stimuli, and 0.34 for blue/yellow stimuli.
+Dichoptic masking remained as strong for the chromatic conditions as for the achromatic stimuli (regression slopes of 1.3 for red/green and 1.21 for blue/yellow).
+The pattern of results for individual participants was consistent with the averages, as shown in Figure \ref{fig:individualdips}.
+
+Modelling
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/modelparams}
+
+}
+
+\caption{Model parameters}\label{fig:params}
+\end{figure}
+
 \hypertarget{experiment-2}{%
 \subsection{Experiment 2}\label{experiment-2}}
+
+In Experiment 2 we focussed on the dichoptic condition at a single mask contrast, and measured full psychometric functions using the method of constant stimuli for all factorial pairings of target and mask chromaticity.
+The pooled results across three participants are shown in Figure \ref{fig:MCSfig}, and results for individual participants are available in Figure \ref{fig:individualMCS}.
+All conditions produced monotonically increasing psychometric functions (panels a-c), but the extent of masking was highly dependent on the relationship between the target and mask chromaticity.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/MCSdata}
+
+}
+
+\caption{Summary of data from Experiment 2.
+Panels (a-c) show psychometric functions for each condition, pooled across participants (600 trials per target contrast level).
+Panel (d) shows the average threshold elevation factor for each combination of target and mask stimulus.
+Panel (e) shows the geometric mean psychometric slope value for each masking condition in Weibull beta units.}\label{fig:MCSfig}
+\end{figure}
+
+Threshold elevation was greatest when the target and mask had the same chromaticity - notice that the psychometric function is shifted furthest to the right for the achromatic target with an achromatic mask (white and black circles in Figure \ref{fig:MCSfig}a), for the red/green target with a red/green mask (red and green circles in Figure \ref{fig:MCSfig}b), and for the blue/yellow target with a blue/yellow mask (blue and yellow circles in Figure \ref{fig:MCSfig}c).
+Masking was weakest between achromatic masks/targets and chromatic masks/targets.
+Finally there was an intermediate level of masking between red/green and blue/yellow stimuli.
+This is summarised in Figure \ref{fig:MCSfig}d, which represents threshold elevation for each combination of target and mask chromaticity.
+Note that the positive diagonal exhibits the highest values, and represents threshold elevation between targets and masks of the same chromaticity.
+
+We also calculated the slope of the psychometric function for each condition, converted to equivalent Weibull \(\beta\) values.
+In the absence of a mask, the average slope was \(\beta\) = 3.42, which is typical for contrast detection tasks.
+Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average \(\beta\) = 5.38).
+These `super-steep' psychometric functions for dichoptic pedestal masking have been reported previously (Baker et al., 2013; Meese et al., 2006), and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \ref{fig:MCSfig}e).
+However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average \(\beta\) = 2.83 for the off-diagonal values).
 
@@
 
-\hypertarget{experiment-4}{%
-\subsection{Experiment 4}\label{experiment-4}}
+In our final experiment, we again measured dipper functions, but this time for a temporally modulating luminance disc.
+This was motivated by our recent work (Segala et al., 2023) that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
+The pattern of dipper functions for a 4Hz flickering disc (see Figure X) was very similar to that observed for achromatic gratings (see Figure \ref{fig:dipperfig}a), and the binocular summation ratio at threshold was also similar (a factor of).
+Fitting the same computational model to the disc data also generated an estimated weight of interocular suppression around 1.
+Data for individual participants are shown in Figure AX.
 
@@
 \section{Discussion}\label{discussion}}
+
+Across three psychophysical experiments, we have demonstrated that:
+
+\begin{itemize}
+\tightlist
+\item
+  Binocular combination of isoluminant chromatic stimuli is similar to that for achromatic stimuli
+\item
+  Interocular suppression is strongest within a chromatic pathway, and weakest between achromatic and chromatic pathways
+\item
+  Binocular combination occurs similarly for temporal and temporal luminance modulations
+\end{itemize}
+
+We now discuss the relationship to previous work, consider the likely physiological substrates of these effects and .
+
+Recent evidence indicates that the physiological substrate of interocular suppression may be neurons in layer 4 of primary visual cortex (Dougherty et al., 2019).
+Most cells in this layer are monocularly exciteable, in that their responses increase only by stimulation of their preferred eye.
+However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed by the two-stage model.
+In terms of perception, the consequence of this early suppression is to achieve `ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes (Baker et al., 2007).
+Similar processes of invariance have also been reported using fMRI (Moradi \& Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).
 
@@
 \hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\section{References}\label{references}}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Anstis1998}{}}%
+Anstis, S., \& Ho, A.
+(1998).
+Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion.
+\emph{Vision Res}, \emph{38}(4), 523--539.
+\url{https://doi.org/10.1016/s0042-6989(97)00167-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
+Baker, D.
+H., Lygo, F.
+A., Meese, T.
+S., \& Georgeson, M.
+A.
+(2018).
+Binocular summation revisited: Beyond \(\sqrt{2}\).
+\emph{Psychol Bull}, \emph{144}(11), 1186--1199.
+\url{https://doi.org/10.1037/bul0000163}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2007b}{}}%
+Baker, D.
+H., \& Meese, T.
+S.
+(2007).
+Binocular contrast interactions: Dichoptic masking is not a single process.
+\emph{Vision Res}, \emph{47}(24), 3096--3107.
+\url{https://doi.org/10.1016/j.visres.2007.08.013}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
+Baker, D.
+H., Meese, T.
+S., \& Georgeson, M.
+A.
+(2007).
+Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
+\emph{Spat Vis}, \emph{20}(5), 397--413.
+\url{https://doi.org/10.1163/156856807781503622}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2013}{}}%
+Baker, D.
+H., Meese, T.
+S., \& Georgeson, M.
+A.
+(2013).
+Paradoxical psychometric functions ("swan functions") are explained by dilution masking in four stimulus dimensions.
+\emph{Iperception}, \emph{4}(1), 17--35.
+\url{https://doi.org/10.1068/i0552}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
+Baker, D.
+H., \& Wade, A.
+R.
+(2017).
+Evidence for an optimal algorithm underlying signal combination in human visual cortex.
+\emph{Cereb Cortex}, \emph{27}(1), 254--264.
+\url{https://doi.org/10.1093/cercor/bhw395}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2012}{}}%
+Baker, D.
+H., Wallis, S.
+A., Georgeson, M.
+A., \& Meese, T.
+S.
+(2012).
+Nonlinearities in the binocular combination of luminance and contrast.
+\emph{Vision Res}, \emph{56}, 1--9.
+\url{https://doi.org/10.1016/j.visres.2012.01.008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
+Campbell, F. W., \& Green, D. G. (1965). Monocular versus binocular visual acuity. \emph{Nature}, \emph{208}(5006), 191--192. \url{https://doi.org/10.1038/208191a0}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker M, Guo J, Li P, Riddell A.
-2017.
+Carpenter, B., Gelman, A., Hoffman, M.
+D., Lee, D., Goodrich, B., Betancourt, M., Brubaker, M., Guo, J., Li, P., \& Riddell, A.
+(2017).
 Stan: A probabilistic programming language.
-\emph{Journal of Statistical Software} \textbf{76}:1--32.
-doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
+\emph{Journal of Statistical Software}, \emph{76}(1), 1--32.
+\url{https://doi.org/10.18637/jss.v076.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Chen2000}{}}%
+Chen, C., Foley, J.
+M., \& Brainard, D.
+H.
+(2000).
+Detection of chromoluminance patterns on chromoluminance pedestals i: Threshold measurements.
+\emph{Vision Res}, \emph{40}(7), 773--788.
+\url{https://doi.org/10.1016/s0042-6989(99)00227-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dougherty2019}{}}%
+Dougherty, K., Cox, M.
+A., Westerberg, J.
+A., \& Maier, A.
+(2019).
+Binocular modulation of monocular V1 neurons.
+\emph{Curr Biol}, \emph{29}(3), 381--391.e4.
+\url{https://doi.org/10.1016/j.cub.2018.12.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Georgeson2016}{}}%
+Georgeson, M.
+A., Wallis, S.
+A., Meese, T.
+S., \& Baker, D.
+H.
+(2016).
+Contrast and lustre: A model that accounts for eleven different forms of contrast discrimination in binocular vision.
+\emph{Vision Res}, \emph{129}, 98--118.
+\url{https://doi.org/10.1016/j.visres.2016.08.001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Horton1981}{}}%
+Horton, J.
+C., \& Hubel, D.
+H.
+(1981).
+Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey.
+\emph{Nature}, \emph{292}(5825), 762--764.
+\url{https://doi.org/10.1038/292762a0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kim2013}{}}%
+Kim, Y.
+J., Gheiratmand, M., \& Mullen, K.
+T.
+(2013).
+Cross-orientation masking in human color vision: Application of a two-stage model to assess dichoptic and monocular sources of suppression.
+\emph{J Vis}, \emph{13}(6), 15.
+\url{https://doi.org/10.1167/13.6.15}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kim2015}{}}%
+Kim, Y.
+J., \& Mullen, K.
+T.
+(2015).
+The dynamics of cross-orientation masking at monocular and interocular sites.
+\emph{Vision Res}, \emph{116}(Pt A), 80--91.
+\url{https://doi.org/10.1016/j.visres.2015.09.008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
+Kingdom, F.
+A.
+A., \& Libenson, L.
+(2015).
+Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
+\emph{J Vis}, \emph{15}(5), 2.
+\url{https://doi.org/10.1167/15.5.2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Legge1979}{}}%
+Legge, G. E. (1979). Spatial frequency masking in human vision: Binocular interactions. \emph{J Opt Soc Am}, \emph{69}(6), 838--847. \url{https://doi.org/10.1364/josa.69.000838}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
+Legge, G. E. (1984). Binocular contrast summation--II. Quadratic summation. \emph{Vision Res}, \emph{24}(4), 385--394. \url{https://doi.org/10.1016/0042-6989(84)90064-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Levelt1965}{}}%
+Levelt, W. J. (1965). Binocular brightness averaging and contour information. \emph{Br J Psychol}, \emph{56}, 1--13. \url{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Livingstone1984}{}}%
+Livingstone, M.
+S., \& Hubel, D.
+H.
+(1984).
+Anatomy and physiology of a color system in the primate visual cortex.
+\emph{J Neurosci}, \emph{4}(1), 309--356.
+\url{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Maehara2005}{}}%
+Maehara, G., \& Goryo, K. (2005). Binocular, monocular and dichoptic pattern masking. \emph{Optical Review}, \emph{12}(2), 76--82. \url{https://doi.org/10.1007/PL00021542}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Medina2009}{}}%
+Medina, J. M., \& Mullen, K. T. (2009). Cross-orientation masking in human color vision. \emph{J Vis}, \emph{9}(3), 20.1--16. \url{https://doi.org/10.1167/9.3.20}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
-Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
+Meese, T. S., Georgeson, M. A., \& Baker, D. H. (2006). Binocular contrast vision at and above threshold. \emph{J Vis}, \emph{6}(11), 1224--1243. \url{https://doi.org/10.1167/6.11.7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+Moradi, F., \& Heeger, D. J. (2009). Inter-ocular contrast normalization in human visual cortex. \emph{J Vis}, \emph{9}(3), 13.1--22. \url{https://doi.org/10.1167/9.3.13}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mullen2014}{}}%
+Mullen, K.
+T., Kim, Y.
+J., \& Gheiratmand, M.
+(2014).
+Contrast normalization in colour vision: The effect of luminance contrast on colour contrast detection.
+\emph{Sci Rep}, \emph{4}, 7350.
+\url{https://doi.org/10.1038/srep07350}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Schutt2016}{}}%
-Schütt HH, Harmeling S, Macke JH, Wichmann FA.
-2016.
+Schütt, H.
+H., Harmeling, S., Macke, J.
+H., \& Wichmann, F.
+A.
+(2016).
 Painfree and accurate bayesian estimation of psychometric functions for (potentially) overdispersed data.
-\emph{Vision Res} \textbf{122}:105--123.
-doi:\href{https://doi.org/10.1016/j.visres.2016.02.002}{10.1016/j.visres.2016.02.002}
+\emph{Vision Res}, \emph{122}, 105--123.
+\url{https://doi.org/10.1016/j.visres.2016.02.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
+Segala, F.
+G., Bruno, A., Martin, J.
+T., Aung, M.
+T., Wade, A.
+R., \& Baker, D.
+H.
+(2023).
+Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
+\emph{eLife}, \emph{12}, RP87048.
+\url{https://doi.org/10.7554/eLife.87048}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Simmons2005}{}}%
+Simmons, D. R. (2005). The binocular combination of chromatic contrast. \emph{Perception}, \emph{34}(8), 1035--1042. \url{https://doi.org/10.1068/p5279}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
-Stockman A, Sharpe LT.
-2000.
+Stockman, A., \& Sharpe, L.
+T.
+(2000).
 The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
-\emph{Vision Res} \textbf{40}:1711--37.
-doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
+\emph{Vision Res}, \emph{40}(13), 1711--1737.
+\url{https://doi.org/10.1016/s0042-6989(00)00021-3}
 
@@
 
+\hypertarget{appendices}{%
+\section{Appendices}\label{appendices}}
+
+\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/individualdippers}
+
+}
+
+\caption{Individual participant data from Experiment 1.}\label{fig:individualdips}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/individualMCS}
+
+}
+
+\caption{Individual participant data from Experiment 2.}\label{fig:individualMCS}
+\end{figure}
+
 \end{document}

### 2024-03-09 experimentcode/isoflickerVisage.m

@@ -1,0 +1,781 @@
+function isoflickerVisage
+
+% experiment for finding the isoluminant point
+% two separate conditions: L-M and S-(L+M)
+% participant adjusts the stimulus to null perceived flicker
+% we define a vector in LMS space that is the ratio of
+% e.g. L and M excitation, and modify the angle theta according to the user input
+% this version generates stimuli on the fly using the ViSage and stereoscope
+% DHB 22/7/22
+
+close all;
+tic
+
+subj = menu('Select participant','DHB','JTM','KJH','FGS','RJH','Test');
+subnamelist = {'P1','P2','P3','P4','P5','XX'};
+E.subj = subnamelist{subj};
+
+useVSG = 1;   % either use Visage or not
+ntrialspercond = 10;
+ntrials = ntrialspercond*2;
+stimtype = 2;
+
+E.nConds = 2;
+ST.contrast = [0.1 0.86];
+ST.lumcontrast = [0 0];
+ST.theta{1} = 60:0.5:179;  % set of theta values for L-M
+ST.theta{2} = 45:0.5:135;  % set of theta values for S-(L+M)
+ST.condlist = Shuffle([ones(1,ntrialspercond) ones(1,ntrialspercond)+1]);
+
+nISIframes = 60;
+responsekeys = {'UpArrow','DownArrow'};
+
+E.exptPath = strcat(pwd, '\');
+KbName('UnifyKeyNames');
+Screen('Preference', 'SkipSyncTests', 1);
+
+% add the colour toolbox to the path, load in the cone fundamentals and display gamut
+addpath('toolbox_v1.3');
+load fundamentals_ss.mat;  % stockman-sharp 2 degree
+load IiyamaSpectraIrradCC.mat;
+phosphors = phosphors .* 1000000;
+load gammavals.mat;
+%ListenChar(-1);
+
+bg_lms = rgb2lms(phosphors,fundamentals,[0.5; 0.5; 0.5]);
+
+if ~exist('Results','dir')
+    mkdir('Results');
+end
+% Pixels per degree at different experimental setups
+ST.nPixelsPerDegree = 48;
+
+% Grating spans 5 degrees of visual angle
+ST.gratingSize = ST.nPixelsPerDegree * 3;
+
+ST.SF = 1;
+ST.nCycles = ST.SF * ST.gratingSize / ST.nPixelsPerDegree;
+ST.TFtarget = 10; % Temporal frequency waveform
+
[…]

### 2024-03-09 experimentcode/runMCScross.m

@@ -1,0 +1,863 @@
+function runMCScross
+
+% dichoptic conditions with method of constant stimuli
+%
+% single script to run colour dipper experiment
+% choose participant ID and which experiment to run
+% DHB 26/8/22
+% updated 25/9/22 to optimise contrast levels for each participant & condition
+% updated 2/1/23 to implement MCS
+
+close all;
+
+subj = menu('Select participant','DHB','FGS','RJH','Test');
+WaitSecs(0.5);
+
+useVSG = 1;
+useRTS = 0;   % this is glitchy so best avoided
+
+subnamelist = {'P1','P4','P5','XX'};
+exptnamelist = {'AC','RG','BY'};
+
+E.exptpath = strcat(pwd, '\'); % Same as above, JTM
+KbName('UnifyKeyNames');
+Screen('Preference', 'SkipSyncTests', 1);
+rng('shuffle');         % reseed the random number generator from the clock
+
+% add the colour toolbox to the path, load in the cone fundamentals and display gamut
+addpath('toolbox_v1.3');
+load fundamentals_ss.mat;    % stockman-sharp 2 degree cone fundamentals
+load IiyamaSpectraIrradCC.mat;          % spectral readings for the Iiyama monitor in counts
+phosphors = phosphors .* 1000000;
+maxcont = [1 0.1 0.88];     % maximum displayable cone contrast for each stimulus type (depends on monitor gamut)
+load gammavals.mat;             % load in gamma parameters from calibration
+
+ST.npixelsperdegree = 48;
+ST.gratingsizedeg = 3;
+ST.gratingsizepix = ST.gratingsizedeg * ST.npixelsperdegree;
+ST.gausssigma = ST.npixelsperdegree;
+ST.SF = 1;
+ST.ncycles = ST.SF * ST.gratingsizedeg;
+ST.duration = 0.2;
+ST.ISI = 0.4;
+ST.postresponseduration = 0.6;
+ST.phaselist = [0 90 180 270];
+
+E.pedcontrastsdB = [0 0 0 24 24 24 36 36 36 36 36 36];
+E.pedcontrastsC = (10.^(E.pedcontrastsdB./20))./100;
+E.pedcontrastsC(1:3) = 0;
+E.pedtype = [0 0 0 1 1 1 2 2 2 3 3 3];
+E.targettype = [1 2 3 1 2 3 1 2 3 1 2 3];
+
+E.targetlevelsdB(1,:) = -8:2:10;  % achromatic target detection
[…]

### 2024-03-09 experimentcode/runcolourdippers.m

@@ -1,0 +1,935 @@
+function runcolourdippers
+
+% single script to run colour dipper experiment
+% choose participant ID and which experiment to run
+% DHB 26/8/22
+% updated 25/9/22 to optimise contrast levels for each participant & condition
+
+close all;
+
+subj = menu('Select participant','DHB','JTM','KJH','Test');
+WaitSecs(0.5);
+expt = menu('Choose experiment','Achromatic','Red/Green','Blue/Yellow');
+
+useVSG = 1;
+useRTS = 0;   % this is glitchy so best avoided
+
+subnamelist = {'P1','P2','P3','XX'};
+exptnamelist = {'AC','RG','BY'};
+
+E.exptpath = strcat(pwd, '\'); % Same as above, JTM
+KbName('UnifyKeyNames');
+Screen('Preference', 'SkipSyncTests', 1);
+rng('shuffle');         % reseed the random number generator from the clock
+
+% add the colour toolbox to the path, load in the cone fundamentals and display gamut
+addpath('toolbox_v1.3');
+load fundamentals_ss.mat;    % stockman-sharp 2 degree cone fundamentals
+load IiyamaSpectraIrradCC.mat;          % spectral readings for the Iiyama monitor in counts
+phosphors = phosphors .* 1000000;
+maxcont = [1 0.1 0.88];     % maximum displayable cone contrast for each stimulus type (depends on monitor gamut)
+load gammavals.mat;             % load in gamma parameters from calibration
+
+ST.npixelsperdegree = 48;
+ST.gratingsizedeg = 3;
+ST.gratingsizepix = ST.gratingsizedeg * ST.npixelsperdegree;
+ST.gausssigma = ST.npixelsperdegree;
+ST.SF = 1;
+ST.ncycles = ST.SF * ST.gratingsizedeg;
+ST.duration = 0.2;
+ST.ISI = 0.4;
+ST.postresponseduration = 0.6;
+ST.phaselist = [0 90 180 270];
+
+E.pedcontrastsdB(1,:) = -12:6:30;   
+E.pedcontrastsdB(2,:) = -6:6:36;    % for the colour conditions this is % of maximum displayable cone contrast
+E.pedcontrastsdB(3,:) = -6:6:36;    
+E.pedcontrastsC = (10.^(E.pedcontrastsdB./20))./100;
+E.pedcontrastsC(:,1) = 0;
+
+nSCs = [4 8 8 8 8 8 8 8];
+
+if ~exist('Results','dir')
+    mkdir('Results');
+end
[…]

### 2024-03-10 manuscript.Rmd
Various updates and improvements

@@
    | Rowan J. Huxley, Joel T. Martin, Maya Rockman & Alex R. Wade
-date: "`r Sys.Date()`"
+date: "Department of Psychology, University of York"
 output:
@@
 
-processdata <- 0
+processdata <- 2
 # the processdata flag has three settings:
@@
 
-nsamples <- 10000    # number of Stan samples for modelling
+nsamples <- 100000    # number of Stan samples for modelling
+ntotalsimplexfits <- 100    # number of random starting vectors for simplex fits
+ncores <- 8    # number of processor cores to use on the host machine
+postsampleres <- 400    # resolution of psignifit posterior sampling
+
+# other Stan settings
+adaptSteps = 5000  # Number of steps to "tune" the samplers
+burnInSteps = 5000
+thinSteps <- 10
+nChains = 64
 
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','doParallel','R.matlab') # list of CRAN packages
+packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','doParallel','R.matlab','bayestestR','alphahull') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 return(contrastinc) }
+
+errorfit <- function(p){
+
+p <- 10^p
+p[2] <- p[2] + 1
+p[2] <- min(p[2],10)
+p[1] <- 1 + p[1] + p[2]
+p[3] <- 1 + p[3]
+
+pedlevelsC <- 10^(pedlist/20)
+pedlevelsC[1] <- 0
+allpred <- array(0,dim=c(4,length(pedlist)))
+
+  for (cond in 1:4){
+    for (pedlev in 1:length(pedlist)){
+      allpred[cond,pedlev] <- discriminate(p,pedlevelsC[pedlev],cond)
+    }
+  }
+
+allpreddB <- 20*log10(allpred)
+rms <- sqrt(mean((allpreddB - datatofit)^2))
+if (is.na(rms)){rms <- 999}
+return(rms)}
+
+extract_polygons <- function(alpha_obj){
+  if(class(alpha_obj) != "ashape") stop("extract_polygons requires an ashape")
+  edge.df <- as.data.frame(alpha_obj$edges)
+  groups <- ns <- xs <- ys <- numeric(nrow(edge.df))
+  m <- cbind(edge.df[[1]], edge.df[[2]])
+  group <- 1
+  repeat {
+    i <- which(groups == 0)[1]
+    if (length(i) == 0 | is.na(i)) break()
+    j <- n <- 1
+    repeat {
+      groups[i] <- group
+      ns[i] <- n
+      if(j == 1) xs[i] <- edge.df$x1[i] else xs[i] <- edge.df$x2[i]
+      if(j == 1) ys[i] <- edge.df$y1[i] else ys[i] <- edge.df$y2[i]
+      next_ind <- which((m[, j] == m[i, j] | m[, (j %% 2 + 1)] == m[i, j]) & groups == 0)
+      if (length(next_ind) == 0) break()
+      j <- which(m[next_ind,] == m[i, j]) %% 2 + 1
+      i <- next_ind
+      n <- n + 1
+    }
+    group <- group + 1
+  }
+  data.frame(x = xs, y = ys, group = as.factor(groups))[order(groups, ns), ]
+}
 
@@
 allthresh[subj,expt,cond,pedlevel] <- res$Fit[1]
-allslope[subj,expt,cond,pedlevel] <- res$Fit[2]/C
+allslope[subj,expt,cond,pedlevel] <- 10.3/(res$Fit[2]/C)
 }
@@
 meanthresh <- apply(allthresh,2:4,mean)
-meanslope <- apply(allslope,2:4,mean)
+meanslope <- 10^apply(log10(allslope),2:4,mean)
 
@@
   MCSthresh[subj,cond] <- res$Fit[1]
-  MCSslope[subj,cond] <- res$Fit[2]/C
+  MCSslope[subj,cond] <- 10.3/(res$Fit[2]/C)
 
@@
 
-slopematrix[subj,1,] <- 10.3/MCSslope[subj,c(4,7,10)]
-slopematrix[subj,2,] <- 10.3/MCSslope[subj,c(5,8,11)]
-slopematrix[subj,3,] <- 10.3/MCSslope[subj,c(6,9,12)]
-}
-detslopes <- 10.3/MCSslope[,1:3]
-
-save(file='local/MCSdata.RData',list=c('MCSthresh','MCSslope','thdelev','slopematrix','detslopes','MCSpropcorr','contrastsdB'))
+slopematrix[subj,1,] <- MCSslope[subj,c(4,7,10)]
+slopematrix[subj,2,] <- MCSslope[subj,c(5,8,11)]
+slopematrix[subj,3,] <- MCSslope[subj,c(6,9,12)]
+}
+detslopes <- MCSslope[,1:3]
+
+options$stepN <- as.integer(c(postsampleres,postsampleres,20,20,20))
+allposteriors <- array(0,dim=c(12,postsampleres,postsampleres))
+allposX <- array(0,dim=c(12,postsampleres))
+allposY <- array(0,dim=c(12,postsampleres))
+
+# now also pool across subjects and fit for plotting the full posterior
+for (cond in 1:12){
+  datatofit <- data.frame(contrastsdB[1,cond,],colSums(ncorrect[,cond,]),colSums(ntrials[,cond,]))
+  colnames(datatofit) <- c('CdB','Ncorrect','Ntrials')
+  res <- ps$psignifit(as.matrix(datatofit),options)
+
+  xycos <- res$X1D
+  a <- res$Posterior
+  sumpos <- apply(a,c(1,2),sum)
+
+  allposteriors[cond,,] <- sumpos
+  allposX[cond,] <- xycos[[1]]
+  allposY[cond,] <- xycos[[2]]
+
+}
+
+save(file='local/MCSdata.RData',list=c('MCSthresh','MCSslope','thdelev','slopematrix','detslopes','MCSpropcorr','contrastsdB','allposteriors','allposX','allposY'))
 
@@
 
-getmodelresp <- function(p,L,R){
-  Lresp <- (L^p[3])/(p[4] + L + p[6]*R)
-  Rresp <- (R^p[3])/(p[4] + R + p[6]*L)
-  bs <- Lresp + Rresp
-  resp <- (bs^p[1])/(p[5] + bs^p[2])
-return(resp)}
-
-discriminate <- function(p,pedC,cond) {
-
-  if (cond==1){baseline <- getmodelresp(p,pedC,0)}
-  if (cond==2){baseline <- getmodelresp(p,pedC,pedC)}
-  if (cond==3){baseline <- getmodelresp(p,pedC,pedC)}
-  if (cond==4){baseline <- getmodelresp(p,pedC,0)}
-
-  modelresp <- -10
-  contrastinc <- 0
-  if (baseline>-999){
-
-    while (((modelresp-baseline) < p[7])){
-      contrastinc <- contrastinc + 0.1
-  if (cond==1){modelresp <- getmodelresp(p,pedC+contrastinc,0)}
-  if (cond==2){modelresp <- getmodelresp(p,pedC+contrastinc,pedC+contrastinc)}
-  if (cond==3){modelresp <- getmodelresp(p,pedC+contrastinc,pedC)}
-  if (cond==4){modelresp <- getmodelresp(p,pedC,contrastinc)}
-    }
-    while (((modelresp-baseline) > p[7])){
-      contrastinc <- contrastinc - 0.001
-  if (cond==1){modelresp <- getmodelresp(p,pedC+contrastinc,0)}
-  if (cond==2){modelresp <- getmodelresp(p,pedC+contrastinc,pedC+contrastinc)}
-  if (cond==3){modelresp <- getmodelresp(p,pedC+contrastinc,pedC)}
-  if (cond==4){modelresp <- getmodelresp(p,pedC,contrastinc)}
-    }    
-    }
-  else{contrastinc <- 99}
-return(contrastinc) }
-
-errorfit <- function(p){
-
-p <- 10^p
-p[2] <- p[2] + 1
-p[2] <- min(p[2],10)
-p[1] <- 1 + p[1] + p[2]
-p[3] <- 1 + p[3]
-
-pedlevelsC <- 10^(pedlist/20)
-pedlevelsC[1] <- 0
-allpred <- array(0,dim=c(4,length(pedlist)))
-
-  for (cond in 1:4){
-    for (pedlev in 1:length(pedlist)){
-      allpred[cond,pedlev] <- discriminate(p,pedlevelsC[pedlev],cond)
-    }
-  }
-
-allpreddB <- 20*log10(allpred)
-rms <- sqrt(mean((allpreddB - datatofit)^2))
-if (is.na(rms)){rms <- 999}
-return(rms)}
-
 if (processdata==2){
 
-ntotalsimplexfits <- 100
-
-cluster <- makeCluster(8)
+cluster <- makeCluster(ncores)
 registerDoParallel(cluster)
@@
 
+load('local/thresholddata.RData')
+
 if (processdata>0){
@@
 title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='Achromatic')
+title(main='(a) Achromatic',cex.main=2)
 
@@
 title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='Red/Green')
+title(main='(b) Red/Green',cex.main=2)
 
@@
 title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='Blue/Yellow')
+title(main='(c) Blue/Yellow',cex.main=2)
 
@@
 
+summation <- meanthresh[,1,1] - meanthresh[,2,1]
+
 ```
@@
 numSavedSteps <- nsamples    # total number of MCMC steps
-  adaptSteps = 200  # Number of steps to "tune" the samplers
-  burnInSteps = 200 
-  thinSteps <- 1
-  nChains = 24
-  options(mc.cores=8)
+options(mc.cores=ncores)
 
@@
   data {
-    int<lower=1> Nsubj ;
+    int<lower=1> Ndatasets ;
     int<lower=1> Ntotal ;
-    int correct[Ntotal] ;
+    int ncorrect[Ntotal] ;
+    int ntrials[Ntotal] ;
     real PedestalContrast[Ntotal] ;
@@
   parameters {
-    real<lower=0> p[Nsubj] ;
-    real<lower=0> q[Nsubj] ;    
-    real<lower=0> m[Nsubj] ;
-    real<lower=0> S[Nsubj] ;  
-    real<lower=0> Z[Nsubj] ;
-    real<lower=0> w[Nsubj] ;
-    real<lower=0> k[Nsubj] ;
+    real<lower=0> p[Ndatasets];
+    real<lower=0> q[Ndatasets];    
+    real<lower=0> m[Ndatasets];
+    real<lower=0> S[Ndatasets];  
+    real<lower=0> Z[Ndatasets];
+    real<lower=0> w[Ndatasets];
+    real<lower=0> k[Ndatasets];
 
@@
     real nullresp ;
+    real dprime ;
 
@@
     nullresp = pow((Ln + Rn), (p[s[i]]+q[s[i]])) / (Z[s[i]] + pow((Ln + Rn), q[s[i]])) ;
-    correct[i] ~ bernoulli((1 + erf((targresp - nullresp)/k[s[i]]))/2) ;
+
+    dprime = (targresp-nullresp)/k[s[i]] ;
+
+    ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;
 
@@
 ex1data <- read.csv('local/Experiment1.csv')
+ex1data$Condition <- ceiling(ex1data$Condition/2)
+
+sublist <- unique(ex1data$Subject)
 explist <- unique(ex1data$Experiment)
-
-for (mod in 1:1){
-  expdata <- subset(ex1data,Experiment==explist[mod])
-  expdata$Participant <- as.numeric(gsub('\\D','',expdata$Subject))
-  expdata$Condition <- ceiling(expdata$Condition/2)
-
-  dataList = list(correct = expdata$IsCorrect, PedestalContrast = expdata$PedestalContrast, TargetContrast = expdata$TargetContrast, c = expdata$Condition, s = expdata$Participant, Nsubj = max(expdata$Participant), Ntotal = nrow(expdata))
+counter <- 0
+datasetcounter <- 0
+ntrials <- NULL
+ncorrect <- NULL
+subjects <- NULL
+experiments <- NULL
+datasets <- NULL
+conditions <- NULL
+pedestals <- NULL
+targets <- NULL
+
+for (s in 1:3){
+  for (e in 1:3){
+    datasetcounter <- datasetcounter + 1
+    for (cond in 1:4){
+      thisdipper <- subset(ex1data,Subject==sublist[s] & Experiment==explist[e] & Condition==cond)
+
+      pedconts <- sort(unique(thisdipper$PedestalContrast))
+
+      for (p in 1:length(pedconts)){
+        thisthresh <- subset(thisdipper,PedestalContrast==pedconts[p])
+        targconts <- sort(unique(thisthresh$TargetContrast))
+        for (t in 1:length(targconts)){
+          counter <- counter + 1
+          thislevel <- subset(thisthresh,TargetContrast==targconts[t])
+          ntrials[counter] <- nrow(thislevel)
+          ncorrect[counter] <- sum(thislevel$IsCorrect)
+          subjects[counter] <- s
+          experiments[counter] <- e
+          datasets[counter] <- datasetcounter
+          conditions[counter] <- cond
+          pedestals[counter] <- pedconts[p]
+          targets[counter] <- targconts[t]
+        }
+      }
+    }
+  }
+}
+
+expdata <- data.frame(datasets,experiments,conditions,pedestals,targets,ntrials,ncorrect)
+
+dataList = list(ncorrect = expdata$ncorrect, ntrials = expdata$ntrials, PedestalContrast = expdata$pedestals, TargetContrast = expdata$targets, c = expdata$conditions, s = expdata$datasets, Ndatasets = max(expdata$datasets), Ntotal = nrow(expdata))
 
@@
                       chains = nChains,
-                        iter = (ceiling(numSavedSteps/nChains)*thinSteps
-                                +burnInSteps), 
+                      iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                       warmup = burnInSteps, 
@@
 
-    # convert stan format to coda format:jkn9
-    mcmcCoda2 = mcmc.list(lapply( 1:ncol(stanFit), function(x){mcmc(as.array(stanFit)[,x,])}))
-
-    save(file=paste0('local/E1mod',mod,'.RData'),list=c('stanFit','mcmcCoda2'))
-
-}
-
-}
-
-```
-
-```{r plotdata, include=FALSE}
-
-load('local/thresholddata.RData')
+  save(file=paste0('local/FullMod.RData'),list=c('stanFit'))
+
+}
+
+```
+
+```{r plotstanmodels, include=FALSE}
 
@@
 
-  paramorder <- c('p','q','m','S','Z','w','k')
-  allsamples <- array(0,dim=c(3,7,10008))
-  for (expt in 1:3){
-    load(file=paste0('local/E1mod',expt,'.RData'))
-    p <- NULL
-    q <- NULL
-    m <- NULL
-    S <- NULL
-    Z <- NULL
-    w <- NULL
-    k <- NULL
-    for (i in 1:length(mcmcCoda2)){
-      p <- c(p,mcmcCoda2[[i]][,23])  
-      q <- c(q,mcmcCoda2[[i]][,24])  
-      m <- c(m,mcmcCoda2[[i]][,25])  
-      S <- c(S,mcmcCoda2[[i]][,26])  
-      Z <- c(Z,mcmcCoda2[[i]][,27])  
-      w <- c(w,mcmcCoda2[[i]][,28])  
-      k <- c(k,mcmcCoda2[[i]][,29])  
-    }        
-    p <- p + q
-allsamples[expt,1,] <- p
-allsamples[expt,2,] <- q
-allsamples[expt,3,] <- m
-allsamples[expt,4,] <- S
-allsamples[expt,5,] <- Z
-allsamples[expt,6,] <- w
-allsamples[expt,7,] <- k
-
-  }
-# meanparams <- 10^apply(log10(allsamples),1:2,mlv,method='meanshift')
-meanparams <- 10^apply(log10(allsamples),1:2,mean)
-# meanparams[2:3,5] <- meanparams[2:3,5]*100
-
-pdf('Figures/modelparams.pdf',width=12,height=8)
+  load(file=paste0('local/FullMod.RData'))
+
+  draws <- extract(stanFit)
+
+  p <- map_estimate(draws$pmu+draws$qmu)
+  q <- map_estimate(draws$qmu)
+  m <- map_estimate(draws$mmu)
+  k <- map_estimate(draws$kmu)
+  S <- map_estimate(draws$Smu)
+  Z <- map_estimate(draws$Zmu)
+  w <- map_estimate(draws$wmu)
+  paramvect <- c(p,q,m,S,Z,w,k)
+
+  plist <- draws$pmu+draws$qmu
+  qlist <- draws$qmu
+  mlist <- draws$mmu
+  klist <- draws$kmu
+  Slist <- draws$Smu
+  Zlist <- draws$Zmu
+  wlist <- draws$wmu
+
+  allsamples <- array(0,dim=c(7,length(plist)))
+    allsamples[1,] <- plist
+    allsamples[2,] <- qlist
+    allsamples[3,] <- mlist
+    allsamples[4,] <- Slist
+    allsamples[5,] <- Zlist
+    allsamples[6,] <- wlist
+    allsamples[7,] <- klist
+
+pdf('Figures/stanoutput.pdf',width=8,height=8)
+
+layout(matrix(c(1,2,3,4,8,8,8,5,8,8,8,6,8,8,8,7),4,4,byrow=TRUE))
+par(mar=c(3,2,1,1))
 
@@
 
-par(pty="s",mfcol=c(2,4))
-
-ticklocsx <- seq(-18,18,6)
-ticklabelsx <- c('1/8','1/4','1/2',1,2,4,8)
+ticklocsx <- seq(-18,24,6)
+ticklabelsx <- c('1/8','1/4','1/2',1,2,4,8,16)
 ticklocsy <- seq(0,1,0.2)
 ticklabelsy <- ticklocsy
+paramorder <- c('p','q','m','w','S','Z','k')
+paramvalorder <- c(1,2,3,6,4,5,7)
 
@@
 
-  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,18), ylim=c(0,1))  
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,24), ylim=c(0,1))
   axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  # axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
   mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+  # mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
   title(xlab=paramorder[param], col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
 
-  for (expt in 1:3){
-
-    svals <- 20*log10(allsamples[expt,param,])
+    svals <- 20*log10(allsamples[paramvalorder[param],])
     a <- density(svals)
     a$y <- a$y/max(a$y)
-    lines(a$x,a$y,col=collist[expt])
-
-    lines(20*log10(meanparams[expt,c(param,param)]),c(0,1),col=collist[expt])
-  }
-
-}
-
-dev.off()
+    # lines(a$x,a$y,col=collist[expt])
+polygon(a$x,a$y,border=NA,col='grey')
+
+}
 
@@
 pedlevelsC[1] <- 0
-allpred <- array(0,dim=c(3,4,length(pedlist)))
-
-for (expt in 1:3){
+allpred <- array(0,dim=c(4,length(pedlist)))
+
   for (cond in 1:4){
     for (pedlev in 1:length(pedlist)){
-      allpred[expt,cond,pedlev] <- discriminate(meanparams[expt,],pedlevelsC[pedlev],cond)
-    }
-  }
-}
+      allpred[cond,pedlev] <- discriminate(paramvect,pedlevelsC[pedlev],cond)
+    }
+  }
+
 allpreddB <- 20*log10(allpred)
 
-pdf('Figures/dippers.pdf',width=12,height=5)
+par(mar=c(5,4,2,2))
 
@@
 
-par(pty="s",mfcol=c(1,3))  # make axis square
 plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))
@@
 title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='Achromatic')
 
@@
 for (cond in 1:4){
-  arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]+SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
- arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]-SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
-  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
-  lines(pedlist,allpreddB[1,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,meanthresh[1,cond,],pch=16,col=collist[cond],cex=1.5)
+  lines(pedlist,allpreddB[cond,],col=collist[cond],lwd=2)
 }
@@
 
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))  
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)    
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='Red/Green')
-
-pedcontrasts <- c(-12,seq(0,36,6))
-
-for (cond in 1:4){
-  arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]+SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
- arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]-SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
- # lines(pedcontrasts,meanthresh[3,cond,],col=collist[cond],lwd=2)
-  lines(pedlist,allpreddB[3,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,meanthresh[3,cond,],pch=16,col=collist[cond],cex=1.5)
-}
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='Blue/Yellow')
-
-for (cond in 1:4){
-  arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]+SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
- arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]-SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
- # lines(pedcontrasts,meanthresh[2,cond,],col=collist[cond],lwd=2)
-  lines(pedlist,allpreddB[2,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,meanthresh[2,cond,],pch=16,col=collist[cond],cex=1.5)
-}
-
 dev.off()
-
-}
-
-summation <- meanthresh[,1,1] - meanthresh[,2,1]
+}
 
@@
 
+  dev.off()
 }
@@
 load('local/MCSdata.RData')
-slopematrix <- 10^(apply(log10(slopematrix),c(2,3),mean))
-slopematrix <- round(slopematrix,digits=2)
+meanslopesMCS <- 10^(apply(log10(slopematrix),c(2,3),mean))
+meanslopesMCS <- round(meanslopesMCS,digits=2)
 
@@
 
-titlelist <- c('(a) Achromatic target','(b) R/G target','(c) B/Y target','(d) Threshold elevation','(e) Psychometric slope')
-
-    pdf(paste0('Figures/MCSdata.pdf'),width=12,height=8)
-
-    layout(matrix(c(1,1,2,2,3,3,0,4,4,5,5,0),2,6,byrow=TRUE))
+titlelist <- c('(a) Achromatic target','(b) R/G target','(c) B/Y target','(d) Achromatic densities','(e) R/G densities','(f) B/Y densities','(g) Threshold elevation','(h) Psychometric slope')
+
+    pdf(paste0('Figures/MCSdata.pdf'),width=12,height=12)
+
+    layout(matrix(c(1,1,2,2,3,3,4,4,5,5,6,6,0,7,7,8,8,0),3,6,byrow=TRUE))
 
@@
 
+  }
+
+outlinecolours <- c('black','black','red','cornflowerblue')
+shadingcolours <- c('black','white','green','gold')
+
+ticklocsx <- seq(-12,42,6)
+ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64','128')
+ticklocsy <- seq(0,24,6)
+ticklabelsy <- c('1','2','4','8','16')
+
+thd <- 0.28
+
+for (cond in 1:3){
+
+    par(pty="s")  
+ plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,42), ylim=c(0,24))
+
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+  title(main=titlelist[cond+3],cex.main=2)
+
+for (block in 1:4){
+condtoplot <- cond + ((block-1)*3)
+
+xvals <- allposX[condtoplot,]
+yvals <- 10.3/(allposY[condtoplot,ncol(allposY):1]/C)
+zvals <- allposteriors[condtoplot,,ncol(allposY):1]
+
+binz <- zvals/max(zvals)
+iind <- which(binz>thd,arr.ind=TRUE)
+
+xy <- matrix(0,nrow=nrow(iind),ncol=2)
+xy[,1] <- xvals[iind[,1]]
+xy[,2] <- yvals[iind[,2]]
+hullobj <- ashape(xy,alpha=1)
+polys <- extract_polygons(hullobj)
+polygon(polys$x,20*log10(polys$y),col=shadingcolours[block],border=NA)
+lines(polys$x[c(1:nrow(polys),1)],20*log10(polys$y[c(1:nrow(polys),1)]),lwd=2,col=outlinecolours[block])
+}
+
+for (block in 1:4){
+condtoplot <- cond + ((block-1)*3)
+points(MCSthresh[,condtoplot],20*log10(MCSslope[,condtoplot]),pch=21,col=outlinecolours[block],bg=shadingcolours[block])
+}
 }
@@
 title(ylab="Mask", col.lab=rgb(0,0,0), line=2.5, cex.lab=1.5)
-title(main=titlelist[4],cex.main=2)
+title(main=titlelist[7],cex.main=2)
 
@@
 title(ylab="Mask", col.lab=rgb(0,0,0), line=2.5, cex.lab=1.5)
-title(main=titlelist[5],cex.main=2)
+title(main=titlelist[8],cex.main=2)
 
@@
 colmatrix2 <- rgb(ramp2(seq(0, 1, length = 101)), max = 255)
-image(1:3,1:3,slopematrix,zlim=c(0,8),col=colmatrix2,add=TRUE,useRaster=FALSE)
+image(1:3,1:3,meanslopesMCS,zlim=c(0,8),col=colmatrix2,add=TRUE,useRaster=FALSE)
 
@@
   for (y in 1:3){
-    text(x,y,slopematrix[x,y],cex=1.6)
+    text(x,y,meanslopesMCS[x,y],cex=1.6)
   }
@@
 load('local/MCSdata.RData')
-slopematrix <- 10^(apply(log10(slopematrix),c(2,3),mean))
-slopematrix <- round(slopematrix,digits=2)
+meanslopesMCS <- 10^(apply(log10(slopematrix),c(2,3),mean))
+meanslopesMCS <- round(meanslopesMCS,digits=2)
 contrastsdB <- contrastsdB[1,,]
@@
   }}
+
+dev.off()
 
@@
 
-Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate full posterior distributions for threshold and slope parameters via a Bayesian numerical integration method [@Schutt2016], fitting a cumulative Gaussian.
-We also implemented a Bayesian hierarchical version of the two stage model of @Meese2006 using the Stan language [@Carpenter2017].
-This used a binomial generator function to model the proportion correct data at each target level, and was fit separately to each chromatic condition of Experiment 1, and the data of Experiment 3 (i.e.
-4 model fits in total).
-The modelling primarily focuses on comparing posterior parameter distributions across conditions and experiments, rather than a model comparison approach.
-We generated over 1 million posterior samples for each model, and retained 10\% of them for plotting.
+Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate threshold and slope parameters via a Bayesian numerical integration method [@Schutt2016].
+A cumulative Gaussian was used as the underlying function, and we converted the slope estimates ($\sigma$ parameters from the fitted Gaussians) to equivalent Weibull $\beta$ values using the approximation $\beta = 10.3/\sigma$.
+
+The two stage model of @Meese2006 was fit to the threshold data from Experiments 1 and 3 using a simplex algorithm to minimise the error between the model and data.
+The model is defined by a series of equations:
+
+$Stage1_L = \frac{C_L^m}{S + C_L + \omega C_R}$
+
+$Stage1_R = \frac{C_L^m}{S + C_R + \omega C_L}$
+
+$binsum = Stage1_L + Stage1_R$
+
+$binresp = \frac{binsum^p}{Z + binsum^q}$
+
+where $C_L$ and $C_R$ are the contrasts displayed to the left and right eyes, and $m$, $S$, $\omega$, $p$, $q$ and $Z$ are free parameters in the model.
+A further free parameter, $k$, represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values.
+Thresholds are defined when the following equality is satisfied:
+
+$binresp_{target+pedestal} - binresp_{pedestal} = k$
+
+and d-prime is defined as:
+
+$d' = \frac{binresp_{target+pedestal} - binresp_{pedestal}}{k}$.
+
+We also implemented a Bayesian hierarchical version of the model using the Stan language [@Carpenter2017].
+This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants and each chromatic condition of Experiment 1.
+This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
+We generated over 1 million posterior samples for the model, and retained 10\% of them for plotting.
 
@@
 Error bars show ±1SE across participants.
-Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).", fig.align="center", echo=FALSE}
+Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).
+Curves show...", fig.align="center", echo=FALSE}
 
@@
 
-Modelling
-
-```{r params, fig.cap="Model parameters", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/modelparams.pdf')
+For consistency with previous work, we initially performed least-squares fits of the two-stage model [@Meese2006] for each of the chromaticity experiments (7 free parameters per fit).
+The best model fits are shown in Figure \@ref(fig:dipperfig), and provide an excellent description of the data, with RMS errors between 1.37 and 1.59dB.
+We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
+This model was fit simultaneously to the full trial-by-trial data from all participants and chromaticity experiments.
+Figure \@ref(fig:bayesianmodel)a summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
+Figure \@ref(fig:bayesianmodel)b-h shows posterior distributions for each model parameter.
+Note in particular that the weight of interocular suppression overlaps 1 for each chromaticity experiment, consistent with the strong dichoptic masking observed in the threshold data.
+
+```{r bayesianmodel, fig.cap="Model parameters", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/stanoutput.pdf')
 
@@
 All conditions produced monotonically increasing psychometric functions (panels a-c), but the extent of masking was highly dependent on the relationship between the target and mask chromaticity.
+Figure \@ref(fig:MCSfig)d-f shows a two-dimensional representation of individual threshold and slope estimates (points), as well as the posterior density estimates for fits to the pooled data (ellipses).
 
@@
 Panels (a-c) show psychometric functions for each condition, pooled across participants (600 trials per target contrast level).
-Panel (d) shows the average threshold elevation factor for each combination of target and mask stimulus.
-Panel (e) shows the geometric mean psychometric slope value for each masking condition in Weibull beta units.", fig.align="center", echo=FALSE}
+Panels (d-f) show threshold and slope estimates for individual participants (points) and the boundary of the posterior density estimates for fits to the pooled data (ellipses).
+Panel (g) shows the average threshold elevation factor for each combination of target and mask stimulus.
+Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull beta units.", fig.align="center", echo=FALSE}
 
@@
 Finally there was an intermediate level of masking between red/green and blue/yellow stimuli.
-This is summarised in Figure \@ref(fig:MCSfig)d, which represents threshold elevation for each combination of target and mask chromaticity.
+This is summarised in Figure \@ref(fig:MCSfig)g, which represents threshold elevation for each combination of target and mask chromaticity.
 Note that the positive diagonal exhibits the highest values, and represents threshold elevation between targets and masks of the same chromaticity.
@@
 In the absence of a mask, the average slope was $\beta$ = `r round(10^(mean(log10(detslopes))),digits=2)`, which is typical for contrast detection tasks.
-Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average $\beta$ = `r round(10^(mean(log10(c(slopematrix[1,1],slopematrix[2,2],slopematrix[3,3])))),digits=2)`).
-These 'super-steep' psychometric functions for dichoptic pedestal masking have been reported previously [@Meese2006; @Baker2013], and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \@ref(fig:MCSfig)e).
-However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average $\beta$ = `r round(10^(mean(log10(c(slopematrix[1,2],slopematrix[1,3],slopematrix[2,1],slopematrix[2,3],slopematrix[3,1],slopematrix[3,2])))),digits=2)` for the off-diagonal values).
+Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,1],meanslopesMCS[2,2],meanslopesMCS[3,3])))),digits=2)`).
+These 'super-steep' psychometric functions for dichoptic pedestal masking have been reported previously [@Meese2006; @Baker2013], and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \@ref(fig:MCSfig)h).
+However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,2],meanslopesMCS[1,3],meanslopesMCS[2,1],meanslopesMCS[2,3],meanslopesMCS[3,1],meanslopesMCS[3,2])))),digits=2)` for the off-diagonal values).
 

### 2024-03-10 manuscript.tex
Various updates and improvements

@@
 Rowan J. Huxley, Joel T. Martin, Maya Rockman \& Alex R. Wade}
-\date{2024-03-09}
+\date{Department of Psychology, University of York}
 
@@
 
-Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate full posterior distributions for threshold and slope parameters via a Bayesian numerical integration method (Schütt et al., 2016), fitting a cumulative Gaussian.
-We also implemented a Bayesian hierarchical version of the two stage model of Meese et al.
-(2006) using the Stan language (Carpenter et al., 2017).
-This used a binomial generator function to model the proportion correct data at each target level, and was fit separately to each chromatic condition of Experiment 1, and the data of Experiment 3 (i.e.~4 model fits in total).
-The modelling primarily focuses on comparing posterior parameter distributions across conditions and experiments, rather than a model comparison approach.
-We generated over 1 million posterior samples for each model, and retained 10\% of them for plotting.
+Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate threshold and slope parameters via a Bayesian numerical integration method (Schütt et al., 2016).
+A cumulative Gaussian was used as the underlying function, and we converted the slope estimates (\(\sigma\) parameters from the fitted Gaussians) to equivalent Weibull \(\beta\) values using the approximation \(\beta = 10.3/\sigma\).
+
+The two stage model of Meese et al.
+(2006) was fit to the threshold data from Experiments 1 and 3 using a simplex algorithm to minimise the error between the model and data.
+The model is defined by a series of equations:
+
+\(Stage1_L = \frac{C_L^m}{S + C_L + \omega C_R}\)
+
+\(Stage1_R = \frac{C_L^m}{S + C_R + \omega C_L}\)
+
+\(binsum = Stage1_L + Stage1_R\)
+
+\(binresp = \frac{binsum^p}{Z + binsum^q}\)
+
+where \(C_L\) and \(C_R\) are the contrasts displayed to the left and right eyes, and \(m\), \(S\), \(\omega\), \(p\), \(q\) and \(Z\) are free parameters in the model.
+A further free parameter, \(k\), represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values.
+Thresholds are defined when the following equality is satisfied:
+
+\(binresp_{target+pedestal} - binresp_{pedestal} = k\)
+
+and d-prime is defined as:
+
+\(d' = \frac{binresp_{target+pedestal} - binresp_{pedestal}}{k}\).
+
+We also implemented a Bayesian hierarchical version of the model using the Stan language (Carpenter et al., 2017).
+This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants and each chromatic condition of Experiment 1.
+This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
+We generated over 1 million posterior samples for the model, and retained 10\% of them for plotting.
 
@@
 Error bars show ±1SE across participants.
-Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).}\label{fig:dipperfig}
+Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).
+Curves show...}\label{fig:dipperfig}
 \end{figure}
@@
 
-Modelling
+For consistency with previous work, we initially performed least-squares fits of the two-stage model (Meese et al., 2006) for each of the chromaticity experiments (7 free parameters per fit).
+The best model fits are shown in Figure \ref{fig:dipperfig}, and provide an excellent description of the data, with RMS errors between 1.37 and 1.59dB.
+We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
+This model was fit simultaneously to the full trial-by-trial data from all participants and chromaticity experiments.
+Figure \ref{fig:bayesianmodel}a summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
+Figure \ref{fig:bayesianmodel}b-h shows posterior distributions for each model parameter.
+Note in particular that the weight of interocular suppression overlaps 1 for each chromaticity experiment, consistent with the strong dichoptic masking observed in the threshold data.
 
@@
 
-{\centering \includegraphics{Figures/modelparams}
+{\centering \includegraphics{Figures/stanoutput}
 
@@
 
-\caption{Model parameters}\label{fig:params}
+\caption{Model parameters}\label{fig:bayesianmodel}
 \end{figure}
@@
 All conditions produced monotonically increasing psychometric functions (panels a-c), but the extent of masking was highly dependent on the relationship between the target and mask chromaticity.
+Figure \ref{fig:MCSfig}d-f shows a two-dimensional representation of individual threshold and slope estimates (points), as well as the posterior density estimates for fits to the pooled data (ellipses).
 
@@
 Panels (a-c) show psychometric functions for each condition, pooled across participants (600 trials per target contrast level).
-Panel (d) shows the average threshold elevation factor for each combination of target and mask stimulus.
-Panel (e) shows the geometric mean psychometric slope value for each masking condition in Weibull beta units.}\label{fig:MCSfig}
+Panels (d-f) show threshold and slope estimates for individual participants (points) and the boundary of the posterior density estimates for fits to the pooled data (ellipses).
+Panel (g) shows the average threshold elevation factor for each combination of target and mask stimulus.
+Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull beta units.}\label{fig:MCSfig}
 \end{figure}
@@
 Finally there was an intermediate level of masking between red/green and blue/yellow stimuli.
-This is summarised in Figure \ref{fig:MCSfig}d, which represents threshold elevation for each combination of target and mask chromaticity.
+This is summarised in Figure \ref{fig:MCSfig}g, which represents threshold elevation for each combination of target and mask chromaticity.
 Note that the positive diagonal exhibits the highest values, and represents threshold elevation between targets and masks of the same chromaticity.
@@
 Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average \(\beta\) = 5.38).
-These `super-steep' psychometric functions for dichoptic pedestal masking have been reported previously (Baker et al., 2013; Meese et al., 2006), and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \ref{fig:MCSfig}e).
+These `super-steep' psychometric functions for dichoptic pedestal masking have been reported previously (Baker et al., 2013; Meese et al., 2006), and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \ref{fig:MCSfig}h).
 However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average \(\beta\) = 2.83 for the off-diagonal values).

### 2024-03-24 manuscript.Rmd
Fixed Stan model!

@@
 
-processdata <- 2
+processdata <- 0
 # the processdata flag has three settings:
@@
 # 1: fit psychometric functions and plot graphs
-# 2: do Stan modelling (takes N hours)
+# 2: do Stan modelling and simplex fitting (takes several hours, simplex sometimes gets stuck!)
 
@@
 ncores <- 8    # number of processor cores to use on the host machine
-postsampleres <- 400    # resolution of psignifit posterior sampling
+postsampleres <- 200    # resolution of psignifit posterior sampling
 
 # other Stan settings
-adaptSteps = 5000  # Number of steps to "tune" the samplers
-burnInSteps = 5000
+burnInSteps <- 5000   # Number of steps to "tune" the samplers
 thinSteps <- 10
-nChains = 64
+nChains <- 8
 
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','doParallel','R.matlab','bayestestR','alphahull') # list of CRAN packages
+packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','parallel','doParallel','R.matlab','bayestestR','alphahull','kableExtra') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 
-# helper function to make colours transparent
+# ncores <- parallel::detectCores()  # auto-detect number of cores (optional)
+
+if (processdata>1){
+  use_miniconda('r-reticulate')
+  # install psignifit in the terminal with:
+  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
+  ps <- import('psignifit')
+  # calculate constant to scale the slope parameter to the Gaussian SD
+  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
+}
+
+knitr::opts_chunk$set(echo = TRUE)
+
+```
+
+```{r subfunctions, include=FALSE}
+
+# helper functions used throughout the manuscript
+
 addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}
@@
 p[2] <- p[2] + 1
-p[2] <- min(p[2],10)
+p[2] <- min(p[2],16)
 p[1] <- 1 + p[1] + p[2]
+p[1] <- min(p[1],20)
 p[3] <- 1 + p[3]
@@
 
-use_miniconda('r-reticulate')
-# install psignifit in the terminal with:
-# sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
-ps <- import('psignifit')
-
-# calculate constant to scale the slope parameter to the Gaussian SD
-C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
-
+mkgrating <- function(regionsize, f, o, p, c){
+# ported from the Matlab function, originally by Tim Meese
+# generates a single component sine wave grating using the following inputs:
+  # regionsize is the width of the stimulus
+  # f is spatial frequency in cycles per image
+  # o is orientation in degrees
+  # p is phase in degrees relative to the centre of the image
+  # c is contrast
+
+p <- p*(pi/180)   # convert phase from degrees to radians
+o <- o*(pi/180)   # convert orientation from degrees to radians
+f <- f/regionsize # scale frequency by image size
+x0 <- (regionsize+1)/2  # locate centre of image
+y0 <- x0
+
+u <- f * cos(o) * 2*pi
+v <- f * sin(o) * 2*pi
+
+gridout <- meshgrid(1:regionsize,1:regionsize)   # generate x and y coordinate systems, requires the pracma package
+xx <- gridout$X
+yy <- gridout$Y
+
+output <- matrix(0,nrow=regionsize,ncol=regionsize)
+output <- (c * sin(u * (xx-x0) + v*(yy-y0) + p))
+
+return(output)}
+
+make_soft_window <- function(W,H,D=0.9){
+  # Mark's function to make sine-wave gratings, ported from Matlab
+  # W is width (in pixels), H is height (in pixels)
+  # D is the diameter of the soft window at half height as a proportion of the width
+
+  radius <- min(W*D/2,H*D/2)     # radius in pixels
+  L <- 2*(min(W/2,H/2) - radius) # blur half-cycle
+  X1 <- seq(-L/2,L/2)
+
+  X <- (1:W) - (W/2)
+  Y <- (1:H) - (H/2)
+  xx <- matrix(rep(X,H),nrow=H,ncol=W,byrow=TRUE)
+  yy <- t(matrix(rep(Y,W),nrow=W,ncol=H,byrow=TRUE))
+
+  mask <- (xx^2 + yy^2)
+  mask[mask<=(radius^2)] <- 1
+  mask[mask>(radius^2)] <- 0
+
+  WinKernel <- cos(X1*pi/L)  # half-cycle cosine
+  convkernW <- (1:W)*0
+  convkernW[(1+(W/2)-length(X1)/2):((W/2)+length(X1)/2)] <- WinKernel
+  convkernH <- (1:H)*0
+  convkernH[(1+(H/2)-length(X1)/2):((H/2)+length(X1)/2)] <- WinKernel
+  cH <- t(apply(mask,2,convolve,convkernH))
+  cH <- cH[,c((1+H/2):H,1:(H/2))]
+  cW <- apply(mask,1,convolve,convkernW)
+  cW <- cW[c((1+W/2):W,1:(W/2)),]
+  mask <- cH * cW
+
+  mask <- mask/max(mask)
+
+  return(mask)}
+
+```
+
+```{r checkfordata, include=FALSE}
+
+# check for presence of essential data files and folders locally - download from OSF if missing
+
+if (!dir.exists('local')){dir.create('local')}
 if (!dir.exists('local/fits')){dir.create('local/fits')}
 
-knitr::opts_chunk$set(echo = TRUE)
+osfrepo <- '3vdga'
+
+if (!file.exists('local/Experiment1.csv')){}
+if (!file.exists('local/Experiment2.csv')){}
+if (!file.exists('local/Experiment3.csv')){}
+if (!file.exists('local/fundamentals.csv')){}
+if (!file.exists('local/isosettings.csv')){}
+if (!file.exists('local/phosphors.csv')){}
+
+if (processdata < 1){
+ if (!file.exists('local/thresholddata.RData')){}
+ if (!file.exists('local/thresholddataDisc.RData')){}
+ if (!file.exists('local/MCSdata.RData')){}
+}
+
+if (processdata < 2){
+ if (!file.exists('local/simplexfits.RData')){}
+ if (!file.exists('local/stanfit1.RData')){}
+ if (!file.exists('local/stanfit2.RData')){}
+ if (!file.exists('local/stanfit3.RData')){}
+ if (!file.exists('local/stanfit4.RData')){}
+}
+
+if (!file.exists('references.bib')){}
+if (!file.exists('journal-of-vision.csl')){}
 
@@
 ex2data <- read.csv('local/Experiment2.csv')
+ex3data <- read.csv('local/Experiment3.csv')
 
@@
 allthresh[subj,expt,cond,pedlevel] <- res$Fit[1]
-allslope[subj,expt,cond,pedlevel] <- 10.3/(res$Fit[2]/C)
+allslope[subj,expt,cond,pedlevel] <- 20*log10(10.3/(res$Fit[2]/C))
 }
@@
 meanthresh <- apply(allthresh,2:4,mean)
-meanslope <- 10^apply(log10(allslope),2:4,mean)
+meanslope <- apply(allslope,2:4,mean)
 
@@
   MCSthresh[subj,cond] <- res$Fit[1]
-  MCSslope[subj,cond] <- 10.3/(res$Fit[2]/C)
+  MCSslope[subj,cond] <- 20*log10(10.3/(res$Fit[2]/C))
 
@@
 
+sublist3 <- unique(ex3data$Subject)
+
+allthresh3 <- array(0,dim=c(length(sublist3),4,8))
+allslope3 <- array(0,dim=c(length(sublist3),4,8))
+for (subj in 1:length(sublist3)){
+  subdata <- subset(ex3data,Subject==sublist3[subj])
+for (cond in 1:4){
+  conddata <- subset(subdata,Condition==(2*cond)|Condition==((2*cond)-1))
+  pedlevs <- unique(conddata$PedestalContrast)
+for (pedlevel in 1:8){
+
+blockdata <- subset(conddata,PedestalContrast==pedlevs[pedlevel])
+
+if (nrow(blockdata)>0){
+targetcontrasts <- sort(unique(blockdata$TargetContrast))
+ntrials <- rep(0,length(targetcontrasts))
+ncorrect <- rep(0,length(targetcontrasts))
+for (lev in 1:length(targetcontrasts)){
+  temp <- subset(blockdata,TargetContrast==targetcontrasts[lev])
+  ntrials[lev] <- nrow(temp)
+  ncorrect[lev] <- sum(temp$IsCorrect)
+}
+
+tofit <- as.matrix(data.frame(20*log10(targetcontrasts),ncorrect,ntrials))
+
+res <- ps$psignifit(tofit,options)
+
+allthresh3[subj,cond,pedlevel] <- res$Fit[1]
+allslope3[subj,cond,pedlevel] <- 20*log10(10.3/(res$Fit[2]/C))
+}
+
+}}}
+
+# shift hbin and dich conditions up one
+allthresh3[,3,2:8] <- allthresh3[,3,1:7]
+allthresh3[,4,2:8] <- allthresh3[,4,1:7]
+allslope3[,3,2:8] <- allslope3[,3,1:7]
+allslope3[,4,2:8] <- allslope3[,4,1:7]
+# duplicate the mon threshold conditions for hbin and dich
+allthresh3[,3,1] <- allthresh3[,1,1]
+allthresh3[,4,1] <- allthresh3[,1,1]
+allslope3[,3,1] <- allslope3[,1,1]
+allslope3[,4,1] <- allslope3[,1,1]
+
+meanthresh3 <- apply(allthresh3,2:3,mean)
+meanslope3 <- apply(allslope3,2:3,mean)
+
+SEthresh3 <- apply(allthresh3,2:3,sd)/sqrt(length(sublist3))
+SEslope3 <- apply(allslope3,2:3,sd)/sqrt(length(sublist3))
+
+save(file='local/thresholddataDisc.RData',list=c('allthresh3','allslope3','meanthresh3','meanslope3','SEthresh3','SEslope3'))
+
 }
@@
 load('local/thresholddata.RData')
+load('local/thresholddataDisc.RData')
 
@@
 pedlist <<- seq(-12,30,6)
-allp <- matrix(0,nrow=3,ncol=7)
-allparams <- array(0,dim=c(3,ntotalsimplexfits,8))
+allp <- matrix(0,nrow=4,ncol=7)
+allparams <- array(0,dim=c(4,ntotalsimplexfits,8))
 allrms <- NULL
@@
    p[2] <- p[2] + 1
-   p[2] <- min(p[2],10)
+   p[2] <- min(p[2],16)
    p[1] <- 1 + p[1] + p[2]
+   p[1] <- min(p[1],20)
    p[3] <- 1 + p[3]
    allp[cond,] <- p
-   pedlist <<- seq(-6,36,6)
-
    allparams[cond,,] <- finalout
- }
+
+   pedlist <<- seq(-6,36,6)  # increase pedestal contrasts for the chromatic conditions
+
+ }
+
+# finally fit the disc data
+pedlist <<- seq(-12,30,6)
+cond <- 4
+
+   print(cond)
+   datatofit <<- meanthresh3
+
+   nfits <- ntotalsimplexfits
+   for (n in 1:ntotalsimplexfits){
+     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){nfits <- nfits-1}
+   }
+
+   if (nfits > 0){
+   foreach(i = 1:nfits, .combine=rbind) %dopar% {
+   sout <- pracma::nelder_mead(errorfit,rnorm(7,sd=0.1)+log10(c(0.5,5.5,0.3,1,0.01,1,0.2)))
+   allout <- c(errorfit(sout$xmin),sout$xmin)
+
+   hassaved <- 0
+   filecount <- 0
+   while (!hassaved){
+     filecount <- filecount + 1
+     if (!file.exists(paste0('local/fits/E',cond,'f',filecount,'.RData'))){
+       save(file=paste0('local/fits/E',cond,'f',filecount,'.RData'),list='allout')
+       hassaved <- 1}
+   }
+   allout <- c(errorfit(sout$xmin),sout$xmin)
+   }
+   }
+
+   finalout <- matrix(0,nrow=ntotalsimplexfits,ncol=8)
+   for (n in 1:ntotalsimplexfits){
+     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){
+       load(file=paste0('local/fits/E',cond,'f',n,'.RData'))
+       finalout[n,] <- allout
+     }
+   }
+   i <- which(finalout[,1]==min(finalout[,1]))
+   p <- 10^finalout[i[1],2:8]
+   allrms[cond] <- finalout[i[1],1]
+   p[2] <- p[2] + 1
+   p[2] <- min(p[2],16)
+   p[1] <- 1 + p[1] + p[2]
+   p[1] <- min(p[1],20)
+   p[3] <- 1 + p[3]
+   allp[cond,] <- p
+   allparams[cond,,] <- finalout
 
@@
 
-```{r plotmodellingsimplex, include=FALSE}
-
-load('local/thresholddata.RData')
+```{r plotdippers, include=FALSE}
 
@@
 pedlevelsC[1] <- 0
-allpred <- array(0,dim=c(3,4,length(pedlist)))
-
-for (expt in 1:3){
+allpred <- array(0,dim=c(4,4,length(pedlist)))
+
+for (expt in 1:4){
   for (cond in 1:4){
@@
 
-pdf('Figures/dipperssimplex.pdf',width=12,height=5)
+pdf('Figures/dipperssimplex.pdf',width=12,height=10)
 
@@
 ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
-
-par(pty="s",mfcol=c(1,3))  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='(a) Achromatic',cex.main=2)
-
 pedcontrasts <- seq(-12,30,6)
 
-for (cond in 1:4){
-  arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]+SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
- arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]-SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
-  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
-  lines(pedlist,allpreddB[1,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,meanthresh[1,cond,],pch=16,col=collist[cond],cex=1.5)
-}
-text(24,-9,paste0('RMS = ',round(allrms[1],digits=2),'dB'),cex=2)
-legend(-12,36,c('Monocular','Binocular','Half-bin','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
-
+exptorder <- c(1,3,2)
+paneltitles <- c('(a) Achromatic thresholds','(b) Red/Green thresholds','(c) Blue/Yellow thresholds')
+par(mfrow=c(2,3))
+for (expt in 1:3){
 par(pty="s")  # make axis square
@@
 title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='(b) Red/Green',cex.main=2)
-
-pedcontrasts <- c(-12,seq(0,36,6))
+title(main=paneltitles[expt],cex.main=2.5)
 
 for (cond in 1:4){
-  arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]+SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
- arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]-SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
- # lines(pedcontrasts,meanthresh[3,cond,],col=collist[cond],lwd=2)
-  lines(pedlist,allpreddB[3,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,meanthresh[3,cond,],pch=16,col=collist[cond],cex=1.5)
-}
-text(24,-9,paste0('RMS = ',round(allrms[2],digits=2),'dB'),cex=2)
+  arrows(pedcontrasts,meanthresh[exptorder[expt],cond,],pedcontrasts,meanthresh[exptorder[expt],cond,]+SEthresh[exptorder[expt],cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanthresh[exptorder[expt],cond,],pedcontrasts,meanthresh[exptorder[expt],cond,]-SEthresh[exptorder[expt],cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
+  lines(pedlist,allpreddB[exptorder[expt],cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanthresh[exptorder[expt],cond,],pch=16,col=collist[cond],cex=1.5)
+}
+text(24,-9,paste0('RMSE = ',round(allrms[expt],digits=2),'dB'),cex=2)
+if (expt==1){legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
+
+pedcontrasts <- c(-12,seq(0,36,6))  # update pedestal contrasts for plotting chromatic conditions
+
+}
+
+paneltitles <- c('(d) Achromatic slopes','(e) Red/Green slopes','(f) Blue/Yellow slopes')
+
+ticklocsy <- seq(-6,18,6)
+ticklabelsy <- c(0.5,1,2,4,8)
+
+for (expt in 1:3){
 
 par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-6,18))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main=paneltitles[expt],cex.main=2.5)
+
+for (cond in 1:4){
+  arrows(pedcontrasts,meanslope[expt,cond,],pedcontrasts,meanslope[expt,cond,]+SEslope[expt,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanslope[expt,cond,],pedcontrasts,meanslope[expt,cond,]-SEslope[expt,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+  lines(pedcontrasts,meanslope[expt,cond,],col=collist[cond],lwd=2)
+  # lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanslope[expt,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+
+}
+
+dev.off()
+
+pdf('Figures/discdata.pdf',width=13,height=7)
+
+par(mfcol=c(1,2))
+pedcontrasts <- seq(-12,30,6)
+
+ticklocsy <- seq(-18,30,6)
+ticklabelsy <- c(0.125,0.25,0.5,1,2,4,8,16,32)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-18,30))   
 axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
 title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='(c) Blue/Yellow',cex.main=2)
+title(main='(a) Flickering disc (thresholds)',cex.main=2)
 
 for (cond in 1:4){
-  arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]+SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
- arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]-SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
- # lines(pedcontrasts,meanthresh[2,cond,],col=collist[cond],lwd=2)
-  lines(pedlist,allpreddB[2,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,meanthresh[2,cond,],pch=16,col=collist[cond],cex=1.5)
-}
-text(24,-9,paste0('RMS = ',round(allrms[3],digits=2),'dB'),cex=2)
+  arrows(pedcontrasts,meanthresh3[cond,],pedcontrasts,meanthresh3[cond,]+SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanthresh3[cond,],pedcontrasts,meanthresh3[cond,]-SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
+  lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanthresh3[cond,],pch=16,col=collist[cond],cex=1.5)
+}
+text(24,-15,paste0('RMSE = ',round(allrms[4],digits=2),'dB'),cex=2)
+legend(-12,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
+
+ticklocsy <- seq(-6,18,6)
+ticklabelsy <- c(0.5,1,2,4,8)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-6,18))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main='(b) Flickering disc (slopes)',cex.main=2)
+
+for (cond in 1:4){
+  arrows(pedcontrasts,meanslope3[cond,],pedcontrasts,meanslope3[cond,]+SEslope3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+ arrows(pedcontrasts,meanslope3[cond,],pedcontrasts,meanslope3[cond,]-SEslope3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+  lines(pedcontrasts,meanslope3[cond,],col=collist[cond],lwd=2)
+  # lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,meanslope3[cond,],pch=16,col=collist[cond],cex=1.5)
+}
 
@@
 summation <- meanthresh[,1,1] - meanthresh[,2,1]
-
-```
-
-```{r domodelling, include=FALSE}
+summationDisc <- meanthresh3[1,1] - meanthresh3[2,1]
+
+```
+
+```{r domodellingstan, include=FALSE}
 
@@
   parameters {
-    real<lower=0> p[Ndatasets];
-    real<lower=0> q[Ndatasets];    
-    real<lower=0> m[Ndatasets];
-    real<lower=0> S[Ndatasets];  
-    real<lower=0> Z[Ndatasets];
-    real<lower=0> w[Ndatasets];
-    real<lower=0> k[Ndatasets];
+    vector<lower=0.1, upper=3>[Ndatasets] p;
+    vector<lower=2, upper=8>[Ndatasets] q;
+    vector<lower=1, upper=2>[Ndatasets] m;
+    vector<lower=0.001, upper=2>[Ndatasets] S;  
+    vector<lower=0.001, upper=1>[Ndatasets] Z;
+    vector<lower=0.001,upper=2>[Ndatasets] w;
+    vector<lower=0.001,upper=1>[Ndatasets] k;
 
     real<lower=0> sigma ;
-    real<lower=0> pmu ; 
-    real<lower=0> qmu ; 
-    real<lower=0> mmu ;
-    real<lower=0> Smu ;
-    real<lower=0> Zmu ; 
-    real<lower=0> wmu ; 
-    real<lower=0> kmu ;
+    real<lower=0.1> pmu ; 
+    real<lower=2> qmu ; 
+    real<lower=1> mmu ;
+    real<lower=0.001> Smu ;
+    real<lower=0.001, upper=1> Zmu ; 
+    real<lower=0.001> wmu ; 
+    real<lower=0.001> kmu ;
 
@@
 
-    pmu ~ normal( 1.4 , 1.4/3 ) ;
-    qmu ~ normal( 6.59 , 6.59/3 ) ;
-    mmu ~ normal( 1.28 , 1.28/3 ) ;
-    Smu ~ normal( 0.985 , 0.985/3 ) ;
-    Zmu ~ uniform( 0.001 , 100 ) ;
-    wmu ~ normal( 1 , 0.3333 ) ;
-    kmu ~ normal( 0.194 , 0.194/2 ) ;
+    pmu ~ normal( 1.4 , 0.1 ) ;
+    qmu ~ normal( 6.59 , 0.5 ) ;
+    mmu ~ normal( 1.28 , 0.2 ) ;
+    Smu ~ normal( 0.985 , 0.2 ) ;
+    Zmu ~ normal( 0.1 , 0.5 ) ;
+    wmu ~ normal( 1 , 0.2 ) ;
+    kmu ~ normal( 0.194 , 0.1 ) ;
     sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
@@
     dprime = (targresp-nullresp)/k[s[i]] ;
-
+    if (is_nan(dprime)){
+       dprime = 0;
+    }
+    if (is_inf(dprime)){
+       dprime = 10;
+    }
+    if (dprime > 10){
+       dprime = 10;
+    }    
     ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;
-
     }
@@
 ex1data$Condition <- ceiling(ex1data$Condition/2)
+ex3data <- read.csv('local/Experiment3.csv')
+ex3data$Condition <- ceiling(ex3data$Condition/2)
 
@@
 
-expdata <- data.frame(datasets,experiments,conditions,pedestals,targets,ntrials,ncorrect)
-
-dataList = list(ncorrect = expdata$ncorrect, ntrials = expdata$ntrials, PedestalContrast = expdata$pedestals, TargetContrast = expdata$targets, c = expdata$conditions, s = expdata$datasets, Ndatasets = max(expdata$datasets), Ntotal = nrow(expdata))
+sublist3 <- unique(ex3data$Subject)
+for (s in 1:length(sublist3)){
+    datasetcounter <- datasetcounter + 1
+    for (cond in 1:4){
+      thisdipper <- subset(ex3data,Subject==sublist3[s] & Condition==cond)
+
+      pedconts <- sort(unique(thisdipper$PedestalContrast))
+
+      for (p in 1:length(pedconts)){
+        thisthresh <- subset(thisdipper,PedestalContrast==pedconts[p])
+        targconts <- sort(unique(thisthresh$TargetContrast))
+        for (t in 1:length(targconts)){
+          counter <- counter + 1
+          thislevel <- subset(thisthresh,TargetContrast==targconts[t])
+          ntrials[counter] <- nrow(thislevel)
+          ncorrect[counter] <- sum(thislevel$IsCorrect)
+          subjects[counter] <- s
+          experiments[counter] <- 4
+          datasets[counter] <- datasetcounter
+          conditions[counter] <- cond
+          pedestals[counter] <- pedconts[p]
+          targets[counter] <- targconts[t]
+        }
+      }
+    }
+}
+
+expdata <- data.frame(datasets,experiments,subjects,conditions,pedestals,targets,ntrials,ncorrect)
+
+for (expt in 1:4){
+
+thisexpt <- subset(expdata, experiments==expt)
+
+dataList = list(ncorrect = thisexpt$ncorrect, ntrials = thisexpt$ntrials, PedestalContrast = thisexpt$pedestals, TargetContrast = thisexpt$targets, c = thisexpt$conditions, s = thisexpt$subjects, Ndatasets = length(unique(thisexpt$subjects)), Ntotal = nrow(thisexpt))
 
@@
 
-  save(file=paste0('local/FullMod.RData'),list=c('stanFit'))
+save(file=paste0('local/stanfit',expt,'.RData'),list=c('stanFit'))
+
+}
 
@@
 
-if (processdata>0){
-
-  load(file=paste0('local/FullMod.RData'))
-
+allstanparams <- matrix(0,nrow=4,ncol=7)
+
+load(paste0('local/stanfit1.RData'))
 draws <- extract(stanFit)
-
-  p <- map_estimate(draws$pmu+draws$qmu)
-  q <- map_estimate(draws$qmu)
-  m <- map_estimate(draws$mmu)
-  k <- map_estimate(draws$kmu)
-  S <- map_estimate(draws$Smu)
-  Z <- map_estimate(draws$Zmu)
-  w <- map_estimate(draws$wmu)
-  paramvect <- c(p,q,m,S,Z,w,k)
+p <- draws$pmu
+allsamples <- array(0,dim=c(4,7,length(p)))
+
+for (expt in 1:4){
+  load(paste0('local/stanfit',expt,'.RData'))
+  draws <- extract(stanFit)
+  p <- mean(draws$pmu+draws$qmu)
+  q <- mean(draws$qmu)
+  m <- mean(draws$mmu)
+  k <- mean(draws$kmu)
+  S <- mean(draws$Smu)
+  Z <- mean(draws$Zmu)
+  w <- mean(draws$wmu)
+  allstanparams[expt,] <- c(p,q,m,S,Z,w,k)
 
@@
 
-  allsamples <- array(0,dim=c(7,length(plist)))
-    allsamples[1,] <- plist
-    allsamples[2,] <- qlist
-    allsamples[3,] <- mlist
-    allsamples[4,] <- Slist
-    allsamples[5,] <- Zlist
-    allsamples[6,] <- wlist
-    allsamples[7,] <- klist
-
-pdf('Figures/stanoutput.pdf',width=8,height=8)
-
-layout(matrix(c(1,2,3,4,8,8,8,5,8,8,8,6,8,8,8,7),4,4,byrow=TRUE))
+  allsamples[expt,1,] <- plist
+  allsamples[expt,2,] <- qlist
+  allsamples[expt,3,] <- mlist
+  allsamples[expt,4,] <- Slist
+  allsamples[expt,5,] <- Zlist
+  allsamples[expt,6,] <- wlist
+  allsamples[expt,7,] <- klist
+}
+
+if (processdata>0){
+
+nrandomdraws <- 200
+
+load('local/thresholddata.RData')
+load('local/thresholddataDisc.RData')
+
+threshtoplot <- array(0,dim=c(4,4,8))
+threshtoplot[1:3,,] <- meanthresh
+threshtoplot[4,,] <- meanthresh3
+
+  pdf(paste0('Figures/stanoutput.pdf'),width=8,height=8)
+
+  layout(matrix(c(1,1,2,2,3,3,4,4,1,1,2,2,3,3,4,4,8,8,8,9,9,9,5,5,8,8,8,9,9,9,5,5,8,8,8,9,9,9,6,6,10,10,10,11,11,11,6,6,10,10,10,11,11,11,7,7,10,10,10,11,11,11,7,7),8,8,byrow=TRUE))
   par(mar=c(3,2,1,1))
 
-collist <- c('black','cornflowerblue','darkred')
-
-ticklocsx <- seq(-18,24,6)
-ticklabelsx <- c('1/8','1/4','1/2',1,2,4,8,16)
-ticklocsy <- seq(0,1,0.2)
-ticklabelsy <- ticklocsy
+  concols1 <- c('black','darkred','darkblue','white')
+  concols2 <- c('black','darkgreen','gold','black')
+
   paramorder <- c('p','q','m','w','S','Z','k')
@@
 
+  xstart <- c(1,1,1/2,1/2,1/4,1/32,1/16)
+  xstartdB <- round(20*log10(xstart))
+  xstep <- c(6,6,3,3,6,12,6)
+
   for (param in 1:7){
 
-  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,24), ylim=c(0,1))
+    ticklocsx <- seq(xstartdB[param],xstartdB[param]+xstep[param]*(4),xstep[param])
+
+    ticklabelsx <- c('1/4','1/2',1,2,4)
+    if (param<3){ticklabelsx <- c(1,2,4,8,16)}
+    if (param==3 || param==4){ticklabelsx <- c('1/2','','1','','2')}
+    if (param>5){ticklabelsx <- c('1/16','1/8','1/4','1/2','1')}
+    if (param==6){ticklabelsx <- c('1/32','1/8','1/2','2','8')}
+
+    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(xstartdB[param],xstartdB[param]+xstep[param]*4), ylim=c(0,1))
     axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
-  # axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
     mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)
-  # mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
     title(xlab=paramorder[param], col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
 
-    svals <- 20*log10(allsamples[paramvalorder[param],])
+    for (expt in 1:4){
+    svals <- 20*log10(allsamples[expt,paramvalorder[param],])
     a <- density(svals)
@@
     # lines(a$x,a$y,col=collist[expt])
-polygon(a$x,a$y,border=NA,col='grey')
-
-}
-
-pedlist <- -12:39
+    polygon(a$x,a$y,border=NA,col=addalpha(concols1[expt],alpha=0.25))
+    lines(a$x,a$y,col=concols2[expt],lwd=2)
+    }
+
+    if (param==1){
+      legend(0,1,c('Achromatic','Red/green','Blue/yellow','Flicker'),fill=addalpha(concols1,alpha=0.25),border=concols2,box.lwd=2)
+    }
+
+  }
+
+paneltitles <- c('Achromatic grating','Red/green grating','Blue/yellow grating','Flickering disc')
+
+  for (expt in 1:4){
+  pedlist <- -12:36
   pedlevelsC <- 10^(pedlist/20)
@@
   allpred <- array(0,dim=c(4,length(pedlist)))
-
+  allrandomdips <- array(0,dim=c(nrandomdraws,4,length(pedlist)))
+  drawindices <- sample(dim(allsamples)[3],nrandomdraws,replace=FALSE)
   for (cond in 1:4){
     for (pedlev in 1:length(pedlist)){
-      allpred[cond,pedlev] <- discriminate(paramvect,pedlevelsC[pedlev],cond)
-    }
-  }
+      allpred[cond,pedlev] <- discriminate(allstanparams[expt,],pedlevelsC[pedlev],cond)
+
+      for (n in 1:nrandomdraws){
+        allrandomdips[n,cond,pedlev] <- discriminate(allsamples[expt,,drawindices[n]],pedlevelsC[pedlev],cond)
+      }
+    }
+  }
+  allrandomdips <- 20*log10(allrandomdips)
+
+  collist <- c('red','blue','orange','darkgreen')
 
@@
 
-par(mar=c(5,4,2,2))
-
-collist <- c('red','blue','orange','darkgreen')
+  par(mar=c(3,4,2,1))
 
@@
   title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
+  title(main=paneltitles[expt],cex.main=2)
   pedcontrasts <- seq(-12,30,6)
@@
   for (cond in 1:4){
+
+    for (n in 1:nrandomdraws){
+      lines(pedlist,allrandomdips[n,cond,],col=addalpha(collist[cond],2/nrandomdraws),lwd=2)
+    }
+
     lines(pedlist,allpreddB[cond,],col=collist[cond],lwd=2)
-}
-legend(-12,36,c('Monocular','Binocular','Half-bin','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
+    # points(pedcontrasts,threshtoplot[expt,cond,],pch=16,col=collist[cond],cex=1.5)
+  }
+  text(-9,33,paste0('(',letters[expt],')'),cex=2)
+  # legend(-12,42,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
+  }
 
   dev.off()
+
 }
@@
 if (processdata>0){
-
-mkgrating <- function(regionsize, f, o, p, c){
-# ported from the Matlab function, originally by Tim Meese
-# generates a single component sine wave grating using the following inputs:
-  # regionsize is the width of the stimulus
-  # f is spatial frequency in cycles per image
-  # o is orientation in degrees
-  # p is phase in degrees relative to the centre of the image
-  # c is contrast
-
-p <- p*(pi/180)   # convert phase from degrees to radians
-o <- o*(pi/180)   # convert orientation from degrees to radians
-f <- f/regionsize # scale frequency by image size
-x0 <- (regionsize+1)/2  # locate centre of image
-y0 <- x0
-
-u <- f * cos(o) * 2*pi
-v <- f * sin(o) * 2*pi
-
-gridout <- meshgrid(1:regionsize,1:regionsize)   # generate x and y coordinate systems, requires the pracma package
-xx <- gridout$X
-yy <- gridout$Y
-
-output <- matrix(0,nrow=regionsize,ncol=regionsize)
-output <- (c * sin(u * (xx-x0) + v*(yy-y0) + p))
-
-return(output)}
-make_soft_window <- function(W,H,D=0.9){
-  # Mark's function to make sine-wave gratings, ported from Matlab
-  # W is width (in pixels), H is height (in pixels)
-  # D is the diameter of the soft window at half height as a proportion of the width
-
-  radius <- min(W*D/2,H*D/2)     # radius in pixels
-  L <- 2*(min(W/2,H/2) - radius) # blur half-cycle
-  X1 <- seq(-L/2,L/2)
-
-  X <- (1:W) - (W/2)
-  Y <- (1:H) - (H/2)
-  xx <- matrix(rep(X,H),nrow=H,ncol=W,byrow=TRUE)
-  yy <- t(matrix(rep(Y,W),nrow=W,ncol=H,byrow=TRUE))
-
-  mask <- (xx^2 + yy^2)
-  mask[mask<=(radius^2)] <- 1
-  mask[mask>(radius^2)] <- 0
-
-  WinKernel <- cos(X1*pi/L)  # half-cycle cosine
-  convkernW <- (1:W)*0
-  convkernW[(1+(W/2)-length(X1)/2):((W/2)+length(X1)/2)] <- WinKernel
-  convkernH <- (1:H)*0
-  convkernH[(1+(H/2)-length(X1)/2):((H/2)+length(X1)/2)] <- WinKernel
-  cH <- t(apply(mask,2,convolve,convkernH))
-  cH <- cH[,c((1+H/2):H,1:(H/2))]
-  cW <- apply(mask,1,convolve,convkernW)
-  cW <- cW[c((1+W/2):W,1:(W/2)),]
-  mask <- cH * cW
-
-  mask <- mask/max(mask)
-
-  return(mask)}
 
@@
 load('local/MCSdata.RData')
-meanslopesMCS <- 10^(apply(log10(slopematrix),c(2,3),mean))
-meanslopesMCS <- round(meanslopesMCS,digits=2)
+meanslopesMCS <- apply(slopematrix,c(2,3),mean)
+meanslopesMCS <- round(10^(meanslopesMCS/20),digits=2)
 
@@
 condtoplot <- cond + ((block-1)*3)
-points(MCSthresh[,condtoplot],20*log10(MCSslope[,condtoplot]),pch=21,col=outlinecolours[block],bg=shadingcolours[block])
+points(MCSthresh[,condtoplot],MCSslope[,condtoplot],pch=21,col=outlinecolours[block],bg=shadingcolours[block])
 }
@@
 
-if (p==1){legend(-12,36,c('Monocular','Binocular','Half-bin','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
+if (p==1){legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
 
@@
 load('local/MCSdata.RData')
-meanslopesMCS <- 10^(apply(log10(slopematrix),c(2,3),mean))
-meanslopesMCS <- round(meanslopesMCS,digits=2)
+meanslopesMCS <- apply(slopematrix,c(2,3),mean)
+meanslopesMCS <- round(10^(meanslopesMCS/20),digits=2)
 contrastsdB <- contrastsdB[1,,]
@@
 
+load('local/thresholddataDisc.RData')
+
+pdf('Figures/individualdiscs.pdf',width=12,height=5)
+par(mfrow=c(1,3))
+
+collist <- c('red','blue','orange','darkgreen')
+
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
+ticklocsy <- seq(-18,30,6)
+ticklabelsy <- c(0.125,0.25,0.5,1,2,4,8,16,32)
+pnos <- c(1,6,7)
+
+for (p in 1:3){
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-18,30))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(main=paste0('(',letters[p],')  P', pnos[p] ,': Flickering disc'),cex.main=2)
+
+pedcontrasts <- seq(-12,30,6)
+
+for (cond in 1:4){
+  lines(pedcontrasts,allthresh3[p,cond,],col=collist[cond],lwd=2)
+  points(pedcontrasts,allthresh3[p,cond,],pch=16,col=collist[cond],cex=1.5)
+}
+
+if (p==1){legend(-12,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
+
+}
+
+dev.off()
+
 }
@@
 The process by which the brain combines independent inputs is of fundamental importance for understanding sensory perception.
-Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains combine the inputs from the left and right eyes to provide binocular single vision.
-In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data across multiple techniques, including psychophysics [@Meese2006], EEG [@Baker2017], fMRI [@Moradi2009] and pupillometry [@Segala2023].
+Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains typically combine the inputs from the left and right eyes to provide binocular single vision.
+In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data from multiple experimental paradigms and techniques, including psychophysics [@Meese2006], EEG [@Baker2017], fMRI [@Moradi2009] and pupillometry [@Segala2023].
 However, the majority of this work has used achromatic (black and white) stimuli; we know comparatively little about how chromatic signals are combined binocularly, or about how signals in different ocular and chromatic channels interact.
@@
 The detailed pattern of results across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
-At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition owing to binocular summation [@Baker2018; @Campbell1965].
+At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition owing to physiological binocular summation by neurons responsive to signals from both eyes [@Baker2018; @Campbell1965].
 However at high pedestal contrasts the 'handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation [@Legge1984; @Maehara2005].
@@
 
-At the output of the human retina, visual signals are split into three chromatic pathways.
+At the output of the human retina, visual signals are split into three distinct pathways.
 The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information, and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
@@
 In primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981].
-The blob regions appear to be largely monocular [@Livingstone1984], suggesting that binocular combination for chromatic stimuli might occur later than for achromatic stimuli and be subject to different constraints.
+The blob regions appear to be largely monocular [@Livingstone1984], suggesting that binocular combination for chromatic stimuli might occur later than for achromatic stimuli, and perhaps be subject to different constraints.
 
@@
 Participants placed their heads in a chin rest mounted on a height-adjustable table, to which the stereoscope was also attached.
-The total optical viewing distance (including the light path through the mirrors) was XXcm, at which distance 1 degree of visual angle encompassed 48 pixels on the monitor.
+The total optical viewing distance (including the light path through the mirrors) was 104cm, at which distance 1 degree of visual angle encompassed 48 pixels on the monitor.
 
@@
 Stimuli were presented that counterphase flickered at 5Hz, defined about either the L-M or S-(L+M) plane in cone space.
-Participants used a trackball to dynamically adjust the angle of the stimulus to minimise the percept of flicker.
+Participants used a trackball to dynamically adjust the colour angle of the stimulus to minimise the percept of flicker.
 Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli for the main experiment for that participant.
@@
 Each pedestal contrast was repeated 3 times by each participant, and the block order was randomised.
-The experiment lasted around 4 hours per participant for each chromatic condition, which took place over the course of several weeks.
+The experiment lasted around 4 hours per participant for each chromatic condition, and took place over the course of several weeks.
 In total, the experiment consisted of `r nrow(ex1data)` trials (pooled across participants).
@@
 2 full cycles of the temporal modulation).
-All other procedures were the same as for Experiment 1, and the experiment comprised a total of X trials (pooled across participants).
+All other procedures were the same as for Experiment 1, and the experiment comprised a total of `r nrow(ex3data)` trials (pooled across participants).
 
@@
 
-$Stage1_L = \frac{C_L^m}{S + C_L + \omega C_R}$
-
-$Stage1_R = \frac{C_L^m}{S + C_R + \omega C_L}$
-
-$binsum = Stage1_L + Stage1_R$
-
-$binresp = \frac{binsum^p}{Z + binsum^q}$
+\begin{equation}
+Stage1_L = \frac{C_L^m}{S + C_L + \omega C_R},
+\end{equation}
+
+\begin{equation}
+Stage1_R = \frac{C_L^m}{S + C_R + \omega C_L},
+\end{equation}
+
+\begin{equation}
+binsum = Stage1_L + Stage1_R,
+\end{equation}
+
+\begin{equation}
+binresp = \frac{binsum^p}{Z + binsum^q},
+\end{equation}
 
@@
 A further free parameter, $k$, represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values.
-Thresholds are defined when the following equality is satisfied:
-
-$binresp_{target+pedestal} - binresp_{pedestal} = k$
-
-and d-prime is defined as:
-
-$d' = \frac{binresp_{target+pedestal} - binresp_{pedestal}}{k}$.
+Thresholds are defined by adjusting the target contrast until the following equality is satisfied:
+
+\begin{equation}
+binresp_{target+pedestal} - binresp_{pedestal} = k,
+\end{equation}
+
+and d-prime for a single target level is defined as:
+
+\begin{equation}
+d' = \frac{binresp_{target+pedestal} - binresp_{pedestal}}{k}.
+\end{equation}
+
+We ran the simplex algorithm from `r ntotalsimplexfits` random starting vectors for each data set, and chose the solution for each data set that gave the smallest RMS error.
 
 We also implemented a Bayesian hierarchical version of the model using the Stan language [@Carpenter2017].
-This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants and each chromatic condition of Experiment 1.
+This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants for a given experiment, but separately for each chromatic condition of Experiment 1, and the flickering disc data from Experiment 3 (i.e.
+four fits in total, as for the simplex fitting).
 This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
@@
 Note that we deviated slightly from the planned preregistration, in that we did not collect data for chromatic flickering discs, or for the cross-pathway dichoptic experiment using disc stimuli.
-This is because the grating data from Experiments 1 and 2, and the achromatic disc data from Experiment 3, were sufficient to address the questions we had wanted to answer from these experiments.
+This is because the grating data from Experiments 1 and 2, and the achromatic disc data from Experiment 3, were sufficient to address the questions we had hoped to answer from these experiments.
 
@@
 
-Dipper functions from Experiment 1 are displayed in Figure \@ref(fig:dipperfig).
+Dipper functions from Experiment 1 are displayed in the upper row of Figure \@ref(fig:dipperfig).
 Panel (a) shows the achromatic results, which replicate the key features from previous work.
-At detection threshold, binocular summation was a factor of `r round(10^(summation[1]/20),digits=2)` (`r round(summation[1],digits=2)`dB), consistent with previous reports.
+At detection threshold, binocular summation was a factor of `r round(10^(summation[1]/20),digits=2)` (`r round(summation[1],digits=2)`dB), consistent with previous reports [@Baker2018].
 Pedestal masking functions follow the typical 'dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
 The monocular and binocular dipper handles converge at high contrasts, whereas the half-binocular thresholds remain above the binocular thresholds across the full range of pedestal contrasts.
-The dichoptic condition produced very high thresholds, with the rising portion of the dipper having a slope around 1 (regression slope of `r round(dichregACH$coefficients[2], digits=2)` across the highest 4 pedestal contrasts in log (dB) units).
-
-```{r dipperfig, fig.cap="Dipper functions from Experiment 1, averaged across three participants.
-Error bars show ±1SE across participants.
+The dichoptic condition produced very high thresholds, with the rising portion of the dipper having a slope around 1 (regression slope of `r round(dichregACH$coefficients[2], digits=2)` in log (dB) units, calculated across the highest 4 pedestal contrasts).
+
+```{r dipperfig, fig.cap="Dipper functions and psychometric slopes from Experiment 1, averaged across three participants.
+Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull beta units.
+Error bars give ±1SE across participants.
 Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).
-Curves show...", fig.align="center", echo=FALSE}
+Curves in panels (a-c) show the best fitting models, optimized using a simplex algorithm (described in section 4.4), and RMSE values give the root mean square errors of the fits.", fig.align="center", echo=FALSE}
 
@@
 Dichoptic masking remained as strong for the chromatic conditions as for the achromatic stimuli (regression slopes of `r round(dichregRG$coefficients[2], digits=2)` for red/green and `r round(dichregBY$coefficients[2], digits=2)` for blue/yellow).
-The pattern of results for individual participants was consistent with the averages, as shown in Figure \@ref(fig:individualdips).
-
-For consistency with previous work, we initially performed least-squares fits of the two-stage model [@Meese2006] for each of the chromaticity experiments (7 free parameters per fit).
-The best model fits are shown in Figure \@ref(fig:dipperfig), and provide an excellent description of the data, with RMS errors between 1.37 and 1.59dB.
-We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
-This model was fit simultaneously to the full trial-by-trial data from all participants and chromaticity experiments.
-Figure \@ref(fig:bayesianmodel)a summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
-Figure \@ref(fig:bayesianmodel)b-h shows posterior distributions for each model parameter.
-Note in particular that the weight of interocular suppression overlaps 1 for each chromaticity experiment, consistent with the strong dichoptic masking observed in the threshold data.
-
-```{r bayesianmodel, fig.cap="Model parameters", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/stanoutput.pdf')
-
-```
+The pattern of results for individual participants was consistent with the group averages, as shown in Figure \@ref(fig:individualdips).
+
+Following @Meese2006, we also inspected the slope of the psychometric function for each condition (see Figure \@ref(fig:dipperfig)d-f).
+At detection threshold, slopes were relatively steep, with $\beta$ values around 4.
+As pedestal contrasts increased, slopes linearized and reduced to around $\beta=1.3$ [@Foley1981; @Meese2006], and remained shallow at high pedestal contrasts.
+The exception to this was the dichoptic condition, where slopes became extremely steep at high dichoptic mask contrasts, consistent with previous observations [@Meese2006; @Baker2013].
+This was clear for all three data sets, with slope values in the range $\beta=4$ to $\beta=8$.
+However, we note that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
+Our second experiment investigated the slope of the psychometric function in more detail using the method of constant stimuli.
 
@@
 In Experiment 2 we focussed on the dichoptic condition at a single mask contrast, and measured full psychometric functions using the method of constant stimuli for all factorial pairings of target and mask chromaticity.
-The pooled results across three participants are shown in Figure \@ref(fig:MCSfig), and results for individual participants are available in Figure \@ref(fig:individualMCS).
+The pooled results across three participants are shown in Figure \@ref(fig:MCSfig)a-c, and results for individual participants are available in Figure \@ref(fig:individualMCS).
 All conditions produced monotonically increasing psychometric functions (panels a-c), but the extent of masking was highly dependent on the relationship between the target and mask chromaticity.
 Figure \@ref(fig:MCSfig)d-f shows a two-dimensional representation of individual threshold and slope estimates (points), as well as the posterior density estimates for fits to the pooled data (ellipses).
+The results are consistent between participants, and at the group level, and show that the presence of a mask has a strong effect on thresholds.
 
@@
 
-We also calculated the slope of the psychometric function for each condition, converted to equivalent Weibull $\beta$ values.
-In the absence of a mask, the average slope was $\beta$ = `r round(10^(mean(log10(detslopes))),digits=2)`, which is typical for contrast detection tasks.
+We also calculated the slope of the psychometric function for each condition, in equivalent Weibull $\beta$ units.
+In the absence of a mask, the average slope was $\beta$ = `r round(10^(mean(detslopes)/20),digits=2)`, which is typical for contrast detection tasks.
 Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,1],meanslopesMCS[2,2],meanslopesMCS[3,3])))),digits=2)`).
-These 'super-steep' psychometric functions for dichoptic pedestal masking have been reported previously [@Meese2006; @Baker2013], and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \@ref(fig:MCSfig)h).
+These 'super-steep' psychometric functions for dichoptic pedestal masking have been reported previously [@Meese2006; @Baker2013], and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \@ref(fig:MCSfig)h, and also Figure \@ref(fig:dipperfig)d-f).
 However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,2],meanslopesMCS[1,3],meanslopesMCS[2,1],meanslopesMCS[2,3],meanslopesMCS[3,1],meanslopesMCS[3,2])))),digits=2)` for the off-diagonal values).
@@
 This was motivated by our recent work [@Segala2023] that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
-The pattern of dipper functions for a 4Hz flickering disc (see Figure X) was very similar to that observed for achromatic gratings (see Figure \@ref(fig:dipperfig)a), and the binocular summation ratio at threshold was also similar (a factor of).
-Fitting the same computational model to the disc data also generated an estimated weight of interocular suppression around 1.
-Data for individual participants are shown in Figure AX.
+The pattern of dipper functions for a 4Hz flickering disc (see Figure \@ref(fig:discdata)a) was very similar to that observed for achromatic gratings (see Figure \@ref(fig:dipperfig)a), and the binocular summation ratio at threshold was also similar (a factor of `r round(10^(summationDisc/20),digits=2)`).
+Threshold data for individual participants are shown in Figure \@ref(fig:individualdiscs).
+We also found a similar pattern of psychometric slope values (Figure \@ref(fig:discdata)b), though we note that the dichoptic condition did not produce the 'super-steep' psychometric functions we had observed in Experiments 1 & 2.
+Nevertheless, its slopes are somewhat above those of the other pedestal arrangements.
+
+```{r discdata, out.width = "80%", fig.cap="Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 3.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/discdata.pdf')
+
+```
+
+## Computational modelling
+
+```{r parametertable, echo=FALSE}
+
+load('local/simplexfits.RData')
+
+tableparams <- matrix(0,nrow=11,ncol=8)
+
+tableparams[1,1:7] <- c(7.99,6.59,1.28,0.99,0.08,1,0.19)
+tableparams[3,1:7] <- allp[1,]
+tableparams[4,1:7] <- allp[2,]
+tableparams[5,1:7] <- allp[3,]
+tableparams[6,1:7] <- allp[4,]
+tableparams[3:6,8] <- allrms
+
+tableparams[8:11,1:7] <- allstanparams
+
+tableparams <- round(tableparams,digits=2)
+
+tableparams <- data.frame(tableparams)
+
+tableparams$Model <- c('Meese et al.
+(2006)','Simplex fits','Achromatic gratings','Red/green gratings','Blue/yellow gratings','Flickering discs','Bayesian model','Achromatic gratings','Red/green gratings','Blue/yellow gratings','Flickering discs')
+
+colnames(tableparams) <- c("p", "q", "m", "S", "Z", "w", "k", "RMSE", "Model fit")
+tableparams$RMSE <- paste(tableparams$RMSE,'dB')
+tableparams <- tableparams[,c(9,1,2,3,4,5,6,7,8)]
+
+tableparams[c(1,2,7:11),9] <- ' '
+tableparams[c(2,7),2:9] <- ' '
+
+knitr::kable(tableparams, caption='Summary of fitted model parameters.
+The upper rows are best fitting parameters from simplex fits to the averaged thresholds for each experiment.
+The final row shows the posterior parameter estimates from the Bayesian model, fitted to data from Experiments 1 and 3.', align='lrrrrrrrr', booktabs = TRUE, linesep='',escape = FALSE) %>%
+row_spec(c(1,6),hline_after=T) %>% row_spec(0,italic=T) %>% row_spec(c(0,2,7),bold=T)
+
+```
+
+For consistency with previous work, we initially performed least-squares fits of the two-stage model [@Meese2006] for each of the chromaticity experiments, and the flickering disc experiment (7 free parameters per fit).
+The best model fits are shown by the curves in Figures \@ref(fig:dipperfig) & \@ref(fig:discdata), and provide an excellent description of the data, with RMS errors between `r round(min(allrms),digits=2)` and `r round(max(allrms),digits=2)`dB.
+Best fitting parameters are shown in the 'Simplex fits' section of Table \@ref(tab:parametertable).
+We note that in previous work, the weight of interocular suppression (*w* in the model) is implicitly fixed at 1.
+Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (0.89) for our flickering discs.
+
+We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
+This model was fit simultaneously to full trial-by-trial data from all participants who participated in a given experiment (i.e.
+the model was fitted separately to each of the four dipper data sets).
+Figure \@ref(fig:bayesianmodel)a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
+Mean posterior parameter values are given in the lower rows of Table \@ref(tab:parametertable).
+These correspond quite closely to the parameters from the simplex fitting and the original @Meese2006 parameters (reproduced in the first row of the table for reference).
+The panels in the right and upper margins of Figure \@ref(fig:bayesianmodel) show posterior distributions for each model parameter.
+Note in particular that the posterior distribution for the weight of interocular suppression (*w*, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
+We note that the distribution for *w* in the flickering disc condition is somewhat lower than for the other three data sets.
+However this difference is not meaningful according to criteria such as comparing the 95% credible intervals of the distribution to a value of *w*=1.
+
+```{r bayesianmodel, fig.cap="Model predictions (a-d) and posterior parameters (top and right margin plots) for the hierarchical Bayesian model.
+Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates, and thin lines are from 200 random posterior draws.
+The probability density functions in the margin plots are peak-normalized, and shown for each of the four data sets in different colours (see legend in upper left plot).
+Distributions are generated from 1000000 samples per data set, using a Markov Chain Monte Carlo sampling algorithm.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/stanoutput.pdf')
+
+```
 
@@
 ```
+
+```{r individualdiscs, fig.cap="Individual participant data from Experiment 3.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/individualdiscs.pdf')
+
+```

### 2024-03-24 manuscript.tex
Fixed Stan model!

@@
 \usepackage{float} \floatplacement{figure}{H} \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \ifLuaTeX
@@
 The process by which the brain combines independent inputs is of fundamental importance for understanding sensory perception.
-Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains combine the inputs from the left and right eyes to provide binocular single vision.
-In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data across multiple techniques, including psychophysics (Meese et al., 2006), EEG (Baker \& Wade, 2017), fMRI (Moradi \& Heeger, 2009) and pupillometry (Segala et al., 2023).
+Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains typically combine the inputs from the left and right eyes to provide binocular single vision.
+In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data from multiple experimental paradigms and techniques, including psychophysics (Meese et al., 2006), EEG (Baker \& Wade, 2017), fMRI (Moradi \& Heeger, 2009) and pupillometry (Segala et al., 2023).
 However, the majority of this work has used achromatic (black and white) stimuli; we know comparatively little about how chromatic signals are combined binocularly, or about how signals in different ocular and chromatic channels interact.
@@
 The detailed pattern of results across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
-At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition owing to binocular summation (Baker et al., 2018; Campbell \& Green, 1965).
+At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition owing to physiological binocular summation by neurons responsive to signals from both eyes (Baker et al., 2018; Campbell \& Green, 1965).
 However at high pedestal contrasts the `handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation (Legge, 1984; Maehara \& Goryo, 2005).
@@
 In primary visual cortex (V1), chromatic signals are processed in `blob' regions that are revealed by cytochrome oxidase staining (Horton \& Hubel, 1981).
-The blob regions appear to be largely monocular (Livingstone \& Hubel, 1984), suggesting that binocular combination for chromatic stimuli might occur later than for achromatic stimuli and be subject to different constraints.
+The blob regions appear to be largely monocular (Livingstone \& Hubel, 1984), suggesting that binocular combination for chromatic stimuli might occur later than for achromatic stimuli, and perhaps be subject to different constraints.
 
@@
 Each pedestal contrast was repeated 3 times by each participant, and the block order was randomised.
-The experiment lasted around 4 hours per participant for each chromatic condition, which took place over the course of several weeks.
+The experiment lasted around 4 hours per participant for each chromatic condition, and took place over the course of several weeks.
 In total, the experiment consisted of 67978 trials (pooled across participants).
@@
 The stimulus counterphase flickered at 4Hz, and was presented for 500ms (i.e.~2 full cycles of the temporal modulation).
-All other procedures were the same as for Experiment 1, and the experiment comprised a total of X trials (pooled across participants).
+All other procedures were the same as for Experiment 1, and the experiment comprised a total of 24610 trials (pooled across participants).
 
@@
 
-\(Stage1_L = \frac{C_L^m}{S + C_L + \omega C_R}\)
+\begin{equation}
+Stage1_L = \frac{C_L^m}{S + C_L + \omega C_R},
+\end{equation}
 
-\(Stage1_R = \frac{C_L^m}{S + C_R + \omega C_L}\)
+\begin{equation}
+Stage1_R = \frac{C_L^m}{S + C_R + \omega C_L},
+\end{equation}
 
-\(binsum = Stage1_L + Stage1_R\)
+\begin{equation}
+binsum = Stage1_L + Stage1_R,
+\end{equation}
 
-\(binresp = \frac{binsum^p}{Z + binsum^q}\)
+\begin{equation}
+binresp = \frac{binsum^p}{Z + binsum^q},
+\end{equation}
 
@@
 A further free parameter, \(k\), represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values.
-Thresholds are defined when the following equality is satisfied:
+Thresholds are defined by adjusting the target contrast until the following equality is satisfied:
 
-\(binresp_{target+pedestal} - binresp_{pedestal} = k\)
+\begin{equation}
+binresp_{target+pedestal} - binresp_{pedestal} = k,
+\end{equation}
 
-and d-prime is defined as:
+and d-prime for a single target level is defined as:
 
-\(d' = \frac{binresp_{target+pedestal} - binresp_{pedestal}}{k}\).
+\begin{equation}
+d' = \frac{binresp_{target+pedestal} - binresp_{pedestal}}{k}.
+\end{equation}
+
+We ran the simplex algorithm from 100 random starting vectors for each data set, and chose the solution for each data set that gave the smallest RMS error.
 
 We also implemented a Bayesian hierarchical version of the model using the Stan language (Carpenter et al., 2017).
-This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants and each chromatic condition of Experiment 1.
+This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants for a given experiment, but separately for each chromatic condition of Experiment 1, and the flickering disc data from Experiment 3 (i.e.~four fits in total, as for the simplex fitting).
 This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
@@
 
-Dipper functions from Experiment 1 are displayed in Figure \ref{fig:dipperfig}.
+Dipper functions from Experiment 1 are displayed in the upper row of Figure \ref{fig:dipperfig}.
 Panel (a) shows the achromatic results, which replicate the key features from previous work.
-At detection threshold, binocular summation was a factor of 1.67 (4.47dB), consistent with previous reports.
+At detection threshold, binocular summation was a factor of 1.67 (4.47dB), consistent with previous reports (Baker et al., 2018).
 Pedestal masking functions follow the typical `dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
 The monocular and binocular dipper handles converge at high contrasts, whereas the half-binocular thresholds remain above the binocular thresholds across the full range of pedestal contrasts.
-The dichoptic condition produced very high thresholds, with the rising portion of the dipper having a slope around 1 (regression slope of 1.06 across the highest 4 pedestal contrasts in log (dB) units).
+The dichoptic condition produced very high thresholds, with the rising portion of the dipper having a slope around 1 (regression slope of 1.06 in log (dB) units, calculated across the highest 4 pedestal contrasts).
 
@@
 
-\caption{Dipper functions from Experiment 1, averaged across three participants.
-Error bars show ±1SE across participants.
+\caption{Dipper functions and psychometric slopes from Experiment 1, averaged across three participants.
+Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull beta units.
+Error bars give ±1SE across participants.
 Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).
-Curves show...}\label{fig:dipperfig}
+Curves in panels (a-c) show the best fitting models, optimized using a simplex algorithm (described in section 4.4), and RMSE values give the root mean square errors of the fits.}\label{fig:dipperfig}
 \end{figure}
@@
 Dichoptic masking remained as strong for the chromatic conditions as for the achromatic stimuli (regression slopes of 1.3 for red/green and 1.21 for blue/yellow).
-The pattern of results for individual participants was consistent with the averages, as shown in Figure \ref{fig:individualdips}.
+The pattern of results for individual participants was consistent with the group averages, as shown in Figure \ref{fig:individualdips}.
 
-For consistency with previous work, we initially performed least-squares fits of the two-stage model (Meese et al., 2006) for each of the chromaticity experiments (7 free parameters per fit).
-The best model fits are shown in Figure \ref{fig:dipperfig}, and provide an excellent description of the data, with RMS errors between 1.37 and 1.59dB.
-We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
-This model was fit simultaneously to the full trial-by-trial data from all participants and chromaticity experiments.
-Figure \ref{fig:bayesianmodel}a summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
-Figure \ref{fig:bayesianmodel}b-h shows posterior distributions for each model parameter.
-Note in particular that the weight of interocular suppression overlaps 1 for each chromaticity experiment, consistent with the strong dichoptic masking observed in the threshold data.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/stanoutput}
-
-}
-
-\caption{Model parameters}\label{fig:bayesianmodel}
-\end{figure}
+Following Meese et al.
+(2006), we also inspected the slope of the psychometric function for each condition (see Figure \ref{fig:dipperfig}d-f).
+At detection threshold, slopes were relatively steep, with \(\beta\) values around 4.
+As pedestal contrasts increased, slopes linearized and reduced to around \(\beta=1.3\) (Foley \& Legge, 1981; Meese et al., 2006), and remained shallow at high pedestal contrasts.
+The exception to this was the dichoptic condition, where slopes became extremely steep at high dichoptic mask contrasts, consistent with previous observations (Baker et al., 2013; Meese et al., 2006).
+This was clear for all three data sets, with slope values in the range \(\beta=4\) to \(\beta=8\).
+However, we note that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
+Our second experiment investigated the slope of the psychometric function in more detail using the method of constant stimuli.
 
@@
 In Experiment 2 we focussed on the dichoptic condition at a single mask contrast, and measured full psychometric functions using the method of constant stimuli for all factorial pairings of target and mask chromaticity.
-The pooled results across three participants are shown in Figure \ref{fig:MCSfig}, and results for individual participants are available in Figure \ref{fig:individualMCS}.
+The pooled results across three participants are shown in Figure \ref{fig:MCSfig}a-c, and results for individual participants are available in Figure \ref{fig:individualMCS}.
 All conditions produced monotonically increasing psychometric functions (panels a-c), but the extent of masking was highly dependent on the relationship between the target and mask chromaticity.
 Figure \ref{fig:MCSfig}d-f shows a two-dimensional representation of individual threshold and slope estimates (points), as well as the posterior density estimates for fits to the pooled data (ellipses).
+The results are consistent between participants, and at the group level, and show that the presence of a mask has a strong effect on thresholds.
 
@@
 
-We also calculated the slope of the psychometric function for each condition, converted to equivalent Weibull \(\beta\) values.
+We also calculated the slope of the psychometric function for each condition, in equivalent Weibull \(\beta\) units.
 In the absence of a mask, the average slope was \(\beta\) = 3.42, which is typical for contrast detection tasks.
 Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average \(\beta\) = 5.38).
-These `super-steep' psychometric functions for dichoptic pedestal masking have been reported previously (Baker et al., 2013; Meese et al., 2006), and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \ref{fig:MCSfig}h).
+These `super-steep' psychometric functions for dichoptic pedestal masking have been reported previously (Baker et al., 2013; Meese et al., 2006), and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \ref{fig:MCSfig}h, and also Figure \ref{fig:dipperfig}d-f).
 However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average \(\beta\) = 2.83 for the off-diagonal values).
@@
 This was motivated by our recent work (Segala et al., 2023) that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
-The pattern of dipper functions for a 4Hz flickering disc (see Figure X) was very similar to that observed for achromatic gratings (see Figure \ref{fig:dipperfig}a), and the binocular summation ratio at threshold was also similar (a factor of).
-Fitting the same computational model to the disc data also generated an estimated weight of interocular suppression around 1.
-Data for individual participants are shown in Figure AX.
+The pattern of dipper functions for a 4Hz flickering disc (see Figure \ref{fig:discdata}a) was very similar to that observed for achromatic gratings (see Figure \ref{fig:dipperfig}a), and the binocular summation ratio at threshold was also similar (a factor of 1.49).
+Threshold data for individual participants are shown in Figure \ref{fig:individualdiscs}.
+We also found a similar pattern of psychometric slope values (Figure \ref{fig:discdata}b), though we note that the dichoptic condition did not produce the `super-steep' psychometric functions we had observed in Experiments 1 \& 2.
+Nevertheless, its slopes are somewhat above those of the other pedestal arrangements.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Figures/discdata}
+
+}
+
+\caption{Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 3.}\label{fig:discdata}
+\end{figure}
+
+\hypertarget{computational-modelling}{%
+\subsection{Computational modelling}\label{computational-modelling}}
+
+\begin{table}
+
+\caption{\label{tab:parametertable}Summary of fitted model parameters.
+The upper rows are best fitting parameters from simplex fits to the averaged thresholds for each experiment.
+The final row shows the posterior parameter estimates from the Bayesian model, fitted to data from Experiments 1 and 3.}
+\centering
+\begin{tabular}[t]{lrrrrrrrr}
+\toprule
+\textbf{\em{Model fit}} & \textbf{\em{p}} & \textbf{\em{q}} & \textbf{\em{m}} & \textbf{\em{S}} & \textbf{\em{Z}} & \textbf{\em{w}} & \textbf{\em{k}} & \textbf{\em{RMSE}}\\
+\midrule
+Meese et al. (2006) & 7.99 & 6.59 & 1.28 & 0.99 & 0.08 & 1 & 0.19 & \\
+\midrule
+\textbf{Simplex fits} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
+Achromatic gratings & 6.51 & 5.1 & 1.31 & 0.83 & 0.16 & 1 & 0.21 & 1.59 dB\\
+Red/green gratings & 19.42 & 1.1 & 1.03 & 0.37 & 1.49 & 1 & 0.29 & 1.43 dB\\
+Blue/yellow gratings & 9.47 & 6.21 & 1.14 & 1.89 & 0.26 & 1 & 0.34 & 1.38 dB\\
+Flickering discs & 6.13 & 4.93 & 1.24 & 0.84 & 0.27 & 0.89 & 0.13 & 1.06 dB\\
+\midrule
+\textbf{Bayesian model} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
+Achromatic gratings & 7.79 & 6.38 & 1.29 & 0.87 & 0.12 & 0.99 & 0.25 & \\
+Red/green gratings & 7.89 & 6.48 & 1.18 & 1.11 & 0.51 & 0.96 & 0.23 & \\
+Blue/yellow gratings & 7.73 & 6.31 & 1.15 & 1.09 & 0.51 & 0.99 & 0.25 & \\
+Flickering discs & 7.7 & 6.29 & 1.26 & 0.83 & 0.21 & 0.91 & 0.23 & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+For consistency with previous work, we initially performed least-squares fits of the two-stage model (Meese et al., 2006) for each of the chromaticity experiments, and the flickering disc experiment (7 free parameters per fit).
+The best model fits are shown by the curves in Figures \ref{fig:dipperfig} \& \ref{fig:discdata}, and provide an excellent description of the data, with RMS errors between 1.06 and 1.59dB.
+Best fitting parameters are shown in the `Simplex fits' section of Table \ref{tab:parametertable}.
+We note that in previous work, the weight of interocular suppression (\emph{w} in the model) is implicitly fixed at 1.
+Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (0.89) for our flickering discs.
+
+We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
+This model was fit simultaneously to full trial-by-trial data from all participants who participated in a given experiment (i.e.~the model was fitted separately to each of the four dipper data sets).
+Figure \ref{fig:bayesianmodel}a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
+Mean posterior parameter values are given in the lower rows of Table \ref{tab:parametertable}.
+These correspond quite closely to the parameters from the simplex fitting and the original Meese et al.
+(2006) parameters (reproduced in the first row of the table for reference).
+The panels in the right and upper margins of Figure \ref{fig:bayesianmodel} show posterior distributions for each model parameter.
+Note in particular that the posterior distribution for the weight of interocular suppression (\emph{w}, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
+We note that the distribution for \emph{w} in the flickering disc condition is somewhat lower than for the other three data sets.
+However this difference is not meaningful according to criteria such as comparing the 95\% credible intervals of the distribution to a value of \emph{w}=1.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/stanoutput}
+
+}
+
+\caption{Model predictions (a-d) and posterior parameters (top and right margin plots) for the hierarchical Bayesian model.
+Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates, and thin lines are from 200 random posterior draws.
+The probability density functions in the margin plots are peak-normalized, and shown for each of the four data sets in different colours (see legend in upper left plot).
+Distributions are generated from 1000000 samples per data set, using a Markov Chain Monte Carlo sampling algorithm.}\label{fig:bayesianmodel}
+\end{figure}
 
@@
 \url{https://doi.org/10.1016/j.cub.2018.12.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Foley1981}{}}%
+Foley, J.
+M., \& Legge, G.
+E.
+(1981).
+Contrast detection and near-threshold discrimination in human vision.
+\emph{Vision Res}, \emph{21}(7), 1041--1053.
+\url{https://doi.org/10.1016/0042-6989(81)90009-2}
 
@@
 
+\begin{figure}
+
+{\centering \includegraphics{Figures/individualdiscs}
+
+}
+
+\caption{Individual participant data from Experiment 3.}\label{fig:individualdiscs}
+\end{figure}
+
 \end{document}

### 2024-03-24 experimentcode/isoflickerVisage.m

@@ -11,7 +11,7 @@ function isoflickerVisage
 close all;
 tic
 
-subj = menu('Select participant','DHB','JTM','KJH','FGS','RJH','Test');
+subj = menu('Select participant','DHB','JTM','KJH','MR','RJH','Test');
 subnamelist = {'P1','P2','P3','P4','P5','XX'};
 E.subj = subnamelist{subj};
 
@@ -353,8 +353,6 @@ WaitSecs(1);
                 trial = 10000;
             end
         end
-        
-        
         
         
         if useVSG

### 2024-03-24 experimentcode/runcolourdippers.m

@@ -7,7 +7,7 @@ function runcolourdippers
 
 close all;
 
-subj = menu('Select participant','DHB','JTM','KJH','Test');
+subj = menu('Select participant','P1','P2','P3','Test');
 WaitSecs(0.5);
 expt = menu('Choose experiment','Achromatic','Red/Green','Blue/Yellow');
 

### 2024-03-24 experimentcode/runflickerdippers.m

@@ -1,26 +1,26 @@
-function runMCScross
+function runflickerdippers
 
-% dichoptic conditions with method of constant stimuli
-%
 % single script to run colour dipper experiment
 % choose participant ID and which experiment to run
 % DHB 26/8/22
 % updated 25/9/22 to optimise contrast levels for each participant & condition
-% updated 2/1/23 to implement MCS
+% 28/1/22 this version to do flicker
 
 close all;
+
 % addpath(genpath('C:\Program Files\Cambridge Research Systems\CRS Toolbox for MATLAB')); 
 % cd('C:\Users\Daniel Baker\Documents\MATLAB\Psychtoolbox');
 % SetupPsychtoolbox;
 % cd('C:\Users\Daniel Baker\Documents\MATLAB\colourdippers');
 
-subj = menu('Select participant','P1','P4','P5','Test');
+subj = menu('Select participant','P1','P6','P7','Test');
 WaitSecs(0.5);
+expt = menu('Choose experiment','Achromatic','Red/Green','Blue/Yellow');
 
 useVSG = 1;
 useRTS = 0;   % this is glitchy so best avoided
 
-subnamelist = {'P1','P4','P5','XX'};
+subnamelist = {'P1','P6','P7','XX'};
 exptnamelist = {'AC','RG','BY'};
 
 E.exptpath = strcat(pwd, '\'); % Same as above, JTM
@@ -40,33 +40,21 @@ ST.npixelsperdegree = 48;
 ST.gratingsizedeg = 3;
 ST.gratingsizepix = ST.gratingsizedeg * ST.npixelsperdegree;
 ST.gausssigma = ST.npixelsperdegree;
-ST.SF = 1;
-ST.ncycles = ST.SF * ST.gratingsizedeg;
-ST.duration = 0.2;
+ST.SF = 0;
+ST.ncycles = 0;
+ST.duration = 0.5;
 ST.ISI = 0.4;
 ST.postresponseduration = 0.6;
-ST.phaselist = [0 90 180 270];
+ST.phaselist = [1 -1];
+ST.TF = 4;
 
-E.pedcontrastsdB = [0 0 0 24 24 24 36 36 36 36 36 36];
+E.pedcontrastsdB(1,:) = -12:6:30;
[…]

### 2024-03-31 manuscript.Rmd
First draft completed

@@
 
-processdata <- 0
+processdata <- 1
 # the processdata flag has three settings:
@@
 thinSteps <- 10
-nChains <- 8
+nChains <- 64
 
@@
 
-if (processdata>1){
+if (processdata>0){
   use_miniconda('r-reticulate')
@@
 title(ylab="M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='L-M gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-text(-0.95,0.9,'(a)',cex=2)
+title(main='(a) L-M gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=2)
 
@@
 title(ylab="S", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='S-(L+M) gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-text(-0.95,0.9,'(b)',cex=2)
+title(main='(b) S-(L+M) gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=2)
 
@@
 
-```{r domodellingstan, include=FALSE}
-
-if (processdata==2){
-
-numSavedSteps <- nsamples    # total number of MCMC steps
-options(mc.cores=ncores)
+```{r stanmodelspecifications, include=FALSE}
 
@@
     vector<lower=2, upper=8>[Ndatasets] q;
-    vector<lower=1, upper=2>[Ndatasets] m;
+    vector<lower=0.5, upper=2>[Ndatasets] m;
     vector<lower=0.001, upper=2>[Ndatasets] S;  
-    vector<lower=0.001, upper=1>[Ndatasets] Z;
-    vector<lower=0.001,upper=2>[Ndatasets] w;
-    vector<lower=0.001,upper=1>[Ndatasets] k;
+    vector<lower=0.001, upper=2>[Ndatasets] Z;
+    vector<lower=0.001, upper=2>[Ndatasets] w;
+    vector<lower=0.001, upper=2>[Ndatasets] k;
 
     real<lower=0> sigma ;
-    real<lower=0.1> pmu ; 
-    real<lower=2> qmu ; 
-    real<lower=1> mmu ;
-    real<lower=0.001> Smu ;
-    real<lower=0.001, upper=1> Zmu ; 
-    real<lower=0.001> wmu ; 
-    real<lower=0.001> kmu ;
+    real<lower=0.1, upper=3> pmu ; 
+    real<lower=2, upper=8> qmu ; 
+    real<lower=0.5, upper=2> mmu ;
+    real<lower=0.001, upper=2> Smu ;
+    real<lower=0.001, upper=2> Zmu ; 
+    real<lower=0.001, upper=2> wmu ; 
+    real<lower=0.001, upper=2> kmu ;
 
@@
     Smu ~ normal( 0.985 , 0.2 ) ;
-    Zmu ~ normal( 0.1 , 0.5 ) ;
+    Zmu ~ normal( 0.08 , 0.5 ) ;
     wmu ~ normal( 1 , 0.2 ) ;
@@
 " # close quote for modelString
+
+crossmodelString = "
+  data {
+    int<lower=1> Ndatasets ;
+    int<lower=1> Ntotal ;
+    int ncorrect[Ntotal] ;
+    int ntrials[Ntotal] ;
+    real PedestalContrast[Ntotal] ;
+    real TargetContrast[Ntotal] ;
+    int<lower=1> c[Ntotal] ;
+    int<lower=1> s[Ntotal] ;  
+  }
+  parameters {
+    vector<lower=0, upper=40>[Ndatasets] Zac;
+    vector<lower=0, upper=40>[Ndatasets] Zrg;
+    vector<lower=0, upper=40>[Ndatasets] Zby;
+    vector<lower=0.001, upper=2>[Ndatasets] wAcR;
+    vector<lower=0.001, upper=2>[Ndatasets] wAcB;
+    vector<lower=0.001, upper=2>[Ndatasets] wRgA;
+    vector<lower=0.001, upper=2>[Ndatasets] wRgB;
+    vector<lower=0.001, upper=2>[Ndatasets] wByA;
+    vector<lower=0.001, upper=2>[Ndatasets] wByR;
+
+    real<lower=0> sigma ;
+    real<lower=0, upper=40> Zacmu ; 
+    real<lower=0, upper=40> Zrgmu ; 
+    real<lower=0, upper=40> Zbymu ; 
+    real<lower=0.001, upper=2> wAcRmu ; 
+    real<lower=0.001, upper=2> wAcBmu ; 
+    real<lower=0.001, upper=2> wRgAmu ; 
+    real<lower=0.001, upper=2> wRgBmu ; 
+    real<lower=0.001, upper=2> wByAmu ; 
+    real<lower=0.001, upper=2> wByRmu ;
+
+    real<lower=0> Zacsigma ;    
+    real<lower=0> Zrgsigma ;    
+    real<lower=0> Zbysigma ;    
+    real<lower=0> wAcRsigma ;
+    real<lower=0> wAcBsigma ;
+    real<lower=0> wRgAsigma ;
+    real<lower=0> wRgBsigma ;
+    real<lower=0> wByAsigma ;
+    real<lower=0> wByRsigma ;
+  }
+  model {
+    Zacmu ~ normal( 10 , 5 ) ;
+    Zrgmu ~ normal( 10 , 5 ) ;
+    Zbymu ~ normal( 10 , 5 ) ;
+    wAcRmu ~ normal( 0.5 , 0.3 ) ;
+    wAcBmu ~ normal( 0.5 , 0.3 ) ;
+    wRgAmu ~ normal( 0.5 , 0.3 ) ;
+    wRgBmu ~ normal( 0.5 , 0.3 ) ;
+    wByAmu ~ normal( 0.5 , 0.3 ) ;
+    wByRmu ~ normal( 0.5 , 0.3 ) ;
+    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    Zacsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
+    Zrgsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
+    Zbysigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
+    wAcRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wAcBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wRgAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wRgBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wByAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wByRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+
+    Zac ~ normal( Zacmu , Zacsigma ) ; // vectorized
+    Zrg ~ normal( Zrgmu , Zrgsigma ) ; // vectorized
+    Zby ~ normal( Zbymu , Zbysigma ) ; // vectorized
+    wAcR ~ normal( wAcRmu , wAcRsigma ) ; // vectorized
+    wAcB ~ normal( wAcBmu , wAcBsigma ) ; // vectorized
+    wRgA ~ normal( wRgAmu , wRgAsigma ) ; // vectorized
+    wRgB ~ normal( wRgBmu , wRgBsigma ) ; // vectorized
+    wByA ~ normal( wByAmu , wByAsigma ) ; // vectorized
+    wByR ~ normal( wByRmu , wByRsigma ) ; // vectorized
+
+    for ( i in 1:Ntotal ) {
+
+    real Lt ;
+    real Rt ;
+    real Ln ;
+    real Rn ;
+    real targresp ;
+    real nullresp ;
+    real dprime ;
+
+    if (c[i]==1) { // achromatic detection condition
+    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
+    Rt = 0 ;
+    Ln = 0 ;
+    Rn = 0 ;
+
+    targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
+    nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;
+
+    }
+
+    if (c[i]==2) { // red/green detection condition
+    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
+    Rt = 0 ;
+    Ln = 0 ;
+    Rn = 0 ;
+
+    targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
+    nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;
+
+    }
+
+    if (c[i]==3) { // blue/yellow detection condition
+    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
+    Rt = 0 ;
+    Ln = 0 ;
+    Rn = 0 ;
+
+    targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
+    nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;
+
+    }
+
+    if (c[i]==4) { // achromatic target, achromatic mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
+      Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
+      Ln = 0 ;
+      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;
+
+    }
+
+    if (c[i]==5) { // red/green target, achromatic mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wRgA[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
+    }
+
+    if (c[i]==6) { // blue/yellow target, achromatic mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wByA[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
+    }
+
+    if (c[i]==7) { // achromatic target, red/green mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wAcR[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;
+
+    }
+
+    if (c[i]==8) { // red/green target, red/green mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
+      Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
+      Ln = 0 ;
+      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
+    }
+
+    if (c[i]==9) { // blue/yellow target, red/green mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wByR[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
+    }
+
+     if (c[i]==10) { // achromatic target, blue/yellow mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wAcB[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;
+
+    }
+
+    if (c[i]==11) { // red/green target, blue/yellow mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wRgB[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
+    }
+
+    if (c[i]==12) { // blue/yellow target, blue/yellow mask
+      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
+     Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
+      Ln = 0 ;
+      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;
+
+      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
+      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
+    }
+
+    dprime = (targresp-nullresp)/0.23 ;
+    if (is_nan(dprime)){
+       dprime = 0;
+    }
+    if (is_inf(dprime)){
+       dprime = 10;
+    }
+    if (dprime > 10){
+       dprime = 10;
+    }    
+    ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;
+    }
+  }  
+" # close quote for modelString
+
+```
+
+```{r domodellingstan, include=FALSE}
+
+if (processdata==2){
+
+numSavedSteps <- nsamples    # total number of MCMC steps
+options(mc.cores=ncores)
 
@@
 allstanparams <- matrix(0,nrow=4,ncol=7)
+upperstanparams <- matrix(0,nrow=4,ncol=7)
+lowerstanparams <- matrix(0,nrow=4,ncol=7)
 
@@
   allsamples[expt,7,] <- klist
+
+  # quants <- quantile(wlist,probs=c(0.025,0.975))
+  # i <- which.min(abs(wlist-quants[1]))
+  # lowerstanparams[expt,] <- allsamples[expt,,i]
+  # i <- which.min(abs(wlist-quants[2]))
+  # upperstanparams[expt,] <- allsamples[expt,,i]
 }
@@
 if (processdata>0){
-
-nrandomdraws <- 200
 
@@
 
-  paramorder <- c('p','q','m','w','S','Z','k')
+  paramorder <- c('p','q','m',expression(omega),'S','Z','k')
   paramvalorder <- c(1,2,3,6,4,5,7)
 
-  xstart <- c(1,1,1/2,1/2,1/4,1/32,1/16)
+  xstart <- c(1,1,1/2,1/2,1/4,1/64,1/16)
   xstartdB <- round(20*log10(xstart))
@@
     if (param>5){ticklabelsx <- c('1/16','1/8','1/4','1/2','1')}
-    if (param==6){ticklabelsx <- c('1/32','1/8','1/2','2','8')}
+    if (param==6){ticklabelsx <- c('1/64','1/16','1/4','1','4')}
 
@@
 
-paneltitles <- c('Achromatic grating','Red/green grating','Blue/yellow grating','Flickering disc')
+paneltitles <- c('(a) Achromatic grating','(b) Red/green grating','(c) Blue/yellow grating','(d) Flickering disc')
 
   for (expt in 1:4){
+    print(expt)
   pedlist <- -12:36
@@
   allpred <- array(0,dim=c(4,length(pedlist)))
-  allrandomdips <- array(0,dim=c(nrandomdraws,4,length(pedlist)))
-  drawindices <- sample(dim(allsamples)[3],nrandomdraws,replace=FALSE)
+  # upperpred <- array(0,dim=c(4,length(pedlist)))
+  # lowerpred <- array(0,dim=c(4,length(pedlist)))
   for (cond in 1:4){
@@
       allpred[cond,pedlev] <- discriminate(allstanparams[expt,],pedlevelsC[pedlev],cond)
-
-      for (n in 1:nrandomdraws){
-        allrandomdips[n,cond,pedlev] <- discriminate(allsamples[expt,,drawindices[n]],pedlevelsC[pedlev],cond)
-      }
-    }
-  }
-  allrandomdips <- 20*log10(allrandomdips)
+      # upperpred[cond,pedlev] <- discriminate(upperstanparams[expt,],pedlevelsC[pedlev],cond)
+      # lowerpred[cond,pedlev] <- discriminate(lowerstanparams[expt,],pedlevelsC[pedlev],cond)
+    }
+  }
 
@@
   allpreddB <- 20*log10(allpred)
+  # lowerpreddB <- 20*log10(lowerpred)
+  # upperpreddB <- 20*log10(upperpred)
 
@@
 
-    for (n in 1:nrandomdraws){
-      lines(pedlist,allrandomdips[n,cond,],col=addalpha(collist[cond],2/nrandomdraws),lwd=2)
-    }
-
+    # polygon(pedlist[c(1:length(pedlist),length(pedlist):1)],c(lowerpreddB[cond,],upperpreddB[cond,length(pedlist):1]),border=NA,col=addalpha(collist[cond],alpha=0.2))
     lines(pedlist,allpreddB[cond,],col=collist[cond],lwd=2)
@@
   }
-  text(-9,33,paste0('(',letters[expt],')'),cex=2)
+  # text(-9,33,paste0('(',letters[expt],')'),cex=2)
   # legend(-12,42,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
@@
 
-}
-
-```
-
-```{r plotexampledips, include=FALSE}
-
-if (processdata>0){
-
-  window <- make_soft_window(256,256)
-  grating <- mkgrating(256,3,90,0,1)
-  stim1 <- (1+(0.5*window*grating))/2
-  stim2 <- (1+(0.25*window*grating))/2
-  stim3 <- (1+(0.75*window*grating))/2
-
-pdf(paste0('Figures/exampledips.pdf'),width=12,height=6.5)
-
-par(mfrow=c(1,2))
-
-  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,4), ylim=c(0,4))
-
-ticklocsx <- seq(0.5,3.5,1)
-ticklabelsx <- c('Left eye','Right eye','Left eye','Right eye')
-ticklocsy <- c(0.5,1.38,1.62,2.5,3.5)
-ticklabelsy <- c('Dichoptic','binocular','Half-','Binocular','Monocular')
-
-  mtext(text = c('Pedestal only','Pedestal + Target'), cex=1.5, side = 3, at=c(1,3), line=0)  
-  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0)   
-  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0, las=1)
-
-  polygon(c(0,4,4,0),c(0,0,4,4),border=NA,col=rgb(0.5,0.5,0.5))
-
-  rasterImage(stim1,0.2,3.2,0.8,3.8)
-  rasterImage(stim1,0.2,2.2,0.8,2.8)
-  rasterImage(stim1,1.2,2.2,1.8,2.8)
-  rasterImage(stim1,0.2,1.2,0.8,1.8)
-  rasterImage(stim1,1.2,1.2,1.8,1.8)
-  rasterImage(stim1,1.2,0.2,1.8,0.8)
-
-  rasterImage(stim3,2.2,3.2,2.8,3.8)
-  rasterImage(stim3,2.2,2.2,2.8,2.8)
-  rasterImage(stim3,3.2,2.2,3.8,2.8)
-  rasterImage(stim3,2.2,1.2,2.8,1.8)
-  rasterImage(stim1,3.2,1.2,3.8,1.8)
-  rasterImage(stim2,2.2,0.2,2.8,0.8)
-  rasterImage(stim1,3.2,0.2,3.8,0.8)
-
-  lines(c(0,4),c(0,0),lwd=3)
-  lines(c(0,4),c(4,4),lwd=3)
-  lines(c(0,0),c(0,4),lwd=3)
-  lines(c(4,4),c(0,4),lwd=3)
-
-  lines(c(0,4),c(1,1),lwd=1.5)
-  lines(c(0,4),c(2,2),lwd=1.5)
-  lines(c(0,4),c(3,3),lwd=1.5)
-
-  lines(c(1,1),c(0,4),lwd=1.5)
-  lines(c(2,2),c(0,4),lwd=3)
-  lines(c(3,3),c(0,4),lwd=1.5)
-
-collist <- c('red','blue','orange','darkgreen')
-
-ticklocsx <- seq(-12,36,6)
-ticklabelsx <- c('0','1/2','1','2','4','8','16','32','64')
-ticklocsy <- seq(-12,36,6)
-ticklabelsy <- c('1/4','1/2','1','2','4','8','16','32','64')
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,36))   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0)     
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-pedlist <- -12:36
-pedlevelsC <- 10^(pedlist/20)
-pedlevelsC[1] <- 0
-exampledip <- array(0,dim=c(4,length(pedlist)))
-  for (cond in 1:4){
-    for (pedlev in 1:length(pedlist)){
-      exampledip[cond,pedlev] <- discriminate(c(7.8,6.5,1.3,1,0.1,1,0.2),pedlevelsC[pedlev],cond)
-    }
-  }
-
-exampledipdB <- 20*log10(exampledip)
-
-for (cond in 1:4){
-  lines(pedlist,exampledipdB[cond,],col=collist[cond],lwd=3)
-}
-
-legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),lwd=3,col=collist,box.lwd=2,cex=1.5)
-
-  dev.off()
 }
@@
 
+```{r domodellingMCS, include=FALSE}
+
+if (processdata==2){
+
+numSavedSteps <- nsamples    # total number of MCMC steps
+options(mc.cores=ncores)
+
+# Translate to C++ and compile to DSO:
+mcsmodel <- stan_model(model_code=crossmodelString)
+
+ex2data <- read.csv('local/Experiment2.csv')
+
+sublist <- unique(ex2data$Subject)
+targetlist <- unique(ex2data$TargetType)
+pedlist <- unique(ex2data$PedestalType)
+pedlist <- pedlist[c(4,1,3,2)]  # reorder to make life easier later
+
+counter <- 0
+datasetcounter <- 0
+ntrials <- NULL
+ncorrect <- NULL
+subjects <- NULL
+datasets <- NULL
+conditions <- NULL
+pedestals <- NULL
+targets <- NULL
+
+for (s in 1:3){
+    datasetcounter <- datasetcounter + 1
+    conditioncounter <- 0
+    for (pedtype in 1:4){
+    for (targtype in 1:3){
+      conditioncounter <- conditioncounter + 1
+      thiscond <- subset(ex2data,Subject==sublist[s] & TargetType==targetlist[targtype] & PedestalType==pedlist[pedtype])
+
+        pedcont <- sort(unique(thiscond$PedestalContrast))
+        targconts <- sort(unique(thiscond$TargetContrast))
+
+        for (t in 1:length(targconts)){
+          counter <- counter + 1
+          thislevel <- subset(thiscond,TargetContrast==targconts[t])
+          ntrials[counter] <- nrow(thislevel)
+          ncorrect[counter] <- sum(thislevel$IsCorrect)
+          subjects[counter] <- s
+          datasets[counter] <- datasetcounter
+          conditions[counter] <- conditioncounter
+          pedestals[counter] <- pedcont
+          targets[counter] <- targconts[t]
+
+      }
+    }
+  }
+}
+
+thisexpt <- data.frame(datasets,subjects,conditions,pedestals,targets,ntrials,ncorrect)
+
+dataList = list(ncorrect = thisexpt$ncorrect, ntrials = thisexpt$ntrials, PedestalContrast = thisexpt$pedestals, TargetContrast = thisexpt$targets, c = thisexpt$conditions, s = thisexpt$subjects, Ndatasets = length(unique(thisexpt$subjects)), Ntotal = nrow(thisexpt))
+
+# Get MC sample of posterior:
+stanFit <- sampling(object=mcsmodel, 
+                    data = dataList, 
+                    chains = nChains,
+                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
+                    warmup = burnInSteps, 
+                    thin = thinSteps,
+                    cores = getOption("mc.cores", 1L))
+
+save(file=paste0('local/MCSfit.RData'),list=c('stanFit'))
+
+}
+
+```
+
+```{r plotMCSstan, include=FALSE}
+
+getmodelresp3inputs <- function(p,La,Ra,Lr,Rr,Lb,Rb){
+
+  maxlength <- max(length(La),length(Ra),length(Lr),length(Rr),length(Lb),length(Rb))
+  resp <- matrix(0,nrow=3,ncol=maxlength)
+
+  LrespA <- (La^1.21)/(1.03 + La + Ra + p[4]*Rr + p[5]*Rb)
+  RrespA <- (Ra^1.21)/(1.03 + Ra + La + p[4]*Lr + p[5]*Lb)
+  LrespR <- (Lr^1.21)/(1.03 + Lr + p[6]*Ra + Rr + p[7]*Rb)
+  RrespR <- (Rr^1.21)/(1.03 + Rr + p[6]*La + Lr + p[7]*Lb)
+  LrespB <- (Lb^1.21)/(1.03 + Lb + p[8]*Ra + p[9]*Rr + Rb)
+  RrespB <- (Rb^1.21)/(1.03 + Rb + p[8]*La + p[9]*Lr + Lb)
+
+  bs <- LrespA + RrespA
+  resp[1,] <- (bs^7.82)/(p[1] + bs^6.4)
+
+  bs <- LrespR + RrespR
+  resp[2,] <- (bs^7.82)/(p[2] + bs^6.4)
+
+  bs <- LrespB + RrespB
+  resp[3,] <- (bs^7.82)/(p[3] + bs^6.4)
+
+return(resp)}
+
+predictpmfs <- function(p){
+
+  contrastsC <- 10^(targetcontsdB/20)
+  pmfout <- matrix(0,nrow=12,ncol=length(contrastsC))
+
+  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
+  dprime <- (tr[1,] - nr[1,])/0.23
+  pmfout[1,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
+  dprime <- (tr[2,] - nr[2,])/0.23
+  pmfout[2,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,0)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
+  dprime <- (tr[3,] - nr[3,])/0.23
+  pmfout[3,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,contrastsC,16,0,0,0,0)
+  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
+  dprime <- (tr[1,] - nr[1,])/0.23
+  pmfout[4,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,16,contrastsC,0,0,0)
+  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
+  dprime <- (tr[2,] - nr[2,])/0.23
+  pmfout[5,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,16,0,0,contrastsC,0)
+  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
+  dprime <- (tr[3,] - nr[3,])/0.23
+  pmfout[6,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,contrastsC,0,0,64,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
+  dprime <- (tr[1,] - nr[1,])/0.23
+  pmfout[7,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,contrastsC,64,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
+  dprime <- (tr[2,] - nr[2,])/0.23
+  pmfout[8,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,0,64,contrastsC,0)
+  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
+  dprime <- (tr[3,] - nr[3,])/0.23
+  pmfout[9,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,64)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
+  dprime <- (tr[1,] - nr[1,])/0.23
+  pmfout[10,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,64)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
+  dprime <- (tr[2,] - nr[2,])/0.23
+  pmfout[11,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,64)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
+  dprime <- (tr[3,] - nr[3,])/0.23
+  pmfout[12,] <- 100*pnorm(dprime/sqrt(2))
+
+return(pmfout)}
+
+load('local/MCSdata.RData')
+meanslopesMCS <- apply(slopematrix,c(2,3),mean)
+meanslopesMCS <- round(10^(meanslopesMCS/20),digits=2)
+
+load('local/MCSfit.RData')
+draws <- extract(stanFit)
+Zac <- mean(draws$Zacmu)
+Zrg <- mean(draws$Zrgmu)
+Zby <- mean(draws$Zbymu)
+wAcR <- mean(draws$wAcRmu)
+wAcB <- mean(draws$wAcBmu)
+wRgA <- mean(draws$wRgAmu)
+wRgB <- mean(draws$wRgBmu)
+wByA <- mean(draws$wByAmu)
+wByR <- mean(draws$wByRmu)
+
+Zaclist <- draws$Zacmu
+Zrglist <- draws$Zrgmu
+Zbylist <- draws$Zbymu
+wAcRlist <- draws$wAcRmu
+wAcBlist <- draws$wAcBmu
+wRgAlist <- draws$wRgAmu
+wRgBlist <- draws$wRgBmu
+wByAlist <- draws$wByAmu
+wByRlist <- draws$wByRmu
+
+if (processdata>0){
+
+propcorr <- apply(MCSpropcorr,2:3,mean)
+contrastsdB <- contrastsdB[1,,]
+
+targetcontsdB <<- seq(-12,42,1)
+allpmfpreds <- predictpmfs(c(Zac,Zrg,Zby,wAcR,wAcB,wRgA,wRgB,wByA,wByR))
+
+ticklocsx <- seq(-12,42,6)
+ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64','128')
+ticklocsy <- seq(0,100,25)
+ticklabelsy <- ticklocsy
+
+titlelist <- c('(a) Achromatic target','(b) R/G target','(c) B/Y target')
+
+    pdf(paste0('Figures/MCSmodel.pdf'),width=12,height=8)
+
+    par(mfrow=c(2,3))
+    # layout(matrix(c(1,1,2,2,3,3,0,4,4,5,5,0),2,6,byrow=TRUE))
+
+  for (cond in 1:3){
+
+  par(pty="s")
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,42), ylim=c(0,100))  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5)     # add the tick labels
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+  title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+  title(ylab="Percent correct", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+  title(main=titlelist[cond],cex.main=2)
+
+  lines(c(-12,42),c(50,50),lty=2)
+
+  lines(targetcontsdB,allpmfpreds[cond,],lwd=3)
+  # lines(targetcontsdB,allmodelpreds[cond,],lwd=3)
+  # points(contrastsdB[cond,],propcorr[cond,],pch=21,lwd=3,cex=2,bg='black')
+
+  lines(targetcontsdB,allpmfpreds[cond+3,],lwd=3,lty=2)
+  # lines(targetcontsdB,allmodelpreds[cond+3,],lwd=3,lty=2)
+  # points(contrastsdB[cond+3,],propcorr[cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
+
+  lines(targetcontsdB,allpmfpreds[cond+6,],lwd=3,col='red')
+  lines(targetcontsdB,allpmfpreds[cond+6,],lwd=3,col='green',lty=2)
+  # lines(targetcontsdB,allmodelpreds[cond+6,],lwd=3,col='red')
+  # lines(targetcontsdB,allmodelpreds[cond+6,],lwd=3,col='green',lty=2)
+  # points(contrastsdB[cond+6,],propcorr[cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
+
+  lines(targetcontsdB,allpmfpreds[cond+9,],lwd=3,col='cornflowerblue')
+  lines(targetcontsdB,allpmfpreds[cond+9,],lwd=3,col='gold',lty=2)     
+  # lines(targetcontsdB,allmodelpreds[cond+9,],lwd=3,col='cornflowerblue')
+  # lines(targetcontsdB,allmodelpreds[cond+9,],lwd=3,col='gold',lty=2)         
+  # points(contrastsdB[cond+9,],propcorr[cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
+
+  # text(18,10,paste(ntrials[1],'trials/level'),pos=4)
+
+  # legend(-2,40,c('Target only','Achromatic mask','R/G mask','B/Y mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)
+
+  }
+
+  par(pty="s")
+
+plotlims <- c(0.5,3.5,0.5,3.5)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocs <- seq(1,3)    # locations of tick marks on x axis
+ticklabels <- c('ACH','R/G','B/Y')
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabels, side = 1, at=ticklocs,line=0.5) 
+mtext(text = ticklabels, side = 2, at=ticklocs, line=0.2, las=1) 
+title(xlab="Target", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Mask", col.lab=rgb(0,0,0), line=2.5, cex.lab=1.5)
+title(main='(d) Suppressive weights',cex.main=2)
+
+weightmatrix <- matrix(1,nrow=3,ncol=3)
+weightmatrix[1,2] <- wAcR
+weightmatrix[1,3] <- wAcB
+weightmatrix[2,1] <- wRgA
+weightmatrix[2,3] <- wRgB
+weightmatrix[3,1] <- wByA
+weightmatrix[3,2] <- wByR
+
+ramp3 <- colorRamp(c("white","darkorange"))  # create a ramp from one colour to another
+colmatrix3 <- rgb(ramp3(seq(0, 1, length = 101)), max = 255)
+image(1:3,1:3,weightmatrix,zlim=c(0,1),col=colmatrix3,add=TRUE,useRaster=FALSE)
+
+contrastmatrix <- matrix(c(16,16,16,64,64,64,64,64,64),nrow=3,ncol=3)
+denommatrix <- round(weightmatrix*contrastmatrix,digits=2)
+weightmatrix <- round(weightmatrix,digits=2)
+
+counter <- 0
+for (x in 1:3){
+  for (y in 1:3){
+    text(x,y+0.1,weightmatrix[x,y],cex=1.6)
+    text(x,y-0.1,paste0('(',denommatrix[x,y],')'),cex=1.6)
+  }
+}
+
+    ticklocsx <- seq(-42,6,12)
+    ticklabelsx <- c('1/128','1/32','1/8','1/2','2')
+
+    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-42,6), ylim=c(0,1))
+    axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+
+    mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)
+    title(main='(e) Posterior distributions',cex.main=2)
+    title(xlab=expression(omega), col.lab=rgb(0,0,0), line=1.5, cex.lab=2.5)
+
+    svals <- 20*log10(wAcRlist)
+    a <- density(svals)
+    a$y <- a$y/max(a$y)
+    polygon(a$x,a$y,border=NA,col=addalpha('red',alpha=0.25))
+    lines(a$x,a$y,col='black',lwd=2)
+
+    svals <- 20*log10(wAcBlist)
+    a <- density(svals)
+    a$y <- a$y/max(a$y)
+    polygon(a$x,a$y,border=NA,col=addalpha('cornflowerblue',alpha=0.25))
+    lines(a$x,a$y,col='black',lwd=2)
+
+    svals <- 20*log10(wRgAlist)
+    a <- density(svals)
+    a$y <- a$y/max(a$y)
+    polygon(a$x,a$y,border=NA,col=addalpha('black',alpha=0.25))
+    lines(a$x,a$y,col='red',lwd=2)
+
+    svals <- 20*log10(wRgBlist)
+    a <- density(svals)
+    a$y <- a$y/max(a$y)
+    polygon(a$x,a$y,border=NA,col=addalpha('cornflowerblue',alpha=0.25))
+    lines(a$x,a$y,col='red',lwd=2)
+
+    svals <- 20*log10(wByAlist)
+    a <- density(svals)
+    a$y <- a$y/max(a$y)
+    polygon(a$x,a$y,border=NA,col=addalpha('black',alpha=0.25))
+    lines(a$x,a$y,col='cornflowerblue',lwd=2)
+
+    svals <- 20*log10(wByRlist)
+    a <- density(svals)
+    a$y <- a$y/max(a$y)
+    polygon(a$x,a$y,border=NA,col=addalpha('red',alpha=0.25))
+    lines(a$x,a$y,col='cornflowerblue',lwd=2)
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  legend(0,1,c('Target only','Achromatic mask','R/G mask','B/Y mask'), lwd=3, col=c('black','black','red','cornflowerblue'),cex=1.9,box.lwd=2)
+
+    legend(0,1,c('Target only','Achromatic mask','R/G mask','B/Y mask'), lty=2, lwd=3, col=c('black','white','green','gold'),cex=1.9,box.lwd=2)
+
+  legend(0.05,0.5,c('Ach target, R/G mask','Ach target, B/Y mask','R/G target, Ach mask','R/G target, B/Y mask','B/Y target, Ach mask','B/Y target, R/G mask'), lwd=3, pch=22, col=c('black','black','red','red','cornflowerblue','cornflowerblue'),pt.bg=addalpha(c('red','cornflowerblue','black','cornflowerblue','black','red'),alpha=0.5),lty=NA,pt.cex=2,cex=1.5,box.lwd=2)
+
+  dev.off()
+
+}
+
+```
+
+```{r plotexampledips, include=FALSE}
+
+if (processdata>0){
+
+  window <- make_soft_window(256,256)
+  grating <- mkgrating(256,3,90,0,1)
+  stim1 <- (1+(0.5*window*grating))/2
+  stim2 <- (1+(0.25*window*grating))/2
+  stim3 <- (1+(0.75*window*grating))/2
+
+pdf(paste0('Figures/exampledips.pdf'),width=12,height=6.5)
+
+par(mfrow=c(1,2))
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,4), ylim=c(0,4))
+
+ticklocsx <- seq(0.5,3.5,1)
+ticklabelsx <- c('Left eye','Right eye','Left eye','Right eye')
+ticklocsy <- c(0.5,1.38,1.62,2.5,3.5)
+ticklabelsy <- c('Dichoptic','binocular','Half-','Binocular','Monocular')
+
+  mtext(text = c('Pedestal only','Pedestal + Target'), cex=1.5, side = 3, at=c(1,3), line=0)  
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0)   
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0, las=1)
+
+  polygon(c(0,4,4,0),c(0,0,4,4),border=NA,col=rgb(0.5,0.5,0.5))
+
+  rasterImage(stim1,0.2,3.2,0.8,3.8)
+  rasterImage(stim1,0.2,2.2,0.8,2.8)
+  rasterImage(stim1,1.2,2.2,1.8,2.8)
+  rasterImage(stim1,0.2,1.2,0.8,1.8)
+  rasterImage(stim1,1.2,1.2,1.8,1.8)
+  rasterImage(stim1,1.2,0.2,1.8,0.8)
+
+  rasterImage(stim3,2.2,3.2,2.8,3.8)
+  rasterImage(stim3,2.2,2.2,2.8,2.8)
+  rasterImage(stim3,3.2,2.2,3.8,2.8)
+  rasterImage(stim3,2.2,1.2,2.8,1.8)
+  rasterImage(stim1,3.2,1.2,3.8,1.8)
+  rasterImage(stim2,2.2,0.2,2.8,0.8)
+  rasterImage(stim1,3.2,0.2,3.8,0.8)
+
+  lines(c(0,4),c(0,0),lwd=3)
+  lines(c(0,4),c(4,4),lwd=3)
+  lines(c(0,0),c(0,4),lwd=3)
+  lines(c(4,4),c(0,4),lwd=3)
+
+  lines(c(0,4),c(1,1),lwd=1.5)
+  lines(c(0,4),c(2,2),lwd=1.5)
+  lines(c(0,4),c(3,3),lwd=1.5)
+
+  lines(c(1,1),c(0,4),lwd=1.5)
+  lines(c(2,2),c(0,4),lwd=3)
+  lines(c(3,3),c(0,4),lwd=1.5)
+
+collist <- c('red','blue','orange','darkgreen')
+
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c('0','1/2','1','2','4','8','16','32','64')
+ticklocsy <- seq(-12,36,6)
+ticklabelsy <- c('1/4','1/2','1','2','4','8','16','32','64')
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,36))   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+pedlist <- -12:36
+pedlevelsC <- 10^(pedlist/20)
+pedlevelsC[1] <- 0
+exampledip <- array(0,dim=c(4,length(pedlist)))
+  for (cond in 1:4){
+    for (pedlev in 1:length(pedlist)){
+      exampledip[cond,pedlev] <- discriminate(c(7.8,6.5,1.3,1,0.1,1,0.2),pedlevelsC[pedlev],cond)
+    }
+  }
+
+exampledipdB <- 20*log10(exampledip)
+
+for (cond in 1:4){
+  lines(pedlist,exampledipdB[cond,],col=collist[cond],lwd=3)
+}
+
+legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),lwd=3,col=collist,box.lwd=2,cex=1.5)
+
+  dev.off()
+
+fundamentals <- read.csv('local/fundamentals.csv')
+phosphors <- read.csv('local/phosphors.csv')
+
+achromatic <- (1+(window*grating))/2
+
+theta <- 135*pi/180
+stimLMS <- c(cos(theta), sin(theta), 0)
+rgbvals <- lms2rgb(phosphors,fundamentals,stimLMS)
+rgbvals <- rgbvals/max(abs(rgbvals))
+
+RGstim <- array(0,dim=c(256,256,3))
+RGstim[,,1] <- (1+(rgbvals[1]*window*grating))/2 
+RGstim[,,2] <- (1+(rgbvals[2]*window*grating))/2 
+RGstim[,,3] <- (1+(rgbvals[3]*window*grating))/2
+
+theta <- 90*pi/180
+stimLMS <- c(cos(theta), cos(theta), sin(theta))
+rgbvals <- lms2rgb(phosphors,fundamentals,stimLMS)
+rgbvals <- rgbvals/max(abs(rgbvals))
+
+BYstim <- array(0,dim=c(256,256,3))
+BYstim[,,1] <- (1+(rgbvals[1]*window*grating))/2 
+BYstim[,,2] <- (1+(rgbvals[2]*window*grating))/2 
+BYstim[,,3] <- (1+(rgbvals[3]*window*grating))/2
+
+t <- seq(0,1,length=9)
+lummod <- sin(t*2*pi)
+discstim <- array(0,dim=c(length(t),256,256))
+
+for (i in 1:length(t)){
+  discstim[i,,] <- (1+(window*lummod[i]))/2
+}
+
+pdf(paste0('Figures/examplestim.pdf'),width=8,height=8.5)
+
+par(mar = c(4,1,1,1))
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,4), ylim=c(0,4))  
+axis(1, at=seq(0,4,4/5), tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+mtext(text = seq(0,250,50), side = 1, at=seq(0,4,4/5), line=0)     
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+rasterImage(achromatic,0,3,1,4)
+rasterImage(RGstim,1.5,3,2.5,4)
+rasterImage(BYstim,3,3,4,4)
+
+text(0.5,2.8,'Achromatic grating',adj=0.5,cex=1.5)
+text(2,2.8,'Red/green grating',adj=0.5,cex=1.5)
+text(3.5,2.8,'Blue/yellow grating',adj=0.5,cex=1.5)
+text(3,1.8,'Flickering disc (4Hz)',adj=0.5,cex=1.5)
+
+for (i in 1:length(t)){
+  rasterImage(discstim[i,,],0+(i-1)*(4/length(t)),2,0.4+(i-1)*(4/length(t)),2.4)
+}
+
+t <- seq(0,1,length=100)
+lummod <- sin(t*2*pi)
+lines(t*4,0.8*lummod+0.9,lwd=3)
+
+dev.off()
+
+}
+
+```
+
 ```{r plotindividual, include=FALSE}
@@
 However, the majority of this work has used achromatic (black and white) stimuli; we know comparatively little about how chromatic signals are combined binocularly, or about how signals in different ocular and chromatic channels interact.
-In this study we use psychophysical detection and discrimination paradigms to explore binocular interactions in the chromatic pathways.
+In this study we use psychophysical detection and discrimination paradigms to explore binocular interactions within and between the chromatic and achromatic pathways.
 
@@
 In the monocular condition, participants must discriminate between stimuli of two contrasts (a 'pedestal', and a 'pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance.
-In the binocular condition, the same stimuli are shown to both eyes.
+Threshold is defined as the minimum target contrast required to make this judgement with 75% accuracy.
+The binocular condition is the same, except that the same stimuli are shown to both eyes.
 In the half-binocular condition the pedestal is shown to both eyes, but the target increment shown only to one eye.
@@
 
-The detailed pattern of results across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
-At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition owing to physiological binocular summation by neurons responsive to signals from both eyes [@Baker2018; @Campbell1965].
+The detailed pattern of thresholds across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
+At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition; this result is attributed to physiological binocular summation by neurons responsive to signals from both eyes [@Baker2018; @Campbell1965].
 However at high pedestal contrasts the 'handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation [@Legge1984; @Maehara2005].
@@
 Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast in order to be detectable [@Legge1979; @Maehara2005; @Baker2007b].
-
-At the output of the human retina, visual signals are split into three distinct pathways.
+The characteristic pattern of dipper functions is well-described by the gain control model of @Meese2006 for achromatic stimuli.
+
+At the output of the human retina, cone responses are split into three distinct pathways.
 The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information, and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
@@
 There are also interactions between chromatic and achromatic pathways both within [@Chen2000] and between [@Mullen2014; @Kingdom2015] the eyes, yet these have not been fully explored for arrangements where the target and mask have the same orientation.
-Finally, the neurophysiological underpinnings of colour vision are distinct from the achromatic system.
+Finally, the neurophysiological underpinnings of colour vision are distinct from those of the achromatic system.
 In primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981].
@@
 
-Strong interocular normalization is well-established when using DC-balanced periodic stimuli such as sine-wave gratings [@Meese2006; @Baker2017; @Moradi2009].
-However there is some evidence that binocular combination is more linear for luminance increments [@Levelt1965; @Anstis1998], particularly against a dark background [@Baker2012].
-Our recent work has extended this finding to flickering discs of luminance, which are DC-balanced across time [@Segala2023].
-Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement, indicating that binocular combination rules may differ for temporal contrast.
+A further property of 'blob' regions is that they are less strongly orientation-tuned than other regions of V1 [@Horton1981; @Livingstone1984], and biased towards low spatial frequencies [@Edwards1995; @Tootell1988].
+Our recent work has investigated binocular combination for flickering discs of luminance, which are DC-balanced across time [@Segala2023].
+Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement.
+This is very different from the 'ocularity invariance' that is well-established when using DC-balanced periodic stimuli such as sine-wave gratings, and implies strong interocular suppression [@Meese2006; @Baker2017; @Moradi2009].
+There is additional psychophysical evidence from matching studies that binocular combination can be close to linear for luminance increments [@Levelt1965; @Anstis1998], particularly against a dark background [@Baker2012].
+Both structural and functional data therefore imply that binocular combination may differ between spatial and temporal contrast.
 
@@
 
-All experiments were completed by the first author (DHB) and two other participants, who differed for each experiment.
+All experiments were completed by the first author (DHB) and two additional participants, who differed for each experiment.
+Participants had no known abnormalities of binocular vision.
 Written informed consent was obtained before data collection began, and all procedures were approved by the ethics committee of the Department of Psychology at the University of York (ID number 2202).
@@
 
-In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg.
+In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg (see examples in Figure \@ref(fig:examplestim)).
 The gratings were windowed by a raised cosine envelope with a diameter of 3 degrees.
 Spatial phase, relative to a central fixation cross, was randomised on each trial across the four cardinal phases.
-In the achromatic conditions, the sine-wave modulated all three colour channels equally.
+In the achromatic conditions, the sine-wave modulated all three monitor colour channels equally (red, green and blue).
 In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant.
@@
 Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals [@Stockman2000].
-The stimuli in Experiment 3 were temporal modulations of luminance, using the same raised cosine envelope as described above, but with no further spatial modulation.
-The stimuli counterphase flickered sinusoidally at 4Hz.
+The stimuli in Experiment 3 were temporal modulations of luminance applied to a disc made using the same raised cosine envelope as described above, but with no further spatial modulation.
+The stimuli counterphase flickered sinusoidally at 4Hz (see examples in the lower portion of Figure \@ref(fig:examplestim)).
 In all experiments, we displayed a binocular fusion lock, consisting of three concentric rings of small square elements with random colour.
 A black central fixation cross was also displayed throughout.
+
+```{r examplestim, out.width = "50%", fig.cap="Example stimuli.
+Upper row shows grating stimuli used in Experiments 1 and 2.
+Lower row shows one cycle of sinusoidal flicker applied to a uniform disc.
+Note that the rendering of all stimuli will depend on the device used to display or print this image, and so the chromatic stimuli are unlikely to appear isoluminant, and there may be additional luminance nonlinearities that were not present in the stimuli displayed during the experiments.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/examplestim.pdf')
+
+```
 
@@
 For the isoluminant chromatic stimuli, the maximum displayable L-M (red/green) cone contrast was 0.1, and the maximum displayable S-(L+M) (blue/yellow) cone contrast was 0.88.
-So an L-M threshold of 50\% is a cone contrast of $0.5\times0.1 = 0.05$, and an S-(L+M) threshold of 50\% is a cone contrast of $0.5\times0.88 = 0.44$.
-The threshold values reported throughout can therefore be converted to cone contrast by a straightforward multiplicative transform.
+An L-M threshold of 50\% therefore corresponds to a cone contrast of $0.5\times0.1 = 0.05$, and an S-(L+M) threshold of 50\% corresponds to a cone contrast of $0.5\times0.88 = 0.44$.
+This means that the threshold values reported throughout can be converted to cone contrast by a straightforward multiplicative transform.
 
@@
 Before beginning primary data collection, each participant in Experiments 1 and 2 completed an isoluminance adjustment task.
-Stimuli were presented that counterphase flickered at 5Hz, defined about either the L-M or S-(L+M) plane in cone space.
+Grating stimuli were presented that counterphase flickered at 5Hz, defined about either the L-M or S-(L+M) plane in cone space.
 Participants used a trackball to dynamically adjust the colour angle of the stimulus to minimise the percept of flicker.
@@
 Each interval was indicated by an auditory beep, and participants made their responses using a two-button trackball.
-Correct trials were indicated by a high pitched tone, and incorrect trials by a low pitched tone.
+Correct responses were followed by a high pitched tone, and incorrect responses by a low pitched tone.
 Each block of the experiment tested a single pedestal contrast level, and lasted around 12 minutes.
 On each trial the target contrast level was determined by a 3-down-1-up staircase procedure.
-There were 8 interleaved staircases in total; four stimulus arrangements (see Figure \@ref(fig:exampledips)) by two target eye assignments.
+There were 8 interleaved staircases in total; four stimulus arrangements (see Figure \@ref(fig:exampledips)) combined factorially with two target eye assignments.
 Each pedestal contrast was repeated 3 times by each participant, and the block order was randomised.
@@
 Mask contrasts were chosen to be approximately 16 times their (monocular) detection threshold, based on the data from Experiment 1.
+As a percentage of the maximum displayable contrast, these were 16% for achromatic stimuli, and 64% for both of the chromatic stimuli.
 Each block of the experiment tested a single condition, and consisted of 200 trials.
@@
 \begin{equation}
-binresp = \frac{binsum^p}{Z + binsum^q},
+Stage2 = \frac{binsum^p}{Z + binsum^q},
 \end{equation}
@@
 where $C_L$ and $C_R$ are the contrasts displayed to the left and right eyes, and $m$, $S$, $\omega$, $p$, $q$ and $Z$ are free parameters in the model.
-A further free parameter, $k$, represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values.
-Thresholds are defined by adjusting the target contrast until the following equality is satisfied:
+A further free parameter, $k$, represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values (note that in the original model specification [@Meese2006] this parameter was called $\sigma$, but we use the $k$ symbol here to avoid confusion with the standard deviation of the cumulative Gaussian used when fitting the psychometric functions to derive thresholds).
+Thresholds are defined by iteratively adjusting the target contrast until the following equality is satisfied:
 
 \begin{equation}
-binresp_{target+pedestal} - binresp_{pedestal} = k,
+Stage2_{target+pedestal} - Stage2_{pedestal} = k,
 \end{equation}
@@
 \begin{equation}
-d' = \frac{binresp_{target+pedestal} - binresp_{pedestal}}{k}.
+d' = \frac{Stage2_{target+pedestal} - Stage2_{pedestal}}{k}.
 \end{equation}
@@
 four fits in total, as for the simplex fitting).
+Prior distributions were Gaussian, with means determined from published values (see first row of Table \@ref(tab:parametertable)).
 This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
 We generated over 1 million posterior samples for the model, and retained 10\% of them for plotting.
+
+Finally, we adapted the two stage model to include parallel pathways to process achromatic, red/green and blue/yellow stimuli, that mutually suppress each other.
+We added additional suppressive terms at the first (monocular) stage of the model, for example:
+
+\begin{equation}
+ACStage1_L = \frac{AC_L^m}{S + AC_L + \omega_A AC_R + \omega_R RG_R + \omega_B BY_R},
+\end{equation}
+
+where *AC* represents the achromatic contrast, *RG* represents the red/green contrast, *BY* represents the blue/yellow contrast, and $\omega_A$, $\omega_R$ and $\omega_B$ are the accompanying weights of interocular suppression.
+There is an equivalent expression for the right eye, and for each of the two isoluminant chromatic pathways.
+To simplify the model, and avoid free parameters that are poorly constrained by the data, we fixed several parameters at the average values from the fits from Experiment 1 (Table \@ref(tab:parametertable)), such that $p=7.82$, $q=6.4$, $m=1.21$, $S=1.03$ and $k=0.23$.
+We additionally fixed the within-mechanism weight of interocular suppression ($\omega$) at 1.
+This left 9 free parameters: a $Z$ parameter for each mechanism, and six cross-mechanism weights of interocular suppression.
+These parameters were again estimated within a Bayesian hierarchical framework, using the trial-wise data from Experiment 2.
+Note that the model as specified does not currently include monocular suppression between different pathways, as we did not collect any data for these conditions.
+Previous work [@Chen2000] has measured such interactions, and they could in principle be incorporated into the denominator of either stage 1 or stage 2 in the model.
 
@@
 Panel (a) shows the achromatic results, which replicate the key features from previous work.
-At detection threshold, binocular summation was a factor of `r round(10^(summation[1]/20),digits=2)` (`r round(summation[1],digits=2)`dB), consistent with previous reports [@Baker2018].
-Pedestal masking functions follow the typical 'dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
+At detection threshold, binocular summation was a factor of `r round(10^(summation[1]/20),digits=2)` (`r round(summation[1],digits=2)`dB), within the range ($\sqrt{2}$ to 2) consistent with previous reports [@Baker2018].
+Pedestal masking functions followed the typical 'dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
 The monocular and binocular dipper handles converge at high contrasts, whereas the half-binocular thresholds remain above the binocular thresholds across the full range of pedestal contrasts.
@@
 ```{r dipperfig, fig.cap="Dipper functions and psychometric slopes from Experiment 1, averaged across three participants.
-Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull beta units.
+Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull $\\beta$ units.
 Error bars give ±1SE across participants.
@@
 Following @Meese2006, we also inspected the slope of the psychometric function for each condition (see Figure \@ref(fig:dipperfig)d-f).
-At detection threshold, slopes were relatively steep, with $\beta$ values around 4.
+At detection threshold, slopes were relatively steep for all stimuli, with $\beta$ values around 4.
 As pedestal contrasts increased, slopes linearized and reduced to around $\beta=1.3$ [@Foley1981; @Meese2006], and remained shallow at high pedestal contrasts.
 The exception to this was the dichoptic condition, where slopes became extremely steep at high dichoptic mask contrasts, consistent with previous observations [@Meese2006; @Baker2013].
-This was clear for all three data sets, with slope values in the range $\beta=4$ to $\beta=8$.
-However, we note that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
-Our second experiment investigated the slope of the psychometric function in more detail using the method of constant stimuli.
+This was clear for all three data sets, with slope values in the range $4 < \beta < 8$.
+However, we observe that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
+Our second experiment therefore investigated the slope of the psychometric function in more detail for dichoptic masking using the method of constant stimuli.
 
@@
 Panel (g) shows the average threshold elevation factor for each combination of target and mask stimulus.
-Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull beta units.", fig.align="center", echo=FALSE}
+Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull $\\beta$ units.", fig.align="center", echo=FALSE}
 
@@
 We also calculated the slope of the psychometric function for each condition, in equivalent Weibull $\beta$ units.
-In the absence of a mask, the average slope was $\beta$ = `r round(10^(mean(detslopes)/20),digits=2)`, which is typical for contrast detection tasks.
+In the absence of a mask, the average slope was $\beta$ = `r round(10^(mean(detslopes)/20),digits=2)`, which is typical for contrast detection tasks [@Wallis2013].
 Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,1],meanslopesMCS[2,2],meanslopesMCS[3,3])))),digits=2)`).
@@
 This was motivated by our recent work [@Segala2023] that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
-The pattern of dipper functions for a 4Hz flickering disc (see Figure \@ref(fig:discdata)a) was very similar to that observed for achromatic gratings (see Figure \@ref(fig:dipperfig)a), and the binocular summation ratio at threshold was also similar (a factor of `r round(10^(summationDisc/20),digits=2)`).
+The pattern of dipper functions for a 4Hz flickering disc (see Figure \@ref(fig:discdata)a) was very similar to that observed for achromatic gratings (see Figure \@ref(fig:dipperfig)a), and the binocular summation ratio at threshold was also similar (a factor of `r round(10^(summationDisc/20),digits=2)` for discs, vs `r round(10^(summation[1]/20),digits=2)` for gratings).
 Threshold data for individual participants are shown in Figure \@ref(fig:individualdiscs).
-We also found a similar pattern of psychometric slope values (Figure \@ref(fig:discdata)b), though we note that the dichoptic condition did not produce the 'super-steep' psychometric functions we had observed in Experiments 1 & 2.
-Nevertheless, its slopes are somewhat above those of the other pedestal arrangements.
-
-```{r discdata, out.width = "80%", fig.cap="Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 3.", fig.align="center", echo=FALSE}
+We also found a similar pattern of psychometric slope values (Figure \@ref(fig:discdata)b) as we had for gratings, though we note that the dichoptic condition did not produce the 'super-steep' psychometric functions we had observed in Experiments 1 & 2.
+Nevertheless, the dichoptic slopes are somewhat above those of the other pedestal arrangements at high contrasts.
+
+```{r discdata, out.width = "80%", fig.cap="Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 4.", fig.align="center", echo=FALSE}
 
@@
 
-tableparams <- round(tableparams,digits=2)
+tableparams <- format(round(tableparams,digits=2),nsmall=2)
 
@@
 
-colnames(tableparams) <- c("p", "q", "m", "S", "Z", "w", "k", "RMSE", "Model fit")
+colnames(tableparams) <- c("p", "q", "m", "S", "Z", "$\\omega$", "k", "RMSE", "Model fit")
 tableparams$RMSE <- paste(tableparams$RMSE,'dB')
@@
 knitr::kable(tableparams, caption='Summary of fitted model parameters.
-The upper rows are best fitting parameters from simplex fits to the averaged thresholds for each experiment.
-The final row shows the posterior parameter estimates from the Bayesian model, fitted to data from Experiments 1 and 3.', align='lrrrrrrrr', booktabs = TRUE, linesep='',escape = FALSE) %>%
+The top row gives the best fitting parameters from the study of Meese et al.
+(2006).
+The second section shows the best fitting parameters from simplex fits to the averaged thresholds for each experiment.
+The final rows show the posterior parameter estimates from the Bayesian model, fitted to each data set from Experiments 1 and 3.', align='lrrrrrrrr', booktabs = TRUE, linesep='',escape = FALSE) %>%
 row_spec(c(1,6),hline_after=T) %>% row_spec(0,italic=T) %>% row_spec(c(0,2,7),bold=T)
@@
 Best fitting parameters are shown in the 'Simplex fits' section of Table \@ref(tab:parametertable).
-We note that in previous work, the weight of interocular suppression (*w* in the model) is implicitly fixed at 1.
-Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (0.89) for our flickering discs.
+We note that in previous work, the weight of interocular suppression ($\omega$ in the model) is implicitly fixed at 1.
+Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (`r round(allp[4,6],digits=2)`) for our flickering discs.
+The exponent values (*p* and *q*) for the red/green gratings are rather different from those of the other conditions.
+In previous work [@Meese2006] the second stage gain control nonlinearity (Equation 4) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper).
+The high value of *p* (`r round(allp[2,1], digits=2)`) is therefore likely to be compensating for the low value of *m* (`r round(allp[2,3], digits=2)`) at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty [@Pelli1985].
 
 We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
-This model was fit simultaneously to full trial-by-trial data from all participants who participated in a given experiment (i.e.
+This model was fit simultaneously to the full trial-by-trial data from all participants who participated in a given experiment (i.e.
 the model was fitted separately to each of the four dipper data sets).
@@
 The panels in the right and upper margins of Figure \@ref(fig:bayesianmodel) show posterior distributions for each model parameter.
-Note in particular that the posterior distribution for the weight of interocular suppression (*w*, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
-We note that the distribution for *w* in the flickering disc condition is somewhat lower than for the other three data sets.
-However this difference is not meaningful according to criteria such as comparing the 95% credible intervals of the distribution to a value of *w*=1.
+Note in particular that the posterior distribution for the weight of interocular suppression ($\omega$, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
+We note that the distribution for $\omega$ in the flickering disc condition is somewhat lower than for the other three data sets.
+However this difference is not meaningful according to criteria such as comparing the 95% credible intervals of the distribution to a value of $\omega=1$.
 
 ```{r bayesianmodel, fig.cap="Model predictions (a-d) and posterior parameters (top and right margin plots) for the hierarchical Bayesian model.
-Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates, and thin lines are from 200 random posterior draws.
+Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates.
 The probability density functions in the margin plots are peak-normalized, and shown for each of the four data sets in different colours (see legend in upper left plot).
-Distributions are generated from 1000000 samples per data set, using a Markov Chain Monte Carlo sampling algorithm.", fig.align="center", echo=FALSE}
+Distributions were generated from 1000000 samples per data set, using a Markov Chain Monte Carlo sampling algorithm.
+Note the logarithmic x-axis for all posterior plots.", fig.align="center", echo=FALSE}
 
@@
 
+Finally we fitted an extended model, that included interocular suppression between the different pathways, to the data of Experiment 2.
+Figure \@ref(fig:MCSmodel) shows the model curves (panels a-c), which correspond closely to the data in Figure \@ref(fig:MCSfig).
+One striking discrepancy is that the model predicts a region of negative d-prime for the case where the target and dichoptic mask have the same chromaticity (see the curved regions below 50\% correct).
+This feature was not generally present in our data, though it can be observed for one participant in Figure \@ref(fig:individualMCS)b,c.
+Our previous work [@Baker2013] has found evidence for this phenomenon (termed 'swan functions'), but it generally requires very high mask contrasts to be measurable empirically, and there may also be some individual differences; both factors might explain its absence here.
+
+Figure \@ref(fig:MCSmodel)d,e shows the model estimates for the weight of interocular suppression in each combination of target and mask chromaticity.
+Although the weights might appear to indicate that (excluding within-mechanism effects) suppression is strongest between blue/yellow targets and achromatic masks (a weight of 0.56), this is somewhat complicated by the differences in sensitivity and mask contrast between conditions.
+We selected mask contrasts that were approximately equal multiples ($16\times$) of their own detection thresholds, based on the data of Experiment 1 (Figure \@ref(fig:dipperfig)a-c).
+However the modelling expressed these contrasts as a percentage of the maximum contrast that it was possible to display on the monitor (see Procedures).
+The values in brackets in Figure \@ref(fig:MCSmodel)d indicate the overall suppressive term on the denominator, calculated by multiplying the mask contrast by the fitted weight.
+These values indicate that the strongest suppression is instead between red/green targets and blue/yellow masks, consistent with the threshold elevation observed empirically (Figure \@ref(fig:MCSfig)g).
+In principle it would be possible to repeat this modelling using either cone contrast values, or contrast expressed relative to detection threshold, which would require re-fitting the model.
+
+```{r MCSmodel, fig.cap="Summary of the model fit to the data of Experiment 2.
+Panels (a-c) show model psychometric functions in the same format as those in Figure 5.
+Panel (d) shows the fitted suppressive weights ($\\omega$ values), with values in brackets indicating the combined suppressive denominator term calculated by multiplying together the suppressive weight and the dichoptic mask contrast.
+Panel (e) shows the posterior distributions for each weight parameter.
+The lower right plot gives the legends for the upper row (top) and the posterior distributions in panel (e).", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/MCSmodel.pdf')
+
+```
+
 # Discussion
@@
 - Binocular combination of isoluminant chromatic stimuli is similar to that for achromatic stimuli
-- Interocular suppression is strongest within a chromatic pathway, and weakest between achromatic and chromatic pathways
-- Binocular combination occurs similarly for temporal and temporal luminance modulations
-
-We now discuss the relationship to previous work, consider the likely physiological substrates of these effects and .
+- Interocular suppression is strongest within a post-retinal pathway, and weakest between achromatic and chromatic pathways
+- Binocular combination occurs similarly for spatial and temporal luminance modulations
+
+We now discuss the relationship to previous work, and consider the likely physiological substrates of these effects.
+
+## Summation at threshold
+
+Estimates of the binocular summation ratio at threshold fell within the range $\sqrt{2}$ to 2 for all four data sets.
+Consistent with previous reports [@Simmons2005], summation was slightly higher for chromatic versus achromatic stimuli, but fell short of perfect linear summation (a ratio of 2).
+In our model, summation at threshold is determined by the exponent at the first gain control stage (the *m* parameter in Equations 1 & 2).
+The summation ratio can be approximated by $2^{1/m}$ [see Figure 9 of @Baker2012], such that an exponent of $m=1$ produces a ratio of 2, and an exponent of $m = 2$ produces a ratio of $\sqrt{2}$.
+Both the simplex and Bayesian model fits (see Table \@ref(tab:parametertable)) generated parameter estimates in the range $1 < m < 1.4$, consistent with the high levels of summation observed empirically.
+
+## Interocular suppression
+
+The weight of interocular suppression is represented by the model parameter, $\omega$ (Equations 1 & 2).
+Posterior distributions of this parameter overlapped 1 for all of our dipper function data sets (see top right panel in Figure \@ref(fig:bayesianmodel)), indicating strong interocular suppression regardless of post-retinal pathway.
+The flickering disc stimuli produced a slightly lower suppression estimate, with $\omega \sim 0.9$.
+This may indicate slightly weaker suppression between the eyes for temporal modulations, but it is much less extreme than our recent estimates using EEG and matching paradigms [@Segala2023].
+One difference between these studies is the luminance of the background, which was set to black for the experiments of @Segala2023, but here was set at the mean luminance.
+Other studies using static luminance increments have also reported differences in the character of binocular combination that are attributable to background luminance [@Baker2012], so this may explain the differences between studies.
+We also note that the weaker interocular suppression for flickering disc stimuli appears to be largely due to one participant (see Figure \@ref(fig:individualdiscs)c), so individual differences might also play a role.
+Future work should manipulate the background luminance systematically to better understand how this modulates interocular suppression.
+
+## Psychometric slopes
+
+Previous work has demonstrated that the slope of the psychometric function in 2AFC tasks can distinguish different types of masking, although it is much less widely reported than threshold measures.
+In particular, pedestal masking linearizes the slope [@Foley1981; @Meese2006], and within-channel dichoptic masking produces very steep slopes [@Meese2006; @Baker2013].
+We replicate both of these effects here, and show that they extend to isoluminant chromatic pathways (see Figures \@ref(fig:dipperfig)d-f, \@ref(fig:MCSfig)).
+We additionally show that dichoptic masking between different pathways does not produce unusually steep slopes (see Figure \@ref(fig:MCSfig)).
+It therefore more closely resembles other types of masking between visual channels, such as cross-orientation masking [@Meese2009], surround masking [@Yu2002], and masking from broadband noise [@Baker2012b; @Lu2008], which also do not impact psychometric slopes.
+
+## Physiological substrates
 
@@
 Most cells in this layer are monocularly exciteable, in that their responses increase only by stimulation of their preferred eye.
-However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed by the two-stage model.
-In terms of perception, the consequence of this early suppression is to achieve 'ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes [@Baker2007].
+However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed at stage 1 of the two-stage model (Equations 1 & 2).
+In terms of perception, one consequence of this early suppression is to achieve 'ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes [@Baker2007].
 Similar processes of invariance have also been reported using fMRI [@Moradi2009] and steady-state EEG [@Baker2017].
 
+In V1, chromatic stimuli are processed in 'blob' regions that are largely monocular as they fall within ocular dominance columns [@Livingstone1984].
+Since our psychophysical results indicate that interocular suppression is equally strong within chromatic and achromatic pathways, it may be that blob regions include interocular suppression.
+Presumably binocular summation of signals occurs at a later stage of processing for chromatic stimuli, but this does not lead to different perceptual outcomes.
+This physiological arrangement might also be responsible for the pattern of between-pathway interocular suppression (see Figure \@ref(fig:MCSfig)g).
+If blobs process signals from both the L-M and S-(L+M) pathways, their close physical proximity might explain the stronger suppression between the two chromatic pathways than between the chromatic and (more distant) achromatic pathways.
+
 # Conclusions
 
+Here we provide estimates of interocular suppression within and between the three primary post-retinal visual pathways.
+These results show that binocular signal combination is similar within each pathway, but that interocular suppression is relatively weak between pathways.
+Our findings could be applied when building models to predict perception of binocular images and movies, for example those generated by virtual and augmented reality systems, or in 3D cinema and television.
+
 # Acknowledgements

### 2024-03-31 manuscript.tex
First draft completed

@@
 In the monocular condition, participants must discriminate between stimuli of two contrasts (a `pedestal', and a `pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance.
-In the binocular condition, the same stimuli are shown to both eyes.
+Threshold is defined as the minimum target contrast required to make this judgement with 75\% accuracy.
+The binocular condition is the same, except that the same stimuli are shown to both eyes.
 In the half-binocular condition the pedestal is shown to both eyes, but the target increment shown only to one eye.
@@
 
-The detailed pattern of results across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
-At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition owing to physiological binocular summation by neurons responsive to signals from both eyes (Baker et al., 2018; Campbell \& Green, 1965).
+The detailed pattern of thresholds across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
+At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition; this result is attributed to physiological binocular summation by neurons responsive to signals from both eyes (Baker et al., 2018; Campbell \& Green, 1965).
 However at high pedestal contrasts the `handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation (Legge, 1984; Maehara \& Goryo, 2005).
@@
 Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast in order to be detectable (Baker \& Meese, 2007; Legge, 1979; Maehara \& Goryo, 2005).
+The characteristic pattern of dipper functions is well-described by the gain control model of Meese et al.
+(2006) for achromatic stimuli.
 
-At the output of the human retina, visual signals are split into three distinct pathways.
+At the output of the human retina, cone responses are split into three distinct pathways.
 The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information, and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
@@
 There are also interactions between chromatic and achromatic pathways both within (Chen et al., 2000) and between (Kingdom \& Libenson, 2015; Mullen et al., 2014) the eyes, yet these have not been fully explored for arrangements where the target and mask have the same orientation.
-Finally, the neurophysiological underpinnings of colour vision are distinct from the achromatic system.
+Finally, the neurophysiological underpinnings of colour vision are distinct from those of the achromatic system.
 In primary visual cortex (V1), chromatic signals are processed in `blob' regions that are revealed by cytochrome oxidase staining (Horton \& Hubel, 1981).
@@
 
-Strong interocular normalization is well-established when using DC-balanced periodic stimuli such as sine-wave gratings (Baker \& Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009).
-However there is some evidence that binocular combination is more linear for luminance increments (Anstis \& Ho, 1998; Levelt, 1965), particularly against a dark background (Baker et al., 2012).
-Our recent work has extended this finding to flickering discs of luminance, which are DC-balanced across time (Segala et al., 2023).
-Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement, indicating that binocular combination rules may differ for temporal contrast.
+A further property of `blob' regions is that they are less strongly orientation-tuned than other regions of V1 (Horton \& Hubel, 1981; Livingstone \& Hubel, 1984), and biased towards low spatial frequencies (Edwards et al., 1995; Tootell et al., 1988).
+Our recent work has investigated binocular combination for flickering discs of luminance, which are DC-balanced across time (Segala et al., 2023).
+Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement.
+This is very different from the `ocularity invariance' that is well-established when using DC-balanced periodic stimuli such as sine-wave gratings, and implies strong interocular suppression (Baker \& Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009).
+There is additional psychophysical evidence from matching studies that binocular combination can be close to linear for luminance increments (Anstis \& Ho, 1998; Levelt, 1965), particularly against a dark background (Baker et al., 2012).
+Both structural and functional data therefore imply that binocular combination may differ between spatial and temporal contrast.
 
@@
 
-In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg.
+In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg (see examples in Figure \ref{fig:examplestim}).
 The gratings were windowed by a raised cosine envelope with a diameter of 3 degrees.
 Spatial phase, relative to a central fixation cross, was randomised on each trial across the four cardinal phases.
-In the achromatic conditions, the sine-wave modulated all three colour channels equally.
+In the achromatic conditions, the sine-wave modulated all three monitor colour channels equally (red, green and blue).
 In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant.
@@
 Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals (Stockman \& Sharpe, 2000).
-The stimuli in Experiment 3 were temporal modulations of luminance, using the same raised cosine envelope as described above, but with no further spatial modulation.
-The stimuli counterphase flickered sinusoidally at 4Hz.
+The stimuli in Experiment 3 were temporal modulations of luminance applied to a disc made using the same raised cosine envelope as described above, but with no further spatial modulation.
+The stimuli counterphase flickered sinusoidally at 4Hz (see examples in the lower portion of Figure \ref{fig:examplestim}).
 In all experiments, we displayed a binocular fusion lock, consisting of three concentric rings of small square elements with random colour.
 A black central fixation cross was also displayed throughout.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/examplestim}
+
+}
+
+\caption{Example stimuli.
+Upper row shows grating stimuli used in Experiments 1 and 2.
+Lower row shows one cycle of sinusoidal flicker applied to a uniform disc.
+Note that the rendering of all stimuli will depend on the device used to display or print this image, and so the chromatic stimuli are unlikely to appear isoluminant, and there may be additional luminance nonlinearities that were not present in the stimuli displayed during the experiments.}\label{fig:examplestim}
+\end{figure}
 
@@
 For the isoluminant chromatic stimuli, the maximum displayable L-M (red/green) cone contrast was 0.1, and the maximum displayable S-(L+M) (blue/yellow) cone contrast was 0.88.
-So an L-M threshold of 50\% is a cone contrast of \(0.5\times0.1 = 0.05\), and an S-(L+M) threshold of 50\% is a cone contrast of \(0.5\times0.88 = 0.44\).
-The threshold values reported throughout can therefore be converted to cone contrast by a straightforward multiplicative transform.
+An L-M threshold of 50\% therefore corresponds to a cone contrast of \(0.5\times0.1 = 0.05\), and an S-(L+M) threshold of 50\% corresponds to a cone contrast of \(0.5\times0.88 = 0.44\).
+This means that the threshold values reported throughout can be converted to cone contrast by a straightforward multiplicative transform.
 
@@
 Each interval was indicated by an auditory beep, and participants made their responses using a two-button trackball.
-Correct trials were indicated by a high pitched tone, and incorrect trials by a low pitched tone.
+Correct responses were followed by a high pitched tone, and incorrect responses by a low pitched tone.
 Each block of the experiment tested a single pedestal contrast level, and lasted around 12 minutes.
 On each trial the target contrast level was determined by a 3-down-1-up staircase procedure.
-There were 8 interleaved staircases in total; four stimulus arrangements (see Figure \ref{fig:exampledips}) by two target eye assignments.
+There were 8 interleaved staircases in total; four stimulus arrangements (see Figure \ref{fig:exampledips}) combined factorially with two target eye assignments.
 Each pedestal contrast was repeated 3 times by each participant, and the block order was randomised.
@@
 Mask contrasts were chosen to be approximately 16 times their (monocular) detection threshold, based on the data from Experiment 1.
+As a percentage of the maximum displayable contrast, these were 16\% for achromatic stimuli, and 64\% for both of the chromatic stimuli.
 Each block of the experiment tested a single condition, and consisted of 200 trials.
@@
 where \(C_L\) and \(C_R\) are the contrasts displayed to the left and right eyes, and \(m\), \(S\), \(\omega\), \(p\), \(q\) and \(Z\) are free parameters in the model.
-A further free parameter, \(k\), represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values.
-Thresholds are defined by adjusting the target contrast until the following equality is satisfied:
+A further free parameter, \(k\), represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values (note that in the original model specification (Meese et al., 2006) this parameter was called \(\sigma\), but we use the \(k\) symbol here to avoid confusion with the standard deviation of the cumulative Gaussian used when fitting the psychometric functions to derive thresholds).
+Thresholds are defined by iteratively adjusting the target contrast until the following equality is satisfied:
 
 \begin{equation}
-binresp_{target+pedestal} - binresp_{pedestal} = k,
+Stage2_{target+pedestal} - Stage2_{pedestal} = k,
 \end{equation}
@@
 This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants for a given experiment, but separately for each chromatic condition of Experiment 1, and the flickering disc data from Experiment 3 (i.e.~four fits in total, as for the simplex fitting).
+Prior distributions were Gaussian, with means determined from published values (see first row of Table \ref{tab:parametertable}).
 This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
 We generated over 1 million posterior samples for the model, and retained 10\% of them for plotting.
+
+Finally, we adapted the two stage model to include parallel pathways to process achromatic, red/green and blue/yellow stimuli, that mutually suppress each other.
+We added additional suppressive terms at the first (monocular) stage of the model, for example:
+
+\begin{equation}
+ACStage1_L = \frac{AC_L^m}{S + AC_L + \omega_A AC_R + \omega_R RG_R + \omega_B BY_R},
+\end{equation}
+
+where \emph{AC} represents the achromatic contrast, \emph{RG} represents the red/green contrast, \emph{BY} represents the blue/yellow contrast, and \(\omega_A\), \(\omega_R\) and \(\omega_B\) are the accompanying weights of interocular suppression.
+There is an equivalent expression for the right eye, and for each of the two isoluminant chromatic pathways.
+To simplify the model, and avoid free parameters that are poorly constrained by the data, we fixed several parameters at the average values from the fits from Experiment 1 (Table \ref{tab:parametertable}), such that \(p=7.82\), \(q=6.4\), \(m=1.21\), \(S=1.03\) and \(k=0.23\).
+We additionally fixed the within-mechanism weight of interocular suppression (\(\omega\)) at 1.
+This left 9 free parameters: a \(Z\) parameter for each mechanism, and six cross-mechanism weights of interocular suppression.
+These parameters were again estimated within a Bayesian hierarchical framework, using the trial-wise data from Experiment 2.
+Note that the model as specified does not currently include monocular suppression between different pathways, as we did not collect any data for these conditions.
+Previous work (Chen et al., 2000) has measured such interactions, and they could in principle be incorporated into the denominator of either stage 1 or stage 2 in the model.
 
@@
 Panel (a) shows the achromatic results, which replicate the key features from previous work.
-At detection threshold, binocular summation was a factor of 1.67 (4.47dB), consistent with previous reports (Baker et al., 2018).
-Pedestal masking functions follow the typical `dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
+At detection threshold, binocular summation was a factor of 1.67 (4.47dB), within the range (\(\sqrt{2}\) to 2) consistent with previous reports (Baker et al., 2018).
+Pedestal masking functions followed the typical `dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
 The monocular and binocular dipper handles converge at high contrasts, whereas the half-binocular thresholds remain above the binocular thresholds across the full range of pedestal contrasts.
@@
 \caption{Dipper functions and psychometric slopes from Experiment 1, averaged across three participants.
-Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull beta units.
+Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull $\beta$ units.
 Error bars give ±1SE across participants.
@@
 (2006), we also inspected the slope of the psychometric function for each condition (see Figure \ref{fig:dipperfig}d-f).
-At detection threshold, slopes were relatively steep, with \(\beta\) values around 4.
+At detection threshold, slopes were relatively steep for all stimuli, with \(\beta\) values around 4.
 As pedestal contrasts increased, slopes linearized and reduced to around \(\beta=1.3\) (Foley \& Legge, 1981; Meese et al., 2006), and remained shallow at high pedestal contrasts.
 The exception to this was the dichoptic condition, where slopes became extremely steep at high dichoptic mask contrasts, consistent with previous observations (Baker et al., 2013; Meese et al., 2006).
-This was clear for all three data sets, with slope values in the range \(\beta=4\) to \(\beta=8\).
-However, we note that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
-Our second experiment investigated the slope of the psychometric function in more detail using the method of constant stimuli.
+This was clear for all three data sets, with slope values in the range \(4 < \beta < 8\).
+However, we observe that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
+Our second experiment therefore investigated the slope of the psychometric function in more detail for dichoptic masking using the method of constant stimuli.
 
@@
 Panel (g) shows the average threshold elevation factor for each combination of target and mask stimulus.
-Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull beta units.}\label{fig:MCSfig}
+Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull $\beta$ units.}\label{fig:MCSfig}
 \end{figure}
@@
 We also calculated the slope of the psychometric function for each condition, in equivalent Weibull \(\beta\) units.
-In the absence of a mask, the average slope was \(\beta\) = 3.42, which is typical for contrast detection tasks.
+In the absence of a mask, the average slope was \(\beta\) = 3.42, which is typical for contrast detection tasks (Wallis et al., 2013).
 Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average \(\beta\) = 5.38).
@@
 This was motivated by our recent work (Segala et al., 2023) that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
-The pattern of dipper functions for a 4Hz flickering disc (see Figure \ref{fig:discdata}a) was very similar to that observed for achromatic gratings (see Figure \ref{fig:dipperfig}a), and the binocular summation ratio at threshold was also similar (a factor of 1.49).
+The pattern of dipper functions for a 4Hz flickering disc (see Figure \ref{fig:discdata}a) was very similar to that observed for achromatic gratings (see Figure \ref{fig:dipperfig}a), and the binocular summation ratio at threshold was also similar (a factor of 1.49 for discs, vs 1.67 for gratings).
 Threshold data for individual participants are shown in Figure \ref{fig:individualdiscs}.
-We also found a similar pattern of psychometric slope values (Figure \ref{fig:discdata}b), though we note that the dichoptic condition did not produce the `super-steep' psychometric functions we had observed in Experiments 1 \& 2.
-Nevertheless, its slopes are somewhat above those of the other pedestal arrangements.
+We also found a similar pattern of psychometric slope values (Figure \ref{fig:discdata}b) as we had for gratings, though we note that the dichoptic condition did not produce the `super-steep' psychometric functions we had observed in Experiments 1 \& 2.
+Nevertheless, the dichoptic slopes are somewhat above those of the other pedestal arrangements at high contrasts.
 
@@
 
-\caption{Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 3.}\label{fig:discdata}
+\caption{Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 4.}\label{fig:discdata}
 \end{figure}
@@
 \caption{\label{tab:parametertable}Summary of fitted model parameters.
-The upper rows are best fitting parameters from simplex fits to the averaged thresholds for each experiment.
-The final row shows the posterior parameter estimates from the Bayesian model, fitted to data from Experiments 1 and 3.}
+The top row gives the best fitting parameters from the study of Meese et al.
+(2006).
+The second section shows the best fitting parameters from simplex fits to the averaged thresholds for each experiment.
+The final rows show the posterior parameter estimates from the Bayesian model, fitted to each data set from Experiments 1 and 3.}
 \centering
@@
 \toprule
-\textbf{\em{Model fit}} & \textbf{\em{p}} & \textbf{\em{q}} & \textbf{\em{m}} & \textbf{\em{S}} & \textbf{\em{Z}} & \textbf{\em{w}} & \textbf{\em{k}} & \textbf{\em{RMSE}}\\
+\textbf{\em{Model fit}} & \textbf{\em{p}} & \textbf{\em{q}} & \textbf{\em{m}} & \textbf{\em{S}} & \textbf{\em{Z}} & \textbf{\em{$\omega$}} & \textbf{\em{k}} & \textbf{\em{RMSE}}\\
 \midrule
-Meese et al. (2006) & 7.99 & 6.59 & 1.28 & 0.99 & 0.08 & 1 & 0.19 & \\
+Meese et al. (2006) & 7.99 & 6.59 & 1.28 & 0.99 & 0.08 & 1.00 & 0.19 & \\
 \midrule
 \textbf{Simplex fits} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
-Achromatic gratings & 6.51 & 5.1 & 1.31 & 0.83 & 0.16 & 1 & 0.21 & 1.59 dB\\
-Red/green gratings & 19.42 & 1.1 & 1.03 & 0.37 & 1.49 & 1 & 0.29 & 1.43 dB\\
-Blue/yellow gratings & 9.47 & 6.21 & 1.14 & 1.89 & 0.26 & 1 & 0.34 & 1.38 dB\\
+Achromatic gratings & 6.51 & 5.10 & 1.31 & 0.83 & 0.16 & 1.00 & 0.21 & 1.59 dB\\
+Red/green gratings & 19.42 & 1.10 & 1.03 & 0.37 & 1.49 & 1.00 & 0.29 & 1.43 dB\\
+Blue/yellow gratings & 9.47 & 6.21 & 1.14 & 1.89 & 0.26 & 1.00 & 0.34 & 1.38 dB\\
 Flickering discs & 6.13 & 4.93 & 1.24 & 0.84 & 0.27 & 0.89 & 0.13 & 1.06 dB\\
@@
 \textbf{Bayesian model} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
-Achromatic gratings & 7.79 & 6.38 & 1.29 & 0.87 & 0.12 & 0.99 & 0.25 & \\
-Red/green gratings & 7.89 & 6.48 & 1.18 & 1.11 & 0.51 & 0.96 & 0.23 & \\
-Blue/yellow gratings & 7.73 & 6.31 & 1.15 & 1.09 & 0.51 & 0.99 & 0.25 & \\
-Flickering discs & 7.7 & 6.29 & 1.26 & 0.83 & 0.21 & 0.91 & 0.23 & \\
+Achromatic gratings & 7.78 & 6.37 & 1.29 & 0.88 & 0.12 & 0.99 & 0.25 & \\
+Red/green gratings & 7.88 & 6.46 & 1.21 & 1.10 & 0.46 & 0.95 & 0.21 & \\
+Blue/yellow gratings & 7.79 & 6.37 & 1.14 & 1.10 & 0.59 & 1.00 & 0.24 & \\
+Flickering discs & 7.72 & 6.32 & 1.26 & 0.83 & 0.22 & 0.90 & 0.23 & \\
 \bottomrule
@@
 Best fitting parameters are shown in the `Simplex fits' section of Table \ref{tab:parametertable}.
-We note that in previous work, the weight of interocular suppression (\emph{w} in the model) is implicitly fixed at 1.
+We note that in previous work, the weight of interocular suppression (\(\omega\) in the model) is implicitly fixed at 1.
 Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (0.89) for our flickering discs.
+The exponent values (\emph{p} and \emph{q}) for the red/green gratings are rather different from those of the other conditions.
+In previous work (Meese et al., 2006) the second stage gain control nonlinearity (Equation 4) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper).
+The high value of \emph{p} (19.42) is therefore likely to be compensating for the low value of \emph{m} (1.03) at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty (Pelli, 1985).
 
 We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
-This model was fit simultaneously to full trial-by-trial data from all participants who participated in a given experiment (i.e.~the model was fitted separately to each of the four dipper data sets).
+This model was fit simultaneously to the full trial-by-trial data from all participants who participated in a given experiment (i.e.~the model was fitted separately to each of the four dipper data sets).
 Figure \ref{fig:bayesianmodel}a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
@@
 The panels in the right and upper margins of Figure \ref{fig:bayesianmodel} show posterior distributions for each model parameter.
-Note in particular that the posterior distribution for the weight of interocular suppression (\emph{w}, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
-We note that the distribution for \emph{w} in the flickering disc condition is somewhat lower than for the other three data sets.
-However this difference is not meaningful according to criteria such as comparing the 95\% credible intervals of the distribution to a value of \emph{w}=1.
+Note in particular that the posterior distribution for the weight of interocular suppression (\(\omega\), top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
+We note that the distribution for \(\omega\) in the flickering disc condition is somewhat lower than for the other three data sets.
+However this difference is not meaningful according to criteria such as comparing the 95\% credible intervals of the distribution to a value of \(\omega=1\).
 
@@
 \caption{Model predictions (a-d) and posterior parameters (top and right margin plots) for the hierarchical Bayesian model.
-Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates, and thin lines are from 200 random posterior draws.
+Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates.
 The probability density functions in the margin plots are peak-normalized, and shown for each of the four data sets in different colours (see legend in upper left plot).
-Distributions are generated from 1000000 samples per data set, using a Markov Chain Monte Carlo sampling algorithm.}\label{fig:bayesianmodel}
+Distributions were generated from 1000000 samples per data set, using a Markov Chain Monte Carlo sampling algorithm.
+Note the logarithmic x-axis for all posterior plots.}\label{fig:bayesianmodel}
+\end{figure}
+
+Finally we fitted an extended model, that included interocular suppression between the different pathways, to the data of Experiment 2.
+Figure \ref{fig:MCSmodel} shows the model curves (panels a-c), which correspond closely to the data in Figure \ref{fig:MCSfig}.
+One striking discrepancy is that the model predicts a region of negative d-prime for the case where the target and dichoptic mask have the same chromaticity (see the curved regions below 50\% correct).
+This feature was not generally present in our data, though it can be observed for one participant in Figure \ref{fig:individualMCS}b,c.~Our previous work (Baker et al., 2013) has found evidence for this phenomenon (termed `swan functions'), but it generally requires very high mask contrasts to be measurable empirically, and there may also be some individual differences; both factors might explain its absence here.
+
+Figure \ref{fig:MCSmodel}d,e shows the model estimates for the weight of interocular suppression in each combination of target and mask chromaticity.
+Although the weights might appear to indicate that (excluding within-mechanism effects) suppression is strongest between blue/yellow targets and achromatic masks (a weight of 0.56), this is somewhat complicated by the differences in sensitivity and mask contrast between conditions.
+We selected mask contrasts that were approximately equal multiples (\(16\times\)) of their own detection thresholds, based on the data of Experiment 1 (Figure \ref{fig:dipperfig}a-c).
+However the modelling expressed these contrasts as a percentage of the maximum contrast that it was possible to display on the monitor (see Procedures).
+The values in brackets in Figure \ref{fig:MCSmodel}d indicate the overall suppressive term on the denominator, calculated by multiplying the mask contrast by the fitted weight.
+These values indicate that the strongest suppression is instead between red/green targets and blue/yellow masks, consistent with the threshold elevation observed empirically (Figure \ref{fig:MCSfig}g).
+In principle it would be possible to repeat this modelling using either cone contrast values, or contrast expressed relative to detection threshold, which would require re-fitting the model.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/MCSmodel}
+
+}
+
+\caption{Summary of the model fit to the data of Experiment 2.
+Panels (a-c) show model psychometric functions in the same format as those in Figure 5.
+Panel (d) shows the fitted suppressive weights ($\omega$ values), with values in brackets indicating the combined suppressive denominator term calculated by multiplying together the suppressive weight and the dichoptic mask contrast.
+Panel (e) shows the posterior distributions for each weight parameter.
+The lower right plot gives the legends for the upper row (top) and the posterior distributions in panel (e).}\label{fig:MCSmodel}
 \end{figure}
@@
 \item
-  Interocular suppression is strongest within a chromatic pathway, and weakest between achromatic and chromatic pathways
+  Interocular suppression is strongest within a post-retinal pathway, and weakest between achromatic and chromatic pathways
 \item
-  Binocular combination occurs similarly for temporal and temporal luminance modulations
+  Binocular combination occurs similarly for spatial and temporal luminance modulations
 \end{itemize}
 
-We now discuss the relationship to previous work, consider the likely physiological substrates of these effects and .
+We now discuss the relationship to previous work, and consider the likely physiological substrates of these effects.
+
+\hypertarget{summation-at-threshold}{%
+\subsection{Summation at threshold}\label{summation-at-threshold}}
+
+Estimates of the binocular summation ratio at threshold fell within the range \(\sqrt{2}\) to 2 for all four data sets.
+Consistent with previous reports (Simmons, 2005), summation was slightly higher for chromatic versus achromatic stimuli, but fell short of perfect linear summation (a ratio of 2).
+In our model, summation at threshold is determined by the exponent at the first gain control stage (the \emph{m} parameter in Equations 1 \& 2).
+The summation ratio can be approximated by \(2^{1/m}\) (see Figure 9 of Baker et al., 2012), such that an exponent of \(m=1\) produces a ratio of 2, and an exponent of \(m = 2\) produces a ratio of \(\sqrt{2}\).
+Both the simplex and Bayesian model fits (see Table \ref{tab:parametertable}) generated parameter estimates in the range \(1 < m < 1.4\), consistent with the high levels of summation observed empirically.
+
+\hypertarget{interocular-suppression}{%
+\subsection{Interocular suppression}\label{interocular-suppression}}
+
+The weight of interocular suppression is represented by the model parameter, \(\omega\) (Equations 1 \& 2).
+Posterior distributions of this parameter overlapped 1 for all of our dipper function data sets (see top right panel in Figure \ref{fig:bayesianmodel}), indicating strong interocular suppression regardless of post-retinal pathway.
+The flickering disc stimuli produced a slightly lower suppression estimate, with \(\omega \sim 0.9\).
+This may indicate slightly weaker suppression between the eyes for temporal modulations, but it is much less extreme than our recent estimates using EEG and matching paradigms (Segala et al., 2023).
+One difference between these studies is the luminance of the background, which was set to black for the experiments of Segala et al.
+(2023), but here was set at the mean luminance.
+Other studies using static luminance increments have also reported differences in the character of binocular combination that are attributable to background luminance (Baker et al., 2012), so this may explain the differences between studies.
+We also note that the weaker interocular suppression for flickering disc stimuli appears to be largely due to one participant (see Figure \ref{fig:individualdiscs}c), so individual differences might also play a role.
+Future work should manipulate the background luminance systematically to better understand how this modulates interocular suppression.
+
+\hypertarget{psychometric-slopes}{%
+\subsection{Psychometric slopes}\label{psychometric-slopes}}
+
+Previous work has demonstrated that the slope of the psychometric function in 2AFC tasks can distinguish different types of masking, although it is much less widely reported than threshold measures.
+In particular, pedestal masking linearizes the slope (Foley \& Legge, 1981; Meese et al., 2006), and within-channel dichoptic masking produces very steep slopes (Baker et al., 2013; Meese et al., 2006).
+We replicate both of these effects here, and show that they extend to isoluminant chromatic pathways (see Figures \ref{fig:dipperfig}d-f, \ref{fig:MCSfig}).
+We additionally show that dichoptic masking between different pathways does not produce unusually steep slopes (see Figure \ref{fig:MCSfig}).
+It therefore more closely resembles other types of masking between visual channels, such as cross-orientation masking (Meese \& Baker, 2009), surround masking (Yu et al., 2002), and masking from broadband noise (Baker \& Meese, 2012; Lu \& Dosher, 2008), which also do not impact psychometric slopes.
+
+\hypertarget{physiological-substrates}{%
+\subsection{Physiological substrates}\label{physiological-substrates}}
 
@@
 Most cells in this layer are monocularly exciteable, in that their responses increase only by stimulation of their preferred eye.
-However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed by the two-stage model.
-In terms of perception, the consequence of this early suppression is to achieve `ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes (Baker et al., 2007).
+However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed at stage 1 of the two-stage model (Equations 1 \& 2).
+In terms of perception, one consequence of this early suppression is to achieve `ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes (Baker et al., 2007).
 Similar processes of invariance have also been reported using fMRI (Moradi \& Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).
+
+In V1, chromatic stimuli are processed in `blob' regions that are largely monocular as they fall within ocular dominance columns (Livingstone \& Hubel, 1984).
+Since our psychophysical results indicate that interocular suppression is equally strong within chromatic and achromatic pathways, it may be that blob regions include interocular suppression.
+Presumably binocular summation of signals occurs at a later stage of processing for chromatic stimuli, but this does not lead to different perceptual outcomes.
+This physiological arrangement might also be responsible for the pattern of between-pathway interocular suppression (see Figure \ref{fig:MCSfig}g).
+If blobs process signals from both the L-M and S-(L+M) pathways, their close physical proximity might explain the stronger suppression between the two chromatic pathways than between the chromatic and (more distant) achromatic pathways.
 
@@
 \section{Conclusions}\label{conclusions}}
+
+Here we provide estimates of interocular suppression within and between the three primary post-retinal visual pathways.
+These results show that binocular signal combination is similar within each pathway, but that interocular suppression is relatively weak between pathways.
+Our findings could be applied when building models to predict perception of binocular images and movies, for example those generated by virtual and augmented reality systems, or in 3D cinema and television.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2012b}{}}%
+Baker, D. H., \& Meese, T. S. (2012). Zero-dimensional noise: The best mask you never saw. \emph{J Vis}, \emph{12}(10). \url{https://doi.org/10.1167/12.10.20}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
@@
 Paradoxical psychometric functions ("swan functions") are explained by dilution masking in four stimulus dimensions.
-\emph{Iperception}, \emph{4}(1), 17--35.
+\emph{{iPerception}}, \emph{4}(1), 17--35.
 \url{https://doi.org/10.1068/i0552}
@@
 \url{https://doi.org/10.1016/j.cub.2018.12.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Edwards1995}{}}%
+Edwards, D.
+P., Purpura, K.
+P., \& Kaplan, E.
+(1995).
+Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
+\emph{Vision Res}, \emph{35}(11), 1501--1523.
+\url{https://doi.org/10.1016/0042-6989(94)00253-i}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Lu2008}{}}%
+Lu, Z.-L., \& Dosher, B.
+A.
+(2008).
+Characterizing observers using external noise and observer models: Assessing internal representations with external noise.
+\emph{Psychol Rev}, \emph{115}(1), 44--82.
+\url{https://doi.org/10.1037/0033-295X.115.1.44}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Maehara2005}{}}%
@@
 Medina, J. M., \& Mullen, K. T. (2009). Cross-orientation masking in human color vision. \emph{J Vis}, \emph{9}(3), 20.1--16. \url{https://doi.org/10.1167/9.3.20}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Meese2009}{}}%
+Meese, T.
+S., \& Baker, D.
+H.
+(2009).
+Cross-orientation masking is speed invariant between ocular pathways but speed dependent within them.
+\emph{J Vis}, \emph{9}(5), 2.1--15.
+\url{https://doi.org/10.1167/9.5.2}
 
@@
 \url{https://doi.org/10.1038/srep07350}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pelli1985}{}}%
+Pelli, D. G. (1985). Uncertainty explains many aspects of visual contrast detection and discrimination. \emph{J Opt Soc Am A}, \emph{2}(9), 1508--1532. \url{https://doi.org/10.1364/josaa.2.001508}
 
@@
 \url{https://doi.org/10.1016/s0042-6989(00)00021-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tootell1988}{}}%
+Tootell, R.
+B., Silverman, M.
+S., Hamilton, S.
+L., De Valois, R.
+L., \& Switkes, E.
+(1988).
+Functional anatomy of macaque striate cortex.
+III.
+color.
+\emph{J Neurosci}, \emph{8}(5), 1569--1593.
+\url{https://doi.org/10.1523/JNEUROSCI.08-05-01569.1988}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wallis2013}{}}%
+Wallis, S.
+A., Baker, D.
+H., Meese, T.
+S., \& Georgeson, M.
+A.
+(2013).
+The slope of the psychometric function and non-stationarity of thresholds in spatiotemporal contrast vision.
+\emph{Vision Res}, \emph{76}, 1--10.
+\url{https://doi.org/10.1016/j.visres.2012.09.019}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Yu2002}{}}%
+Yu, C., Klein, S.
+A., \& Levi, D.
+M.
+(2002).
+Facilitation of contrast detection by cross-oriented surround stimuli and its psychophysical mechanisms.
+\emph{J Vis}, \emph{2}(3), 243--255.
+\url{https://doi.org/10.1167/2.3.4}
 

### 2024-03-31 manuscript.Rmd
Added autobuild files

@@
 
-processdata <- 1
+processdata <- 0
 # the processdata flag has three settings:
@@
 osfrepo <- '3vdga'
-
-if (!file.exists('local/Experiment1.csv')){}
-if (!file.exists('local/Experiment2.csv')){}
-if (!file.exists('local/Experiment3.csv')){}
-if (!file.exists('local/fundamentals.csv')){}
-if (!file.exists('local/isosettings.csv')){}
-if (!file.exists('local/phosphors.csv')){}
+osfproject <- osf_retrieve_node(osfrepo)
+osffiles <- osf_ls_files(osfproject,n_max=300)
+
+if (!file.exists('local/Experiment1.csv')){osf_download(osffiles[which(osffiles$name=='Experiment1.csv'),],'local/',progress=TRUE)}
+if (!file.exists('local/Experiment2.csv')){osf_download(osffiles[which(osffiles$name=='Experiment2.csv'),],'local/',progress=TRUE)}
+if (!file.exists('local/Experiment3.csv')){osf_download(osffiles[which(osffiles$name=='Experiment3.csv'),],'local/',progress=TRUE)}
+if (!file.exists('local/fundamentals.csv')){osf_download(osffiles[which(osffiles$name=='fundamentals.csv'),],'local/',progress=TRUE)}
+if (!file.exists('local/isosettings.csv')){osf_download(osffiles[which(osffiles$name=='isosettings.csv'),],'local/',progress=TRUE)}
+if (!file.exists('local/phosphors.csv')){osf_download(osffiles[which(osffiles$name=='phosphors.csv'),],'local/',progress=TRUE)}
 
 if (processdata < 1){
- if (!file.exists('local/thresholddata.RData')){}
- if (!file.exists('local/thresholddataDisc.RData')){}
- if (!file.exists('local/MCSdata.RData')){}
+ if (!file.exists('local/thresholddata.RData')){osf_download(osffiles[which(osffiles$name=='thresholddata.RData'),],'local/',progress=TRUE)}
+ if (!file.exists('local/thresholddataDisc.RData')){osf_download(osffiles[which(osffiles$name=='thresholddataDisc.RData'),],'local/',progress=TRUE)}
+ if (!file.exists('local/MCSdata.RData')){osf_download(osffiles[which(osffiles$name=='MCSdata.RData'),],'local/',progress=TRUE)}
 }
@@
 if (processdata < 2){
- if (!file.exists('local/simplexfits.RData')){}
- if (!file.exists('local/stanfit1.RData')){}
- if (!file.exists('local/stanfit2.RData')){}
- if (!file.exists('local/stanfit3.RData')){}
- if (!file.exists('local/stanfit4.RData')){}
-}
-
-if (!file.exists('references.bib')){}
-if (!file.exists('journal-of-vision.csl')){}
+ if (!file.exists('local/simplexfits.RData')){osf_download(osffiles[which(osffiles$name=='simplexfits.RData'),],'local/',progress=TRUE)}
+ if (!file.exists('local/stanfit1.RData')){osf_download(osffiles[which(osffiles$name=='stanfit1.RData'),],'local/',progress=TRUE)}
+ if (!file.exists('local/stanfit2.RData')){osf_download(osffiles[which(osffiles$name=='stanfit2.RData'),],'local/',progress=TRUE)}
+ if (!file.exists('local/stanfit3.RData')){osf_download(osffiles[which(osffiles$name=='stanfit3.RData'),],'local/',progress=TRUE)}
+ if (!file.exists('local/stanfit4.RData')){osf_download(osffiles[which(osffiles$name=='stanfit4.RData'),],'local/',progress=TRUE)}
+}
+
+# if (!file.exists('references.bib')){}
+# if (!file.exists('journal-of-vision.csl')){}
 
@@
 In previous work [@Meese2006] the second stage gain control nonlinearity (Equation 4) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper).
-The high value of *p* (`r round(allp[2,1], digits=2)`) is therefore likely to be compensating for the low value of *m* (`r round(allp[2,3], digits=2)`) at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty [@Pelli1985].
+The high value of *p* = `r round(allp[2,1], digits=2)` is therefore likely to be compensating for the low value of *m* = `r round(allp[2,3], digits=2)` at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty [@Pelli1985].
 

### 2024-03-31 manuscript.Rmd
Fixed to download MCS fits if missing

@@
  if (!file.exists('local/stanfit4.RData')){osf_download(osffiles[which(osffiles$name=='stanfit4.RData'),],'local/',progress=TRUE)}
+if (!file.exists('local/MCSfit.RData')){osf_download(osffiles[which(osffiles$name=='MCSfit.RData'),],'local/',progress=TRUE)}
 }

### 2024-03-31 manuscript.Rmd
Trying python without miniconda

@@
 if (processdata>0){
-  use_miniconda('r-reticulate')
+  # use_miniconda('r-reticulate')
   # install psignifit in the terminal with:

### 2024-03-31 manuscript.Rmd
Trying different python setup

--- 2024-03-31 manuscript.Rmd
@@
 if (processdata>0){
-  use_miniconda('r-reticulate')
+  reticulate::use_python("/usr/bin/python3")
+  # use_miniconda('r-reticulate')
   # install psignifit in the terminal with:

### 2024-03-31 manuscript.Rmd
Trying python again

--- 2024-03-31 manuscript.Rmd
@@
 if (processdata>0){
-  use_miniconda('r-reticulate')
+  reticulate::use_python("/usr/local/lib/python3.10/")
+  # use_miniconda('r-reticulate')
   # install psignifit in the terminal with:

### 2024-03-31 manuscript.Rmd
Trying miniconda

--- 2024-03-31 manuscript.Rmd
@@
 if (processdata>0){
-  # use_miniconda('r-reticulate')
+  install_miniconda()
+  use_miniconda('r-reticulate')
+  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
   # install psignifit in the terminal with:

### 2024-04-01 manuscript.qmd
Switched to Quarto

--- 2024-03-31 manuscript.Rmd
@@
 title: "Binocular integration of chromatic and luminance signals"
-author: |
-   | Daniel H. Baker, Kirralise J. Hansford, Federico G. Segala, Annie Y. Morsi,
-   | Rowan J. Huxley, Joel T. Martin, Maya Rockman & Alex R. Wade
-date: "Department of Psychology, University of York"
-output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    toc: no
-    keep_tex: yes
-  word_document: default
-  html_document: default
+author:
+  - Daniel H. Baker
+  - Kirralise J. Hansford
+  - Federico G. Segala
+  - Annie Y. Morsi
+  - Rowan J. Huxley
+  - Joel T. Martin
+  - Maya Rockman
+  - Alex R. Wade
+format: pdf
+execute:
+  echo: false
 bibliography: references.bib
@@
 This model features interocular suppression between monocular channels, followed by binocular summation.
-The model accounts well for the pattern of contrast discrimination ('dipper') functions for four distinct ocular configurations [see also @Georgeson2016], illustrated in Figure \@ref(fig:exampledips).
+The model accounts well for the pattern of contrast discrimination ('dipper') functions for four distinct ocular configurations [see also @Georgeson2016], illustrated in @fig-exampledips.
 In the monocular condition, participants must discriminate between stimuli of two contrasts (a 'pedestal', and a 'pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance.
@@
 
-```{r exampledips, fig.cap="Illustration of stimulus conditions (left) and example dipper functions (right).", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/exampledips.pdf')
-
-```
+![Illustration of stimulus conditions (left) and example dipper functions (right).](Figures/exampledips.pdf){#fig-exampledips}
 
@@
 
-In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg (see examples in Figure \@ref(fig:examplestim)).
+In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg (see examples in @fig-examplestim).
 The gratings were windowed by a raised cosine envelope with a diameter of 3 degrees.
@@
 The stimuli in Experiment 3 were temporal modulations of luminance applied to a disc made using the same raised cosine envelope as described above, but with no further spatial modulation.
-The stimuli counterphase flickered sinusoidally at 4Hz (see examples in the lower portion of Figure \@ref(fig:examplestim)).
+The stimuli counterphase flickered sinusoidally at 4Hz (see examples in the lower portion of @fig-examplestim).
 In all experiments, we displayed a binocular fusion lock, consisting of three concentric rings of small square elements with random colour.
@@
 
-```{r examplestim, out.width = "50%", fig.cap="Example stimuli.
+![Example stimuli.
 Upper row shows grating stimuli used in Experiments 1 and 2.
 Lower row shows one cycle of sinusoidal flicker applied to a uniform disc.
-Note that the rendering of all stimuli will depend on the device used to display or print this image, and so the chromatic stimuli are unlikely to appear isoluminant, and there may be additional luminance nonlinearities that were not present in the stimuli displayed during the experiments.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/examplestim.pdf')
-
-```
+Note that the rendering of all stimuli will depend on the device used to display or print this image, and so the chromatic stimuli are unlikely to appear isoluminant, and there may be additional luminance nonlinearities that were not present in the stimuli displayed during the experiments.](Figures/examplestim.pdf){#fig-examplestim width=50%}
 
@@
 Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli for the main experiment for that participant.
-Settings were very similar across participants for the S-(L+M) direction, and  somewhat more heterogeneous for the L-M direction (see Figure \@ref(fig:isofig)).
-
-```{r isofig, fig.cap="Isoluminance settings from all participants in Experiments 1 and 2.
+Settings were very similar across participants for the S-(L+M) direction, and  somewhat more heterogeneous for the L-M direction (see @fig-isofig).
+
+![Isoluminance settings from all participants in Experiments 1 and 2.
 Panel (a) shows red/green and panel (b) shows blue/yellow settings that were subsequently used to generate stimuli in the main experiments.
-Within each panel, solid lines show the mean settings for each participant, and black curves show the range of possible stimuli displayed during the adjustment task.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/isosettings.pdf')
-
-```
+Within each panel, solid lines show the mean settings for each participant, and black curves show the range of possible stimuli displayed during the adjustment task.](Figures/isosettings.pdf){#fig-isofig}
 
@@
 On each trial the target contrast level was determined by a 3-down-1-up staircase procedure.
-There were 8 interleaved staircases in total; four stimulus arrangements (see Figure \@ref(fig:exampledips)) combined factorially with two target eye assignments.
+There were 8 interleaved staircases in total; four stimulus arrangements (see @fig-exampledips) combined factorially with two target eye assignments.
 Each pedestal contrast was repeated 3 times by each participant, and the block order was randomised.
@@
 four fits in total, as for the simplex fitting).
-Prior distributions were Gaussian, with means determined from published values (see first row of Table \@ref(tab:parametertable)).
+Prior distributions were Gaussian, with means determined from published values (see first row of @tbl-parametertable).
 This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
@@
 There is an equivalent expression for the right eye, and for each of the two isoluminant chromatic pathways.
-To simplify the model, and avoid free parameters that are poorly constrained by the data, we fixed several parameters at the average values from the fits from Experiment 1 (Table \@ref(tab:parametertable)), such that $p=7.82$, $q=6.4$, $m=1.21$, $S=1.03$ and $k=0.23$.
+To simplify the model, and avoid free parameters that are poorly constrained by the data, we fixed several parameters at the average values from the fits from Experiment 1 (@tbl-parametertable), such that $p=7.82$, $q=6.4$, $m=1.21$, $S=1.03$ and $k=0.23$.
 We additionally fixed the within-mechanism weight of interocular suppression ($\omega$) at 1.
@@
 
-Dipper functions from Experiment 1 are displayed in the upper row of Figure \@ref(fig:dipperfig).
+Dipper functions from Experiment 1 are displayed in the upper row of @fig-dipperfig.
 Panel (a) shows the achromatic results, which replicate the key features from previous work.
@@
 
-```{r dipperfig, fig.cap="Dipper functions and psychometric slopes from Experiment 1, averaged across three participants.
-Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull $\\beta$ units.
+![Dipper functions and psychometric slopes from Experiment 1, averaged across three participants.
+Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull $\beta$ units.
 Error bars give ±1SE across participants.
 Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).
-Curves in panels (a-c) show the best fitting models, optimized using a simplex algorithm (described in section 4.4), and RMSE values give the root mean square errors of the fits.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/dipperssimplex.pdf')
-
-```
-
-A similar pattern of results was observed for both the red/green and blue/yellow isoluminant stimuli (see Figure \@ref(fig:dipperfig)b,c).
+Curves in panels (a-c) show the best fitting models, optimized using a simplex algorithm (described in section 4.4), and RMSE values give the root mean square errors of the fits.](Figures/dipperssimplex.pdf){#fig-dipperfig}
+
+A similar pattern of results was observed for both the red/green and blue/yellow isoluminant stimuli (see [@fig-dipperfig]b,c).
 Summation at threshold was a factor of `r round(10^(summation[3]/20),digits=2)` (`r round(summation[3],digits=2)`dB) for the red/green targets, and a factor of `r round(10^(summation[2]/20),digits=2)` (`r round(summation[2],digits=2)`dB) for the blue/yellow targets, and so was marginally higher than for achromatic stimuli.
@@
 Dichoptic masking remained as strong for the chromatic conditions as for the achromatic stimuli (regression slopes of `r round(dichregRG$coefficients[2], digits=2)` for red/green and `r round(dichregBY$coefficients[2], digits=2)` for blue/yellow).
-The pattern of results for individual participants was consistent with the group averages, as shown in Figure \@ref(fig:individualdips).
-
-Following @Meese2006, we also inspected the slope of the psychometric function for each condition (see Figure \@ref(fig:dipperfig)d-f).
+The pattern of results for individual participants was consistent with the group averages, as shown in [@fig-individualdippers].
+
+Following @Meese2006, we also inspected the slope of the psychometric function for each condition (see [@fig-dipperfig]d-f).
 At detection threshold, slopes were relatively steep for all stimuli, with $\beta$ values around 4.
@@
 In Experiment 2 we focussed on the dichoptic condition at a single mask contrast, and measured full psychometric functions using the method of constant stimuli for all factorial pairings of target and mask chromaticity.
-The pooled results across three participants are shown in Figure \@ref(fig:MCSfig)a-c, and results for individual participants are available in Figure \@ref(fig:individualMCS).
+The pooled results across three participants are shown in [@fig-MCSfig]a-c, and results for individual participants are available in [@fig-individualMCS].
 All conditions produced monotonically increasing psychometric functions (panels a-c), but the extent of masking was highly dependent on the relationship between the target and mask chromaticity.
-Figure \@ref(fig:MCSfig)d-f shows a two-dimensional representation of individual threshold and slope estimates (points), as well as the posterior density estimates for fits to the pooled data (ellipses).
+[@fig-MCSfig]d-f shows a two-dimensional representation of individual threshold and slope estimates (points), as well as the posterior density estimates for fits to the pooled data (ellipses).
 The results are consistent between participants, and at the group level, and show that the presence of a mask has a strong effect on thresholds.
 
-```{r MCSfig, fig.cap="Summary of data from Experiment 2.
+![Summary of data from Experiment 2.
 Panels (a-c) show psychometric functions for each condition, pooled across participants (600 trials per target contrast level).
@@
 Panel (g) shows the average threshold elevation factor for each combination of target and mask stimulus.
-Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull $\\beta$ units.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/MCSdata.pdf')
-
-```
-
-Threshold elevation was greatest when the target and mask had the same chromaticity - notice that the psychometric function is shifted furthest to the right for the achromatic target with an achromatic mask (white and black circles in Figure \@ref(fig:MCSfig)a), for the red/green target with a red/green mask (red and green circles in Figure \@ref(fig:MCSfig)b), and for the blue/yellow target with a blue/yellow mask (blue and yellow circles in Figure \@ref(fig:MCSfig)c).
+Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull $\beta$ units.](Figures/MCSdata.pdf){#fig-MCSfig}
+
+Threshold elevation was greatest when the target and mask had the same chromaticity - notice that the psychometric function is shifted furthest to the right for the achromatic target with an achromatic mask (white and black circles in [@fig-MCSfig]a), for the red/green target with a red/green mask (red and green circles in [@fig-MCSfig]b), and for the blue/yellow target with a blue/yellow mask (blue and yellow circles in [@fig-MCSfig]c).
 Masking was weakest between achromatic masks/targets and chromatic masks/targets.
 Finally there was an intermediate level of masking between red/green and blue/yellow stimuli.
-This is summarised in Figure \@ref(fig:MCSfig)g, which represents threshold elevation for each combination of target and mask chromaticity.
+This is summarised in [@fig-MCSfig]g, which represents threshold elevation for each combination of target and mask chromaticity.
 Note that the positive diagonal exhibits the highest values, and represents threshold elevation between targets and masks of the same chromaticity.
@@
 Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,1],meanslopesMCS[2,2],meanslopesMCS[3,3])))),digits=2)`).
-These 'super-steep' psychometric functions for dichoptic pedestal masking have been reported previously [@Meese2006; @Baker2013], and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \@ref(fig:MCSfig)h, and also Figure \@ref(fig:dipperfig)d-f).
+These 'super-steep' psychometric functions for dichoptic pedestal masking have been reported previously [@Meese2006; @Baker2013], and are observed for the first time here using chromatic stimuli (see diagonal values in [@fig-MCSfig]h, and also [@fig-dipperfig]d-f).
 However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,2],meanslopesMCS[1,3],meanslopesMCS[2,1],meanslopesMCS[2,3],meanslopesMCS[3,1],meanslopesMCS[3,2])))),digits=2)` for the off-diagonal values).
@@
 This was motivated by our recent work [@Segala2023] that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
-The pattern of dipper functions for a 4Hz flickering disc (see Figure \@ref(fig:discdata)a) was very similar to that observed for achromatic gratings (see Figure \@ref(fig:dipperfig)a), and the binocular summation ratio at threshold was also similar (a factor of `r round(10^(summationDisc/20),digits=2)` for discs, vs `r round(10^(summation[1]/20),digits=2)` for gratings).
-Threshold data for individual participants are shown in Figure \@ref(fig:individualdiscs).
-We also found a similar pattern of psychometric slope values (Figure \@ref(fig:discdata)b) as we had for gratings, though we note that the dichoptic condition did not produce the 'super-steep' psychometric functions we had observed in Experiments 1 & 2.
+The pattern of dipper functions for a 4Hz flickering disc (see [@fig-discdata]a) was very similar to that observed for achromatic gratings (see [@fig-dipperfig]a), and the binocular summation ratio at threshold was also similar (a factor of `r round(10^(summationDisc/20),digits=2)` for discs, vs `r round(10^(summation[1]/20),digits=2)` for gratings).
+Threshold data for individual participants are shown in [@fig-individualdiscs].
+We also found a similar pattern of psychometric slope values ([@fig-discdata]b) as we had for gratings, though we note that the dichoptic condition did not produce the 'super-steep' psychometric functions we had observed in Experiments 1 & 2.
 Nevertheless, the dichoptic slopes are somewhat above those of the other pedestal arrangements at high contrasts.
 
-```{r discdata, out.width = "80%", fig.cap="Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 4.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/discdata.pdf')
-
-```
+![Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 4.](Figures/discdata.pdf){#fig-discdata width=80%}
 
@@
 
-```{r parametertable, echo=FALSE}
+```{r setuptable}
+#| echo: false
 
@@
 tableparams[c(2,7),2:9] <- ' '
-
-knitr::kable(tableparams, caption='Summary of fitted model parameters.
+```
+
+```{r}
+#| label: tbl-parametertable
+#| echo: false
+#| tbl-cap: 'Summary of fitted model parameters.
 The top row gives the best fitting parameters from the study of Meese et al.
@@
 The second section shows the best fitting parameters from simplex fits to the averaged thresholds for each experiment.
-The final rows show the posterior parameter estimates from the Bayesian model, fitted to each data set from Experiments 1 and 3.', align='lrrrrrrrr', booktabs = TRUE, linesep='',escape = FALSE) %>%
+The final rows show the posterior parameter estimates from the Bayesian model, fitted to each data set from Experiments 1 and 3.'
+
+knitr::kable(tableparams, align='lrrrrrrrr', booktabs = TRUE, linesep='',escape = FALSE) %>%
 row_spec(c(1,6),hline_after=T) %>% row_spec(0,italic=T) %>% row_spec(c(0,2,7),bold=T)
@@
 For consistency with previous work, we initially performed least-squares fits of the two-stage model [@Meese2006] for each of the chromaticity experiments, and the flickering disc experiment (7 free parameters per fit).
-The best model fits are shown by the curves in Figures \@ref(fig:dipperfig) & \@ref(fig:discdata), and provide an excellent description of the data, with RMS errors between `r round(min(allrms),digits=2)` and `r round(max(allrms),digits=2)`dB.
-Best fitting parameters are shown in the 'Simplex fits' section of Table \@ref(tab:parametertable).
+The best model fits are shown by the curves in @fig-dipperfig & @fig-discdata, and provide an excellent description of the data, with RMS errors between `r round(min(allrms),digits=2)` and `r round(max(allrms),digits=2)`dB.
+Best fitting parameters are shown in the 'Simplex fits' section of @tbl-parametertable.
 We note that in previous work, the weight of interocular suppression ($\omega$ in the model) is implicitly fixed at 1.
@@
 the model was fitted separately to each of the four dipper data sets).
-Figure \@ref(fig:bayesianmodel)a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
-Mean posterior parameter values are given in the lower rows of Table \@ref(tab:parametertable).
+[@fig-bayesianmodel]a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
+Mean posterior parameter values are given in the lower rows of @tbl-parametertable.
 These correspond quite closely to the parameters from the simplex fitting and the original @Meese2006 parameters (reproduced in the first row of the table for reference).
-The panels in the right and upper margins of Figure \@ref(fig:bayesianmodel) show posterior distributions for each model parameter.
+The panels in the right and upper margins of [@fig-bayesianmodel] show posterior distributions for each model parameter.
 Note in particular that the posterior distribution for the weight of interocular suppression ($\omega$, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
@@
 
-```{r bayesianmodel, fig.cap="Model predictions (a-d) and posterior parameters (top and right margin plots) for the hierarchical Bayesian model.
+![Model predictions (a-d) and posterior parameters (top and right margin plots) for the hierarchical Bayesian model.
 Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates.
@@
 Distributions were generated from 1000000 samples per data set, using a Markov Chain Monte Carlo sampling algorithm.
-Note the logarithmic x-axis for all posterior plots.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/stanoutput.pdf')
-
-```
+Note the logarithmic x-axis for all posterior plots.](Figures/stanoutput.pdf){#fig-bayesianmodel}
 
 Finally we fitted an extended model, that included interocular suppression between the different pathways, to the data of Experiment 2.
-Figure \@ref(fig:MCSmodel) shows the model curves (panels a-c), which correspond closely to the data in Figure \@ref(fig:MCSfig).
+[@fig-MCSmodel] shows the model curves (panels a-c), which correspond closely to the data in [@fig-MCSfig].
 One striking discrepancy is that the model predicts a region of negative d-prime for the case where the target and dichoptic mask have the same chromaticity (see the curved regions below 50\% correct).
-This feature was not generally present in our data, though it can be observed for one participant in Figure \@ref(fig:individualMCS)b,c.
+This feature was not generally present in our data, though it can be observed for one participant in [@fig-individualMCS]b,c.
 Our previous work [@Baker2013] has found evidence for this phenomenon (termed 'swan functions'), but it generally requires very high mask contrasts to be measurable empirically, and there may also be some individual differences; both factors might explain its absence here.
 
-Figure \@ref(fig:MCSmodel)d,e shows the model estimates for the weight of interocular suppression in each combination of target and mask chromaticity.
+[@fig-MCSmodel]d,e shows the model estimates for the weight of interocular suppression in each combination of target and mask chromaticity.
 Although the weights might appear to indicate that (excluding within-mechanism effects) suppression is strongest between blue/yellow targets and achromatic masks (a weight of 0.56), this is somewhat complicated by the differences in sensitivity and mask contrast between conditions.
-We selected mask contrasts that were approximately equal multiples ($16\times$) of their own detection thresholds, based on the data of Experiment 1 (Figure \@ref(fig:dipperfig)a-c).
+We selected mask contrasts that were approximately equal multiples ($16\times$) of their own detection thresholds, based on the data of Experiment 1 ([@fig-dipperfig]a-c).
 However the modelling expressed these contrasts as a percentage of the maximum contrast that it was possible to display on the monitor (see Procedures).
-The values in brackets in Figure \@ref(fig:MCSmodel)d indicate the overall suppressive term on the denominator, calculated by multiplying the mask contrast by the fitted weight.
-These values indicate that the strongest suppression is instead between red/green targets and blue/yellow masks, consistent with the threshold elevation observed empirically (Figure \@ref(fig:MCSfig)g).
+The values in brackets in [@fig-MCSmodel]d indicate the overall suppressive term on the denominator, calculated by multiplying the mask contrast by the fitted weight.
+These values indicate that the strongest suppression is instead between red/green targets and blue/yellow masks, consistent with the threshold elevation observed empirically ([@fig-MCSfig]g).
 In principle it would be possible to repeat this modelling using either cone contrast values, or contrast expressed relative to detection threshold, which would require re-fitting the model.
 
-```{r MCSmodel, fig.cap="Summary of the model fit to the data of Experiment 2.
+![Summary of the model fit to the data of Experiment 2.
 Panels (a-c) show model psychometric functions in the same format as those in Figure 5.
-Panel (d) shows the fitted suppressive weights ($\\omega$ values), with values in brackets indicating the combined suppressive denominator term calculated by multiplying together the suppressive weight and the dichoptic mask contrast.
+Panel (d) shows the fitted suppressive weights ($\omega$ values), with values in brackets indicating the combined suppressive denominator term calculated by multiplying together the suppressive weight and the dichoptic mask contrast.
 Panel (e) shows the posterior distributions for each weight parameter.
-The lower right plot gives the legends for the upper row (top) and the posterior distributions in panel (e).", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/MCSmodel.pdf')
-
-```
+The lower right plot gives the legends for the upper row (top) and the posterior distributions in panel (e).](Figures/MCSmodel.pdf){#fig-MCSmodel}
 
@@
 The summation ratio can be approximated by $2^{1/m}$ [see Figure 9 of @Baker2012], such that an exponent of $m=1$ produces a ratio of 2, and an exponent of $m = 2$ produces a ratio of $\sqrt{2}$.
-Both the simplex and Bayesian model fits (see Table \@ref(tab:parametertable)) generated parameter estimates in the range $1 < m < 1.4$, consistent with the high levels of summation observed empirically.
+Both the simplex and Bayesian model fits (see @tbl-parametertable) generated parameter estimates in the range $1 < m < 1.4$, consistent with the high levels of summation observed empirically.
 
@@
 The weight of interocular suppression is represented by the model parameter, $\omega$ (Equations 1 & 2).
-Posterior distributions of this parameter overlapped 1 for all of our dipper function data sets (see top right panel in Figure \@ref(fig:bayesianmodel)), indicating strong interocular suppression regardless of post-retinal pathway.
+Posterior distributions of this parameter overlapped 1 for all of our dipper function data sets (see top right panel in [@fig-bayesianmodel]), indicating strong interocular suppression regardless of post-retinal pathway.
 The flickering disc stimuli produced a slightly lower suppression estimate, with $\omega \sim 0.9$.
@@
 Other studies using static luminance increments have also reported differences in the character of binocular combination that are attributable to background luminance [@Baker2012], so this may explain the differences between studies.
-We also note that the weaker interocular suppression for flickering disc stimuli appears to be largely due to one participant (see Figure \@ref(fig:individualdiscs)c), so individual differences might also play a role.
+We also note that the weaker interocular suppression for flickering disc stimuli appears to be largely due to one participant (see [@fig-individualdiscs]c), so individual differences might also play a role.
 Future work should manipulate the background luminance systematically to better understand how this modulates interocular suppression.
@@
 In particular, pedestal masking linearizes the slope [@Foley1981; @Meese2006], and within-channel dichoptic masking produces very steep slopes [@Meese2006; @Baker2013].
-We replicate both of these effects here, and show that they extend to isoluminant chromatic pathways (see Figures \@ref(fig:dipperfig)d-f, \@ref(fig:MCSfig)).
-We additionally show that dichoptic masking between different pathways does not produce unusually steep slopes (see Figure \@ref(fig:MCSfig)).
+We replicate both of these effects here, and show that they extend to isoluminant chromatic pathways (see [@fig-dipperfig]d-f & @fig-MCSfig).
+We additionally show that dichoptic masking between different pathways does not produce unusually steep slopes (see [@fig-MCSfig]).
 It therefore more closely resembles other types of masking between visual channels, such as cross-orientation masking [@Meese2009], surround masking [@Yu2002], and masking from broadband noise [@Baker2012b; @Lu2008], which also do not impact psychometric slopes.
@@
 Presumably binocular summation of signals occurs at a later stage of processing for chromatic stimuli, but this does not lead to different perceptual outcomes.
-This physiological arrangement might also be responsible for the pattern of between-pathway interocular suppression (see Figure \@ref(fig:MCSfig)g).
+This physiological arrangement might also be responsible for the pattern of between-pathway interocular suppression (see [@fig-MCSfig]g).
 If blobs process signals from both the L-M and S-(L+M) pathways, their close physical proximity might explain the stronger suppression between the two chromatic pathways than between the chromatic and (more distant) achromatic pathways.
@@
 
-```{r individualdips, fig.cap="Individual participant data from Experiment 1.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/individualdippers.pdf')
-
-```
-
-```{r individualMCS, fig.cap="Individual participant data from Experiment 2.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/individualMCS.pdf')
-
-```
-
-```{r individualdiscs, fig.cap="Individual participant data from Experiment 3.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/individualdiscs.pdf')
-
-```
+![Individual participant data from Experiment 1.](Figures/individualdippers.pdf){#fig-individualdippers}
+
+![Individual participant data from Experiment 2.](Figures/individualMCS.pdf){#fig-individualMCS}
+
+![Individual participant data from Experiment 3.](Figures/individualdiscs.pdf){#fig-individualdiscs}

### 2024-04-01 manuscript.tex
Trying again

@@
 \PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
 %
 \documentclass[
-]{article}
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
+
 \usepackage{amsmath,amssymb}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 \usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
 \newlength{\cslhangindent}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\usepackage{float} \floatplacement{figure}{H} \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
+
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
+\KOMAoption{captions}{tableheading}
+\usepackage{float} \floatplacement{figure}{H} \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\makeatother
 \ifLuaTeX
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
+\urlstyle{same} % disable monospaced font for URLs
 \hypersetup{
   pdftitle={Binocular integration of chromatic and luminance signals},
-  hidelinks,
+  pdfauthor={Daniel H. Baker; Kirralise J. Hansford; Federico G. Segala; Annie Y. Morsi; Rowan J. Huxley; Joel T. Martin; Maya Rockman; Alex R. Wade},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
   pdfcreator={LaTeX via pandoc}}
@@
 \title{Binocular integration of chromatic and luminance signals}
-\author{Daniel H. Baker, Kirralise J. Hansford, Federico G. Segala, Annie Y. Morsi,\\
-Rowan J. Huxley, Joel T. Martin, Maya Rockman \& Alex R. Wade}
-\date{Department of Psychology, University of York}
+\author{Daniel H. Baker \and Kirralise J. Hansford \and Federico G.
+Segala \and Annie Y. Morsi \and Rowan J. Huxley \and Joel T.
+Martin \and Maya Rockman \and Alex R. Wade}
+\date{}
 
@@
 \maketitle
-
 \hypertarget{abstract}{%
@@
 
-The process by which the brain combines independent inputs is of fundamental importance for understanding sensory perception.
-Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains typically combine the inputs from the left and right eyes to provide binocular single vision.
-In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data from multiple experimental paradigms and techniques, including psychophysics (Meese et al., 2006), EEG (Baker \& Wade, 2017), fMRI (Moradi \& Heeger, 2009) and pupillometry (Segala et al., 2023).
-However, the majority of this work has used achromatic (black and white) stimuli; we know comparatively little about how chromatic signals are combined binocularly, or about how signals in different ocular and chromatic channels interact.
-In this study we use psychophysical detection and discrimination paradigms to explore binocular interactions within and between the chromatic and achromatic pathways.
-
-A useful framework for understanding binocular signal processing is the two-stage gain control model of binocular combination introduced by Meese et al.
-(2006).
-This model features interocular suppression between monocular channels, followed by binocular summation.
-The model accounts well for the pattern of contrast discrimination (`dipper') functions for four distinct ocular configurations (see also Georgeson et al., 2016), illustrated in Figure \ref{fig:exampledips}.
-In the monocular condition, participants must discriminate between stimuli of two contrasts (a `pedestal', and a `pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance.
-Threshold is defined as the minimum target contrast required to make this judgement with 75\% accuracy.
-The binocular condition is the same, except that the same stimuli are shown to both eyes.
-In the half-binocular condition the pedestal is shown to both eyes, but the target increment shown only to one eye.
-Finally, the dichoptic condition involves presenting the pedestal to one eye, and the target increment to the other eye.
+The process by which the brain combines independent inputs is of
+fundamental importance for understanding sensory perception. Binocular
+vision is a useful test-case for determining the general principles
+involved in neural signal combination, as our brains typically combine
+the inputs from the left and right eyes to provide binocular single
+vision. In recent years our understanding has been facilitated by the
+development of binocular gain control models that provide a framework to
+interpret empirical data from multiple experimental paradigms and
+techniques, including psychophysics (Meese et al., 2006), EEG (Baker \&
+Wade, 2017), fMRI (Moradi \& Heeger, 2009) and pupillometry (Segala et
+al., 2023). However, the majority of this work has used achromatic
+(black and white) stimuli; we know comparatively little about how
+chromatic signals are combined binocularly, or about how signals in
+different ocular and chromatic channels interact. In this study we use
+psychophysical detection and discrimination paradigms to explore
+binocular interactions within and between the chromatic and achromatic
+pathways.
+
+A useful framework for understanding binocular signal processing is the
+two-stage gain control model of binocular combination introduced by
+Meese et al. (2006). This model features interocular suppression between
+monocular channels, followed by binocular summation. The model accounts
+well for the pattern of contrast discrimination (`dipper') functions for
+four distinct ocular configurations (see also Georgeson et al., 2016),
+illustrated in Figure~\ref{fig-exampledips}. In the monocular condition,
+participants must discriminate between stimuli of two contrasts (a
+`pedestal', and a `pedestal plus target') that are both presented to one
+eye, whilst the other eye views mean luminance. Threshold is defined as
+the minimum target contrast required to make this judgement with 75\%
+accuracy. The binocular condition is the same, except that the same
+stimuli are shown to both eyes. In the half-binocular condition the
+pedestal is shown to both eyes, but the target increment shown only to
+one eye. Finally, the dichoptic condition involves presenting the
+pedestal to one eye, and the target increment to the other eye.
 
@@
 
-{\centering \includegraphics{Figures/exampledips}
+{\centering \includegraphics{Figures/exampledips.pdf}
 
@@
 
-\caption{Illustration of stimulus conditions (left) and example dipper functions (right).}\label{fig:exampledips}
+\caption{\label{fig-exampledips}Illustration of stimulus conditions
+(left) and example dipper functions (right).}
+
 \end{figure}
 
-The detailed pattern of thresholds across these four conditions is complex, and for achromatic stimuli has several distinctive features that have been replicated in multiple studies.
-At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition; this result is attributed to physiological binocular summation by neurons responsive to signals from both eyes (Baker et al., 2018; Campbell \& Green, 1965).
-However at high pedestal contrasts the `handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation (Legge, 1984; Maehara \& Goryo, 2005).
-The half-binocular condition avoids confounding the number of eyes seeing the target with the number of eyes seeing the pedestal (Meese et al., 2006).
-The pedestal is always binocular in this condition, whereas the target increment is monocular, and thresholds are consistently higher than in the binocular condition across the full range of pedestal contrasts.
-This demonstrates that binocular summation occurs across the full contrast range, when the pedestal ocularity is appropriately controlled.
-Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast in order to be detectable (Baker \& Meese, 2007; Legge, 1979; Maehara \& Goryo, 2005).
-The characteristic pattern of dipper functions is well-described by the gain control model of Meese et al.
-(2006) for achromatic stimuli.
-
-At the output of the human retina, cone responses are split into three distinct pathways.
-The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information, and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
-The difference of long- and medium-wavelength cone outputs (L-M) is responsive to chromatic stimuli modulating along a red/green axis in colour space.
-Finally the short wavelength cone outputs (S-(L+M)) code chromatic stimuli modulating along a blue/yellow axis.
-There has not yet been a detailed investigation of binocular contrast discrimination in either of these chromatic pathways, however there is reason to believe they may differ from the achromatic pathway.
-At detection threshold, binocular summation is greater for chromatic versus achromatic stimuli (Simmons, 2005), implying a more linear initial stage of processing.
-For cross-orientation masking, there are differences in the magnitude of masking between chromatic (red/green) and achromatic stimuli (Kim et al., 2013; Medina \& Mullen, 2009), as well as differences in their temporal dynamics (Kim \& Mullen, 2015).
-There are also interactions between chromatic and achromatic pathways both within (Chen et al., 2000) and between (Kingdom \& Libenson, 2015; Mullen et al., 2014) the eyes, yet these have not been fully explored for arrangements where the target and mask have the same orientation.
-Finally, the neurophysiological underpinnings of colour vision are distinct from those of the achromatic system.
-In primary visual cortex (V1), chromatic signals are processed in `blob' regions that are revealed by cytochrome oxidase staining (Horton \& Hubel, 1981).
-The blob regions appear to be largely monocular (Livingstone \& Hubel, 1984), suggesting that binocular combination for chromatic stimuli might occur later than for achromatic stimuli, and perhaps be subject to different constraints.
-
-A further property of `blob' regions is that they are less strongly orientation-tuned than other regions of V1 (Horton \& Hubel, 1981; Livingstone \& Hubel, 1984), and biased towards low spatial frequencies (Edwards et al., 1995; Tootell et al., 1988).
-Our recent work has investigated binocular combination for flickering discs of luminance, which are DC-balanced across time (Segala et al., 2023).
-Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement.
-This is very different from the `ocularity invariance' that is well-established when using DC-balanced periodic stimuli such as sine-wave gratings, and implies strong interocular suppression (Baker \& Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009).
-There is additional psychophysical evidence from matching studies that binocular combination can be close to linear for luminance increments (Anstis \& Ho, 1998; Levelt, 1965), particularly against a dark background (Baker et al., 2012).
-Both structural and functional data therefore imply that binocular combination may differ between spatial and temporal contrast.
-
-The main aim of the present study is to characterise binocular signal combination for chromatic stimuli, and for temporal modulations of luminance.
-We also aimed to investigate interocular suppression between chromatic and achromatic pathways.
-We therefore preregistered a series of psychophysical experiments (see: \url{https://osf.io/3vdga/}).
-In Experiment 1 we replicate the four key pedestal masking conditions of Meese et al.
-(2006) described above for achromatic grating stimuli, and extend this to both red/green and blue/yellow isoluminant chromatic stimuli.
-In Experiment 2 we explore dichoptic masking within and between these stimuli.
-Experiment 3 repeats the achromatic condition from the first experiment, but using a temporally modulated disc rather than sine-wave gratings.
-We take a Bayesian approach to data analysis and modelling; by fitting a hierarchical version of the two-stage gain control model (Meese et al., 2006) we compare posterior parameter distributions to understand how model parameters such as the weight of interocular suppression vary across visual pathways.
+The detailed pattern of thresholds across these four conditions is
+complex, and for achromatic stimuli has several distinctive features
+that have been replicated in multiple studies. At low pedestal
+contrasts, the binocular condition yields lower thresholds than the
+monocular condition; this result is attributed to physiological
+binocular summation by neurons responsive to signals from both eyes
+(Baker et al., 2018; Campbell \& Green, 1965). However at high pedestal
+contrasts the `handle' regions of the dipper functions for these
+conditions converge: a consequence of interocular suppression
+compensating for the increased excitation during binocular stimulation
+(Legge, 1984; Maehara \& Goryo, 2005). The half-binocular condition
+avoids confounding the number of eyes seeing the target with the number
+of eyes seeing the pedestal (Meese et al., 2006). The pedestal is always
+binocular in this condition, whereas the target increment is monocular,
+and thresholds are consistently higher than in the binocular condition
+across the full range of pedestal contrasts. This demonstrates that
+binocular summation occurs across the full contrast range, when the
+pedestal ocularity is appropriately controlled. Finally, the dichoptic
+condition produces extremely strong masking of the target, such that
+when the pedestal is visible, the target must equal or exceed its
+contrast in order to be detectable (Baker \& Meese, 2007; Legge, 1979;
+Maehara \& Goryo, 2005). The characteristic pattern of dipper functions
+is well-described by the gain control model of Meese et al. (2006) for
+achromatic stimuli.
+
+At the output of the human retina, cone responses are split into three
+distinct pathways. The sum of long- and medium-wavelength cone outputs
+(L+M) transmits luminance information, and is likely responsible for the
+binocular combination effects previously studied using achromatic
+stimuli (see above). The difference of long- and medium-wavelength cone
+outputs (L-M) is responsive to chromatic stimuli modulating along a
+red/green axis in colour space. Finally the short wavelength cone
+outputs (S-(L+M)) code chromatic stimuli modulating along a blue/yellow
+axis. There has not yet been a detailed investigation of binocular
+contrast discrimination in either of these chromatic pathways, however
+there is reason to believe they may differ from the achromatic pathway.
+At detection threshold, binocular summation is greater for chromatic
+versus achromatic stimuli (Simmons, 2005), implying a more linear
+initial stage of processing. For cross-orientation masking, there are
+differences in the magnitude of masking between chromatic (red/green)
+and achromatic stimuli (Kim et al., 2013; Medina \& Mullen, 2009), as
+well as differences in their temporal dynamics (Kim \& Mullen, 2015).
+There are also interactions between chromatic and achromatic pathways
+both within (Chen et al., 2000) and between (Kingdom \& Libenson, 2015;
+Mullen et al., 2014) the eyes, yet these have not been fully explored
+for arrangements where the target and mask have the same orientation.
+Finally, the neurophysiological underpinnings of colour vision are
+distinct from those of the achromatic system. In primary visual cortex
+(V1), chromatic signals are processed in `blob' regions that are
+revealed by cytochrome oxidase staining (Horton \& Hubel, 1981). The
+blob regions appear to be largely monocular (Livingstone \& Hubel,
+1984), suggesting that binocular combination for chromatic stimuli might
+occur later than for achromatic stimuli, and perhaps be subject to
+different constraints.
+
+A further property of `blob' regions is that they are less strongly
+orientation-tuned than other regions of V1 (Horton \& Hubel, 1981;
+Livingstone \& Hubel, 1984), and biased towards low spatial frequencies
+(Edwards et al., 1995; Tootell et al., 1988). Our recent work has
+investigated binocular combination for flickering discs of luminance,
+which are DC-balanced across time (Segala et al., 2023). Steady-state
+EEG responses from early visual cortex and psychophysical contrast
+matching data were both consistent with weak interocular suppression
+when using this stimulus arrangement. This is very different from the
+`ocularity invariance' that is well-established when using DC-balanced
+periodic stimuli such as sine-wave gratings, and implies strong
+interocular suppression (Baker \& Wade, 2017; Meese et al., 2006; Moradi
+\& Heeger, 2009). There is additional psychophysical evidence from
+matching studies that binocular combination can be close to linear for
+luminance increments (Anstis \& Ho, 1998; Levelt, 1965), particularly
+against a dark background (Baker et al., 2012). Both structural and
+functional data therefore imply that binocular combination may differ
+between spatial and temporal contrast.
+
+The main aim of the present study is to characterise binocular signal
+combination for chromatic stimuli, and for temporal modulations of
+luminance. We also aimed to investigate interocular suppression between
+chromatic and achromatic pathways. We therefore preregistered a series
+of psychophysical experiments (see: \url{https://osf.io/3vdga/}). In
+Experiment 1 we replicate the four key pedestal masking conditions of
+Meese et al. (2006) described above for achromatic grating stimuli, and
+extend this to both red/green and blue/yellow isoluminant chromatic
+stimuli. In Experiment 2 we explore dichoptic masking within and between
+these stimuli. Experiment 3 repeats the achromatic condition from the
+first experiment, but using a temporally modulated disc rather than
+sine-wave gratings. We take a Bayesian approach to data analysis and
+modelling; by fitting a hierarchical version of the two-stage gain
+control model (Meese et al., 2006) we compare posterior parameter
+distributions to understand how model parameters such as the weight of
+interocular suppression vary across visual pathways.
 
@@
 
-All experiments were completed by the first author (DHB) and two additional participants, who differed for each experiment.
-Participants had no known abnormalities of binocular vision.
-Written informed consent was obtained before data collection began, and all procedures were approved by the ethics committee of the Department of Psychology at the University of York (ID number 2202).
+All experiments were completed by the first author (DHB) and two
+additional participants, who differed for each experiment. Participants
+had no known abnormalities of binocular vision. Written informed consent
+was obtained before data collection began, and all procedures were
+approved by the ethics committee of the Department of Psychology at the
+University of York (ID number 2202).
 
@@
 
-In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings with a spatial frequency of 1c/deg (see examples in Figure \ref{fig:examplestim}).
-The gratings were windowed by a raised cosine envelope with a diameter of 3 degrees.
-Spatial phase, relative to a central fixation cross, was randomised on each trial across the four cardinal phases.
-In the achromatic conditions, the sine-wave modulated all three monitor colour channels equally (red, green and blue).
-In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant.
-In the S-(L+M) condition, the isoluminant stimuli maximised S-cone contrast.
-Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals (Stockman \& Sharpe, 2000).
-The stimuli in Experiment 3 were temporal modulations of luminance applied to a disc made using the same raised cosine envelope as described above, but with no further spatial modulation.
-The stimuli counterphase flickered sinusoidally at 4Hz (see examples in the lower portion of Figure \ref{fig:examplestim}).
-In all experiments, we displayed a binocular fusion lock, consisting of three concentric rings of small square elements with random colour.
-A black central fixation cross was also displayed throughout.
+In Experiments 1 and 2, the stimuli were horizontal sinusoidal gratings
+with a spatial frequency of 1c/deg (see examples in
+Figure~\ref{fig-examplestim}). The gratings were windowed by a raised
+cosine envelope with a diameter of 3 degrees. Spatial phase, relative to
+a central fixation cross, was randomised on each trial across the four
+cardinal phases. In the achromatic conditions, the sine-wave modulated
+all three monitor colour channels equally (red, green and blue). In the
+L-M condition, we generated isoluminant stimuli for each participant
+(see Procedures) designed to maximise contrast between L and M cones,
+whilst keeping S cone activity constant. In the S-(L+M) condition, the
+isoluminant stimuli maximised S-cone contrast. Stimuli were converted
+from cone space to monitor RGB coordinates using the monitor spectral
+readings and the Stockman-Sharpe 2 degree cone fundamentals (Stockman \&
+Sharpe, 2000). The stimuli in Experiment 3 were temporal modulations of
+luminance applied to a disc made using the same raised cosine envelope
+as described above, but with no further spatial modulation. The stimuli
+counterphase flickered sinusoidally at 4Hz (see examples in the lower
+portion of Figure~\ref{fig-examplestim}). In all experiments, we
+displayed a binocular fusion lock, consisting of three concentric rings
+of small square elements with random colour. A black central fixation
+cross was also displayed throughout.
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{Figures/examplestim}
+{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{Figures/examplestim.pdf}
 
@@
 
-\caption{Example stimuli.
-Upper row shows grating stimuli used in Experiments 1 and 2.
-Lower row shows one cycle of sinusoidal flicker applied to a uniform disc.
-Note that the rendering of all stimuli will depend on the device used to display or print this image, and so the chromatic stimuli are unlikely to appear isoluminant, and there may be additional luminance nonlinearities that were not present in the stimuli displayed during the experiments.}\label{fig:examplestim}
+\caption{\label{fig-examplestim}Example stimuli. Upper row shows grating
+stimuli used in Experiments 1 and 2. Lower row shows one cycle of
+sinusoidal flicker applied to a uniform disc. Note that the rendering of
+all stimuli will depend on the device used to display or print this
+image, and so the chromatic stimuli are unlikely to appear isoluminant,
+and there may be additional luminance nonlinearities that were not
+present in the stimuli displayed during the experiments.}
+
 \end{figure}
 
-All stimuli were presented on an Iiyama VisionMaster Pro 510 CRT monitor, with a refresh rate of 100Hz, and a resolution of 1024 x 768 pixels.
-The display was driven by a ViSaGe MkII stimulus generator (Cambridge Research Systems Ltd., Kent, UK) running in 42-bit colour mode (14 bits per colour channel).
-We presented stimuli to the left and right eyes independently using a four-mirror stereoscope with front-silvered mirrors.
-The display was luminance calibrated using a ColourCal photometer (Cambridge Research Systems), and gamma corrected by fitting a four-parameter gamma function to the output of each CRT gun.
-The maximum luminance was 87 cd/m\(^2\).
-We also measured the spectral output of each phosphor using a Jaz spectroradiometer (Ocean Insight, Florida), and used these measurements to convert between LMS (cone) space and the monitor RGB coordinates.
-
-For convenience, we express stimulus contrast as a percentage of the maximum possible contrast that could be displayed on our system.
-For achromatic stimuli, the maximum contrast is 1, so this is equivalent to the standard Michelson contrast expressed as a percentage.
-For the isoluminant chromatic stimuli, the maximum displayable L-M (red/green) cone contrast was 0.1, and the maximum displayable S-(L+M) (blue/yellow) cone contrast was 0.88.
-An L-M threshold of 50\% therefore corresponds to a cone contrast of \(0.5\times0.1 = 0.05\), and an S-(L+M) threshold of 50\% corresponds to a cone contrast of \(0.5\times0.88 = 0.44\).
-This means that the threshold values reported throughout can be converted to cone contrast by a straightforward multiplicative transform.
+All stimuli were presented on an Iiyama VisionMaster Pro 510 CRT
+monitor, with a refresh rate of 100Hz, and a resolution of 1024 x 768
+pixels. The display was driven by a ViSaGe MkII stimulus generator
+(Cambridge Research Systems Ltd., Kent, UK) running in 42-bit colour
+mode (14 bits per colour channel). We presented stimuli to the left and
+right eyes independently using a four-mirror stereoscope with
+front-silvered mirrors. The display was luminance calibrated using a
+ColourCal photometer (Cambridge Research Systems), and gamma corrected
+by fitting a four-parameter gamma function to the output of each CRT
+gun. The maximum luminance was 87 cd/m\(^2\). We also measured the
+spectral output of each phosphor using a Jaz spectroradiometer (Ocean
+Insight, Florida), and used these measurements to convert between LMS
+(cone) space and the monitor RGB coordinates.
+
+For convenience, we express stimulus contrast as a percentage of the
+maximum possible contrast that could be displayed on our system. For
+achromatic stimuli, the maximum contrast is 1, so this is equivalent to
+the standard Michelson contrast expressed as a percentage. For the
+isoluminant chromatic stimuli, the maximum displayable L-M (red/green)
+cone contrast was 0.1, and the maximum displayable S-(L+M) (blue/yellow)
+cone contrast was 0.88. An L-M threshold of 50\% therefore corresponds
+to a cone contrast of \(0.5\times0.1 = 0.05\), and an S-(L+M) threshold
+of 50\% corresponds to a cone contrast of \(0.5\times0.88 = 0.44\). This
+means that the threshold values reported throughout can be converted to
+cone contrast by a straightforward multiplicative transform.
 
@@
 
-All experiments took place in a darkened room.
-Participants placed their heads in a chin rest mounted on a height-adjustable table, to which the stereoscope was also attached.
-The total optical viewing distance (including the light path through the mirrors) was 104cm, at which distance 1 degree of visual angle encompassed 48 pixels on the monitor.
-
-Before beginning primary data collection, each participant in Experiments 1 and 2 completed an isoluminance adjustment task.
-Grating stimuli were presented that counterphase flickered at 5Hz, defined about either the L-M or S-(L+M) plane in cone space.
-Participants used a trackball to dynamically adjust the colour angle of the stimulus to minimise the percept of flicker.
-Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli for the main experiment for that participant.
-Settings were very similar across participants for the S-(L+M) direction, and somewhat more heterogeneous for the L-M direction (see Figure \ref{fig:isofig}).
+All experiments took place in a darkened room. Participants placed their
+heads in a chin rest mounted on a height-adjustable table, to which the
+stereoscope was also attached. The total optical viewing distance
+(including the light path through the mirrors) was 104cm, at which
+distance 1 degree of visual angle encompassed 48 pixels on the monitor.
+
+Before beginning primary data collection, each participant in
+Experiments 1 and 2 completed an isoluminance adjustment task. Grating
+stimuli were presented that counterphase flickered at 5Hz, defined about
+either the L-M or S-(L+M) plane in cone space. Participants used a
+trackball to dynamically adjust the colour angle of the stimulus to
+minimise the percept of flicker. Each participant completed ten such
+trials for each colour plane, and the average angle across repetition
+was taken as the isoluminant point, and used to generate stimuli for the
+main experiment for that participant. Settings were very similar across
+participants for the S-(L+M) direction, and somewhat more heterogeneous
+for the L-M direction (see Figure~\ref{fig-isofig}).
 
@@
 
-{\centering \includegraphics{Figures/isosettings}
+{\centering \includegraphics{Figures/isosettings.pdf}
 
@@
 
-\caption{Isoluminance settings from all participants in Experiments 1 and 2.
-Panel (a) shows red/green and panel (b) shows blue/yellow settings that were subsequently used to generate stimuli in the main experiments.
-Within each panel, solid lines show the mean settings for each participant, and black curves show the range of possible stimuli displayed during the adjustment task.}\label{fig:isofig}
+\caption{\label{fig-isofig}Isoluminance settings from all participants
+in Experiments 1 and 2. Panel (a) shows red/green and panel (b) shows
+blue/yellow settings that were subsequently used to generate stimuli in
+the main experiments. Within each panel, solid lines show the mean
+settings for each participant, and black curves show the range of
+possible stimuli displayed during the adjustment task.}
+
 \end{figure}
 
-In Experiment 1, participants completed a two-interval-forced-choice (2IFC) contrast discrimination task.
-Stimuli were presented for 200ms, with an interstimulus interval of 400ms.
-Each interval was indicated by an auditory beep, and participants made their responses using a two-button trackball.
-Correct responses were followed by a high pitched tone, and incorrect responses by a low pitched tone.
-Each block of the experiment tested a single pedestal contrast level, and lasted around 12 minutes.
-On each trial the target contrast level was determined by a 3-down-1-up staircase procedure.
-There were 8 interleaved staircases in total; four stimulus arrangements (see Figure \ref{fig:exampledips}) combined factorially with two target eye assignments.
-Each pedestal contrast was repeated 3 times by each participant, and the block order was randomised.
-The experiment lasted around 4 hours per participant for each chromatic condition, and took place over the course of several weeks.
-In total, the experiment consisted of 67978 trials (pooled across participants).
+In Experiment 1, participants completed a two-interval-forced-choice
+(2IFC) contrast discrimination task. Stimuli were presented for 200ms,
+with an interstimulus interval of 400ms. Each interval was indicated by
+an auditory beep, and participants made their responses using a
+two-button trackball. Correct responses were followed by a high pitched
+tone, and incorrect responses by a low pitched tone. Each block of the
+experiment tested a single pedestal contrast level, and lasted around 12
+minutes. On each trial the target contrast level was determined by a
+3-down-1-up staircase procedure. There were 8 interleaved staircases in
+total; four stimulus arrangements (see Figure~\ref{fig-exampledips})
+combined factorially with two target eye assignments. Each pedestal
+contrast was repeated 3 times by each participant, and the block order
+was randomised. The experiment lasted around 4 hours per participant for
+each chromatic condition, and took place over the course of several
+weeks. In total, the experiment consisted of 67978 trials (pooled across
+participants).
 
 In Experiment 2, participants completed a 2IFC dichoptic masking task.
-The stimuli and trial protocol were the same as for Experiment 1, except that the target contrast was chosen from a set of 10 possible values, determined in advance based on the data of Experiment 1.
-There were 12 possible conditions: baseline detection thresholds for achromatic, red/green and blue/yellow stimuli, and the nine possible factorial pairings obtained by assigning these conditions to be target and dichoptic mask stimuli.
-Mask contrasts were chosen to be approximately 16 times their (monocular) detection threshold, based on the data from Experiment 1.
-As a percentage of the maximum displayable contrast, these were 16\% for achromatic stimuli, and 64\% for both of the chromatic stimuli.
-Each block of the experiment tested a single condition, and consisted of 200 trials.
-A high contrast example of the target stimulus was displayed at the foot of the screen throughout, so that there was no ambiguity about the target identity on a given block.
-Participants completed 10 repetitions of each condition (120 blocks of \textasciitilde6 minutes each), lasting around 12 hours, for a total of 72000 trials (pooled across participants).
-
-In Experiment 3, the achromatic conditions from Experiment 1 were repeated using a flickering disc stimulus.
-The stimulus counterphase flickered at 4Hz, and was presented for 500ms (i.e.~2 full cycles of the temporal modulation).
-All other procedures were the same as for Experiment 1, and the experiment comprised a total of 24610 trials (pooled across participants).
+The stimuli and trial protocol were the same as for Experiment 1, except
+that the target contrast was chosen from a set of 10 possible values,
+determined in advance based on the data of Experiment 1. There were 12
+possible conditions: baseline detection thresholds for achromatic,
+red/green and blue/yellow stimuli, and the nine possible factorial
+pairings obtained by assigning these conditions to be target and
+dichoptic mask stimuli. Mask contrasts were chosen to be approximately
+16 times their (monocular) detection threshold, based on the data from
+Experiment 1. As a percentage of the maximum displayable contrast, these
+were 16\% for achromatic stimuli, and 64\% for both of the chromatic
+stimuli. Each block of the experiment tested a single condition, and
+consisted of 200 trials. A high contrast example of the target stimulus
+was displayed at the foot of the screen throughout, so that there was no
+ambiguity about the target identity on a given block. Participants
+completed 10 repetitions of each condition (120 blocks of
+\textasciitilde6 minutes each), lasting around 12 hours, for a total of
+72000 trials (pooled across participants).
+
+In Experiment 3, the achromatic conditions from Experiment 1 were
+repeated using a flickering disc stimulus. The stimulus counterphase
+flickered at 4Hz, and was presented for 500ms (i.e.~2 full cycles of the
+temporal modulation). All other procedures were the same as for
+Experiment 1, and the experiment comprised a total of 24610 trials
+(pooled across participants).
 
 \hypertarget{data-analysis-and-computational-modelling}{%
-\subsection{Data analysis and computational modelling}\label{data-analysis-and-computational-modelling}}
-
-Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate threshold and slope parameters via a Bayesian numerical integration method (Schütt et al., 2016).
-A cumulative Gaussian was used as the underlying function, and we converted the slope estimates (\(\sigma\) parameters from the fitted Gaussians) to equivalent Weibull \(\beta\) values using the approximation \(\beta = 10.3/\sigma\).
-
-The two stage model of Meese et al.
-(2006) was fit to the threshold data from Experiments 1 and 3 using a simplex algorithm to minimise the error between the model and data.
-The model is defined by a series of equations:
+\subsection{Data analysis and computational
+modelling}\label{data-analysis-and-computational-modelling}}
+
+Psychometric functions from each experiment were fit using
+\emph{psignifit} 4 to estimate threshold and slope parameters via a
+Bayesian numerical integration method (Schütt et al., 2016). A
+cumulative Gaussian was used as the underlying function, and we
+converted the slope estimates (\(\sigma\) parameters from the fitted
+Gaussians) to equivalent Weibull \(\beta\) values using the
+approximation \(\beta = 10.3/\sigma\).
+
+The two stage model of Meese et al. (2006) was fit to the threshold data
+from Experiments 1 and 3 using a simplex algorithm to minimise the error
+between the model and data. The model is defined by a series of
+equations:
 
@@
 
-where \(C_L\) and \(C_R\) are the contrasts displayed to the left and right eyes, and \(m\), \(S\), \(\omega\), \(p\), \(q\) and \(Z\) are free parameters in the model.
-A further free parameter, \(k\), represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values (note that in the original model specification (Meese et al., 2006) this parameter was called \(\sigma\), but we use the \(k\) symbol here to avoid confusion with the standard deviation of the cumulative Gaussian used when fitting the psychometric functions to derive thresholds).
-Thresholds are defined by iteratively adjusting the target contrast until the following equality is satisfied:
+where \(C_L\) and \(C_R\) are the contrasts displayed to the left and
+right eyes, and \(m\), \(S\), \(\omega\), \(p\), \(q\) and \(Z\) are
+free parameters in the model. A further free parameter, \(k\),
+represents additive internal noise, and is used to convert the model
+outputs to either d-prime or threshold values (note that in the original
+model specification (Meese et al., 2006) this parameter was called
+\(\sigma\), but we use the \(k\) symbol here to avoid confusion with the
+standard deviation of the cumulative Gaussian used when fitting the
+psychometric functions to derive thresholds). Thresholds are defined by
+iteratively adjusting the target contrast until the following equality
+is satisfied:
 
@@
 
-We ran the simplex algorithm from 100 random starting vectors for each data set, and chose the solution for each data set that gave the smallest RMS error.
-
-We also implemented a Bayesian hierarchical version of the model using the Stan language (Carpenter et al., 2017).
-This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants for a given experiment, but separately for each chromatic condition of Experiment 1, and the flickering disc data from Experiment 3 (i.e.~four fits in total, as for the simplex fitting).
-Prior distributions were Gaussian, with means determined from published values (see first row of Table \ref{tab:parametertable}).
-This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
-We generated over 1 million posterior samples for the model, and retained 10\% of them for plotting.
-
-Finally, we adapted the two stage model to include parallel pathways to process achromatic, red/green and blue/yellow stimuli, that mutually suppress each other.
-We added additional suppressive terms at the first (monocular) stage of the model, for example:
+We ran the simplex algorithm from 100 random starting vectors for each
+data set, and chose the solution for each data set that gave the
+smallest RMS error.
+
+We also implemented a Bayesian hierarchical version of the model using
+the Stan language (Carpenter et al., 2017). This used a binomial
+generator function to model the proportion correct data at each target
+level, and was fit simultaneously to all participants for a given
+experiment, but separately for each chromatic condition of Experiment 1,
+and the flickering disc data from Experiment 3 (i.e.~four fits in total,
+as for the simplex fitting). Prior distributions were Gaussian, with
+means determined from published values (see first row of
+Table~\ref{tbl-parametertable}). This modelling primarily focuses on
+examining posterior parameter distributions, rather than a model
+comparison approach. We generated over 1 million posterior samples for
+the model, and retained 10\% of them for plotting.
+
+Finally, we adapted the two stage model to include parallel pathways to
+process achromatic, red/green and blue/yellow stimuli, that mutually
+suppress each other. We added additional suppressive terms at the first
+(monocular) stage of the model, for example:
 
@@
 
-where \emph{AC} represents the achromatic contrast, \emph{RG} represents the red/green contrast, \emph{BY} represents the blue/yellow contrast, and \(\omega_A\), \(\omega_R\) and \(\omega_B\) are the accompanying weights of interocular suppression.
-There is an equivalent expression for the right eye, and for each of the two isoluminant chromatic pathways.
-To simplify the model, and avoid free parameters that are poorly constrained by the data, we fixed several parameters at the average values from the fits from Experiment 1 (Table \ref{tab:parametertable}), such that \(p=7.82\), \(q=6.4\), \(m=1.21\), \(S=1.03\) and \(k=0.23\).
-We additionally fixed the within-mechanism weight of interocular suppression (\(\omega\)) at 1.
-This left 9 free parameters: a \(Z\) parameter for each mechanism, and six cross-mechanism weights of interocular suppression.
-These parameters were again estimated within a Bayesian hierarchical framework, using the trial-wise data from Experiment 2.
-Note that the model as specified does not currently include monocular suppression between different pathways, as we did not collect any data for these conditions.
-Previous work (Chen et al., 2000) has measured such interactions, and they could in principle be incorporated into the denominator of either stage 1 or stage 2 in the model.
+where \emph{AC} represents the achromatic contrast, \emph{RG} represents
+the red/green contrast, \emph{BY} represents the blue/yellow contrast,
+and \(\omega_A\), \(\omega_R\) and \(\omega_B\) are the accompanying
+weights of interocular suppression. There is an equivalent expression
+for the right eye, and for each of the two isoluminant chromatic
+pathways. To simplify the model, and avoid free parameters that are
+poorly constrained by the data, we fixed several parameters at the
+average values from the fits from Experiment 1
+(Table~\ref{tbl-parametertable}), such that \(p=7.82\), \(q=6.4\),
+\(m=1.21\), \(S=1.03\) and \(k=0.23\). We additionally fixed the
+within-mechanism weight of interocular suppression (\(\omega\)) at 1.
+This left 9 free parameters: a \(Z\) parameter for each mechanism, and
+six cross-mechanism weights of interocular suppression. These parameters
+were again estimated within a Bayesian hierarchical framework, using the
+trial-wise data from Experiment 2. Note that the model as specified does
+not currently include monocular suppression between different pathways,
+as we did not collect any data for these conditions. Previous work (Chen
+et al., 2000) has measured such interactions, and they could in
+principle be incorporated into the denominator of either stage 1 or
+stage 2 in the model.
 
@@
 
-All experimental code, raw data and analysis scripts are available at: \url{https://osf.io/3vdga/}.
-The linked GitHub repository also contains a fully reproducible version of the manuscript.
-Note that we deviated slightly from the planned preregistration, in that we did not collect data for chromatic flickering discs, or for the cross-pathway dichoptic experiment using disc stimuli.
-This is because the grating data from Experiments 1 and 2, and the achromatic disc data from Experiment 3, were sufficient to address the questions we had hoped to answer from these experiments.
+All experimental code, raw data and analysis scripts are available at:
+https://osf.io/3vdga/. The linked GitHub repository also contains a
+fully reproducible version of the manuscript. Note that we deviated
+slightly from the planned preregistration, in that we did not collect
+data for chromatic flickering discs, or for the cross-pathway dichoptic
+experiment using disc stimuli. This is because the grating data from
+Experiments 1 and 2, and the achromatic disc data from Experiment 3,
+were sufficient to address the questions we had hoped to answer from
+these experiments.
 
@@
 
-Dipper functions from Experiment 1 are displayed in the upper row of Figure \ref{fig:dipperfig}.
-Panel (a) shows the achromatic results, which replicate the key features from previous work.
-At detection threshold, binocular summation was a factor of 1.67 (4.47dB), within the range (\(\sqrt{2}\) to 2) consistent with previous reports (Baker et al., 2018).
-Pedestal masking functions followed the typical `dipper' shape in all conditions, with a region of facilitation at low pedestal contrasts, and masking at higher contrasts.
-The monocular and binocular dipper handles converge at high contrasts, whereas the half-binocular thresholds remain above the binocular thresholds across the full range of pedestal contrasts.
-The dichoptic condition produced very high thresholds, with the rising portion of the dipper having a slope around 1 (regression slope of 1.06 in log (dB) units, calculated across the highest 4 pedestal contrasts).
+Dipper functions from Experiment 1 are displayed in the upper row of
+Figure~\ref{fig-dipperfig}. Panel (a) shows the achromatic results,
+which replicate the key features from previous work. At detection
+threshold, binocular summation was a factor of 1.67 (4.47dB), within the
+range (\(\sqrt{2}\) to 2) consistent with previous reports (Baker et
+al., 2018). Pedestal masking functions followed the typical `dipper'
+shape in all conditions, with a region of facilitation at low pedestal
+contrasts, and masking at higher contrasts. The monocular and binocular
+dipper handles converge at high contrasts, whereas the half-binocular
+thresholds remain above the binocular thresholds across the full range
+of pedestal contrasts. The dichoptic condition produced very high
+thresholds, with the rising portion of the dipper having a slope around
+1 (regression slope of 1.06 in log (dB) units, calculated across the
+highest 4 pedestal contrasts).
 
@@
 
-{\centering \includegraphics{Figures/dipperssimplex}
+{\centering \includegraphics{Figures/dipperssimplex.pdf}
 
@@
 
-\caption{Dipper functions and psychometric slopes from Experiment 1, averaged across three participants.
-Panels (a-c) show threshold data, and panels (d-f) represent the slope of the psychometric function expressed in Weibull $\beta$ units.
-Error bars give ±1SE across participants.
-Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).
-Curves in panels (a-c) show the best fitting models, optimized using a simplex algorithm (described in section 4.4), and RMSE values give the root mean square errors of the fits.}\label{fig:dipperfig}
+\caption{\label{fig-dipperfig}Dipper functions and psychometric slopes
+from Experiment 1, averaged across three participants. Panels (a-c) show
+threshold data, and panels (d-f) represent the slope of the psychometric
+function expressed in Weibull \(\beta\) units. Error bars give ±1SE
+across participants. Note that contrast values are expressed as a
+percentage of the maximum displayable contrast (see Procedures for
+details). Curves in panels (a-c) show the best fitting models, optimized
+using a simplex algorithm (described in section 4.4), and RMSE values
+give the root mean square errors of the fits.}
+
 \end{figure}
 
-A similar pattern of results was observed for both the red/green and blue/yellow isoluminant stimuli (see Figure \ref{fig:dipperfig}b,c).
-Summation at threshold was a factor of 1.71 (4.66dB) for the red/green targets, and a factor of 1.73 (4.77dB) for the blue/yellow targets, and so was marginally higher than for achromatic stimuli.
-The general character of the dipper functions was largely consistent with the achromatic results, though we observed shallower facilitation and weaker masking, especially for the blue/yellow stimuli.
-For example, the strongest facilitation in the binocular condition for achromatic stimuli was a factor of 2.63, whereas it reduced to a factor of 2.35 for red/green stimuli and 1.57 for blue/yellow stimuli.
-The slope of the binocular dipper handle was 0.52 for achromatic stimuli, 0.58 for red/green stimuli, and 0.34 for blue/yellow stimuli.
-Dichoptic masking remained as strong for the chromatic conditions as for the achromatic stimuli (regression slopes of 1.3 for red/green and 1.21 for blue/yellow).
-The pattern of results for individual participants was consistent with the group averages, as shown in Figure \ref{fig:individualdips}.
-
-Following Meese et al.
-(2006), we also inspected the slope of the psychometric function for each condition (see Figure \ref{fig:dipperfig}d-f).
-At detection threshold, slopes were relatively steep for all stimuli, with \(\beta\) values around 4.
-As pedestal contrasts increased, slopes linearized and reduced to around \(\beta=1.3\) (Foley \& Legge, 1981; Meese et al., 2006), and remained shallow at high pedestal contrasts.
-The exception to this was the dichoptic condition, where slopes became extremely steep at high dichoptic mask contrasts, consistent with previous observations (Baker et al., 2013; Meese et al., 2006).
-This was clear for all three data sets, with slope values in the range \(4 < \beta < 8\).
-However, we observe that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
-Our second experiment therefore investigated the slope of the psychometric function in more detail for dichoptic masking using the method of constant stimuli.
+A similar pattern of results was observed for both the red/green and
+blue/yellow isoluminant stimuli (see Figure~\ref{fig-dipperfig}b,c).
+Summation at threshold was a factor of 1.71 (4.66dB) for the red/green
+targets, and a factor of 1.73 (4.77dB) for the blue/yellow targets, and
+so was marginally higher than for achromatic stimuli. The general
+character of the dipper functions was largely consistent with the
+achromatic results, though we observed shallower facilitation and weaker
+masking, especially for the blue/yellow stimuli. For example, the
+strongest facilitation in the binocular condition for achromatic stimuli
+was a factor of 2.63, whereas it reduced to a factor of 2.35 for
+red/green stimuli and 1.57 for blue/yellow stimuli. The slope of the
+binocular dipper handle was 0.52 for achromatic stimuli, 0.58 for
+red/green stimuli, and 0.34 for blue/yellow stimuli. Dichoptic masking
+remained as strong for the chromatic conditions as for the achromatic
+stimuli (regression slopes of 1.3 for red/green and 1.21 for
+blue/yellow). The pattern of results for individual participants was
+consistent with the group averages, as shown in
+Figure~\ref{fig-individualdippers}.
+
+Following Meese et al. (2006), we also inspected the slope of the
+psychometric function for each condition (see
+Figure~\ref{fig-dipperfig}d-f). At detection threshold, slopes were
+relatively steep for all stimuli, with \(\beta\) values around 4. As
+pedestal contrasts increased, slopes linearized and reduced to around
+\(\beta=1.3\) (Foley \& Legge, 1981; Meese et al., 2006), and remained
+shallow at high pedestal contrasts. The exception to this was the
+dichoptic condition, where slopes became extremely steep at high
+dichoptic mask contrasts, consistent with previous observations (Baker
+et al., 2013; Meese et al., 2006). This was clear for all three data
+sets, with slope values in the range \(4 < \beta < 8\). However, we
+observe that slope estimates are more variable than threshold estimates
+(note the large error bars), particularly when using adaptive
+staircases, which deploy the majority of trials close to threshold. Our
+second experiment therefore investigated the slope of the psychometric
+function in more detail for dichoptic masking using the method of
+constant stimuli.
 
@@
 
-In Experiment 2 we focussed on the dichoptic condition at a single mask contrast, and measured full psychometric functions using the method of constant stimuli for all factorial pairings of target and mask chromaticity.
-The pooled results across three participants are shown in Figure \ref{fig:MCSfig}a-c, and results for individual participants are available in Figure \ref{fig:individualMCS}.
-All conditions produced monotonically increasing psychometric functions (panels a-c), but the extent of masking was highly dependent on the relationship between the target and mask chromaticity.
-Figure \ref{fig:MCSfig}d-f shows a two-dimensional representation of individual threshold and slope estimates (points), as well as the posterior density estimates for fits to the pooled data (ellipses).
-The results are consistent between participants, and at the group level, and show that the presence of a mask has a strong effect on thresholds.
+In Experiment 2 we focussed on the dichoptic condition at a single mask
+contrast, and measured full psychometric functions using the method of
+constant stimuli for all factorial pairings of target and mask
+chromaticity. The pooled results across three participants are shown in
+Figure~\ref{fig-MCSfig}a-c, and results for individual participants are
+available in Figure~\ref{fig-individualMCS}. All conditions produced
+monotonically increasing psychometric functions (panels a-c), but the
+extent of masking was highly dependent on the relationship between the
+target and mask chromaticity. Figure~\ref{fig-MCSfig}d-f shows a
+two-dimensional representation of individual threshold and slope
+estimates (points), as well as the posterior density estimates for fits
+to the pooled data (ellipses). The results are consistent between
+participants, and at the group level, and show that the presence of a
+mask has a strong effect on thresholds.
 
@@
 
-{\centering \includegraphics{Figures/MCSdata}
+{\centering \includegraphics{Figures/MCSdata.pdf}
 
@@
 
-\caption{Summary of data from Experiment 2.
-Panels (a-c) show psychometric functions for each condition, pooled across participants (600 trials per target contrast level).
-Panels (d-f) show threshold and slope estimates for individual participants (points) and the boundary of the posterior density estimates for fits to the pooled data (ellipses).
-Panel (g) shows the average threshold elevation factor for each combination of target and mask stimulus.
-Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull $\beta$ units.}\label{fig:MCSfig}
+\caption{\label{fig-MCSfig}Summary of data from Experiment 2. Panels
+(a-c) show psychometric functions for each condition, pooled across
+participants (600 trials per target contrast level). Panels (d-f) show
+threshold and slope estimates for individual participants (points) and
+the boundary of the posterior density estimates for fits to the pooled
+data (ellipses). Panel (g) shows the average threshold elevation factor
+for each combination of target and mask stimulus. Panel (h) shows the
+geometric mean psychometric slope value for each masking condition in
+Weibull \(\beta\) units.}
+
 \end{figure}
 
-Threshold elevation was greatest when the target and mask had the same chromaticity - notice that the psychometric function is shifted furthest to the right for the achromatic target with an achromatic mask (white and black circles in Figure \ref{fig:MCSfig}a), for the red/green target with a red/green mask (red and green circles in Figure \ref{fig:MCSfig}b), and for the blue/yellow target with a blue/yellow mask (blue and yellow circles in Figure \ref{fig:MCSfig}c).
-Masking was weakest between achromatic masks/targets and chromatic masks/targets.
-Finally there was an intermediate level of masking between red/green and blue/yellow stimuli.
-This is summarised in Figure \ref{fig:MCSfig}g, which represents threshold elevation for each combination of target and mask chromaticity.
-Note that the positive diagonal exhibits the highest values, and represents threshold elevation between targets and masks of the same chromaticity.
-
-We also calculated the slope of the psychometric function for each condition, in equivalent Weibull \(\beta\) units.
-In the absence of a mask, the average slope was \(\beta\) = 3.42, which is typical for contrast detection tasks (Wallis et al., 2013).
-Slopes became substantially steeper when the dichoptic mask matched the target in chromaticity (average \(\beta\) = 5.38).
-These `super-steep' psychometric functions for dichoptic pedestal masking have been reported previously (Baker et al., 2013; Meese et al., 2006), and are observed for the first time here using chromatic stimuli (see diagonal values in Figure \ref{fig:MCSfig}h, and also Figure \ref{fig:dipperfig}d-f).
-However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average \(\beta\) = 2.83 for the off-diagonal values).
+Threshold elevation was greatest when the target and mask had the same
+chromaticity - notice that the psychometric function is shifted furthest
+to the right for the achromatic target with an achromatic mask (white
+and black circles in Figure~\ref{fig-MCSfig}a), for the red/green target
+with a red/green mask (red and green circles in
+Figure~\ref{fig-MCSfig}b), and for the blue/yellow target with a
+blue/yellow mask (blue and yellow circles in Figure~\ref{fig-MCSfig}c).
+Masking was weakest between achromatic masks/targets and chromatic
+masks/targets. Finally there was an intermediate level of masking
+between red/green and blue/yellow stimuli. This is summarised in
+Figure~\ref{fig-MCSfig}g, which represents threshold elevation for each
+combination of target and mask chromaticity. Note that the positive
+diagonal exhibits the highest values, and represents threshold elevation
+between targets and masks of the same chromaticity.
+
+We also calculated the slope of the psychometric function for each
+condition, in equivalent Weibull \(\beta\) units. In the absence of a
+mask, the average slope was \(\beta\) = 3.42, which is typical for
+contrast detection tasks (Wallis et al., 2013). Slopes became
+substantially steeper when the dichoptic mask matched the target in
+chromaticity (average \(\beta\) = 5.38). These `super-steep'
+psychometric functions for dichoptic pedestal masking have been reported
+previously (Baker et al., 2013; Meese et al., 2006), and are observed
+for the first time here using chromatic stimuli (see diagonal values in
+Figure~\ref{fig-MCSfig}h, and also Figure~\ref{fig-dipperfig}d-f).
+However we did not see such markedly steep functions for any of the
+cross-chromaticity masking conditions (average \(\beta\) = 2.83 for the
+off-diagonal values).
 
@@
 
-In our final experiment, we again measured dipper functions, but this time for a temporally modulating luminance disc.
-This was motivated by our recent work (Segala et al., 2023) that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
-The pattern of dipper functions for a 4Hz flickering disc (see Figure \ref{fig:discdata}a) was very similar to that observed for achromatic gratings (see Figure \ref{fig:dipperfig}a), and the binocular summation ratio at threshold was also similar (a factor of 1.49 for discs, vs 1.67 for gratings).
-Threshold data for individual participants are shown in Figure \ref{fig:individualdiscs}.
-We also found a similar pattern of psychometric slope values (Figure \ref{fig:discdata}b) as we had for gratings, though we note that the dichoptic condition did not produce the `super-steep' psychometric functions we had observed in Experiments 1 \& 2.
-Nevertheless, the dichoptic slopes are somewhat above those of the other pedestal arrangements at high contrasts.
+In our final experiment, we again measured dipper functions, but this
+time for a temporally modulating luminance disc. This was motivated by
+our recent work (Segala et al., 2023) that appeared to show increased
+binocular facilitation and reduced interocular suppression for
+flickering disc stimuli (relative to gratings), measured using EEG and a
+psychophysical matching paradigm. The pattern of dipper functions for a
+4Hz flickering disc (see Figure~\ref{fig-discdata}a) was very similar to
+that observed for achromatic gratings (see Figure~\ref{fig-dipperfig}a),
+and the binocular summation ratio at threshold was also similar (a
+factor of 1.49 for discs, vs 1.67 for gratings). Threshold data for
+individual participants are shown in Figure~\ref{fig-individualdiscs}.
+We also found a similar pattern of psychometric slope values
+(Figure~\ref{fig-discdata}b) as we had for gratings, though we note that
+the dichoptic condition did not produce the `super-steep' psychometric
+functions we had observed in Experiments 1 \& 2. Nevertheless, the
+dichoptic slopes are somewhat above those of the other pedestal
+arrangements at high contrasts.
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Figures/discdata}
+{\centering \includegraphics[width=0.8\textwidth,height=\textheight]{Figures/discdata.pdf}
 
@@
 
-\caption{Thresholds for the flickering disc experiment. Plotting conventions mirror those in Figure 4.}\label{fig:discdata}
+\caption{\label{fig-discdata}Thresholds for the flickering disc
+experiment. Plotting conventions mirror those in Figure 4.}
+
 \end{figure}
@@
 
+\hypertarget{tbl-parametertable}{}
 \begin{table}
-
-\caption{\label{tab:parametertable}Summary of fitted model parameters.
-The top row gives the best fitting parameters from the study of Meese et al.
-(2006).
-The second section shows the best fitting parameters from simplex fits to the averaged thresholds for each experiment.
-The final rows show the posterior parameter estimates from the Bayesian model, fitted to each data set from Experiments 1 and 3.}
+\caption{\label{tbl-parametertable}Summary of fitted model parameters. The top row gives the best fitting
+parameters from the study of Meese et al. (2006). The second section
+shows the best fitting parameters from simplex fits to the averaged
+thresholds for each experiment. The final rows show the posterior
+parameter estimates from the Bayesian model, fitted to each data set
+from Experiments 1 and 3. }\tabularnewline
+
 \centering
-\begin{tabular}[t]{lrrrrrrrr}
+\begin{tabular}{lrrrrrrrr}
 \toprule
@@
 
-For consistency with previous work, we initially performed least-squares fits of the two-stage model (Meese et al., 2006) for each of the chromaticity experiments, and the flickering disc experiment (7 free parameters per fit).
-The best model fits are shown by the curves in Figures \ref{fig:dipperfig} \& \ref{fig:discdata}, and provide an excellent description of the data, with RMS errors between 1.06 and 1.59dB.
-Best fitting parameters are shown in the `Simplex fits' section of Table \ref{tab:parametertable}.
-We note that in previous work, the weight of interocular suppression (\(\omega\) in the model) is implicitly fixed at 1.
-Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (0.89) for our flickering discs.
-The exponent values (\emph{p} and \emph{q}) for the red/green gratings are rather different from those of the other conditions.
-In previous work (Meese et al., 2006) the second stage gain control nonlinearity (Equation 4) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper).
-The high value of \emph{p} (19.42) is therefore likely to be compensating for the low value of \emph{m} (1.03) at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty (Pelli, 1985).
-
-We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
-This model was fit simultaneously to the full trial-by-trial data from all participants who participated in a given experiment (i.e.~the model was fitted separately to each of the four dipper data sets).
-Figure \ref{fig:bayesianmodel}a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
-Mean posterior parameter values are given in the lower rows of Table \ref{tab:parametertable}.
-These correspond quite closely to the parameters from the simplex fitting and the original Meese et al.
-(2006) parameters (reproduced in the first row of the table for reference).
-The panels in the right and upper margins of Figure \ref{fig:bayesianmodel} show posterior distributions for each model parameter.
-Note in particular that the posterior distribution for the weight of interocular suppression (\(\omega\), top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
-We note that the distribution for \(\omega\) in the flickering disc condition is somewhat lower than for the other three data sets.
-However this difference is not meaningful according to criteria such as comparing the 95\% credible intervals of the distribution to a value of \(\omega=1\).
+For consistency with previous work, we initially performed least-squares
+fits of the two-stage model (Meese et al., 2006) for each of the
+chromaticity experiments, and the flickering disc experiment (7 free
+parameters per fit). The best model fits are shown by the curves in
+Figure~\ref{fig-dipperfig} \& Figure~\ref{fig-discdata}, and provide an
+excellent description of the data, with RMS errors between 1.06 and
+1.59dB. Best fitting parameters are shown in the `Simplex fits' section
+of Table~\ref{tbl-parametertable}. We note that in previous work, the
+weight of interocular suppression (\(\omega\) in the model) is
+implicitly fixed at 1. Here we allowed it to vary, but it still received
+a value of exactly 1 in all of our grating conditions, and slightly
+below 1 (0.89) for our flickering discs. The exponent values (\emph{p}
+and \emph{q}) for the red/green gratings are rather different from those
+of the other conditions. In previous work (Meese et al., 2006) the
+second stage gain control nonlinearity (Equation 4) does typically have
+quite substantial exponent values, which balance the relatively mild
+nonlinearity at the first stage, and produce a compressive transducer
+that results in contrast masking (the handle of the dipper). The high
+value of \emph{p} = 19.42 is therefore likely to be compensating for the
+low value of \emph{m} = 1.03 at stage one, but may well represent the
+combination of several successive stages of nonlinearity, and perhaps
+also other phenomena such as uncertainty (Pelli, 1985).
+
+We additionally implemented a hierarchical Bayesian version of the model
+in order to estimate full posterior parameter distributions. This model
+was fit simultaneously to the full trial-by-trial data from all
+participants who participated in a given experiment (i.e.~the model was
+fitted separately to each of the four dipper data sets).
+Figure~\ref{fig-bayesianmodel}a-d summarises the model behaviour, which
+displays the same pattern of dipper functions as we found empirically.
+Mean posterior parameter values are given in the lower rows of
+Table~\ref{tbl-parametertable}. These correspond quite closely to the
+parameters from the simplex fitting and the original Meese et al. (2006)
+parameters (reproduced in the first row of the table for reference). The
+panels in the right and upper margins of Figure~\ref{fig-bayesianmodel}
+show posterior distributions for each model parameter. Note in
+particular that the posterior distribution for the weight of interocular
+suppression (\(\omega\), top right panel) overlaps 1 for each
+experiment, consistent with the strong dichoptic masking observed in the
+threshold data. We note that the distribution for \(\omega\) in the
+flickering disc condition is somewhat lower than for the other three
+data sets. However this difference is not meaningful according to
+criteria such as comparing the 95\% credible intervals of the
+distribution to a value of \(\omega=1\).
 
@@
 
-{\centering \includegraphics{Figures/stanoutput}
+{\centering \includegraphics{Figures/stanoutput.pdf}
 
@@
 
-\caption{Model predictions (a-d) and posterior parameters (top and right margin plots) for the hierarchical Bayesian model.
-Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates.
-The probability density functions in the margin plots are peak-normalized, and shown for each of the four data sets in different colours (see legend in upper left plot).
-Distributions were generated from 1000000 samples per data set, using a Markov Chain Monte Carlo sampling algorithm.
-Note the logarithmic x-axis for all posterior plots.}\label{fig:bayesianmodel}
+\caption{\label{fig-bayesianmodel}Model predictions (a-d) and posterior
+parameters (top and right margin plots) for the hierarchical Bayesian
+model. Thick lines in panels (a-d) show curves generated from the mean
+posterior parameter estimates. The probability density functions in the
+margin plots are peak-normalized, and shown for each of the four data
+sets in different colours (see legend in upper left plot). Distributions
+were generated from 1000000 samples per data set, using a Markov Chain
+Monte Carlo sampling algorithm. Note the logarithmic x-axis for all
+posterior plots.}
+
 \end{figure}
 
-Finally we fitted an extended model, that included interocular suppression between the different pathways, to the data of Experiment 2.
-Figure \ref{fig:MCSmodel} shows the model curves (panels a-c), which correspond closely to the data in Figure \ref{fig:MCSfig}.
-One striking discrepancy is that the model predicts a region of negative d-prime for the case where the target and dichoptic mask have the same chromaticity (see the curved regions below 50\% correct).
-This feature was not generally present in our data, though it can be observed for one participant in Figure \ref{fig:individualMCS}b,c.~Our previous work (Baker et al., 2013) has found evidence for this phenomenon (termed `swan functions'), but it generally requires very high mask contrasts to be measurable empirically, and there may also be some individual differences; both factors might explain its absence here.
-
-Figure \ref{fig:MCSmodel}d,e shows the model estimates for the weight of interocular suppression in each combination of target and mask chromaticity.
-Although the weights might appear to indicate that (excluding within-mechanism effects) suppression is strongest between blue/yellow targets and achromatic masks (a weight of 0.56), this is somewhat complicated by the differences in sensitivity and mask contrast between conditions.
-We selected mask contrasts that were approximately equal multiples (\(16\times\)) of their own detection thresholds, based on the data of Experiment 1 (Figure \ref{fig:dipperfig}a-c).
-However the modelling expressed these contrasts as a percentage of the maximum contrast that it was possible to display on the monitor (see Procedures).
-The values in brackets in Figure \ref{fig:MCSmodel}d indicate the overall suppressive term on the denominator, calculated by multiplying the mask contrast by the fitted weight.
-These values indicate that the strongest suppression is instead between red/green targets and blue/yellow masks, consistent with the threshold elevation observed empirically (Figure \ref{fig:MCSfig}g).
-In principle it would be possible to repeat this modelling using either cone contrast values, or contrast expressed relative to detection threshold, which would require re-fitting the model.
+Finally we fitted an extended model, that included interocular
+suppression between the different pathways, to the data of Experiment 2.
+Figure~\ref{fig-MCSmodel} shows the model curves (panels a-c), which
+correspond closely to the data in Figure~\ref{fig-MCSfig}. One striking
+discrepancy is that the model predicts a region of negative d-prime for
+the case where the target and dichoptic mask have the same chromaticity
+(see the curved regions below 50\% correct). This feature was not
+generally present in our data, though it can be observed for one
+participant in Figure~\ref{fig-individualMCS}b,c.~Our previous work
+(Baker et al., 2013) has found evidence for this phenomenon (termed
+`swan functions'), but it generally requires very high mask contrasts to
+be measurable empirically, and there may also be some individual
+differences; both factors might explain its absence here.
+
+Figure~\ref{fig-MCSmodel}d,e shows the model estimates for the weight of
+interocular suppression in each combination of target and mask
+chromaticity. Although the weights might appear to indicate that
+(excluding within-mechanism effects) suppression is strongest between
+blue/yellow targets and achromatic masks (a weight of 0.56), this is
+somewhat complicated by the differences in sensitivity and mask contrast
+between conditions. We selected mask contrasts that were approximately
+equal multiples (\(16\times\)) of their own detection thresholds, based
+on the data of Experiment 1 (Figure~\ref{fig-dipperfig}a-c). However the
+modelling expressed these contrasts as a percentage of the maximum
+contrast that it was possible to display on the monitor (see
+Procedures). The values in brackets in Figure~\ref{fig-MCSmodel}d
+indicate the overall suppressive term on the denominator, calculated by
+multiplying the mask contrast by the fitted weight. These values
+indicate that the strongest suppression is instead between red/green
+targets and blue/yellow masks, consistent with the threshold elevation
+observed empirically (Figure~\ref{fig-MCSfig}g). In principle it would
+be possible to repeat this modelling using either cone contrast values,
+or contrast expressed relative to detection threshold, which would
+require re-fitting the model.
 
@@
 
-{\centering \includegraphics{Figures/MCSmodel}
+{\centering \includegraphics{Figures/MCSmodel.pdf}
 
@@
 
-\caption{Summary of the model fit to the data of Experiment 2.
-Panels (a-c) show model psychometric functions in the same format as those in Figure 5.
-Panel (d) shows the fitted suppressive weights ($\omega$ values), with values in brackets indicating the combined suppressive denominator term calculated by multiplying together the suppressive weight and the dichoptic mask contrast.
-Panel (e) shows the posterior distributions for each weight parameter.
-The lower right plot gives the legends for the upper row (top) and the posterior distributions in panel (e).}\label{fig:MCSmodel}
+\caption{\label{fig-MCSmodel}Summary of the model fit to the data of
+Experiment 2. Panels (a-c) show model psychometric functions in the same
+format as those in Figure 5. Panel (d) shows the fitted suppressive
+weights (\(\omega\) values), with values in brackets indicating the
+combined suppressive denominator term calculated by multiplying together
+the suppressive weight and the dichoptic mask contrast. Panel (e) shows
+the posterior distributions for each weight parameter. The lower right
+plot gives the legends for the upper row (top) and the posterior
+distributions in panel (e).}
+
 \end{figure}
@@
 \item
-  Binocular combination of isoluminant chromatic stimuli is similar to that for achromatic stimuli
+  Binocular combination of isoluminant chromatic stimuli is similar to
+  that for achromatic stimuli
 \item
-  Interocular suppression is strongest within a post-retinal pathway, and weakest between achromatic and chromatic pathways
+  Interocular suppression is strongest within a post-retinal pathway,
+  and weakest between achromatic and chromatic pathways
 \item
-  Binocular combination occurs similarly for spatial and temporal luminance modulations
+  Binocular combination occurs similarly for spatial and temporal
+  luminance modulations
 \end{itemize}
 
-We now discuss the relationship to previous work, and consider the likely physiological substrates of these effects.
+We now discuss the relationship to previous work, and consider the
+likely physiological substrates of these effects.
 
@@
 
-Estimates of the binocular summation ratio at threshold fell within the range \(\sqrt{2}\) to 2 for all four data sets.
-Consistent with previous reports (Simmons, 2005), summation was slightly higher for chromatic versus achromatic stimuli, but fell short of perfect linear summation (a ratio of 2).
-In our model, summation at threshold is determined by the exponent at the first gain control stage (the \emph{m} parameter in Equations 1 \& 2).
-The summation ratio can be approximated by \(2^{1/m}\) (see Figure 9 of Baker et al., 2012), such that an exponent of \(m=1\) produces a ratio of 2, and an exponent of \(m = 2\) produces a ratio of \(\sqrt{2}\).
-Both the simplex and Bayesian model fits (see Table \ref{tab:parametertable}) generated parameter estimates in the range \(1 < m < 1.4\), consistent with the high levels of summation observed empirically.
+Estimates of the binocular summation ratio at threshold fell within the
+range \(\sqrt{2}\) to 2 for all four data sets. Consistent with previous
+reports (Simmons, 2005), summation was slightly higher for chromatic
+versus achromatic stimuli, but fell short of perfect linear summation (a
+ratio of 2). In our model, summation at threshold is determined by the
+exponent at the first gain control stage (the \emph{m} parameter in
+Equations 1 \& 2). The summation ratio can be approximated by
+\(2^{1/m}\) (see Figure 9 of Baker et al., 2012), such that an exponent
+of \(m=1\) produces a ratio of 2, and an exponent of \(m = 2\) produces
+a ratio of \(\sqrt{2}\). Both the simplex and Bayesian model fits (see
+Table~\ref{tbl-parametertable}) generated parameter estimates in the
+range \(1 < m < 1.4\), consistent with the high levels of summation
+observed empirically.
 
@@
 
-The weight of interocular suppression is represented by the model parameter, \(\omega\) (Equations 1 \& 2).
-Posterior distributions of this parameter overlapped 1 for all of our dipper function data sets (see top right panel in Figure \ref{fig:bayesianmodel}), indicating strong interocular suppression regardless of post-retinal pathway.
-The flickering disc stimuli produced a slightly lower suppression estimate, with \(\omega \sim 0.9\).
-This may indicate slightly weaker suppression between the eyes for temporal modulations, but it is much less extreme than our recent estimates using EEG and matching paradigms (Segala et al., 2023).
-One difference between these studies is the luminance of the background, which was set to black for the experiments of Segala et al.
-(2023), but here was set at the mean luminance.
-Other studies using static luminance increments have also reported differences in the character of binocular combination that are attributable to background luminance (Baker et al., 2012), so this may explain the differences between studies.
-We also note that the weaker interocular suppression for flickering disc stimuli appears to be largely due to one participant (see Figure \ref{fig:individualdiscs}c), so individual differences might also play a role.
-Future work should manipulate the background luminance systematically to better understand how this modulates interocular suppression.
+The weight of interocular suppression is represented by the model
+parameter, \(\omega\) (Equations 1 \& 2). Posterior distributions of
+this parameter overlapped 1 for all of our dipper function data sets
+(see top right panel in Figure~\ref{fig-bayesianmodel}), indicating
+strong interocular suppression regardless of post-retinal pathway. The
+flickering disc stimuli produced a slightly lower suppression estimate,
+with \(\omega \sim 0.9\). This may indicate slightly weaker suppression
+between the eyes for temporal modulations, but it is much less extreme
+than our recent estimates using EEG and matching paradigms (Segala et
+al., 2023). One difference between these studies is the luminance of the
+background, which was set to black for the experiments of Segala et al.
+(2023), but here was set at the mean luminance. Other studies using
+static luminance increments have also reported differences in the
+character of binocular combination that are attributable to background
+luminance (Baker et al., 2012), so this may explain the differences
+between studies. We also note that the weaker interocular suppression
+for flickering disc stimuli appears to be largely due to one participant
+(see Figure~\ref{fig-individualdiscs}c), so individual differences might
+also play a role. Future work should manipulate the background luminance
+systematically to better understand how this modulates interocular
+suppression.
 
@@
 
-Previous work has demonstrated that the slope of the psychometric function in 2AFC tasks can distinguish different types of masking, although it is much less widely reported than threshold measures.
-In particular, pedestal masking linearizes the slope (Foley \& Legge, 1981; Meese et al., 2006), and within-channel dichoptic masking produces very steep slopes (Baker et al., 2013; Meese et al., 2006).
-We replicate both of these effects here, and show that they extend to isoluminant chromatic pathways (see Figures \ref{fig:dipperfig}d-f, \ref{fig:MCSfig}).
-We additionally show that dichoptic masking between different pathways does not produce unusually steep slopes (see Figure \ref{fig:MCSfig}).
-It therefore more closely resembles other types of masking between visual channels, such as cross-orientation masking (Meese \& Baker, 2009), surround masking (Yu et al., 2002), and masking from broadband noise (Baker \& Meese, 2012; Lu \& Dosher, 2008), which also do not impact psychometric slopes.
+Previous work has demonstrated that the slope of the psychometric
+function in 2AFC tasks can distinguish different types of masking,
+although it is much less widely reported than threshold measures. In
+particular, pedestal masking linearizes the slope (Foley \& Legge, 1981;
+Meese et al., 2006), and within-channel dichoptic masking produces very
+steep slopes (Baker et al., 2013; Meese et al., 2006). We replicate both
+of these effects here, and show that they extend to isoluminant
+chromatic pathways (see Figure~\ref{fig-dipperfig}d-f \&
+Figure~\ref{fig-MCSfig}). We additionally show that dichoptic masking
+between different pathways does not produce unusually steep slopes (see
+Figure~\ref{fig-MCSfig}). It therefore more closely resembles other
+types of masking between visual channels, such as cross-orientation
+masking (Meese \& Baker, 2009), surround masking (Yu et al., 2002), and
+masking from broadband noise (Baker \& Meese, 2012; Lu \& Dosher, 2008),
+which also do not impact psychometric slopes.
 
@@
 
-Recent evidence indicates that the physiological substrate of interocular suppression may be neurons in layer 4 of primary visual cortex (Dougherty et al., 2019).
-Most cells in this layer are monocularly exciteable, in that their responses increase only by stimulation of their preferred eye.
-However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed at stage 1 of the two-stage model (Equations 1 \& 2).
-In terms of perception, one consequence of this early suppression is to achieve `ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes (Baker et al., 2007).
-Similar processes of invariance have also been reported using fMRI (Moradi \& Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).
-
-In V1, chromatic stimuli are processed in `blob' regions that are largely monocular as they fall within ocular dominance columns (Livingstone \& Hubel, 1984).
-Since our psychophysical results indicate that interocular suppression is equally strong within chromatic and achromatic pathways, it may be that blob regions include interocular suppression.
-Presumably binocular summation of signals occurs at a later stage of processing for chromatic stimuli, but this does not lead to different perceptual outcomes.
-This physiological arrangement might also be responsible for the pattern of between-pathway interocular suppression (see Figure \ref{fig:MCSfig}g).
-If blobs process signals from both the L-M and S-(L+M) pathways, their close physical proximity might explain the stronger suppression between the two chromatic pathways than between the chromatic and (more distant) achromatic pathways.
+Recent evidence indicates that the physiological substrate of
+interocular suppression may be neurons in layer 4 of primary visual
+cortex (Dougherty et al., 2019). Most cells in this layer are
+monocularly exciteable, in that their responses increase only by
+stimulation of their preferred eye. However, simultaneous stimulation of
+the non-preferred eye can modulate the response, usually in an
+inhibitory fashion, exactly as proposed at stage 1 of the two-stage
+model (Equations 1 \& 2). In terms of perception, one consequence of
+this early suppression is to achieve `ocularity invariance', whereby the
+perceived contrast of a stimulus viewed by one eye is equivalent to that
+of the same stimulus viewed by both eyes (Baker et al., 2007). Similar
+processes of invariance have also been reported using fMRI (Moradi \&
+Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).
+
+In V1, chromatic stimuli are processed in `blob' regions that are
+largely monocular as they fall within ocular dominance columns
+(Livingstone \& Hubel, 1984). Since our psychophysical results indicate
+that interocular suppression is equally strong within chromatic and
+achromatic pathways, it may be that blob regions include interocular
+suppression. Presumably binocular summation of signals occurs at a later
+stage of processing for chromatic stimuli, but this does not lead to
+different perceptual outcomes. This physiological arrangement might also
+be responsible for the pattern of between-pathway interocular
+suppression (see Figure~\ref{fig-MCSfig}g). If blobs process signals
+from both the L-M and S-(L+M) pathways, their close physical proximity
+might explain the stronger suppression between the two chromatic
+pathways than between the chromatic and (more distant) achromatic
+pathways.
 
@@
 
-Here we provide estimates of interocular suppression within and between the three primary post-retinal visual pathways.
-These results show that binocular signal combination is similar within each pathway, but that interocular suppression is relatively weak between pathways.
-Our findings could be applied when building models to predict perception of binocular images and movies, for example those generated by virtual and augmented reality systems, or in 3D cinema and television.
+Here we provide estimates of interocular suppression within and between
+the three primary post-retinal visual pathways. These results show that
+binocular signal combination is similar within each pathway, but that
+interocular suppression is relatively weak between pathways. Our
+findings could be applied when building models to predict perception of
+binocular images and movies, for example those generated by virtual and
+augmented reality systems, or in 3D cinema and television.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Anstis1998}{}}%
-Anstis, S., \& Ho, A.
-(1998).
-Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion.
-\emph{Vision Res}, \emph{38}(4), 523--539.
+Anstis, S., \& Ho, A. (1998). Nonlinear combination of luminance
+excursions during flicker, simultaneous contrast, afterimages and
+binocular fusion. \emph{Vision Res}, \emph{38}(4), 523--539.
 \url{https://doi.org/10.1016/s0042-6989(97)00167-3}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
-Baker, D.
-H., Lygo, F.
-A., Meese, T.
-S., \& Georgeson, M.
-A.
-(2018).
-Binocular summation revisited: Beyond \(\sqrt{2}\).
-\emph{Psychol Bull}, \emph{144}(11), 1186--1199.
-\url{https://doi.org/10.1037/bul0000163}
+Baker, D. H., Lygo, F. A., Meese, T. S., \& Georgeson, M. A. (2018).
+Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull},
+\emph{144}(11), 1186--1199. \url{https://doi.org/10.1037/bul0000163}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2007b}{}}%
-Baker, D.
-H., \& Meese, T.
-S.
-(2007).
-Binocular contrast interactions: Dichoptic masking is not a single process.
-\emph{Vision Res}, \emph{47}(24), 3096--3107.
+Baker, D. H., \& Meese, T. S. (2007). Binocular contrast interactions:
+Dichoptic masking is not a single process. \emph{Vision Res},
+\emph{47}(24), 3096--3107.
 \url{https://doi.org/10.1016/j.visres.2007.08.013}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2012b}{}}%
-Baker, D. H., \& Meese, T. S. (2012). Zero-dimensional noise: The best mask you never saw. \emph{J Vis}, \emph{12}(10). \url{https://doi.org/10.1167/12.10.20}
+Baker, D. H., \& Meese, T. S. (2012). Zero-dimensional noise: The best
+mask you never saw. \emph{J Vis}, \emph{12}(10).
+\url{https://doi.org/10.1167/12.10.20}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
-Baker, D.
-H., Meese, T.
-S., \& Georgeson, M.
-A.
-(2007).
-Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
-\emph{Spat Vis}, \emph{20}(5), 397--413.
+Baker, D. H., Meese, T. S., \& Georgeson, M. A. (2007). Binocular
+interaction: Contrast matching and contrast discrimination are predicted
+by the same model. \emph{Spat Vis}, \emph{20}(5), 397--413.
 \url{https://doi.org/10.1163/156856807781503622}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2013}{}}%
-Baker, D.
-H., Meese, T.
-S., \& Georgeson, M.
-A.
-(2013).
-Paradoxical psychometric functions ("swan functions") are explained by dilution masking in four stimulus dimensions.
-\emph{{iPerception}}, \emph{4}(1), 17--35.
-\url{https://doi.org/10.1068/i0552}
+Baker, D. H., Meese, T. S., \& Georgeson, M. A. (2013). Paradoxical
+psychometric functions ("swan functions") are explained by dilution
+masking in four stimulus dimensions. \emph{{iPerception}}, \emph{4}(1),
+17--35. \url{https://doi.org/10.1068/i0552}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
-Baker, D.
-H., \& Wade, A.
-R.
-(2017).
-Evidence for an optimal algorithm underlying signal combination in human visual cortex.
-\emph{Cereb Cortex}, \emph{27}(1), 254--264.
+Baker, D. H., \& Wade, A. R. (2017). Evidence for an optimal algorithm
+underlying signal combination in human visual cortex. \emph{Cereb
+Cortex}, \emph{27}(1), 254--264.
 \url{https://doi.org/10.1093/cercor/bhw395}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2012}{}}%
-Baker, D.
-H., Wallis, S.
-A., Georgeson, M.
-A., \& Meese, T.
-S.
-(2012).
+Baker, D. H., Wallis, S. A., Georgeson, M. A., \& Meese, T. S. (2012).
 Nonlinearities in the binocular combination of luminance and contrast.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
-Campbell, F. W., \& Green, D. G. (1965). Monocular versus binocular visual acuity. \emph{Nature}, \emph{208}(5006), 191--192. \url{https://doi.org/10.1038/208191a0}
+Campbell, F. W., \& Green, D. G. (1965). Monocular versus binocular
+visual acuity. \emph{Nature}, \emph{208}(5006), 191--192.
+\url{https://doi.org/10.1038/208191a0}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
-Carpenter, B., Gelman, A., Hoffman, M.
-D., Lee, D., Goodrich, B., Betancourt, M., Brubaker, M., Guo, J., Li, P., \& Riddell, A.
-(2017).
-Stan: A probabilistic programming language.
-\emph{Journal of Statistical Software}, \emph{76}(1), 1--32.
+Carpenter, B., Gelman, A., Hoffman, M. D., Lee, D., Goodrich, B.,
+Betancourt, M., Brubaker, M., Guo, J., Li, P., \& Riddell, A. (2017).
+Stan: A probabilistic programming language. \emph{Journal of Statistical
+Software}, \emph{76}(1), 1--32.
 \url{https://doi.org/10.18637/jss.v076.i01}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Chen2000}{}}%
-Chen, C., Foley, J.
-M., \& Brainard, D.
-H.
-(2000).
-Detection of chromoluminance patterns on chromoluminance pedestals i: Threshold measurements.
-\emph{Vision Res}, \emph{40}(7), 773--788.
+Chen, C., Foley, J. M., \& Brainard, D. H. (2000). Detection of
+chromoluminance patterns on chromoluminance pedestals i: Threshold
+measurements. \emph{Vision Res}, \emph{40}(7), 773--788.
 \url{https://doi.org/10.1016/s0042-6989(99)00227-8}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Dougherty2019}{}}%
-Dougherty, K., Cox, M.
-A., Westerberg, J.
-A., \& Maier, A.
-(2019).
-Binocular modulation of monocular V1 neurons.
-\emph{Curr Biol}, \emph{29}(3), 381--391.e4.
+Dougherty, K., Cox, M. A., Westerberg, J. A., \& Maier, A. (2019).
+Binocular modulation of monocular V1 neurons. \emph{Curr Biol},
+\emph{29}(3), 381--391.e4.
 \url{https://doi.org/10.1016/j.cub.2018.12.004}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Edwards1995}{}}%
-Edwards, D.
-P., Purpura, K.
-P., \& Kaplan, E.
-(1995).
-Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
-\emph{Vision Res}, \emph{35}(11), 1501--1523.
+Edwards, D. P., Purpura, K. P., \& Kaplan, E. (1995). Contrast
+sensitivity and spatial frequency response of primate cortical neurons
+in and around the cytochrome oxidase blobs. \emph{Vision Res},
+\emph{35}(11), 1501--1523.
 \url{https://doi.org/10.1016/0042-6989(94)00253-i}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Foley1981}{}}%
-Foley, J.
-M., \& Legge, G.
-E.
-(1981).
-Contrast detection and near-threshold discrimination in human vision.
-\emph{Vision Res}, \emph{21}(7), 1041--1053.
+Foley, J. M., \& Legge, G. E. (1981). Contrast detection and
+near-threshold discrimination in human vision. \emph{Vision Res},
+\emph{21}(7), 1041--1053.
 \url{https://doi.org/10.1016/0042-6989(81)90009-2}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Georgeson2016}{}}%
-Georgeson, M.
-A., Wallis, S.
-A., Meese, T.
-S., \& Baker, D.
-H.
-(2016).
-Contrast and lustre: A model that accounts for eleven different forms of contrast discrimination in binocular vision.
-\emph{Vision Res}, \emph{129}, 98--118.
-\url{https://doi.org/10.1016/j.visres.2016.08.001}
+Georgeson, M. A., Wallis, S. A., Meese, T. S., \& Baker, D. H. (2016).
+Contrast and lustre: A model that accounts for eleven different forms of
+contrast discrimination in binocular vision. \emph{Vision Res},
+\emph{129}, 98--118. \url{https://doi.org/10.1016/j.visres.2016.08.001}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Horton1981}{}}%
-Horton, J.
-C., \& Hubel, D.
-H.
-(1981).
-Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey.
+Horton, J. C., \& Hubel, D. H. (1981). Regular patchy distribution of
+cytochrome oxidase staining in primary visual cortex of macaque monkey.
 \emph{Nature}, \emph{292}(5825), 762--764.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Kim2013}{}}%
-Kim, Y.
-J., Gheiratmand, M., \& Mullen, K.
-T.
-(2013).
-Cross-orientation masking in human color vision: Application of a two-stage model to assess dichoptic and monocular sources of suppression.
-\emph{J Vis}, \emph{13}(6), 15.
-\url{https://doi.org/10.1167/13.6.15}
+Kim, Y. J., Gheiratmand, M., \& Mullen, K. T. (2013). Cross-orientation
+masking in human color vision: Application of a two-stage model to
+assess dichoptic and monocular sources of suppression. \emph{J Vis},
+\emph{13}(6), 15. \url{https://doi.org/10.1167/13.6.15}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kim2015}{}}%
-Kim, Y.
-J., \& Mullen, K.
-T.
-(2015).
-The dynamics of cross-orientation masking at monocular and interocular sites.
-\emph{Vision Res}, \emph{116}(Pt A), 80--91.
+Kim, Y. J., \& Mullen, K. T. (2015). The dynamics of cross-orientation
+masking at monocular and interocular sites. \emph{Vision Res},
+\emph{116}(Pt A), 80--91.
 \url{https://doi.org/10.1016/j.visres.2015.09.008}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
-Kingdom, F.
-A.
-A., \& Libenson, L.
-(2015).
-Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
-\emph{J Vis}, \emph{15}(5), 2.
-\url{https://doi.org/10.1167/15.5.2}
+Kingdom, F. A. A., \& Libenson, L. (2015). Dichoptic color saturation
+mixture: Binocular luminance contrast promotes perceptual averaging.
+\emph{J Vis}, \emph{15}(5), 2. \url{https://doi.org/10.1167/15.5.2}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Legge1979}{}}%
-Legge, G. E. (1979). Spatial frequency masking in human vision: Binocular interactions. \emph{J Opt Soc Am}, \emph{69}(6), 838--847. \url{https://doi.org/10.1364/josa.69.000838}
+Legge, G. E. (1979). Spatial frequency masking in human vision:
+Binocular interactions. \emph{J Opt Soc Am}, \emph{69}(6), 838--847.
+\url{https://doi.org/10.1364/josa.69.000838}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
-Legge, G. E. (1984). Binocular contrast summation--II. Quadratic summation. \emph{Vision Res}, \emph{24}(4), 385--394. \url{https://doi.org/10.1016/0042-6989(84)90064-6}
+Legge, G. E. (1984). Binocular contrast summation--II. Quadratic
+summation. \emph{Vision Res}, \emph{24}(4), 385--394.
+\url{https://doi.org/10.1016/0042-6989(84)90064-6}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Levelt1965}{}}%
-Levelt, W. J. (1965). Binocular brightness averaging and contour information. \emph{Br J Psychol}, \emph{56}, 1--13. \url{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}
+Levelt, W. J. (1965). Binocular brightness averaging and contour
+information. \emph{Br J Psychol}, \emph{56}, 1--13.
+\url{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Livingstone1984}{}}%
-Livingstone, M.
-S., \& Hubel, D.
-H.
-(1984).
-Anatomy and physiology of a color system in the primate visual cortex.
-\emph{J Neurosci}, \emph{4}(1), 309--356.
+Livingstone, M. S., \& Hubel, D. H. (1984). Anatomy and physiology of a
+color system in the primate visual cortex. \emph{J Neurosci},
+\emph{4}(1), 309--356.
 \url{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lu2008}{}}%
-Lu, Z.-L., \& Dosher, B.
-A.
-(2008).
-Characterizing observers using external noise and observer models: Assessing internal representations with external noise.
-\emph{Psychol Rev}, \emph{115}(1), 44--82.
+Lu, Z.-L., \& Dosher, B. A. (2008). Characterizing observers using
+external noise and observer models: Assessing internal representations
+with external noise. \emph{Psychol Rev}, \emph{115}(1), 44--82.
 \url{https://doi.org/10.1037/0033-295X.115.1.44}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Maehara2005}{}}%
-Maehara, G., \& Goryo, K. (2005). Binocular, monocular and dichoptic pattern masking. \emph{Optical Review}, \emph{12}(2), 76--82. \url{https://doi.org/10.1007/PL00021542}
+Maehara, G., \& Goryo, K. (2005). Binocular, monocular and dichoptic
+pattern masking. \emph{Optical Review}, \emph{12}(2), 76--82.
+\url{https://doi.org/10.1007/PL00021542}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Medina2009}{}}%
-Medina, J. M., \& Mullen, K. T. (2009). Cross-orientation masking in human color vision. \emph{J Vis}, \emph{9}(3), 20.1--16. \url{https://doi.org/10.1167/9.3.20}
+Medina, J. M., \& Mullen, K. T. (2009). Cross-orientation masking in
+human color vision. \emph{J Vis}, \emph{9}(3), 20.1--16.
+\url{https://doi.org/10.1167/9.3.20}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Meese2009}{}}%
-Meese, T.
-S., \& Baker, D.
-H.
-(2009).
-Cross-orientation masking is speed invariant between ocular pathways but speed dependent within them.
-\emph{J Vis}, \emph{9}(5), 2.1--15.
-\url{https://doi.org/10.1167/9.5.2}
+Meese, T. S., \& Baker, D. H. (2009). Cross-orientation masking is speed
+invariant between ocular pathways but speed dependent within them.
+\emph{J Vis}, \emph{9}(5), 2.1--15. \url{https://doi.org/10.1167/9.5.2}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
-Meese, T. S., Georgeson, M. A., \& Baker, D. H. (2006). Binocular contrast vision at and above threshold. \emph{J Vis}, \emph{6}(11), 1224--1243. \url{https://doi.org/10.1167/6.11.7}
+Meese, T. S., Georgeson, M. A., \& Baker, D. H. (2006). Binocular
+contrast vision at and above threshold. \emph{J Vis}, \emph{6}(11),
+1224--1243. \url{https://doi.org/10.1167/6.11.7}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
-Moradi, F., \& Heeger, D. J. (2009). Inter-ocular contrast normalization in human visual cortex. \emph{J Vis}, \emph{9}(3), 13.1--22. \url{https://doi.org/10.1167/9.3.13}
+Moradi, F., \& Heeger, D. J. (2009). Inter-ocular contrast normalization
+in human visual cortex. \emph{J Vis}, \emph{9}(3), 13.1--22.
+\url{https://doi.org/10.1167/9.3.13}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Mullen2014}{}}%
-Mullen, K.
-T., Kim, Y.
-J., \& Gheiratmand, M.
-(2014).
-Contrast normalization in colour vision: The effect of luminance contrast on colour contrast detection.
-\emph{Sci Rep}, \emph{4}, 7350.
+Mullen, K. T., Kim, Y. J., \& Gheiratmand, M. (2014). Contrast
+normalization in colour vision: The effect of luminance contrast on
+colour contrast detection. \emph{Sci Rep}, \emph{4}, 7350.
 \url{https://doi.org/10.1038/srep07350}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Pelli1985}{}}%
-Pelli, D. G. (1985). Uncertainty explains many aspects of visual contrast detection and discrimination. \emph{J Opt Soc Am A}, \emph{2}(9), 1508--1532. \url{https://doi.org/10.1364/josaa.2.001508}
+Pelli, D. G. (1985). Uncertainty explains many aspects of visual
+contrast detection and discrimination. \emph{J Opt Soc Am A},
+\emph{2}(9), 1508--1532. \url{https://doi.org/10.1364/josaa.2.001508}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Schutt2016}{}}%
-Schütt, H.
-H., Harmeling, S., Macke, J.
-H., \& Wichmann, F.
-A.
-(2016).
-Painfree and accurate bayesian estimation of psychometric functions for (potentially) overdispersed data.
-\emph{Vision Res}, \emph{122}, 105--123.
-\url{https://doi.org/10.1016/j.visres.2016.02.002}
+Schütt, H. H., Harmeling, S., Macke, J. H., \& Wichmann, F. A. (2016).
+Painfree and accurate bayesian estimation of psychometric functions for
+(potentially) overdispersed data. \emph{Vision Res}, \emph{122},
+105--123. \url{https://doi.org/10.1016/j.visres.2016.02.002}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
-Segala, F.
-G., Bruno, A., Martin, J.
-T., Aung, M.
-T., Wade, A.
-R., \& Baker, D.
-H.
-(2023).
-Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
-\emph{eLife}, \emph{12}, RP87048.
-\url{https://doi.org/10.7554/eLife.87048}
+Segala, F. G., Bruno, A., Martin, J. T., Aung, M. T., Wade, A. R., \&
+Baker, D. H. (2023). Different rules for binocular combination of
+luminance flicker in cortical and subcortical pathways. \emph{eLife},
+\emph{12}, RP87048. \url{https://doi.org/10.7554/eLife.87048}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Simmons2005}{}}%
-Simmons, D. R. (2005). The binocular combination of chromatic contrast. \emph{Perception}, \emph{34}(8), 1035--1042. \url{https://doi.org/10.1068/p5279}
+Simmons, D. R. (2005). The binocular combination of chromatic contrast.
+\emph{Perception}, \emph{34}(8), 1035--1042.
+\url{https://doi.org/10.1068/p5279}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
-Stockman, A., \& Sharpe, L.
-T.
-(2000).
-The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
-\emph{Vision Res}, \emph{40}(13), 1711--1737.
-\url{https://doi.org/10.1016/s0042-6989(00)00021-3}
+Stockman, A., \& Sharpe, L. T. (2000). The spectral sensitivities of the
+middle- and long-wavelength-sensitive cones derived from measurements in
+observers of known genotype. \emph{Vision Res}, \emph{40}(13),
+1711--1737. \url{https://doi.org/10.1016/s0042-6989(00)00021-3}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Tootell1988}{}}%
-Tootell, R.
-B., Silverman, M.
-S., Hamilton, S.
-L., De Valois, R.
-L., \& Switkes, E.
-(1988).
-Functional anatomy of macaque striate cortex.
-III.
-color.
-\emph{J Neurosci}, \emph{8}(5), 1569--1593.
+Tootell, R. B., Silverman, M. S., Hamilton, S. L., De Valois, R. L., \&
+Switkes, E. (1988). Functional anatomy of macaque striate cortex. III.
+color. \emph{J Neurosci}, \emph{8}(5), 1569--1593.
 \url{https://doi.org/10.1523/JNEUROSCI.08-05-01569.1988}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wallis2013}{}}%
-Wallis, S.
-A., Baker, D.
-H., Meese, T.
-S., \& Georgeson, M.
-A.
-(2013).
-The slope of the psychometric function and non-stationarity of thresholds in spatiotemporal contrast vision.
-\emph{Vision Res}, \emph{76}, 1--10.
-\url{https://doi.org/10.1016/j.visres.2012.09.019}
+Wallis, S. A., Baker, D. H., Meese, T. S., \& Georgeson, M. A. (2013).
+The slope of the psychometric function and non-stationarity of
+thresholds in spatiotemporal contrast vision. \emph{Vision Res},
+\emph{76}, 1--10. \url{https://doi.org/10.1016/j.visres.2012.09.019}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Yu2002}{}}%
-Yu, C., Klein, S.
-A., \& Levi, D.
-M.
-(2002).
-Facilitation of contrast detection by cross-oriented surround stimuli and its psychophysical mechanisms.
-\emph{J Vis}, \emph{2}(3), 243--255.
+Yu, C., Klein, S. A., \& Levi, D. M. (2002). Facilitation of contrast
+detection by cross-oriented surround stimuli and its psychophysical
+mechanisms. \emph{J Vis}, \emph{2}(3), 243--255.
 \url{https://doi.org/10.1167/2.3.4}
@@
 
-\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}
+\beginsupplement
 
@@
 
-{\centering \includegraphics{Figures/individualdippers}
+{\centering \includegraphics{Figures/individualdippers.pdf}
 
@@
 
-\caption{Individual participant data from Experiment 1.}\label{fig:individualdips}
+\caption{\label{fig-individualdippers}Individual participant data from
+Experiment 1.}
+
 \end{figure}
@@
 
-{\centering \includegraphics{Figures/individualMCS}
+{\centering \includegraphics{Figures/individualMCS.pdf}
 
@@
 
-\caption{Individual participant data from Experiment 2.}\label{fig:individualMCS}
+\caption{\label{fig-individualMCS}Individual participant data from
+Experiment 2.}
+
 \end{figure}
@@
 
-{\centering \includegraphics{Figures/individualdiscs}
+{\centering \includegraphics{Figures/individualdiscs.pdf}
 
@@
 
-\caption{Individual participant data from Experiment 3.}\label{fig:individualdiscs}
+\caption{\label{fig-individualdiscs}Individual participant data from
+Experiment 3.}
+
 \end{figure}

### 2024-04-01 manuscript.qmd
Trying again
Testing specified latex engine, and also reticulate function

@@
   - Alex R. Wade
-format: pdf
+format:
+  pdf:
+    keep-tex: true
+pdf-engine: xelatex
 execute:
@@
 if (processdata>0){
-  install_miniconda()
-  use_miniconda('r-reticulate')
-  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
+  # install_miniconda()
+  # use_miniconda('r-reticulate')
+  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
   # install psignifit in the terminal with:

### 2024-04-01 manuscript.qmd
Try installing psignifit during the R script

@@
   # install_miniconda()
-  # use_miniconda('r-reticulate')
-  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
+  use_miniconda('r-reticulate')
+  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
   # install psignifit in the terminal with:

### 2024-04-01 manuscript.qmd
Test alternative python location

@@
 if (processdata>0){
-  install_miniconda()
-  use_miniconda('r-reticulate')
+  use_python('/usr/local/bin/python')
+  # install_miniconda()
+  # use_miniconda('r-reticulate')
   py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')

### 2024-04-01 manuscript.qmd
Change path to python

--- 2024-04-01 manuscript.qmd
@@
 if (processdata>0){
-  install_miniconda()
-  use_miniconda('r-reticulate')
+  use_python('/usr/local/bin/python3')
+  # install_miniconda()
+  # use_miniconda('r-reticulate')
   py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')

### 2024-04-01 manuscript.qmd
Trying different python

--- 2024-04-01 manuscript.qmd
@@
 if (processdata>0){
-  install_miniconda()
-  use_miniconda('r-reticulate')
-  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
+  use_python('/lib/python3')
+  # install_miniconda()
+  # use_miniconda('r-reticulate')
+  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
   # install psignifit in the terminal with:

### 2024-04-01 manuscript.qmd
minor change

@@
   # use_miniconda('r-reticulate')
-  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
+  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
   # install psignifit in the terminal with:

### 2024-04-01 manuscript.qmd
Changing python path again

@@
 if (processdata>0){
-  use_python('/lib/python3')
+  use_python('/usr/bin/python3')
   # install_miniconda()

### 2024-04-01 manuscript.qmd
Try getting different python

--- 2024-04-01 manuscript.qmd
@@
 if (processdata>0){
-  use_python('/lib/python3')
+  # use_python('/usr/bin/python3')
   # install_miniconda()

### 2024-04-02 manuscript.qmd
Forcing to python 3.9 to avoid package install problem

--- 2024-04-01 manuscript.qmd
@@
 if (processdata>0){
-  use_python('/lib/python3')
+  use_python_version("3.9:latest")
+  # use_python('/usr/bin/python3')
   # install_miniconda()

### 2024-04-02 manuscript.qmd
Trying to find out which python versions are available

--- 2024-04-01 manuscript.qmd
@@
 pdf-engine: xelatex
-execute:
-  echo: false
+# execute:
+#   echo: false
 bibliography: references.bib
@@
 if (processdata>0){
-  use_python('/usr/bin/python3')
+  install_python(list = TRUE)
+  # use_python_version("3.9:latest")
+  # use_python('/usr/bin/python3')
   # install_miniconda()

### 2024-04-02 manuscript.qmd
Try specific earlier version of python

@@
 if (processdata>0){
-  install_python(list = TRUE)
-  # use_python_version("3.9:latest")
+  install_python(version="3.9.19")
+  use_python_version("3.9.19")
   # use_python('/usr/bin/python3')

### 2024-04-02 manuscript.qmd
Last try before I get frustrated and give up

@@
 if (processdata>0){
-  install_python(version="3.9.19")
-  use_python_version("3.9.19")
-  # use_python('/usr/bin/python3')
+  # install_python(version="3.9.19")
+  # use_python_version("3.9.19")
+  use_python('/usr/bin/python3.9')
   # install_miniconda()
   # use_miniconda('r-reticulate')
+  # py_install('pip')
   py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
@@
 Threshold is defined as the minimum target contrast required to make this judgement with 75% accuracy.
-The binocular condition is the same, except that the same stimuli are shown to both eyes.
-In the half-binocular condition the pedestal is shown to both eyes, but the target increment shown only to one eye.
+The binocular condition is the same, except that the stimuli are shown to both eyes.
+In the half-binocular condition the pedestal is shown to both eyes, but the target increment is shown only to one eye.
 Finally, the dichoptic condition involves presenting the pedestal to one eye, and the target increment to the other eye.

### 2024-04-02 manuscript.qmd
Minor edits to text

@@
     keep-tex: true
+  # docx:
+  #   toc: false
+  #   number-sections: true
+# prefer-html: true
 pdf-engine: xelatex
@@
 Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement.
-This is very different from the 'ocularity invariance' that is well-established when using DC-balanced periodic stimuli such as sine-wave gratings, and implies strong interocular suppression [@Meese2006; @Baker2017; @Moradi2009].
+This is very different from the 'ocularity invariance' (where binocular and monocular stimuli appear equal) that is well-established when using DC-balanced periodic stimuli such as sine-wave gratings, and implies strong interocular suppression [@Meese2006; @Baker2017; @Moradi2009].
 There is additional psychophysical evidence from matching studies that binocular combination can be close to linear for luminance increments [@Levelt1965; @Anstis1998], particularly against a dark background [@Baker2012].
@@
 All experiments were completed by the first author (DHB) and two additional participants, who differed for each experiment.
-Participants had no known abnormalities of binocular vision.
+Participants had no known abnormalities of binocular or colour vision.
 Written informed consent was obtained before data collection began, and all procedures were approved by the ethics committee of the Department of Psychology at the University of York (ID number 2202).
@@
 Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate threshold and slope parameters via a Bayesian numerical integration method [@Schutt2016].
-A cumulative Gaussian was used as the underlying function, and we converted the slope estimates ($\sigma$ parameters from the fitted Gaussians) to equivalent Weibull $\beta$ values using the approximation $\beta = 10.3/\sigma$.
+A cumulative Gaussian was used as the underlying function, with contrast values expressed in decibel (dB) units (where $C_{dB} = 20log_{10}(C_\%)$).
+We converted the slope estimates ($\sigma$ parameters from the fitted Gaussians) to equivalent Weibull $\beta$ values using the approximation $\beta = 10.3/\sigma$.
+Threshold was defined as the target contrast corresponding to an accuracy of 75% correct.
 
@@
 \begin{equation}
-Stage1_R = \frac{C_L^m}{S + C_R + \omega C_L},
+Stage1_R = \frac{C_R^m}{S + C_R + \omega C_L},
 \end{equation}
@@
 where $C_L$ and $C_R$ are the contrasts displayed to the left and right eyes, and $m$, $S$, $\omega$, $p$, $q$ and $Z$ are free parameters in the model.
-A further free parameter, $k$, represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values (note that in the original model specification [@Meese2006] this parameter was called $\sigma$, but we use the $k$ symbol here to avoid confusion with the standard deviation of the cumulative Gaussian used when fitting the psychometric functions to derive thresholds).
+A further free parameter, $k$, represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values (note that in the original model specification [@Meese2006] this parameter was called $\sigma$, but we use the $k$ symbol here to avoid confusion with the standard deviation of the cumulative Gaussian used when fitting the psychometric functions to estimate thresholds).
 Thresholds are defined by iteratively adjusting the target contrast until the following equality is satisfied:
@@
 
-We ran the simplex algorithm from `r ntotalsimplexfits` random starting vectors for each data set, and chose the solution for each data set that gave the smallest RMS error.
+We ran the simplex algorithm from `r ntotalsimplexfits` random starting vectors for each data set, and chose the solution for each data set that gave the smallest root mean squared error (RMSE) between the model and data.
 
@@
 Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).
-Curves in panels (a-c) show the best fitting models, optimized using a simplex algorithm (described in section 4.4), and RMSE values give the root mean square errors of the fits.](Figures/dipperssimplex.pdf){#fig-dipperfig}
+Curves in panels (a-c) show the best fitting models, optimized using a simplex algorithm, and RMSE values give the root mean squared errors of the fits.](Figures/dipperssimplex.pdf){#fig-dipperfig}
 
@@
 Following @Meese2006, we also inspected the slope of the psychometric function for each condition (see [@fig-dipperfig]d-f).
-At detection threshold, slopes were relatively steep for all stimuli, with $\beta$ values around 4.
+At detection threshold, slopes were relatively steep for all stimuli, with values around $\beta=4$.
 As pedestal contrasts increased, slopes linearized and reduced to around $\beta=1.3$ [@Foley1981; @Meese2006], and remained shallow at high pedestal contrasts.
@@
 However, we observe that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
-Our second experiment therefore investigated the slope of the psychometric function in more detail for dichoptic masking using the method of constant stimuli.
+Our second experiment therefore investigated the slope of the psychometric function in more detail for dichoptic masking using the method of constant stimuli, as well as exploring dichoptic interactions between chromatic channels.
 
@@
 
-In our final experiment, we again measured dipper functions, but this time for a temporally modulating luminance disc.
+In our final experiment, we again measured dipper functions, but this time for a disc temporally modulating in luminance.
 This was motivated by our recent work [@Segala2023] that appeared to show increased binocular facilitation and reduced interocular suppression for flickering disc stimuli (relative to gratings), measured using EEG and a psychophysical matching paradigm.
@@
 For consistency with previous work, we initially performed least-squares fits of the two-stage model [@Meese2006] for each of the chromaticity experiments, and the flickering disc experiment (7 free parameters per fit).
-The best model fits are shown by the curves in @fig-dipperfig & @fig-discdata, and provide an excellent description of the data, with RMS errors between `r round(min(allrms),digits=2)` and `r round(max(allrms),digits=2)`dB.
+The best model fits are shown by the curves in @fig-dipperfig and @fig-discdata, and provide an excellent description of the data, with RMS errors between `r round(min(allrms),digits=2)` and `r round(max(allrms),digits=2)`dB.
 Best fitting parameters are shown in the 'Simplex fits' section of @tbl-parametertable.
@@
 We note that the distribution for $\omega$ in the flickering disc condition is somewhat lower than for the other three data sets.
-However this difference is not meaningful according to criteria such as comparing the 95% credible intervals of the distribution to a value of $\omega=1$.
+However this difference is not meaningful according to widely accepted criteria such as comparing the 95% intervals of the distribution to a value of $\omega=1$.
 
@@
 One striking discrepancy is that the model predicts a region of negative d-prime for the case where the target and dichoptic mask have the same chromaticity (see the curved regions below 50\% correct).
-This feature was not generally present in our data, though it can be observed for one participant in [@fig-individualMCS]b,c.
-Our previous work [@Baker2013] has found evidence for this phenomenon (termed 'swan functions'), but it generally requires very high mask contrasts to be measurable empirically, and there may also be some individual differences; both factors might explain its absence here.
+This happens in the model because low contrast targets suppress the mask more than they excite the detecting mechanism, producing a net decrease in response.
+The feature (termed a 'swan function') was not generally present in our empirical data, though it can be observed for one participant in [@fig-individualMCS]b,c.
+Our previous work [@Baker2013] has found evidence for this phenomenon, but it generally requires very high mask contrasts to be measurable empirically, and there may also be some individual differences; both factors might explain its absence here.
 
 [@fig-MCSmodel]d,e shows the model estimates for the weight of interocular suppression in each combination of target and mask chromaticity.
-Although the weights might appear to indicate that (excluding within-mechanism effects) suppression is strongest between blue/yellow targets and achromatic masks (a weight of 0.56), this is somewhat complicated by the differences in sensitivity and mask contrast between conditions.
+Although the weights might appear to indicate that (excluding within-mechanism effects) suppression is strongest between blue/yellow targets and achromatic masks (a weight of 0.56), this is somewhat complicated by the differences in mask contrast between conditions.
 We selected mask contrasts that were approximately equal multiples ($16\times$) of their own detection thresholds, based on the data of Experiment 1 ([@fig-dipperfig]a-c).
 However the modelling expressed these contrasts as a percentage of the maximum contrast that it was possible to display on the monitor (see Procedures).
-The values in brackets in [@fig-MCSmodel]d indicate the overall suppressive term on the denominator, calculated by multiplying the mask contrast by the fitted weight.
+The values in brackets in [@fig-MCSmodel]d indicate the overall suppressive term on the denominator of the model at stage 1, calculated by multiplying the mask contrast by the fitted weight.
 These values indicate that the strongest suppression is instead between red/green targets and blue/yellow masks, consistent with the threshold elevation observed empirically ([@fig-MCSfig]g).
@@
 
-Estimates of the binocular summation ratio at threshold fell within the range $\sqrt{2}$ to 2 for all four data sets.
+Estimates of the binocular summation ratio at threshold fell within the range $\sqrt{2}$ to 2 for all four stimuli tested here.
 Consistent with previous reports [@Simmons2005], summation was slightly higher for chromatic versus achromatic stimuli, but fell short of perfect linear summation (a ratio of 2).
@@
 In particular, pedestal masking linearizes the slope [@Foley1981; @Meese2006], and within-channel dichoptic masking produces very steep slopes [@Meese2006; @Baker2013].
-We replicate both of these effects here, and show that they extend to isoluminant chromatic pathways (see [@fig-dipperfig]d-f & @fig-MCSfig).
+We replicate both of these effects here, and show that they extend to the isoluminant chromatic pathways (see [@fig-dipperfig]d-f & @fig-MCSfig).
 We additionally show that dichoptic masking between different pathways does not produce unusually steep slopes (see [@fig-MCSfig]).
@@
 In terms of perception, one consequence of this early suppression is to achieve 'ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes [@Baker2007].
-Similar processes of invariance have also been reported using fMRI [@Moradi2009] and steady-state EEG [@Baker2017].
+Similar processes of response invariance have also been reported using fMRI [@Moradi2009] and steady-state EEG [@Baker2017].
 

### 2024-04-02 manuscript.tex
Minor edits to text

@@
 the minimum target contrast required to make this judgement with 75\%
-accuracy. The binocular condition is the same, except that the same
-stimuli are shown to both eyes. In the half-binocular condition the
-pedestal is shown to both eyes, but the target increment shown only to
-one eye. Finally, the dichoptic condition involves presenting the
-pedestal to one eye, and the target increment to the other eye.
+accuracy. The binocular condition is the same, except that the stimuli
+are shown to both eyes. In the half-binocular condition the pedestal is
+shown to both eyes, but the target increment is shown only to one eye.
+Finally, the dichoptic condition involves presenting the pedestal to one
+eye, and the target increment to the other eye.
 
@@
 when using this stimulus arrangement. This is very different from the
-`ocularity invariance' that is well-established when using DC-balanced
-periodic stimuli such as sine-wave gratings, and implies strong
-interocular suppression (Baker \& Wade, 2017; Meese et al., 2006; Moradi
-\& Heeger, 2009). There is additional psychophysical evidence from
-matching studies that binocular combination can be close to linear for
-luminance increments (Anstis \& Ho, 1998; Levelt, 1965), particularly
-against a dark background (Baker et al., 2012). Both structural and
-functional data therefore imply that binocular combination may differ
-between spatial and temporal contrast.
+`ocularity invariance' (where binocular and monocular stimuli appear
+equal) that is well-established when using DC-balanced periodic stimuli
+such as sine-wave gratings, and implies strong interocular suppression
+(Baker \& Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009). There
+is additional psychophysical evidence from matching studies that
+binocular combination can be close to linear for luminance increments
+(Anstis \& Ho, 1998; Levelt, 1965), particularly against a dark
+background (Baker et al., 2012). Both structural and functional data
+therefore imply that binocular combination may differ between spatial
+and temporal contrast.
 
@@
 additional participants, who differed for each experiment. Participants
-had no known abnormalities of binocular vision. Written informed consent
-was obtained before data collection began, and all procedures were
-approved by the ethics committee of the Department of Psychology at the
-University of York (ID number 2202).
+had no known abnormalities of binocular or colour vision. Written
+informed consent was obtained before data collection began, and all
+procedures were approved by the ethics committee of the Department of
+Psychology at the University of York (ID number 2202).
 
@@
 Bayesian numerical integration method (Schütt et al., 2016). A
-cumulative Gaussian was used as the underlying function, and we
-converted the slope estimates (\(\sigma\) parameters from the fitted
-Gaussians) to equivalent Weibull \(\beta\) values using the
-approximation \(\beta = 10.3/\sigma\).
+cumulative Gaussian was used as the underlying function, with contrast
+values expressed in decibel (dB) units (where
+\(C_{dB} = 20log_{10}(C_\%)\)). We converted the slope estimates
+(\(\sigma\) parameters from the fitted Gaussians) to equivalent Weibull
+\(\beta\) values using the approximation \(\beta = 10.3/\sigma\).
+Threshold was defined as the target contrast corresponding to an
+accuracy of 75\% correct.
 
@@
 standard deviation of the cumulative Gaussian used when fitting the
-psychometric functions to derive thresholds). Thresholds are defined by
-iteratively adjusting the target contrast until the following equality
-is satisfied:
+psychometric functions to estimate thresholds). Thresholds are defined
+by iteratively adjusting the target contrast until the following
+equality is satisfied:
 
@@
 data set, and chose the solution for each data set that gave the
-smallest RMS error.
+smallest root mean squared error (RMSE) between the model and data.
 
@@
 details). Curves in panels (a-c) show the best fitting models, optimized
-using a simplex algorithm (described in section 4.4), and RMSE values
-give the root mean square errors of the fits.}
+using a simplex algorithm, and RMSE values give the root mean squared
+errors of the fits.}
 
@@
 Figure~\ref{fig-dipperfig}d-f). At detection threshold, slopes were
-relatively steep for all stimuli, with \(\beta\) values around 4. As
+relatively steep for all stimuli, with values around \(\beta=4\). As
 pedestal contrasts increased, slopes linearized and reduced to around
@@
 function in more detail for dichoptic masking using the method of
-constant stimuli.
+constant stimuli, as well as exploring dichoptic interactions between
+chromatic channels.
 
@@
 In our final experiment, we again measured dipper functions, but this
-time for a temporally modulating luminance disc. This was motivated by
-our recent work (Segala et al., 2023) that appeared to show increased
+time for a disc temporally modulating in luminance. This was motivated
+by our recent work (Segala et al., 2023) that appeared to show increased
 binocular facilitation and reduced interocular suppression for
@@
 parameters per fit). The best model fits are shown by the curves in
-Figure~\ref{fig-dipperfig} \& Figure~\ref{fig-discdata}, and provide an
+Figure~\ref{fig-dipperfig} and Figure~\ref{fig-discdata}, and provide an
 excellent description of the data, with RMS errors between 1.06 and
@@
 flickering disc condition is somewhat lower than for the other three
-data sets. However this difference is not meaningful according to
-criteria such as comparing the 95\% credible intervals of the
+data sets. However this difference is not meaningful according to widely
+accepted criteria such as comparing the 95\% intervals of the
 distribution to a value of \(\omega=1\).
@@
 the case where the target and dichoptic mask have the same chromaticity
-(see the curved regions below 50\% correct). This feature was not
-generally present in our data, though it can be observed for one
-participant in Figure~\ref{fig-individualMCS}b,c.~Our previous work
-(Baker et al., 2013) has found evidence for this phenomenon (termed
-`swan functions'), but it generally requires very high mask contrasts to
-be measurable empirically, and there may also be some individual
-differences; both factors might explain its absence here.
+(see the curved regions below 50\% correct). This happens in the model
+because low contrast targets suppress the mask more than they excite the
+detecting mechanism, producing a net decrease in response. The feature
+(termed a `swan function') was not generally present in our empirical
+data, though it can be observed for one participant in
+Figure~\ref{fig-individualMCS}b,c.~Our previous work (Baker et al.,
+2013) has found evidence for this phenomenon, but it generally requires
+very high mask contrasts to be measurable empirically, and there may
+also be some individual differences; both factors might explain its
+absence here.
 
@@
 blue/yellow targets and achromatic masks (a weight of 0.56), this is
-somewhat complicated by the differences in sensitivity and mask contrast
-between conditions. We selected mask contrasts that were approximately
-equal multiples (\(16\times\)) of their own detection thresholds, based
-on the data of Experiment 1 (Figure~\ref{fig-dipperfig}a-c). However the
+somewhat complicated by the differences in mask contrast between
+conditions. We selected mask contrasts that were approximately equal
+multiples (\(16\times\)) of their own detection thresholds, based on the
+data of Experiment 1 (Figure~\ref{fig-dipperfig}a-c). However the
 modelling expressed these contrasts as a percentage of the maximum
@@
 Procedures). The values in brackets in Figure~\ref{fig-MCSmodel}d
-indicate the overall suppressive term on the denominator, calculated by
-multiplying the mask contrast by the fitted weight. These values
-indicate that the strongest suppression is instead between red/green
-targets and blue/yellow masks, consistent with the threshold elevation
-observed empirically (Figure~\ref{fig-MCSfig}g). In principle it would
-be possible to repeat this modelling using either cone contrast values,
-or contrast expressed relative to detection threshold, which would
-require re-fitting the model.
+indicate the overall suppressive term on the denominator of the model at
+stage 1, calculated by multiplying the mask contrast by the fitted
+weight. These values indicate that the strongest suppression is instead
+between red/green targets and blue/yellow masks, consistent with the
+threshold elevation observed empirically (Figure~\ref{fig-MCSfig}g). In
+principle it would be possible to repeat this modelling using either
+cone contrast values, or contrast expressed relative to detection
+threshold, which would require re-fitting the model.
 
@@
 Estimates of the binocular summation ratio at threshold fell within the
-range \(\sqrt{2}\) to 2 for all four data sets. Consistent with previous
-reports (Simmons, 2005), summation was slightly higher for chromatic
-versus achromatic stimuli, but fell short of perfect linear summation (a
-ratio of 2). In our model, summation at threshold is determined by the
-exponent at the first gain control stage (the \emph{m} parameter in
-Equations 1 \& 2). The summation ratio can be approximated by
-\(2^{1/m}\) (see Figure 9 of Baker et al., 2012), such that an exponent
-of \(m=1\) produces a ratio of 2, and an exponent of \(m = 2\) produces
-a ratio of \(\sqrt{2}\). Both the simplex and Bayesian model fits (see
-Table~\ref{tbl-parametertable}) generated parameter estimates in the
-range \(1 < m < 1.4\), consistent with the high levels of summation
-observed empirically.
+range \(\sqrt{2}\) to 2 for all four stimuli tested here. Consistent
+with previous reports (Simmons, 2005), summation was slightly higher for
+chromatic versus achromatic stimuli, but fell short of perfect linear
+summation (a ratio of 2). In our model, summation at threshold is
+determined by the exponent at the first gain control stage (the \emph{m}
+parameter in Equations 1 \& 2). The summation ratio can be approximated
+by \(2^{1/m}\) (see Figure 9 of Baker et al., 2012), such that an
+exponent of \(m=1\) produces a ratio of 2, and an exponent of \(m = 2\)
+produces a ratio of \(\sqrt{2}\). Both the simplex and Bayesian model
+fits (see Table~\ref{tbl-parametertable}) generated parameter estimates
+in the range \(1 < m < 1.4\), consistent with the high levels of
+summation observed empirically.
 
@@
 steep slopes (Baker et al., 2013; Meese et al., 2006). We replicate both
-of these effects here, and show that they extend to isoluminant
+of these effects here, and show that they extend to the isoluminant
 chromatic pathways (see Figure~\ref{fig-dipperfig}d-f \&
@@
 of the same stimulus viewed by both eyes (Baker et al., 2007). Similar
-processes of invariance have also been reported using fMRI (Moradi \&
-Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).
+processes of response invariance have also been reported using fMRI
+(Moradi \& Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).
 

### 2024-04-02 manuscript.qmd
Hopefully fixed python issue

@@
 if (processdata>0){
-  # install_python(version="3.9.19")
+  install_python(version="3.6")
   # use_python_version("3.9.19")
-  use_python('/usr/bin/python3.9')
+  # use_python('/usr/bin/python3.9')
   # install_miniconda()

### 2024-04-07 manuscript.qmd
Added affiliations and abstract

@@
 author:
-  - Daniel H. Baker
-  - Kirralise J. Hansford
-  - Federico G. Segala
-  - Annie Y. Morsi
-  - Rowan J. Huxley
-  - Joel T. Martin
-  - Maya Rockman
-  - Alex R. Wade
+  - name: Daniel H. Baker$^{1,2,*}$
+  - name: Kirralise J. Hansford$^1$
+  - name: Federico G. Segala$^1$
+  - name: Annie Y. Morsi$^1$
+  - name: Rowan J. Huxley$^{1,3}$
+  - name: Joel T. Martin$^{1,4}$
+  - name: Maya Rockman$^1$
+  - name: Alex R. Wade$^{1,2}$
+pdf-engine: xelatex
+bibliography: references.bib
+csl: journal-of-vision.csl
 format:
@@
     keep-tex: true
-  # docx:
-  #   toc: false
-  #   number-sections: true
-# prefer-html: true
-pdf-engine: xelatex
-# execute:
-#   echo: false
-bibliography: references.bib
-csl: journal-of-vision.csl
 header-includes: 
@@
 ---
+
+$^1$Department of Psychology, University of York, UK
+
+$^2$York Biomedical Research Institute, University of York, UK
+
+$^3$School of Psychology, University of Nottingham, UK
+
+$^4$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, UK
+
+$^*$Corresponding author, email: daniel.baker\@york.ac.uk
 
@@
 
+Much progress has been made in understanding how the brain combines signals from the two eyes.
+However most of this work has involved achromatic (black and white) stimuli, and it is not clear if the same processes apply in colour-sensitive pathways.
+In our first experiment, we measured contrast discrimination ('dipper') functions for four key ocular configurations (monocular, binocular, half-binocular and dichoptic), for achromatic, isoluminant red/green and isoluminant blue/yellow sine-wave grating stimuli.
+We find a similar pattern of results across stimuli, implying equivalently strong interocular suppression within each pathway.
+Our second experiment measured dichoptic masking within and between pathways using the method of constant stimuli.
+Masking was strongest within-pathway, and weakest between chromatic and achromatic mechanisms.
+Finally, we repeated the dipper experiment using temporal luminance modulations, which produced slightly weaker interocular suppression than for spatially modulated stimuli.
+We interpret our results in the context of a contemporary two-stage model of binocular contrast gain control, implemented here using a hierarchical Bayesian framework.
+Posterior distributions of the weight of interocular suppression overlapped with a value of 1 for all dipper data sets, and the model captured well the pattern of threshold and slope values from all three experiments.
+
+**Keywords**: *isoluminant*, *dichoptic*, *binocular interactions*, *gain control*, *summation*, *suppression*, *masking*, *psychophysics*
+
 # Introduction
@@
 A further property of 'blob' regions is that they are less strongly orientation-tuned than other regions of V1 [@Horton1981; @Livingstone1984], and biased towards low spatial frequencies [@Edwards1995; @Tootell1988].
-Our recent work has investigated binocular combination for flickering discs of luminance, which are DC-balanced across time [@Segala2023].
+Our recent work [@Segala2023] has investigated binocular combination for flickering discs of luminance, which are DC-balanced across time (i.e.
+the time-averaged luminance is equal to the background).
 Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement.
@@
 
-The main aim of the present study is to characterise binocular signal combination for chromatic stimuli, and for temporal modulations of luminance.
+The main aim of the present study was to characterise binocular signal combination for chromatic stimuli, and for temporal modulations of luminance.
 We also aimed to investigate interocular suppression between chromatic and achromatic pathways.

### 2024-04-07 manuscript.tex
Added affiliations and abstract

@@
   pdftitle={Binocular integration of chromatic and luminance signals},
-  pdfauthor={Daniel H. Baker; Kirralise J. Hansford; Federico G. Segala; Annie Y. Morsi; Rowan J. Huxley; Joel T. Martin; Maya Rockman; Alex R. Wade},
+  pdfauthor={Daniel H.
+Baker\^{}\{1,2,*\}; Kirralise J.
+Hansford\^{}1; Federico G.
+Segala\^{}1; Annie Y.
+Morsi\^{}1; Rowan J.
+Huxley\^{}\{1,3\}; Joel T.
+Martin\^{}\{1,4\}; Maya Rockman\^{}1; Alex R.
+Wade\^{}\{1,2\}},
   colorlinks=true,
@@
 \title{Binocular integration of chromatic and luminance signals}
-\author{Daniel H. Baker \and Kirralise J. Hansford \and Federico G.
-Segala \and Annie Y. Morsi \and Rowan J. Huxley \and Joel T.
-Martin \and Maya Rockman \and Alex R. Wade}
+\author{Daniel H. Baker\(^{1,2,*}\) \and Kirralise J.
+Hansford\(^1\) \and Federico G. Segala\(^1\) \and Annie Y.
+Morsi\(^1\) \and Rowan J. Huxley\(^{1,3}\) \and Joel T.
+Martin\(^{1,4}\) \and Maya Rockman\(^1\) \and Alex R. Wade\(^{1,2}\)}
 \date{}
@@
 \maketitle
+\(^1\)Department of Psychology, University of York, UK
+
+\(^2\)York Biomedical Research Institute, University of York, UK
+
+\(^3\)School of Psychology, University of Nottingham, UK
+
+\(^4\)School of Philosophy, Psychology and Language Sciences, University
+of Edinburgh, UK
+
+\(^*\)Corresponding author, email: daniel.baker@york.ac.uk
+
 \hypertarget{abstract}{%
 \section{Abstract}\label{abstract}}
+
+Much progress has been made in understanding how the brain combines
+signals from the two eyes. However most of this work has involved
+achromatic (black and white) stimuli, and it is not clear if the same
+processes apply in colour-sensitive pathways. In our first experiment,
+we measured contrast discrimination (`dipper') functions for four key
+ocular configurations (monocular, binocular, half-binocular and
+dichoptic), for achromatic, isoluminant red/green and isoluminant
+blue/yellow sine-wave grating stimuli. We find a similar pattern of
+results across stimuli, implying equivalently strong interocular
+suppression within each pathway. Our second experiment measured
+dichoptic masking within and between pathways using the method of
+constant stimuli. Masking was strongest within-pathway, and weakest
+between chromatic and achromatic mechanisms. Finally, we repeated the
+dipper experiment using temporal luminance modulations, which produced
+slightly weaker interocular suppression than for spatially modulated
+stimuli. We interpret our results in the context of a contemporary
+two-stage model of binocular contrast gain control, implemented here
+using a hierarchical Bayesian framework. Posterior distributions of the
+weight of interocular suppression overlapped with a value of 1 for all
+dipper data sets, and the model captured well the pattern of threshold
+and slope values from all three experiments.
+
+\textbf{Keywords}: \emph{isoluminant}, \emph{dichoptic}, \emph{binocular
+interactions}, \emph{gain control}, \emph{summation},
+\emph{suppression}, \emph{masking}, \emph{psychophysics}
 
@@
 Livingstone \& Hubel, 1984), and biased towards low spatial frequencies
-(Edwards et al., 1995; Tootell et al., 1988). Our recent work has
-investigated binocular combination for flickering discs of luminance,
-which are DC-balanced across time (Segala et al., 2023). Steady-state
-EEG responses from early visual cortex and psychophysical contrast
-matching data were both consistent with weak interocular suppression
-when using this stimulus arrangement. This is very different from the
-`ocularity invariance' (where binocular and monocular stimuli appear
-equal) that is well-established when using DC-balanced periodic stimuli
-such as sine-wave gratings, and implies strong interocular suppression
-(Baker \& Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009). There
-is additional psychophysical evidence from matching studies that
-binocular combination can be close to linear for luminance increments
-(Anstis \& Ho, 1998; Levelt, 1965), particularly against a dark
-background (Baker et al., 2012). Both structural and functional data
-therefore imply that binocular combination may differ between spatial
-and temporal contrast.
-
-The main aim of the present study is to characterise binocular signal
+(Edwards et al., 1995; Tootell et al., 1988). Our recent work (Segala et
+al., 2023) has investigated binocular combination for flickering discs
+of luminance, which are DC-balanced across time (i.e.~the time-averaged
+luminance is equal to the background). Steady-state EEG responses from
+early visual cortex and psychophysical contrast matching data were both
+consistent with weak interocular suppression when using this stimulus
+arrangement. This is very different from the `ocularity invariance'
+(where binocular and monocular stimuli appear equal) that is
+well-established when using DC-balanced periodic stimuli such as
+sine-wave gratings, and implies strong interocular suppression (Baker \&
+Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009). There is
+additional psychophysical evidence from matching studies that binocular
+combination can be close to linear for luminance increments (Anstis \&
+Ho, 1998; Levelt, 1965), particularly against a dark background (Baker
+et al., 2012). Both structural and functional data therefore imply that
+binocular combination may differ between spatial and temporal contrast.
+
+The main aim of the present study was to characterise binocular signal
 combination for chromatic stimuli, and for temporal modulations of

### 2024-04-15 manuscript.qmd
Switched to using normalized contrast values

@@
 
-$^1$Department of Psychology, University of York, UK
-
-$^2$York Biomedical Research Institute, University of York, UK
-
-$^3$School of Psychology, University of Nottingham, UK
-
-$^4$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, UK
-
+$^1$Department of Psychology, University of York, UK\
+$^2$York Biomedical Research Institute, University of York, UK\
+$^3$School of Psychology, University of Nottingham, UK\
+$^4$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, UK\
 $^*$Corresponding author, email: daniel.baker\@york.ac.uk
@@
 if (processdata>0){
-  install_python(version="3.6")
-  # use_python_version("3.9.19")
-  # use_python('/usr/bin/python3.9')
-  # install_miniconda()
-  # use_miniconda('r-reticulate')
-  # py_install('pip')
-  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
+  # install_python(version="3.6")
+  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
+
+  use_miniconda('r-reticulate')
+
   # install psignifit in the terminal with:
@@
 sublist <- unique(ex1data$Subject)
-explist <- unique(ex1data$Experiment)
+explist <- c('AC','RG','BY')  # hard coded in this order to avoid confusion later on
 
@@
 
+pooledthresh <- NULL
 # now also pool across subjects and fit for plotting the full posterior
@@
   allposY[cond,] <- xycos[[2]]
-
-}
-
-save(file='local/MCSdata.RData',list=c('MCSthresh','MCSslope','thdelev','slopematrix','detslopes','MCSpropcorr','contrastsdB','allposteriors','allposX','allposY'))
+  pooledthresh[cond] <- res$Fit[1]
+}
+
+save(file='local/MCSdata.RData',list=c('MCSthresh','MCSslope','thdelev','slopematrix','detslopes','MCSpropcorr','contrastsdB','allposteriors','allposX','allposY','pooledthresh'))
 
@@
 
+temp <- array(0,dim=c(4,4,8))
+temp[1,,] <- meanthresh[1,,]
+temp[2,,] <- meanthresh[2,,]
+temp[3,,] <- meanthresh[3,,]
+temp[4,,] <- meanthresh3
+meanthresh <- temp
+
+scalefactdB <- meanthresh[,1,1]
+scalefact <- 10^(scalefactdB/20)
+
 if (processdata==2){
@@
 
-pedlist <<- seq(-12,30,6)
 allp <- matrix(0,nrow=4,ncol=7)
@@
 allrms <- NULL
- for (cond in 1:3){
+for (cond in 1:4){
   print(cond)
-   datatofit <<- meanthresh[cond,,]
+  if (cond==1){pedlist <<- seq(-12,30,6) - scalefactdB[cond]}
+  if (cond==2){pedlist <<- seq(-6,36,6) - scalefactdB[cond]}
+  if (cond==3){pedlist <<- seq(-6,36,6) - scalefactdB[cond]}
+  if (cond==4){pedlist <<- seq(-12,30,6) - scalefactdB[cond]}
+
+  datatofit <<- meanthresh[cond,,] - scalefactdB[cond]
 
@@
 
-   pedlist <<- seq(-6,36,6)  # increase pedestal contrasts for the chromatic conditions
-
- }
-
-# finally fit the disc data
-pedlist <<- seq(-12,30,6)
-cond <- 4
-
-   print(cond)
-   datatofit <<- meanthresh3
-
-   nfits <- ntotalsimplexfits
-   for (n in 1:ntotalsimplexfits){
-     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){nfits <- nfits-1}
-   }
-
-   if (nfits > 0){
-   foreach(i = 1:nfits, .combine=rbind) %dopar% {
-   sout <- pracma::nelder_mead(errorfit,rnorm(7,sd=0.1)+log10(c(0.5,5.5,0.3,1,0.01,1,0.2)))
-   allout <- c(errorfit(sout$xmin),sout$xmin)
-
-   hassaved <- 0
-   filecount <- 0
-   while (!hassaved){
-     filecount <- filecount + 1
-     if (!file.exists(paste0('local/fits/E',cond,'f',filecount,'.RData'))){
-       save(file=paste0('local/fits/E',cond,'f',filecount,'.RData'),list='allout')
-       hassaved <- 1}
-   }
-   allout <- c(errorfit(sout$xmin),sout$xmin)
-   }
-   }
-
-   finalout <- matrix(0,nrow=ntotalsimplexfits,ncol=8)
-   for (n in 1:ntotalsimplexfits){
-     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){
-       load(file=paste0('local/fits/E',cond,'f',n,'.RData'))
-       finalout[n,] <- allout
-     }
-   }
-   i <- which(finalout[,1]==min(finalout[,1]))
-   p <- 10^finalout[i[1],2:8]
-   allrms[cond] <- finalout[i[1],1]
-   p[2] <- p[2] + 1
-   p[2] <- min(p[2],16)
-   p[1] <- 1 + p[1] + p[2]
-   p[1] <- min(p[1],20)
-   p[3] <- 1 + p[3]
-   allp[cond,] <- p
-   allparams[cond,,] <- finalout
+}
 
@@
 stopCluster(cluster)
-
 }
@@
 
+  scalefactdB <- c(meanthresh[,1,1],meanthresh3[1,1])
+  scalefact <- 10^(scalefactdB/20)
+
   load('local/simplexfits.RData')
 
-pedlist <- -12:39
+  pedlist <- -24:39
   pedlevelsC <- 10^(pedlist/20)
@@
 
-ticklocsx <- seq(-12,36,6)
-ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
-ticklocsy <- seq(-12,36,6)
-ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
-pedcontrasts <- seq(-12,30,6)
-
-exptorder <- c(1,3,2)
   paneltitles <- c('(a) Achromatic thresholds','(b) Red/Green thresholds','(c) Blue/Yellow thresholds')
@@
   for (expt in 1:3){
+
+    ticklocsx <- seq(-24,30,6)
+    ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+    ticklocsy <- seq(-24,30,6)
+    ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)
+
     par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(min(ticklocsy),max(ticklocsy)))   
     axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
     mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+    title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+    title(ylab='Normalized threshold contrast', col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
     title(main=paneltitles[expt],cex.main=2.5)
 
+    if (expt==1){pedcontrasts <- seq(-12,30,6) - scalefactdB[expt]}
+    if (expt>1){pedcontrasts <- seq(-6,36,6) - scalefactdB[expt]}
+    pedcontrasts[1] <- min(ticklocsx)
+
     for (cond in 1:4){
-  arrows(pedcontrasts,meanthresh[exptorder[expt],cond,],pedcontrasts,meanthresh[exptorder[expt],cond,]+SEthresh[exptorder[expt],cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
- arrows(pedcontrasts,meanthresh[exptorder[expt],cond,],pedcontrasts,meanthresh[exptorder[expt],cond,]-SEthresh[exptorder[expt],cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+      arrows(pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt],pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt]+SEthresh[expt,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+      arrows(pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt],pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt]-SEthresh[expt,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
       # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
-  lines(pedlist,allpreddB[exptorder[expt],cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,meanthresh[exptorder[expt],cond,],pch=16,col=collist[cond],cex=1.5)
-}
-text(24,-9,paste0('RMSE = ',round(allrms[expt],digits=2),'dB'),cex=2)
-if (expt==1){legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
-
-pedcontrasts <- c(-12,seq(0,36,6))  # update pedestal contrasts for plotting chromatic conditions
+      lines(pedlist,allpreddB[expt,cond,],col=collist[cond],lwd=2)
+      points(pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt],pch=16,col=collist[cond],cex=1.5)
+    }
+    text(ticklocsx[7]+3,ticklocsy[1]+3,paste0('RMSE = ',round(allrms[expt],digits=2),'dB'),cex=2)
+    if (expt==1){legend(-24,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
 
@@
 
+    ticklocsx <- seq(-24,30,6)
+    ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+
+    if (expt==1){pedcontrasts <- seq(-12,30,6) - scalefactdB[expt]}
+    if (expt>1){pedcontrasts <- seq(-6,36,6) - scalefactdB[expt]}
+    pedcontrasts[1] <- min(ticklocsx)
+
     par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-6,18))   
+    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(-6,18))   
     axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
     mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+    title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
     title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
@@
 
-pdf('Figures/discdata.pdf',width=13,height=7)
+  pdf('Figures/discdata.pdf',width=10,height=6)
 
   par(mfcol=c(1,2))
-pedcontrasts <- seq(-12,30,6)
-
-ticklocsy <- seq(-18,30,6)
-ticklabelsy <- c(0.125,0.25,0.5,1,2,4,8,16,32)
+  pedcontrasts <- seq(-12,30,6) - scalefactdB[4]
+  pedcontrasts[1] <- -24
+
+  ticklocsx <- seq(-24,30,6)
+  ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+  ticklocsy <- seq(-24,30,6)
+  ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)
 
   par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-18,30))   
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
   axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
   mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='(a) Flickering disc (thresholds)',cex.main=2)
+  title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+  title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+  title(main='(a) Flickering disc (thresholds)',cex.main=1.5)
 
   for (cond in 1:4){
-  arrows(pedcontrasts,meanthresh3[cond,],pedcontrasts,meanthresh3[cond,]+SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
- arrows(pedcontrasts,meanthresh3[cond,],pedcontrasts,meanthresh3[cond,]-SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
+    arrows(pedcontrasts,meanthresh3[cond,]-scalefactdB[4],pedcontrasts,meanthresh3[cond,]-scalefactdB[4]+SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
+    arrows(pedcontrasts,meanthresh3[cond,]-scalefactdB[4],pedcontrasts,meanthresh3[cond,]-scalefactdB[4]-SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
     # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
     lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,meanthresh3[cond,],pch=16,col=collist[cond],cex=1.5)
-}
-text(24,-15,paste0('RMSE = ',round(allrms[4],digits=2),'dB'),cex=2)
-legend(-12,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
+    points(pedcontrasts,meanthresh3[cond,]-scalefactdB[4],pch=16,col=collist[cond],cex=1.5)
+  }
+  text(ticklocsx[7]+3,ticklocsy[1]+3,paste0('RMSE = ',round(allrms[4],digits=2),'dB'),cex=1.5)
+  legend(-24,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.2)
 
@@
   par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-6,18))   
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-6,18))   
   axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
   mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+  title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
   title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(main='(b) Flickering disc (slopes)',cex.main=2)
+  title(main='(b) Flickering disc (slopes)',cex.main=1.5)
 
@@
 
-```{r stanmodelspecifications, include=FALSE}
+```{r stanmodelspecification, include=FALSE}
 
@@
   parameters {
-    vector<lower=0.1, upper=3>[Ndatasets] p;
-    vector<lower=2, upper=8>[Ndatasets] q;
+    vector<lower=1, upper=3>[Ndatasets] p;
+    vector<lower=2, upper=16>[Ndatasets] q;
     vector<lower=0.5, upper=2>[Ndatasets] m;
-    vector<lower=0.001, upper=2>[Ndatasets] S;  
-    vector<lower=0.001, upper=2>[Ndatasets] Z;
-    vector<lower=0.001, upper=2>[Ndatasets] w;
-    vector<lower=0.001, upper=2>[Ndatasets] k;
+    vector<lower=0, upper=2>[Ndatasets] S;  
+    vector<lower=0, upper=1>[Ndatasets] Z;
+    vector<lower=0, upper=2>[Ndatasets] w;
+    vector<lower=0, upper=2>[Ndatasets] k;
 
     real<lower=0> sigma ;
-    real<lower=0.1, upper=3> pmu ; 
-    real<lower=2, upper=8> qmu ; 
+    real<lower=1, upper=3> pmu ; 
+    real<lower=2, upper=16> qmu ; 
     real<lower=0.5, upper=2> mmu ;
-    real<lower=0.001, upper=2> Smu ;
-    real<lower=0.001, upper=2> Zmu ; 
-    real<lower=0.001, upper=2> wmu ; 
-    real<lower=0.001, upper=2> kmu ;
+    real<lower=0, upper=2> Smu ;
+    real<lower=0, upper=1> Zmu ; 
+    real<lower=0, upper=2> wmu ; 
+    real<lower=0, upper=2> kmu ;
 
@@
 
-    pmu ~ normal( 1.4 , 0.1 ) ;
-    qmu ~ normal( 6.59 , 0.5 ) ;
+    pmu ~ normal( 1.4 , 0.2 ) ;
+    qmu ~ normal( 6.59 , 2 ) ;
     mmu ~ normal( 1.28 , 0.2 ) ;
-    Smu ~ normal( 0.985 , 0.2 ) ;
-    Zmu ~ normal( 0.08 , 0.5 ) ;
+    Smu ~ uniform( 0, 2 ) ;
+    Zmu ~ uniform( 0, 1 ) ;
     wmu ~ normal( 1 , 0.2 ) ;
-    kmu ~ normal( 0.194 , 0.1 ) ;
+    kmu ~ uniform( 0, 2 ) ;
     sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
@@
 
-crossmodelString = "
-  data {
-    int<lower=1> Ndatasets ;
-    int<lower=1> Ntotal ;
-    int ncorrect[Ntotal] ;
-    int ntrials[Ntotal] ;
-    real PedestalContrast[Ntotal] ;
-    real TargetContrast[Ntotal] ;
-    int<lower=1> c[Ntotal] ;
-    int<lower=1> s[Ntotal] ;  
-  }
-  parameters {
-    vector<lower=0, upper=40>[Ndatasets] Zac;
-    vector<lower=0, upper=40>[Ndatasets] Zrg;
-    vector<lower=0, upper=40>[Ndatasets] Zby;
-    vector<lower=0.001, upper=2>[Ndatasets] wAcR;
-    vector<lower=0.001, upper=2>[Ndatasets] wAcB;
-    vector<lower=0.001, upper=2>[Ndatasets] wRgA;
-    vector<lower=0.001, upper=2>[Ndatasets] wRgB;
-    vector<lower=0.001, upper=2>[Ndatasets] wByA;
-    vector<lower=0.001, upper=2>[Ndatasets] wByR;
-
-    real<lower=0> sigma ;
-    real<lower=0, upper=40> Zacmu ; 
-    real<lower=0, upper=40> Zrgmu ; 
-    real<lower=0, upper=40> Zbymu ; 
-    real<lower=0.001, upper=2> wAcRmu ; 
-    real<lower=0.001, upper=2> wAcBmu ; 
-    real<lower=0.001, upper=2> wRgAmu ; 
-    real<lower=0.001, upper=2> wRgBmu ; 
-    real<lower=0.001, upper=2> wByAmu ; 
-    real<lower=0.001, upper=2> wByRmu ;
-
-    real<lower=0> Zacsigma ;    
-    real<lower=0> Zrgsigma ;    
-    real<lower=0> Zbysigma ;    
-    real<lower=0> wAcRsigma ;
-    real<lower=0> wAcBsigma ;
-    real<lower=0> wRgAsigma ;
-    real<lower=0> wRgBsigma ;
-    real<lower=0> wByAsigma ;
-    real<lower=0> wByRsigma ;
-  }
-  model {
-    Zacmu ~ normal( 10 , 5 ) ;
-    Zrgmu ~ normal( 10 , 5 ) ;
-    Zbymu ~ normal( 10 , 5 ) ;
-    wAcRmu ~ normal( 0.5 , 0.3 ) ;
-    wAcBmu ~ normal( 0.5 , 0.3 ) ;
-    wRgAmu ~ normal( 0.5 , 0.3 ) ;
-    wRgBmu ~ normal( 0.5 , 0.3 ) ;
-    wByAmu ~ normal( 0.5 , 0.3 ) ;
-    wByRmu ~ normal( 0.5 , 0.3 ) ;
-    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
-    Zacsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
-    Zrgsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
-    Zbysigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
-    wAcRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
-    wAcBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
-    wRgAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
-    wRgBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
-    wByAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
-    wByRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
-
-    Zac ~ normal( Zacmu , Zacsigma ) ; // vectorized
-    Zrg ~ normal( Zrgmu , Zrgsigma ) ; // vectorized
-    Zby ~ normal( Zbymu , Zbysigma ) ; // vectorized
-    wAcR ~ normal( wAcRmu , wAcRsigma ) ; // vectorized
-    wAcB ~ normal( wAcBmu , wAcBsigma ) ; // vectorized
-    wRgA ~ normal( wRgAmu , wRgAsigma ) ; // vectorized
-    wRgB ~ normal( wRgBmu , wRgBsigma ) ; // vectorized
-    wByA ~ normal( wByAmu , wByAsigma ) ; // vectorized
-    wByR ~ normal( wByRmu , wByRsigma ) ; // vectorized
-
-    for ( i in 1:Ntotal ) {
-
-    real Lt ;
-    real Rt ;
-    real Ln ;
-    real Rn ;
-    real targresp ;
-    real nullresp ;
-    real dprime ;
-
-    if (c[i]==1) { // achromatic detection condition
-    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
-    Rt = 0 ;
-    Ln = 0 ;
-    Rn = 0 ;
-
-    targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
-    nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;
-
-    }
-
-    if (c[i]==2) { // red/green detection condition
-    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
-    Rt = 0 ;
-    Ln = 0 ;
-    Rn = 0 ;
-
-    targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
-    nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;
-
-    }
-
-    if (c[i]==3) { // blue/yellow detection condition
-    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
-    Rt = 0 ;
-    Ln = 0 ;
-    Rn = 0 ;
-
-    targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
-    nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;
-
-    }
-
-    if (c[i]==4) { // achromatic target, achromatic mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
-      Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
-      Ln = 0 ;
-      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;
-
-    }
-
-    if (c[i]==5) { // red/green target, achromatic mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wRgA[s[i]]*PedestalContrast[i]) ;
-      Rt = 0 ;
-      Ln = 0 ;
-      Rn = 0 ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
-    }
-
-    if (c[i]==6) { // blue/yellow target, achromatic mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wByA[s[i]]*PedestalContrast[i]) ;
-      Rt = 0 ;
-      Ln = 0 ;
-      Rn = 0 ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
-    }
-
-    if (c[i]==7) { // achromatic target, red/green mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wAcR[s[i]]*PedestalContrast[i]) ;
-      Rt = 0 ;
-      Ln = 0 ;
-      Rn = 0 ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;
-
-    }
-
-    if (c[i]==8) { // red/green target, red/green mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
-      Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
-      Ln = 0 ;
-      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
-    }
-
-    if (c[i]==9) { // blue/yellow target, red/green mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wByR[s[i]]*PedestalContrast[i]) ;
-      Rt = 0 ;
-      Ln = 0 ;
-      Rn = 0 ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
-    }
-
-     if (c[i]==10) { // achromatic target, blue/yellow mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wAcB[s[i]]*PedestalContrast[i]) ;
-      Rt = 0 ;
-      Ln = 0 ;
-      Rn = 0 ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;
-
-    }
-
-    if (c[i]==11) { // red/green target, blue/yellow mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wRgB[s[i]]*PedestalContrast[i]) ;
-      Rt = 0 ;
-      Ln = 0 ;
-      Rn = 0 ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
-    }
-
-    if (c[i]==12) { // blue/yellow target, blue/yellow mask
-      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
-     Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
-      Ln = 0 ;
-      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;
-
-      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
-      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
-    }
-
-    dprime = (targresp-nullresp)/0.23 ;
-    if (is_nan(dprime)){
-       dprime = 0;
-    }
-    if (is_inf(dprime)){
-       dprime = 10;
-    }
-    if (dprime > 10){
-       dprime = 10;
-    }    
-    ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;
-    }
-  }  
-" # close quote for modelString
-
 ```
@@
 dipmodel <- stan_model(model_code=modelString)
+
+load('local/thresholddata.RData')
+load('local/thresholddataDisc.RData')
+scalefactdB <- c(meanthresh[,1,1],meanthresh3[1,1])
+scalefact <- 10^(scalefactdB/20)
+scalefactind <- 10^(cbind(allthresh[,,1,1],allthresh3[,1,1])/20)
 
@@
 sublist <- unique(ex1data$Subject)
-explist <- unique(ex1data$Experiment)
+explist <- c('AC','RG','BY')  # hard coded in this order to avoid confusion later on
 counter <- 0
@@
           conditions[counter] <- cond
-          pedestals[counter] <- pedconts[p]
-          targets[counter] <- targconts[t]
+          pedestals[counter] <- pedconts[p]/scalefactind[s,e]
+          targets[counter] <- targconts[t]/scalefactind[s,e]
         }
@@
         conditions[counter] <- cond
-          pedestals[counter] <- pedconts[p]
-          targets[counter] <- targconts[t]
+        pedestals[counter] <- pedconts[p]/scalefactind[s,4]
+        targets[counter] <- targconts[t]/scalefactind[s,4]
       }
@@
 
+if (processdata>0){
+
 allstanparams <- matrix(0,nrow=4,ncol=7)
-upperstanparams <- matrix(0,nrow=4,ncol=7)
-lowerstanparams <- matrix(0,nrow=4,ncol=7)
 
@@
   draws <- extract(stanFit)
-  p <- mean(draws$pmu+draws$qmu)
-  q <- mean(draws$qmu)
-  m <- mean(draws$mmu)
-  k <- mean(draws$kmu)
-  S <- mean(draws$Smu)
-  Z <- mean(draws$Zmu)
-  w <- mean(draws$wmu)
+  p <- as.numeric(map_estimate(draws$pmu+draws$qmu))
+  q <- as.numeric(map_estimate(draws$qmu))
+  m <- as.numeric(map_estimate(draws$mmu))
+  k <- as.numeric(map_estimate(draws$kmu))
+  S <- as.numeric(map_estimate(draws$Smu))
+  Z <- as.numeric(map_estimate(draws$Zmu))
+  w <- as.numeric(map_estimate(draws$wmu))
   allstanparams[expt,] <- c(p,q,m,S,Z,w,k)
@@
   allsamples[expt,3,] <- mlist
-  allsamples[expt,4,] <- Slist
-  allsamples[expt,5,] <- Zlist
-  allsamples[expt,6,] <- wlist
+  allsamples[expt,4,] <- wlist
+  allsamples[expt,5,] <- Slist
+  allsamples[expt,6,] <- Zlist
   allsamples[expt,7,] <- klist
 
-  # quants <- quantile(wlist,probs=c(0.025,0.975))
-  # i <- which.min(abs(wlist-quants[1]))
-  # lowerstanparams[expt,] <- allsamples[expt,,i]
-  # i <- which.min(abs(wlist-quants[2]))
-  # upperstanparams[expt,] <- allsamples[expt,,i]
-}
-
-if (processdata>0){
-
-load('local/thresholddata.RData')
-load('local/thresholddataDisc.RData')
-
-threshtoplot <- array(0,dim=c(4,4,8))
-threshtoplot[1:3,,] <- meanthresh
-threshtoplot[4,,] <- meanthresh3
+}
 
@@
 paramorder <- c('p','q','m',expression(omega),'S','Z','k')
-  paramvalorder <- c(1,2,3,6,4,5,7)
-
-  xstart <- c(1,1,1/2,1/2,1/4,1/64,1/16)
+
+xstart <- c(1,1,1/2,1/2,1/8,1/256,1/16)
 xstartdB <- round(20*log10(xstart))
@@
 
-    ticklabelsx <- c('1/4','1/2',1,2,4)
-    if (param<3){ticklabelsx <- c(1,2,4,8,16)}
-    if (param==3 || param==4){ticklabelsx <- c('1/2','','1','','2')}
-    if (param>5){ticklabelsx <- c('1/16','1/8','1/4','1/2','1')}
-    if (param==6){ticklabelsx <- c('1/64','1/16','1/4','1','4')}
+  if (param==1){ticklabelsx <- c(1,2,4,8,16)}
+  if (param==2){ticklabelsx <- c(1,2,4,8,16)}
+  if (param==3){ticklabelsx <- c('1/2','','1','','2')}
+  if (param==4){ticklabelsx <- c('1/2','','1','','2')}
+  if (param==5){ticklabelsx <- c('1/8','1/4','1/2','1','2')}
+  if (param==6){ticklabelsx <- c('1/256','1/64','1/16','1/4','1')}
+  if (param==7){ticklabelsx <- c('1/16','1/8','1/4','1/2','1')}
 
@@
   for (expt in 1:4){
-    svals <- 20*log10(allsamples[expt,paramvalorder[param],])
+    svals <- 20*log10(allsamples[expt,param,])
     a <- density(svals)
@@
   if (param==1){
-      legend(0,1,c('Achromatic','Red/green','Blue/yellow','Flicker'),fill=addalpha(concols1,alpha=0.25),border=concols2,box.lwd=2)
+    legend(0,1,c('Achromatic','Red/green','Blue/yellow','Flicker'),fill=addalpha(concols1,alpha=0.25),border=concols2,box.lwd=2,cex=0.95)
   }
@@
 paneltitles <- c('(a) Achromatic grating','(b) Red/green grating','(c) Blue/yellow grating','(d) Flickering disc')
+collist <- c('red','blue','orange','darkgreen')
+
+pedlist <- -24:36
+pedlevelsC <- 10^(pedlist/20)
+pedlevelsC[1] <- 0
 
@@
   print(expt)
-  pedlist <- -12:36
-  pedlevelsC <- 10^(pedlist/20)
-  pedlevelsC[1] <- 0
+
   allpred <- array(0,dim=c(4,length(pedlist)))
-  # upperpred <- array(0,dim=c(4,length(pedlist)))
-  # lowerpred <- array(0,dim=c(4,length(pedlist)))
   for (cond in 1:4){
@@
       allpred[cond,pedlev] <- discriminate(allstanparams[expt,],pedlevelsC[pedlev],cond)
-      # upperpred[cond,pedlev] <- discriminate(upperstanparams[expt,],pedlevelsC[pedlev],cond)
-      # lowerpred[cond,pedlev] <- discriminate(lowerstanparams[expt,],pedlevelsC[pedlev],cond)
-    }
-  }
-
-  collist <- c('red','blue','orange','darkgreen')
+    }
+  }
 
   allpreddB <- 20*log10(allpred)
-  # lowerpreddB <- 20*log10(lowerpred)
-  # upperpreddB <- 20*log10(upperpred)
 
@@
 
-  ticklocsx <- seq(-12,36,6)
-  ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
-  ticklocsy <- seq(-12,36,6)
-  ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
-
-  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))
+  ticklocsx <- seq(-24,30,6)
+  ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+  ticklocsy <- seq(-24,30,6)
+  ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(min(ticklocsy),max(ticklocsy)))
   axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
   mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-  title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-  title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+  title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+  title(ylab='Normalized threshold contrast', col.lab=rgb(0,0,0), line=2.4, cex.lab=1.5)
   title(main=paneltitles[expt],cex.main=2)
-  pedcontrasts <- seq(-12,30,6)
+  # pedcontrasts <- seq(-12,30,6)
 
@@
   propcorr <- apply(MCSpropcorr,2:3,mean)
-  contrastsdB <- contrastsdB[1,,]
-
-ticklocsx <- seq(-12,42,6)
-ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64','128')
+  normcontrasts <- contrastsdB[1,,]
+  normcontrasts[seq(1,12,3),] <- normcontrasts[seq(1,12,3),] - pooledthresh[1]
+  normcontrasts[seq(2,12,3),] <- normcontrasts[seq(2,12,3),] - pooledthresh[2]
+  normcontrasts[seq(3,12,3),] <- normcontrasts[seq(3,12,3),] - pooledthresh[3]
+
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64')
 ticklocsy <- seq(0,100,25)
@@
 
-  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,42), ylim=c(0,100))  
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(0,100))  
   axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
   mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-  title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+  title(xlab="Normalized target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
   title(ylab="Percent correct", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
@@
 
-  lines(contrastsdB[cond,],propcorr[cond,],lwd=3)
-  points(contrastsdB[cond,],propcorr[cond,],pch=21,lwd=3,cex=2,bg='black')
-
-  lines(contrastsdB[cond+3,],propcorr[cond+3,],lwd=3)
-  points(contrastsdB[cond+3,],propcorr[cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
-
-  lines(contrastsdB[cond+6,],propcorr[cond+6,],lwd=3)
-  points(contrastsdB[cond+6,],propcorr[cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
-
-  lines(contrastsdB[cond+9,],propcorr[cond+9,],lwd=3)
-  points(contrastsdB[cond+9,],propcorr[cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
+  lines(normcontrasts[cond,],propcorr[cond,],lwd=3)
+  points(normcontrasts[cond,],propcorr[cond,],pch=21,lwd=3,cex=2,bg='black')
+
+  lines(normcontrasts[cond+3,],propcorr[cond+3,],lwd=3)
+  points(normcontrasts[cond+3,],propcorr[cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
+
+  lines(normcontrasts[cond+6,],propcorr[cond+6,],lwd=3)
+  points(normcontrasts[cond+6,],propcorr[cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
+
+  lines(normcontrasts[cond+9,],propcorr[cond+9,],lwd=3)
+  points(normcontrasts[cond+9,],propcorr[cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
 
@@
 
-ticklocsx <- seq(-12,42,6)
-ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64','128')
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64')
 ticklocsy <- seq(0,24,6)
@@
     par(pty="s")  
- plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,42), ylim=c(0,24))
+ plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(0,24))
 
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+title(xlab="Normalized target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
 title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
@@
 
-xvals <- allposX[condtoplot,]
+xvals <- allposX[condtoplot,] - pooledthresh[cond]
 yvals <- 10.3/(allposY[condtoplot,ncol(allposY):1]/C)
@@
 condtoplot <- cond + ((block-1)*3)
-points(MCSthresh[,condtoplot],MCSslope[,condtoplot],pch=21,col=outlinecolours[block],bg=shadingcolours[block])
+points(MCSthresh[,condtoplot]-MCSthresh[,cond],MCSslope[,condtoplot],pch=21,col=outlinecolours[block],bg=shadingcolours[block])
 }
@@
 
+```{r stanmodelspecification2, include=FALSE}
+
+allstanparams <- matrix(0,nrow=4,ncol=7)
+
+load(paste0('local/stanfit1.RData'))
+draws <- extract(stanFit)
+p <- draws$pmu
+allsamples <- array(0,dim=c(4,7,length(p)))
+
+for (expt in 1:4){
+  load(paste0('local/stanfit',expt,'.RData'))
+  draws <- extract(stanFit)
+  p <- as.numeric(map_estimate(draws$pmu+draws$qmu))
+  q <- as.numeric(map_estimate(draws$qmu))
+  m <- as.numeric(map_estimate(draws$mmu))
+  k <- as.numeric(map_estimate(draws$kmu))
+  S <- as.numeric(map_estimate(draws$Smu))
+  Z <- as.numeric(map_estimate(draws$Zmu))
+  w <- as.numeric(map_estimate(draws$wmu))
+  allstanparams[expt,] <- c(p,q,m,S,Z,w,k)
+
+  plist <- draws$pmu+draws$qmu
+  qlist <- draws$qmu
+  mlist <- draws$mmu
+  klist <- draws$kmu
+  Slist <- draws$Smu
+  Zlist <- draws$Zmu
+  wlist <- draws$wmu
+
+  allsamples[expt,1,] <- plist
+  allsamples[expt,2,] <- qlist
+  allsamples[expt,3,] <- mlist
+  allsamples[expt,4,] <- wlist
+  allsamples[expt,5,] <- Slist
+  allsamples[expt,6,] <- Zlist
+  allsamples[expt,7,] <- klist
+
+}
+
+crossmodelString = paste0("
+  data {
+    int<lower=1> Ndatasets ;
+    int<lower=1> Ntotal ;
+    int ncorrect[Ntotal] ;
+    int ntrials[Ntotal] ;
+    real PedestalContrast[Ntotal] ;
+    real TargetContrast[Ntotal] ;
+    int<lower=1> c[Ntotal] ;
+    int<lower=1> s[Ntotal] ;  
+  }
+  parameters {
+    vector<lower=0, upper=1>[Ndatasets] ZAc;
+    vector<lower=0, upper=1>[Ndatasets] ZRg;
+    vector<lower=0, upper=1>[Ndatasets] ZBy;
+    vector<lower=0, upper=8>[Ndatasets] wAcR;
+    vector<lower=0, upper=8>[Ndatasets] wAcB;
+    vector<lower=0, upper=8>[Ndatasets] wRgA;
+    vector<lower=0, upper=8>[Ndatasets] wRgB;
+    vector<lower=0, upper=8>[Ndatasets] wByA;
+    vector<lower=0, upper=8>[Ndatasets] wByR;
+
+    real<lower=0> sigma ;
+    real<lower=0, upper=1> ZAcmu ; 
+    real<lower=0, upper=1> ZRgmu ;     
+    real<lower=0, upper=1> ZBymu ; 
+    real<lower=0, upper=8> wAcRmu ; 
+    real<lower=0, upper=8> wAcBmu ; 
+    real<lower=0, upper=8> wRgAmu ; 
+    real<lower=0, upper=8> wRgBmu ; 
+    real<lower=0, upper=8> wByAmu ; 
+    real<lower=0, upper=8> wByRmu ;
+
+    real<lower=0> ZAcsigma ;
+    real<lower=0> ZRgsigma ;
+    real<lower=0> ZBysigma ;
+    real<lower=0> wAcRsigma ;
+    real<lower=0> wAcBsigma ;
+    real<lower=0> wRgAsigma ;
+    real<lower=0> wRgBsigma ;
+    real<lower=0> wByAsigma ;
+    real<lower=0> wByRsigma ;
+  }
+  model {
+    ZAcmu ~ uniform( 0 , 1 ) ;
+    ZRgmu ~ uniform( 0 , 1 ) ;
+    ZBymu ~ uniform( 0 , 1 ) ;
+    wAcRmu ~ uniform( 0 , 8 ) ;
+    wAcBmu ~ uniform( 0 , 8 ) ;
+    wRgAmu ~ uniform( 0 , 8 ) ;
+    wRgBmu ~ uniform( 0 , 8 ) ;
+    wByAmu ~ uniform( 0 , 8 ) ;
+    wByRmu ~ uniform( 0 , 8 ) ;
+    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    ZAcsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    ZRgsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    ZBysigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wAcRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wAcBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wRgAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wRgBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wByAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wByRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+
+    ZAc ~ normal( ZAcmu , ZAcsigma ) ; // vectorized
+    ZRg ~ normal( ZRgmu , ZRgsigma ) ; // vectorized
+    ZBy ~ normal( ZBymu , ZBysigma ) ; // vectorized
+    wAcR ~ normal( wAcRmu , wAcRsigma ) ; // vectorized
+    wAcB ~ normal( wAcBmu , wAcBsigma ) ; // vectorized
+    wRgA ~ normal( wRgAmu , wRgAsigma ) ; // vectorized
+    wRgB ~ normal( wRgBmu , wRgBsigma ) ; // vectorized
+    wByA ~ normal( wByAmu , wByAsigma ) ; // vectorized
+    wByR ~ normal( wByRmu , wByRsigma ) ; // vectorized
+
+    for ( i in 1:Ntotal ) {
+
+    real Lt ;
+    real Rt ;
+    real Ln ;
+    real Rn ;
+    real targresp ;
+    real nullresp ;
+    real dprime ;
+
+    if (c[i]==1) { // achromatic detection condition
+    Lt = pow(TargetContrast[i],",allstanparams[1,3],") / (",allstanparams[1,4]," + (TargetContrast[i])) ;
+    Rt = 0 ;
+    Ln = 0 ;
+    Rn = 0 ;
+
+    targresp = pow((Lt + Rt), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Lt + Rt), ",allstanparams[1,2],")) ;
+    nullresp = pow((Ln + Rn), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Ln + Rn), ",allstanparams[1,2],")) ;     
+    dprime = (targresp-nullresp)/",allstanparams[1,7]," ;
+
+    }
+
+    if (c[i]==2) { // red/green detection condition
+    Lt = pow(TargetContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + (TargetContrast[i])) ;
+    Rt = 0 ;
+    Ln = 0 ;
+    Rn = 0 ;
+
+    targresp = pow((Lt + Rt), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Lt + Rt), ",allstanparams[2,2],")) ;
+    nullresp = pow((Ln + Rn), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Ln + Rn), ",allstanparams[2,2],")) ;     
+    dprime = (targresp-nullresp)/",allstanparams[2,7]," ;
+
+    }
+
+    if (c[i]==3) { // blue/yellow detection condition
+    Lt = pow(TargetContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4],"  + (TargetContrast[i])) ;
+    Rt = 0 ;
+    Ln = 0 ;
+    Rn = 0 ;
+
+    targresp = pow((Lt + Rt), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Lt + Rt), ",allstanparams[3,2],")) ;
+    nullresp = pow((Ln + Rn), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Ln + Rn), ",allstanparams[3,2],")) ;     
+    dprime = (targresp-nullresp)/",allstanparams[3,7]," ;
+
+    }
+
+    if (c[i]==4) { // achromatic target, achromatic mask
+      Lt = pow(TargetContrast[i],",allstanparams[1,3],") / (",allstanparams[1,4]," + TargetContrast[i] + ",allstanparams[1,6],"*PedestalContrast[i]) ;
+      Rt = pow(PedestalContrast[i],",allstanparams[1,3],") / (",allstanparams[1,4]," + PedestalContrast[i] + ",allstanparams[1,6],"*TargetContrast[i]) ;
+      Ln = 0 ;
+      Rn = pow(PedestalContrast[i],",allstanparams[1,3],") / (",allstanparams[1,4]," + PedestalContrast[i]) ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Lt + Rt), ",allstanparams[1,2],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Ln + Rn), ",allstanparams[1,2],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[1,7]," ;
+
+    }
+
+    if (c[i]==5) { // red/green target, achromatic mask
+      Lt = pow(TargetContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + TargetContrast[i] + wRgA[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Lt + Rt), ",allstanparams[2,2],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Ln + Rn), ",allstanparams[2,2],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[2,7]," ;
+    }
+
+    if (c[i]==6) { // blue/yellow target, achromatic mask
+      Lt = pow(TargetContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4]," + TargetContrast[i] + wByA[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Lt + Rt), ",allstanparams[3,2],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Ln + Rn), ",allstanparams[3,2],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[3,7]," ;
+    }
+
+    if (c[i]==7) { // achromatic target, red/green mask
+      Lt = pow(TargetContrast[i],",allstanparams[1,3],") / (",allstanparams[1,4]," + TargetContrast[i] + wAcR[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Lt + Rt), ",allstanparams[1,2],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Ln + Rn), ",allstanparams[1,2],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[1,7]," ;
+
+    }
+
+    if (c[i]==8) { // red/green target, red/green mask
+      Lt = pow(TargetContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + TargetContrast[i] + ",allstanparams[2,6],"*PedestalContrast[i]) ;
+      Rt = pow(PedestalContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + PedestalContrast[i] + ",allstanparams[2,6],"*TargetContrast[i]) ;
+      Ln = 0 ;
+      Rn = pow(PedestalContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + PedestalContrast[i]) ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Lt + Rt), ",allstanparams[2,2],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Ln + Rn), ",allstanparams[2,2],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[2,7]," ;
+    }
+
+    if (c[i]==9) { // blue/yellow target, red/green mask
+      Lt = pow(TargetContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4]," + TargetContrast[i] + wByR[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Lt + Rt), ",allstanparams[3,4],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Ln + Rn), ",allstanparams[3,4],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[3,7]," ;
+    }
+
+     if (c[i]==10) { // achromatic target, blue/yellow mask
+      Lt = pow(TargetContrast[i],",allstanparams[1,3],") / (",allstanparams[1,4]," + TargetContrast[i] + wAcB[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Lt + Rt), ",allstanparams[1,2],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Ln + Rn), ",allstanparams[1,2],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[1,7]," ;
+
+    }
+
+    if (c[i]==11) { // red/green target, blue/yellow mask
+      Lt = pow(TargetContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + TargetContrast[i] + wRgB[s[i]]*PedestalContrast[i]) ;
+      Rt = 0 ;
+      Ln = 0 ;
+      Rn = 0 ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Lt + Rt), ",allstanparams[2,2],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Ln + Rn), ",allstanparams[2,2],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[2,7]," ;
+    }
+
+    if (c[i]==12) { // blue/yellow target, blue/yellow mask
+      Lt = pow(TargetContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4]," + TargetContrast[i] + ",allstanparams[3,6],"*PedestalContrast[i]) ;
+      Rt = pow(PedestalContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4]," + PedestalContrast[i] + ",allstanparams[3,6],"*TargetContrast[i]) ;
+      Ln = 0 ;
+      Rn = pow(PedestalContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4]," + PedestalContrast[i]) ;
+
+      targresp = pow((Lt + Rt), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Lt + Rt), ",allstanparams[3,2],")) ;
+      nullresp = pow((Ln + Rn), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Ln + Rn), ",allstanparams[3,2],")) ;     
+      dprime = (targresp-nullresp)/",allstanparams[3,7]," ;
+    }
+
+    if (is_nan(dprime)){
+       dprime = 0;
+    }
+    if (is_inf(dprime)){
+       dprime = 10;
+    }
+    if (dprime > 10){
+       dprime = 10;
+    }    
+    ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;
+    }
+  }  
+") # close quote for modelString
+
+```
+
 ```{r domodellingMCS, include=FALSE}
@@
 mcsmodel <- stan_model(model_code=crossmodelString)
+
+load('local/MCSdata.RData')
+meanthresh <- colMeans(MCSthresh)
+scalefactdB <- meanthresh[1:3]
+scalefact <- 10^(scalefactdB/20)
+scalefactind <- 10^(MCSthresh[1:3,1:3]/20)
 
@@
 pedlist <- pedlist[c(4,1,3,2)]  # reorder to make life easier later
+maskvals <- c(0,0,0,16,16,16,64,64,64,64,64,64)
 
@@
         conditions[counter] <- conditioncounter
-          pedestals[counter] <- pedcont
-          targets[counter] <- targconts[t]
+        if (pedtype==1){pedestals[counter] <- 0}
+        if (pedtype>1){pedestals[counter] <- maskvals[conditioncounter]/scalefactind[s,pedtype-1]}
+        targets[counter] <- targconts[t]/scalefactind[s,targtype]
 
@@
 
+if (processdata>0){
+
 getmodelresp3inputs <- function(p,La,Ra,Lr,Rr,Lb,Rb){
@@
 
-  LrespA <- (La^1.21)/(1.03 + La + Ra + p[4]*Rr + p[5]*Rb)
-  RrespA <- (Ra^1.21)/(1.03 + Ra + La + p[4]*Lr + p[5]*Lb)
-  LrespR <- (Lr^1.21)/(1.03 + Lr + p[6]*Ra + Rr + p[7]*Rb)
-  RrespR <- (Rr^1.21)/(1.03 + Rr + p[6]*La + Lr + p[7]*Lb)
-  LrespB <- (Lb^1.21)/(1.03 + Lb + p[8]*Ra + p[9]*Rr + Rb)
-  RrespB <- (Rb^1.21)/(1.03 + Rb + p[8]*La + p[9]*Lr + Lb)
+  LrespA <- (La^p[1,3])/(p[1,4] + La + p[1,6]*Ra + p[1,8]*Rr + p[1,9]*Rb)
+  RrespA <- (Ra^p[1,3])/(p[1,4] + Ra + p[1,6]*La + p[1,8]*Lr + p[1,9]*Lb)
+  LrespR <- (Lr^p[2,3])/(p[2,4] + Lr + p[2,8]*Ra + p[2,6]*Rr + p[2,9]*Rb)
+  RrespR <- (Rr^p[2,3])/(p[2,4] + Rr + p[2,8]*La + p[2,6]*Lr + p[2,9]*Lb)
+  LrespB <- (Lb^p[3,3])/(p[3,4] + Lb + p[3,8]*Ra + p[3,9]*Rr + p[3,6]*Rb)
+  RrespB <- (Rb^p[3,3])/(p[3,4] + Rb + p[3,8]*La + p[3,9]*Lr + p[3,6]*Lb)
 
   bs <- LrespA + RrespA
-  resp[1,] <- (bs^7.82)/(p[1] + bs^6.4)
+  resp[1,] <- (bs^p[1,1])/(p[1,5] + bs^p[1,2])
 
   bs <- LrespR + RrespR
-  resp[2,] <- (bs^7.82)/(p[2] + bs^6.4)
+  resp[2,] <- (bs^p[2,1])/(p[2,5] + bs^p[2,2])
 
   bs <- LrespB + RrespB
-  resp[3,] <- (bs^7.82)/(p[3] + bs^6.4)
+  resp[3,] <- (bs^p[3,1])/(p[3,5] + bs^p[3,2])
 
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[1,] - nr[1,])/0.23
+  dprime <- (tr[1,] - nr[1,])/p[1,7]
   pmfout[1,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[2,] - nr[2,])/0.23
+  dprime <- (tr[2,] - nr[2,])/p[2,7]
   pmfout[2,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[3,] - nr[3,])/0.23
+  dprime <- (tr[3,] - nr[3,])/p[3,7]
   pmfout[3,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[1,] - nr[1,])/0.23
+  dprime <- (tr[1,] - nr[1,])/p[1,7]
   pmfout[4,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[2,] - nr[2,])/0.23
+  dprime <- (tr[2,] - nr[2,])/p[2,7]
   pmfout[5,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[3,] - nr[3,])/0.23
+  dprime <- (tr[3,] - nr[3,])/p[3,7]
   pmfout[6,] <- 100*pnorm(dprime/sqrt(2))
 
-  tr <- getmodelresp3inputs(p,contrastsC,0,0,64,0,0)
-  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
-  dprime <- (tr[1,] - nr[1,])/0.23
+  tr <- getmodelresp3inputs(p,contrastsC,0,0,16,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
+  dprime <- (tr[1,] - nr[1,])/p[1,7]
   pmfout[7,] <- 100*pnorm(dprime/sqrt(2))
 
-  tr <- getmodelresp3inputs(p,0,0,contrastsC,64,0,0)
-  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
-  dprime <- (tr[2,] - nr[2,])/0.23
+  tr <- getmodelresp3inputs(p,0,0,contrastsC,16,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
+  dprime <- (tr[2,] - nr[2,])/p[2,7]
   pmfout[8,] <- 100*pnorm(dprime/sqrt(2))
 
-  tr <- getmodelresp3inputs(p,0,0,0,64,contrastsC,0)
-  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
-  dprime <- (tr[3,] - nr[3,])/0.23
+  tr <- getmodelresp3inputs(p,0,0,0,16,contrastsC,0)
+  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
+  dprime <- (tr[3,] - nr[3,])/p[3,7]
   pmfout[9,] <- 100*pnorm(dprime/sqrt(2))
 
-  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,64)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
-  dprime <- (tr[1,] - nr[1,])/0.23
+  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,16)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
+  dprime <- (tr[1,] - nr[1,])/p[1,7]
   pmfout[10,] <- 100*pnorm(dprime/sqrt(2))
 
-  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,64)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
-  dprime <- (tr[2,] - nr[2,])/0.23
+  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,16)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
+  dprime <- (tr[2,] - nr[2,])/p[2,7]
   pmfout[11,] <- 100*pnorm(dprime/sqrt(2))
 
-  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,64)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
-  dprime <- (tr[3,] - nr[3,])/0.23
+  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,16)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
+  dprime <- (tr[3,] - nr[3,])/p[3,7]
   pmfout[12,] <- 100*pnorm(dprime/sqrt(2))
@@
 draws <- extract(stanFit)
-Zac <- mean(draws$Zacmu)
-Zrg <- mean(draws$Zrgmu)
-Zby <- mean(draws$Zbymu)
-wAcR <- mean(draws$wAcRmu)
-wAcB <- mean(draws$wAcBmu)
-wRgA <- mean(draws$wRgAmu)
-wRgB <- mean(draws$wRgBmu)
-wByA <- mean(draws$wByAmu)
-wByR <- mean(draws$wByRmu)
-
-Zaclist <- draws$Zacmu
-Zrglist <- draws$Zrgmu
-Zbylist <- draws$Zbymu
+ZAc <- as.numeric(map_estimate(draws$ZAcmu))
+ZRg <- as.numeric(map_estimate(draws$ZRgmu))
+ZBy <- as.numeric(map_estimate(draws$ZBymu))
+wAcR <- as.numeric(map_estimate(draws$wAcRmu))
+wAcB <- as.numeric(map_estimate(draws$wAcBmu))
+wRgA <- as.numeric(map_estimate(draws$wRgAmu))
+wRgB <- as.numeric(map_estimate(draws$wRgBmu))
+wByA <- as.numeric(map_estimate(draws$wByAmu))
+wByR <- as.numeric(map_estimate(draws$wByRmu))
+
 wAcRlist <- draws$wAcRmu
@@
 
-if (processdata>0){
+fullparams <- matrix(0,nrow=3,ncol=9)
+fullparams[1,1:7] <- allstanparams[1,]
+fullparams[2,1:7] <- allstanparams[2,]
+fullparams[3,1:7] <- allstanparams[3,]
+fullparams[1,8:9] <- c(wAcR,wAcB)
+fullparams[2,8:9] <- c(wRgA,wRgB)
+fullparams[3,8:9] <- c(wByA,wByR)
+fullparams[,5] <- c(ZAc,ZRg,ZBy)
 
@@
 
-targetcontsdB <<- seq(-12,42,1)
-allpmfpreds <- predictpmfs(c(Zac,Zrg,Zby,wAcR,wAcB,wRgA,wRgB,wByA,wByR))
-
-ticklocsx <- seq(-12,42,6)
-ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64','128')
+  targetcontsdB <<- seq(-21,42,1)
+  allpmfpreds <- predictpmfs(fullparams)
+
+  ticklocsx <- seq(-12,36,6)
+  ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64')
   ticklocsy <- seq(0,100,25)
@@
   par(mfrow=c(2,3))
-    # layout(matrix(c(1,1,2,2,3,3,0,4,4,5,5,0),2,6,byrow=TRUE))
 
@@
 
-  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,42), ylim=c(0,100))  
+    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(0,100))  
     axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
     mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-  title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+    title(xlab='Normalized target contrast', col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
     title(ylab="Percent correct", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
@@
 
+    # lines(c(-12,36),c(75,75),lty=3)
+    # lines(c(0,0),c(0,100),lty=3)
+
     lines(c(-12,42),c(50,50),lty=2)
@@
     # lines(targetcontsdB,allmodelpreds[cond,],lwd=3)
-  # points(contrastsdB[cond,],propcorr[cond,],pch=21,lwd=3,cex=2,bg='black')
+    # points(contrastsdB[cond,]-scalefactdB[cond],propcorr[cond,],pch=21,lwd=3,cex=2,bg='black')
 
     lines(targetcontsdB,allpmfpreds[cond+3,],lwd=3,lty=2)
-  # lines(targetcontsdB,allmodelpreds[cond+3,],lwd=3,lty=2)
-  # points(contrastsdB[cond+3,],propcorr[cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
+    # points(contrastsdB[cond+3,]-scalefactdB[cond],propcorr[cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
 
@@
     lines(targetcontsdB,allpmfpreds[cond+6,],lwd=3,col='green',lty=2)
-  # lines(targetcontsdB,allmodelpreds[cond+6,],lwd=3,col='red')
-  # lines(targetcontsdB,allmodelpreds[cond+6,],lwd=3,col='green',lty=2)
-  # points(contrastsdB[cond+6,],propcorr[cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
+    # points(contrastsdB[cond+6,]-scalefactdB[cond],propcorr[cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
 
@@
     lines(targetcontsdB,allpmfpreds[cond+9,],lwd=3,col='gold',lty=2)     
-  # lines(targetcontsdB,allmodelpreds[cond+9,],lwd=3,col='cornflowerblue')
-  # lines(targetcontsdB,allmodelpreds[cond+9,],lwd=3,col='gold',lty=2)         
-  # points(contrastsdB[cond+9,],propcorr[cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
-
-  # text(18,10,paste(ntrials[1],'trials/level'),pos=4)
+    # points(contrastsdB[cond+9,]-scalefactdB[cond],propcorr[cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
 
@@
   weightmatrix <- matrix(1,nrow=3,ncol=3)
+  weightmatrix[1,1] <- allstanparams[1,6]
   weightmatrix[1,2] <- wAcR
   weightmatrix[1,3] <- wAcB
+  weightmatrix[2,2] <- allstanparams[2,6]
   weightmatrix[2,1] <- wRgA
   weightmatrix[2,3] <- wRgB
+  weightmatrix[3,3] <- allstanparams[3,6]
   weightmatrix[3,1] <- wByA
@@
   colmatrix3 <- rgb(ramp3(seq(0, 1, length = 101)), max = 255)
-image(1:3,1:3,weightmatrix,zlim=c(0,1),col=colmatrix3,add=TRUE,useRaster=FALSE)
-
-contrastmatrix <- matrix(c(16,16,16,64,64,64,64,64,64),nrow=3,ncol=3)
-denommatrix <- round(weightmatrix*contrastmatrix,digits=2)
+
+  # contrastmatrix <- matrix(c(16,16,16,64*0.1,64*0.1,64*0.1,64*0.88,64*0.88,64*0.88),nrow=3,ncol=3)
+  # contrastmatrix <- matrix(16,nrow=3,ncol=3)
+  # denommatrix <- round(weightmatrix*contrastmatrix,digits=2)
+
+  weightsdB <- 20*log10(weightmatrix)
+  image(1:3,1:3,weightsdB,zlim=c(-30,18),col=colmatrix3,add=TRUE,useRaster=FALSE)
+
   weightmatrix <- round(weightmatrix,digits=2)
-
   counter <- 0
@@
     for (y in 1:3){
-    text(x,y+0.1,weightmatrix[x,y],cex=1.6)
-    text(x,y-0.1,paste0('(',denommatrix[x,y],')'),cex=1.6)
-  }
-}
-
-    ticklocsx <- seq(-42,6,12)
-    ticklabelsx <- c('1/128','1/32','1/8','1/2','2')
-
-    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-42,6), ylim=c(0,1))
+      text(x,y,weightmatrix[x,y],cex=1.6)
+      # text(x,y-0.1,paste0('(',denommatrix[x,y],')'),cex=1.6)
+    }
+  }
+
+  ticklocsx <- seq(-42,18,12)
+  ticklabelsx <- c('1/128','1/32','1/8','1/2','2','8')
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-42,18), ylim=c(0,1))
   axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
@@
 
-ticklocsx <- seq(-12,36,6)
-ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
-ticklocsy <- seq(-12,36,6)
-ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
+ticklocsx <- seq(-24,30,6)
+ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+ticklocsy <- seq(-24,30,6)
+ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)
 
@@
 par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
 axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
 title(main=paste0('(',letters[(3*(p-1)+1)],')  P',p,': Achromatic'),cex.main=2)
 
-pedcontrasts <- seq(-12,30,6)
+pedcontrasts <- seq(-12,30,6)-allthresh[p,1,1,1]
+pedcontrasts[1] <- -24
 
 for (cond in 1:4){
-  lines(pedcontrasts,allthresh[p,1,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,allthresh[p,1,cond,],pch=16,col=collist[cond],cex=1.5)
-}
-
-if (p==1){legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
+  lines(pedcontrasts,allthresh[p,1,cond,]-allthresh[p,1,1,1],col=collist[cond],lwd=2)
+  points(pedcontrasts,allthresh[p,1,cond,]-allthresh[p,1,1,1],pch=16,col=collist[cond],cex=1.5)
+}
+
+if (p==1){legend(-24,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
 
 par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))  
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
 axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
 title(main=paste0('(',letters[(3*(p-1)+2)],')  P',p,': Red/Green'),cex.main=2)
 
-pedcontrasts <- c(-12,seq(0,36,6))
+pedcontrasts <- c(-12,seq(0,36,6))-allthresh[p,2,1,1]
+pedcontrasts[1] <- -24
 
 for (cond in 1:4){
-  lines(pedcontrasts,allthresh[p,3,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,allthresh[p,3,cond,],pch=16,col=collist[cond],cex=1.5)
+  lines(pedcontrasts,allthresh[p,2,cond,]-allthresh[p,2,1,1],col=collist[cond],lwd=2)
+  points(pedcontrasts,allthresh[p,2,cond,]-allthresh[p,2,1,1],pch=16,col=collist[cond],cex=1.5)
 }
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
 title(main=paste0('(',letters[(3*(p-1)+3)],')  P',p,': Blue/Yellow'),cex.main=2)
 
+pedcontrasts <- c(-12,seq(0,36,6))-allthresh[p,3,1,1]
+pedcontrasts[1] <- -24
+
 for (cond in 1:4){
-  lines(pedcontrasts,allthresh[p,2,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,allthresh[p,2,cond,],pch=16,col=collist[cond],cex=1.5)
+  lines(pedcontrasts,allthresh[p,3,cond,]-allthresh[p,3,1,1],col=collist[cond],lwd=2)
+  points(pedcontrasts,allthresh[p,3,cond,]-allthresh[p,3,1,1],pch=16,col=collist[cond],cex=1.5)
 }
@@
 
-ticklocsx <- seq(-12,42,6)
-ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64','128')
+ticklocsx <- seq(-12,36,6)
+ticklabelsx <- c('1/4','1/2','1','2','4','8','16','32','64')
 ticklocsy <- seq(0,100,25)
@@
 
-  lines(contrastsdB[cond,],MCSpropcorr[p,cond,],lwd=3)
-  points(contrastsdB[cond,],MCSpropcorr[p,cond,],pch=21,lwd=3,cex=2,bg='black')
-
-  lines(contrastsdB[cond+3,],MCSpropcorr[p,cond+3,],lwd=3)
-  points(contrastsdB[cond+3,],MCSpropcorr[p,cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
-
-  lines(contrastsdB[cond+6,],MCSpropcorr[p,cond+6,],lwd=3)
-  points(contrastsdB[cond+6,],MCSpropcorr[p,cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
-
-  lines(contrastsdB[cond+9,],MCSpropcorr[p,cond+9,],lwd=3)
-  points(contrastsdB[cond+9,],MCSpropcorr[p,cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
+  lines(contrastsdB[cond,]-MCSthresh[p,cond],MCSpropcorr[p,cond,],lwd=3)
+  points(contrastsdB[cond,]-MCSthresh[p,cond],MCSpropcorr[p,cond,],pch=21,lwd=3,cex=2,bg='black')
+
+  lines(contrastsdB[cond+3,]-MCSthresh[p,cond],MCSpropcorr[p,cond+3,],lwd=3)
+  points(contrastsdB[cond+3,]-MCSthresh[p,cond],MCSpropcorr[p,cond+3,],pch=21,lwd=3,cex=2,col='black',bg='white')
+
+  lines(contrastsdB[cond+6,]-MCSthresh[p,cond],MCSpropcorr[p,cond+6,],lwd=3)
+  points(contrastsdB[cond+6,]-MCSthresh[p,cond],MCSpropcorr[p,cond+6,],pch=21,lwd=3,cex=2,col='red',bg='green')
+
+  lines(contrastsdB[cond+9,]-MCSthresh[p,cond],MCSpropcorr[p,cond+9,],lwd=3)
+  points(contrastsdB[cond+9,]-MCSthresh[p,cond],MCSpropcorr[p,cond+9,],pch=21,lwd=3,cex=2,col='cornflowerblue',bg='gold')
 
@@
 
-ticklocsx <- seq(-12,36,6)
-ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
-ticklocsy <- seq(-18,30,6)
-ticklabelsy <- c(0.125,0.25,0.5,1,2,4,8,16,32)
+ticklocsx <- seq(-24,30,6)
+ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+ticklocsy <- seq(-24,30,6)
+ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)
 pnos <- c(1,6,7)
@@
 par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-18,30))   
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
 axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
 title(main=paste0('(',letters[p],')  P', pnos[p] ,': Flickering disc'),cex.main=2)
 
-pedcontrasts <- seq(-12,30,6)
+pedcontrasts <- seq(-12,30,6)-allthresh3[p,1,1]
+pedcontrasts[1] <- -24
 
 for (cond in 1:4){
-  lines(pedcontrasts,allthresh3[p,cond,],col=collist[cond],lwd=2)
-  points(pedcontrasts,allthresh3[p,cond,],pch=16,col=collist[cond],cex=1.5)
-}
-
-if (p==1){legend(-12,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
+  lines(pedcontrasts,allthresh3[p,cond,]-allthresh3[p,1,1],col=collist[cond],lwd=2)
+  points(pedcontrasts,allthresh3[p,cond,]-allthresh3[p,1,1],pch=16,col=collist[cond],cex=1.5)
+}
+
+if (p==1){legend(-24,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}
 
@@
 Much progress has been made in understanding how the brain combines signals from the two eyes.
-However most of this work has involved achromatic (black and white) stimuli, and it is not clear if the same processes apply in colour-sensitive pathways.
+However, most of this work has involved achromatic (black and white) stimuli, and it is not clear if the same processes apply in colour-sensitive pathways.
 In our first experiment, we measured contrast discrimination ('dipper') functions for four key ocular configurations (monocular, binocular, half-binocular and dichoptic), for achromatic, isoluminant red/green and isoluminant blue/yellow sine-wave grating stimuli.
@@
 In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data from multiple experimental paradigms and techniques, including psychophysics [@Meese2006], EEG [@Baker2017], fMRI [@Moradi2009] and pupillometry [@Segala2023].
-However, the majority of this work has used achromatic (black and white) stimuli; we know comparatively little about how chromatic signals are combined binocularly, or about how signals in different ocular and chromatic channels interact.
+However, most of this work has used achromatic (black and white) stimuli; we know comparatively little about how chromatic signals are combined binocularly, or about how signals in different ocular and chromatic channels interact.
 In this study we use psychophysical detection and discrimination paradigms to explore binocular interactions within and between the chromatic and achromatic pathways.
@@
 At low pedestal contrasts, the binocular condition yields lower thresholds than the monocular condition; this result is attributed to physiological binocular summation by neurons responsive to signals from both eyes [@Baker2018; @Campbell1965].
-However at high pedestal contrasts the 'handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation [@Legge1984; @Maehara2005].
+However, at high pedestal contrasts the 'handle' regions of the dipper functions for these conditions converge: a consequence of interocular suppression compensating for the increased excitation during binocular stimulation [@Legge1984; @Maehara2005].
 The half-binocular condition avoids confounding the number of eyes seeing the target with the number of eyes seeing the pedestal [@Meese2006].
@@
 This demonstrates that binocular summation occurs across the full contrast range, when the pedestal ocularity is appropriately controlled.
-Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast in order to be detectable [@Legge1979; @Maehara2005; @Baker2007b].
+Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast to be detectable [@Legge1979; @Maehara2005; @Baker2007b].
 The characteristic pattern of dipper functions is well-described by the gain control model of @Meese2006 for achromatic stimuli.
@@
 At the output of the human retina, cone responses are split into three distinct pathways.
-The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information, and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
+The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information [see @Sharpe2011], and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
 The difference of long- and medium-wavelength cone outputs (L-M) is responsive to chromatic stimuli modulating along a red/green axis in colour space.
-Finally the short wavelength cone outputs (S-(L+M)) code chromatic stimuli modulating along a blue/yellow axis.
+Finally the opponent (S-(L+M)) channel codes chromatic stimuli modulating along a blue/yellow axis.
+At isoluminance, where (L+M) is held constant, this channel is driven purely by the S-cone outputs.
+
 There has not yet been a detailed investigation of binocular contrast discrimination in either of these chromatic pathways, however there is reason to believe they may differ from the achromatic pathway.
@@
 
-A further property of 'blob' regions is that they are less strongly orientation-tuned than other regions of V1 [@Horton1981; @Livingstone1984], and biased towards low spatial frequencies [@Edwards1995; @Tootell1988].
+A further property of 'blob' regions is that they are less strongly orientation-tuned than other regions of V1 [@Horton1981; @Livingstone1984], and biased towards low spatial frequencies [@Edwards1995; @Tootell1988; though see @Economides2011].
 Our recent work [@Segala2023] has investigated binocular combination for flickering discs of luminance, which are DC-balanced across time (i.e.
@@
 We therefore preregistered a series of psychophysical experiments (see: [https://osf.io/3vdga/](https://osf.io/3vdga/)).
-In Experiment 1 we replicate the four key pedestal masking conditions of @Meese2006 described above for achromatic grating stimuli, and extend this to both red/green and blue/yellow isoluminant chromatic stimuli.
+In Experiment 1 we replicate the four key pedestal masking conditions of @Meese2006 described above for achromatic grating stimuli and extend this to both red/green and blue/yellow isoluminant chromatic stimuli.
 In Experiment 2 we explore dichoptic masking within and between these stimuli.
-Experiment 3 repeats the achromatic condition from the first experiment, but using a temporally modulated disc rather than sine-wave gratings.
+Experiment 3 repeats the achromatic condition from the first experiment but using a temporally modulated disc rather than sine-wave gratings.
 We take a Bayesian approach to data analysis and modelling; by fitting a hierarchical version of the two-stage gain control model [@Meese2006] we compare posterior parameter distributions to understand how model parameters such as the weight of interocular suppression vary across visual pathways.
@@
 Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals [@Stockman2000].
+The maximum displayable cone contrasts on our system were 0.1 for L-M, and 0.88 for S-(L+M).
 The stimuli in Experiment 3 were temporal modulations of luminance applied to a disc made using the same raised cosine envelope as described above, but with no further spatial modulation.
@@
 We also measured the spectral output of each phosphor using a Jaz spectroradiometer (Ocean Insight, Florida), and used these measurements to convert between LMS (cone) space and the monitor RGB coordinates.
-
-For convenience, we express stimulus contrast as a percentage of the maximum possible contrast that could be displayed on our system.
-For achromatic stimuli, the maximum contrast is 1, so this is equivalent to the standard Michelson contrast expressed as a percentage.
-For the isoluminant chromatic stimuli, the maximum displayable L-M (red/green) cone contrast was 0.1, and the maximum displayable S-(L+M) (blue/yellow) cone contrast was 0.88.
-An L-M threshold of 50\% therefore corresponds to a cone contrast of $0.5\times0.1 = 0.05$, and an S-(L+M) threshold of 50\% corresponds to a cone contrast of $0.5\times0.88 = 0.44$.
-This means that the threshold values reported throughout can be converted to cone contrast by a straightforward multiplicative transform.
+We express contrast values in normalized units, relative to the monocular threshold for each stimulus type.
 
@@
 Before beginning primary data collection, each participant in Experiments 1 and 2 completed an isoluminance adjustment task.
-Grating stimuli were presented that counterphase flickered at 5Hz, defined about either the L-M or S-(L+M) plane in cone space.
+Grating stimuli were presented that counterphase flickered at 5Hz, with contrast variations defined about either the L-M or S-(L+M) plane in cone space.
 Participants used a trackball to dynamically adjust the colour angle of the stimulus to minimise the percept of flicker.
@@
 Each interval was indicated by an auditory beep, and participants made their responses using a two-button trackball.
-Correct responses were followed by a high pitched tone, and incorrect responses by a low pitched tone.
-Each block of the experiment tested a single pedestal contrast level, and lasted around 12 minutes.
+Correct responses were followed by a high-pitched tone, and incorrect responses by a low-pitched tone.
+Each block of the experiment tested a single pedestal contrast level and lasted around 12 minutes.
 On each trial the target contrast level was determined by a 3-down-1-up staircase procedure.
@@
 Mask contrasts were chosen to be approximately 16 times their (monocular) detection threshold, based on the data from Experiment 1.
-As a percentage of the maximum displayable contrast, these were 16% for achromatic stimuli, and 64% for both of the chromatic stimuli.
+The contrasts were 16% Michelson contrast for the achromatic stimuli, 6.4% cone contrast for L-M and 56% cone contrast for S-(L+M).
 Each block of the experiment tested a single condition, and consisted of 200 trials.
@@
 
-Psychometric functions from each experiment were fit using \emph{psignifit} 4 to estimate threshold and slope parameters via a Bayesian numerical integration method [@Schutt2016].
+Psychometric functions from each experiment were fit using *psignifit* 4 to estimate threshold and slope parameters via a Bayesian numerical integration method [@Schutt2016].
 A cumulative Gaussian was used as the underlying function, with contrast values expressed in decibel (dB) units (where $C_{dB} = 20log_{10}(C_\%)$).
@@
 
-The two stage model of @Meese2006 was fit to the threshold data from Experiments 1 and 3 using a simplex algorithm to minimise the error between the model and data.
+The two-stage model of @Meese2006 was fit to the threshold data from Experiments 1 and 3 using a simplex algorithm to minimise the error between the model and data.
+We normalized the thresholds and pedestal contrasts to the appropriate monocular threshold for each stimulus type.
 The model is defined by a series of equations:
@@
 
-where $C_L$ and $C_R$ are the contrasts displayed to the left and right eyes, and $m$, $S$, $\omega$, $p$, $q$ and $Z$ are free parameters in the model.
+where $C_L$ and $C_R$ are the (normalized) contrasts displayed to the left and right eyes, and $m$, $S$, $\omega$, $p$, $q$ and $Z$ are free parameters in the model.
 A further free parameter, $k$, represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values (note that in the original model specification [@Meese2006] this parameter was called $\sigma$, but we use the $k$ symbol here to avoid confusion with the standard deviation of the cumulative Gaussian used when fitting the psychometric functions to estimate thresholds).
@@
 four fits in total, as for the simplex fitting).
-Prior distributions were Gaussian, with means determined from published values (see first row of @tbl-parametertable).
+Prior distributions for the parameters *p*, *q*, *m* and $\omega$ were Gaussian, with means determined from published values (see first row of @tbl-parametertable).
+Priors for parameters *S*, *Z* and *k* were uniform.
 This modelling primarily focuses on examining posterior parameter distributions, rather than a model comparison approach.
@@
 There is an equivalent expression for the right eye, and for each of the two isoluminant chromatic pathways.
-To simplify the model, and avoid free parameters that are poorly constrained by the data, we fixed several parameters at the average values from the fits from Experiment 1 (@tbl-parametertable), such that $p=7.82$, $q=6.4$, $m=1.21$, $S=1.03$ and $k=0.23$.
-We additionally fixed the within-mechanism weight of interocular suppression ($\omega$) at 1.
+To simplify the model, and avoid free parameters that are poorly constrained by the data, we fixed several parameters (*p*, *q*, *m*, *S*, *k*, and $\omega$ for the within-pathway suppression) at the values from the fits from Experiment 1 (@tbl-parametertable, lower rows).
 This left 9 free parameters: a $Z$ parameter for each mechanism, and six cross-mechanism weights of interocular suppression.
@@
 regdata <- NULL
-regdata$thd <- meanthresh[3,2,5:8]
+regdata$thd <- meanthresh[2,2,5:8]
 regdata$ped <- seq(12,30,6)
@@
 regdata <- NULL
-regdata$thd <- meanthresh[2,2,5:8]
+regdata$thd <- meanthresh[3,2,5:8]
 regdata$ped <- seq(12,30,6)
@@
 regdata <- NULL
-regdata$thd <- meanthresh[3,4,5:8]
+regdata$thd <- meanthresh[2,4,5:8]
 regdata$ped <- seq(12,30,6)
@@
 regdata <- NULL
-regdata$thd <- meanthresh[2,4,5:8]
+regdata$thd <- meanthresh[3,4,5:8]
 regdata$ped <- seq(12,30,6)
@@
 Error bars give ±1SE across participants.
-Note that contrast values are expressed as a percentage of the maximum displayable contrast (see Procedures for details).
+Note that all contrast values for both thresholds and pedestals are normalized to the monocular detection threshold in each panel.
 Curves in panels (a-c) show the best fitting models, optimized using a simplex algorithm, and RMSE values give the root mean squared errors of the fits.](Figures/dipperssimplex.pdf){#fig-dipperfig}
@@
 A similar pattern of results was observed for both the red/green and blue/yellow isoluminant stimuli (see [@fig-dipperfig]b,c).
-Summation at threshold was a factor of `r round(10^(summation[3]/20),digits=2)` (`r round(summation[3],digits=2)`dB) for the red/green targets, and a factor of `r round(10^(summation[2]/20),digits=2)` (`r round(summation[2],digits=2)`dB) for the blue/yellow targets, and so was marginally higher than for achromatic stimuli.
+Summation at threshold was a factor of `r round(10^(summation[2]/20),digits=2)` (`r round(summation[2],digits=2)`dB) for the red/green targets, and a factor of `r round(10^(summation[3]/20),digits=2)` (`r round(summation[3],digits=2)`dB) for the blue/yellow targets, and so was marginally higher than for achromatic stimuli.
 The general character of the dipper functions was largely consistent with the achromatic results, though we observed shallower facilitation and weaker masking, especially for the blue/yellow stimuli.
-For example, the strongest facilitation in the binocular condition for achromatic stimuli was a factor of `r round(10^((meanthresh[1,2,1]-meanthresh[1,2,3])/20),digits=2)`, whereas it reduced to a factor of `r round(10^((meanthresh[3,2,1]-meanthresh[3,2,3])/20),digits=2)` for red/green stimuli and `r round(10^((meanthresh[2,2,1]-meanthresh[2,2,3])/20),digits=2)` for blue/yellow stimuli.
+For example, the strongest facilitation in the binocular condition for achromatic stimuli was a factor of `r round(10^((meanthresh[1,2,1]-meanthresh[1,2,3])/20),digits=2)`, whereas it reduced to a factor of `r round(10^((meanthresh[2,2,1]-meanthresh[2,2,3])/20),digits=2)` for red/green stimuli and `r round(10^((meanthresh[3,2,1]-meanthresh[3,2,3])/20),digits=2)` for blue/yellow stimuli.
 The slope of the binocular dipper handle was `r round(binregACH$coefficients[2], digits=2)` for achromatic stimuli, `r round(binregRG$coefficients[2], digits=2)` for red/green stimuli, and `r round(binregBY$coefficients[2], digits=2)` for blue/yellow stimuli.
@@
 This was clear for all three data sets, with slope values in the range $4 < \beta < 8$.
-However, we observe that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy the majority of trials close to threshold.
+However, we observe that slope estimates are more variable than threshold estimates (note the large error bars), particularly when using adaptive staircases, which deploy most trials close to threshold.
 Our second experiment therefore investigated the slope of the psychometric function in more detail for dichoptic masking using the method of constant stimuli, as well as exploring dichoptic interactions between chromatic channels.
@@
 Panel (g) shows the average threshold elevation factor for each combination of target and mask stimulus.
-Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull $\beta$ units.](Figures/MCSdata.pdf){#fig-MCSfig}
+Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull $\beta$ units.
+Contrast values are expressed relative to the target only threshold for each stimulus type.](Figures/MCSdata.pdf){#fig-MCSfig}
 
@@
 Masking was weakest between achromatic masks/targets and chromatic masks/targets.
-Finally there was an intermediate level of masking between red/green and blue/yellow stimuli.
+Finally, there was an intermediate level of masking between red/green and blue/yellow stimuli.
 This is summarised in [@fig-MCSfig]g, which represents threshold elevation for each combination of target and mask chromaticity.
@@
 These 'super-steep' psychometric functions for dichoptic pedestal masking have been reported previously [@Meese2006; @Baker2013], and are observed for the first time here using chromatic stimuli (see diagonal values in [@fig-MCSfig]h, and also [@fig-dipperfig]d-f).
-However we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,2],meanslopesMCS[1,3],meanslopesMCS[2,1],meanslopesMCS[2,3],meanslopesMCS[3,1],meanslopesMCS[3,2])))),digits=2)` for the off-diagonal values).
+However, we did not see such markedly steep functions for any of the cross-chromaticity masking conditions (average $\beta$ = `r round(10^(mean(log10(c(meanslopesMCS[1,2],meanslopesMCS[1,3],meanslopesMCS[2,1],meanslopesMCS[2,3],meanslopesMCS[3,1],meanslopesMCS[3,2])))),digits=2)` for the off-diagonal values).
 
@@
 Best fitting parameters are shown in the 'Simplex fits' section of @tbl-parametertable.
-We note that in previous work, the weight of interocular suppression ($\omega$ in the model) is implicitly fixed at 1.
-Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (`r round(allp[4,6],digits=2)`) for our flickering discs.
-The exponent values (*p* and *q*) for the red/green gratings are rather different from those of the other conditions.
+We note that in previous work, the weight of interocular suppression ($\omega$ in the model) was implicitly fixed at 1.
+Here we allowed it to vary, but it still received a value very close to 1 in all of our grating conditions, and slightly below 1 (`r round(allp[4,6],digits=2)`) for our flickering discs.
+The exponent values (*p* and *q*) for the blue/yellow gratings are rather different from those of the other conditions.
 In previous work [@Meese2006] the second stage gain control nonlinearity (Equation 4) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper).
-The high value of *p* = `r round(allp[2,1], digits=2)` is therefore likely to be compensating for the low value of *m* = `r round(allp[2,3], digits=2)` at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty [@Pelli1985].
-
-We additionally implemented a hierarchical Bayesian version of the model in order to estimate full posterior parameter distributions.
+The high value of *p* = `r round(allp[3,1], digits=2)` is therefore likely to be compensating for the low value of *m* = `r round(allp[3,3], digits=2)` at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty [@Pelli1985].
+
+We additionally implemented a hierarchical Bayesian version of the model to estimate full posterior parameter distributions.
 This model was fit simultaneously to the full trial-by-trial data from all participants who participated in a given experiment (i.e.
@@
 [@fig-bayesianmodel]a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically.
-Mean posterior parameter values are given in the lower rows of @tbl-parametertable.
+Modal posterior parameter values (maximum a posteriori (MAP) estimates) are given in the lower rows of @tbl-parametertable.
 These correspond quite closely to the parameters from the simplex fitting and the original @Meese2006 parameters (reproduced in the first row of the table for reference).
@@
 ![Model predictions (a-d) and posterior parameters (top and right margin plots) for the hierarchical Bayesian model.
-Thick lines in panels (a-d) show curves generated from the mean posterior parameter estimates.
+Curves in panels (a-d) show thresholds generated using the maximum a posteriori parameter estimates.
 The probability density functions in the margin plots are peak-normalized, and shown for each of the four data sets in different colours (see legend in upper left plot).
@@
 [@fig-MCSmodel]d,e shows the model estimates for the weight of interocular suppression in each combination of target and mask chromaticity.
-Although the weights might appear to indicate that (excluding within-mechanism effects) suppression is strongest between blue/yellow targets and achromatic masks (a weight of 0.56), this is somewhat complicated by the differences in mask contrast between conditions.
-We selected mask contrasts that were approximately equal multiples ($16\times$) of their own detection thresholds, based on the data of Experiment 1 ([@fig-dipperfig]a-c).
-However the modelling expressed these contrasts as a percentage of the maximum contrast that it was possible to display on the monitor (see Procedures).
-The values in brackets in [@fig-MCSmodel]d indicate the overall suppressive term on the denominator of the model at stage 1, calculated by multiplying the mask contrast by the fitted weight.
-These values indicate that the strongest suppression is instead between red/green targets and blue/yellow masks, consistent with the threshold elevation observed empirically ([@fig-MCSfig]g).
-In principle it would be possible to repeat this modelling using either cone contrast values, or contrast expressed relative to detection threshold, which would require re-fitting the model.
+The weakest suppression was between achromatic targets and masks and blue/yellow targets and masks, and the strongest suppression was between red/green targets and blue/yellow masks.
+Note that the weight parameter value of 1.21 for this condition is higher than that of the within-channel weights (values around 1), even though the within-channel conditions generate more threshold elevation.
+In the model, high thresholds for within-channel dichoptic masks occur because the target and mask are summed together, which causes additional masking [see @Baker2013].
+There do not appear to be any other salient patterns in the suppressive weight estimates.
 
@@
 Panels (a-c) show model psychometric functions in the same format as those in Figure 5.
-Panel (d) shows the fitted suppressive weights ($\omega$ values), with values in brackets indicating the combined suppressive denominator term calculated by multiplying together the suppressive weight and the dichoptic mask contrast.
-Panel (e) shows the posterior distributions for each weight parameter.
+Panel (d) shows the fitted suppressive weights ($\omega$ values) estiamted by the model, and panel (e) shows the posterior distributions for each weight parameter.
 The lower right plot gives the legends for the upper row (top) and the posterior distributions in panel (e).](Figures/MCSmodel.pdf){#fig-MCSmodel}
@@
 Recent evidence indicates that the physiological substrate of interocular suppression may be neurons in layer 4 of primary visual cortex [@Dougherty2019].
-Most cells in this layer are monocularly exciteable, in that their responses increase only by stimulation of their preferred eye.
+Most cells in this layer are monocularly excitable, in that their responses increase only by stimulation of their preferred eye.
 However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed at stage 1 of the two-stage model (Equations 1 & 2).

### 2024-04-15 manuscript.tex
Switched to using normalized contrast values

@@
 \maketitle
-\(^1\)Department of Psychology, University of York, UK
-
-\(^2\)York Biomedical Research Institute, University of York, UK
-
-\(^3\)School of Psychology, University of Nottingham, UK
-
+\(^1\)Department of Psychology, University of York, UK\\
+\(^2\)York Biomedical Research Institute, University of York, UK\\
+\(^3\)School of Psychology, University of Nottingham, UK\\
 \(^4\)School of Philosophy, Psychology and Language Sciences, University
-of Edinburgh, UK
-
+of Edinburgh, UK\\
 \(^*\)Corresponding author, email: daniel.baker@york.ac.uk
@@
 Much progress has been made in understanding how the brain combines
-signals from the two eyes. However most of this work has involved
+signals from the two eyes. However, most of this work has involved
 achromatic (black and white) stimuli, and it is not clear if the same
@@
 Wade, 2017), fMRI (Moradi \& Heeger, 2009) and pupillometry (Segala et
-al., 2023). However, the majority of this work has used achromatic
-(black and white) stimuli; we know comparatively little about how
-chromatic signals are combined binocularly, or about how signals in
-different ocular and chromatic channels interact. In this study we use
-psychophysical detection and discrimination paradigms to explore
-binocular interactions within and between the chromatic and achromatic
-pathways.
+al., 2023). However, most of this work has used achromatic (black and
+white) stimuli; we know comparatively little about how chromatic signals
+are combined binocularly, or about how signals in different ocular and
+chromatic channels interact. In this study we use psychophysical
+detection and discrimination paradigms to explore binocular interactions
+within and between the chromatic and achromatic pathways.
 
@@
 binocular summation by neurons responsive to signals from both eyes
-(Baker et al., 2018; Campbell \& Green, 1965). However at high pedestal
+(Baker et al., 2018; Campbell \& Green, 1965). However, at high pedestal
 contrasts the `handle' regions of the dipper functions for these
@@
 when the pedestal is visible, the target must equal or exceed its
-contrast in order to be detectable (Baker \& Meese, 2007; Legge, 1979;
-Maehara \& Goryo, 2005). The characteristic pattern of dipper functions
-is well-described by the gain control model of Meese et al. (2006) for
+contrast to be detectable (Baker \& Meese, 2007; Legge, 1979; Maehara \&
+Goryo, 2005). The characteristic pattern of dipper functions is
+well-described by the gain control model of Meese et al. (2006) for
 achromatic stimuli.
@@
 distinct pathways. The sum of long- and medium-wavelength cone outputs
-(L+M) transmits luminance information, and is likely responsible for the
-binocular combination effects previously studied using achromatic
-stimuli (see above). The difference of long- and medium-wavelength cone
-outputs (L-M) is responsive to chromatic stimuli modulating along a
-red/green axis in colour space. Finally the short wavelength cone
-outputs (S-(L+M)) code chromatic stimuli modulating along a blue/yellow
-axis. There has not yet been a detailed investigation of binocular
-contrast discrimination in either of these chromatic pathways, however
-there is reason to believe they may differ from the achromatic pathway.
-At detection threshold, binocular summation is greater for chromatic
-versus achromatic stimuli (Simmons, 2005), implying a more linear
-initial stage of processing. For cross-orientation masking, there are
-differences in the magnitude of masking between chromatic (red/green)
-and achromatic stimuli (Kim et al., 2013; Medina \& Mullen, 2009), as
-well as differences in their temporal dynamics (Kim \& Mullen, 2015).
-There are also interactions between chromatic and achromatic pathways
-both within (Chen et al., 2000) and between (Kingdom \& Libenson, 2015;
-Mullen et al., 2014) the eyes, yet these have not been fully explored
-for arrangements where the target and mask have the same orientation.
+(L+M) transmits luminance information (see Sharpe et al., 2011), and is
+likely responsible for the binocular combination effects previously
+studied using achromatic stimuli (see above). The difference of long-
+and medium-wavelength cone outputs (L-M) is responsive to chromatic
+stimuli modulating along a red/green axis in colour space. Finally the
+opponent (S-(L+M)) channel codes chromatic stimuli modulating along a
+blue/yellow axis. At isoluminance, where (L+M) is held constant, this
+channel is driven purely by the S-cone outputs.
+
+There has not yet been a detailed investigation of binocular contrast
+discrimination in either of these chromatic pathways, however there is
+reason to believe they may differ from the achromatic pathway. At
+detection threshold, binocular summation is greater for chromatic versus
+achromatic stimuli (Simmons, 2005), implying a more linear initial stage
+of processing. For cross-orientation masking, there are differences in
+the magnitude of masking between chromatic (red/green) and achromatic
+stimuli (Kim et al., 2013; Medina \& Mullen, 2009), as well as
+differences in their temporal dynamics (Kim \& Mullen, 2015). There are
+also interactions between chromatic and achromatic pathways both within
+(Chen et al., 2000) and between (Kingdom \& Libenson, 2015; Mullen et
+al., 2014) the eyes, yet these have not been fully explored for
+arrangements where the target and mask have the same orientation.
 Finally, the neurophysiological underpinnings of colour vision are
@@
 Livingstone \& Hubel, 1984), and biased towards low spatial frequencies
-(Edwards et al., 1995; Tootell et al., 1988). Our recent work (Segala et
-al., 2023) has investigated binocular combination for flickering discs
-of luminance, which are DC-balanced across time (i.e.~the time-averaged
-luminance is equal to the background). Steady-state EEG responses from
-early visual cortex and psychophysical contrast matching data were both
-consistent with weak interocular suppression when using this stimulus
-arrangement. This is very different from the `ocularity invariance'
-(where binocular and monocular stimuli appear equal) that is
-well-established when using DC-balanced periodic stimuli such as
-sine-wave gratings, and implies strong interocular suppression (Baker \&
-Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009). There is
-additional psychophysical evidence from matching studies that binocular
-combination can be close to linear for luminance increments (Anstis \&
-Ho, 1998; Levelt, 1965), particularly against a dark background (Baker
-et al., 2012). Both structural and functional data therefore imply that
-binocular combination may differ between spatial and temporal contrast.
+(Edwards et al., 1995; Tootell et al., 1988; though see Economides et
+al., 2011). Our recent work (Segala et al., 2023) has investigated
+binocular combination for flickering discs of luminance, which are
+DC-balanced across time (i.e.~the time-averaged luminance is equal to
+the background). Steady-state EEG responses from early visual cortex and
+psychophysical contrast matching data were both consistent with weak
+interocular suppression when using this stimulus arrangement. This is
+very different from the `ocularity invariance' (where binocular and
+monocular stimuli appear equal) that is well-established when using
+DC-balanced periodic stimuli such as sine-wave gratings, and implies
+strong interocular suppression (Baker \& Wade, 2017; Meese et al., 2006;
+Moradi \& Heeger, 2009). There is additional psychophysical evidence
+from matching studies that binocular combination can be close to linear
+for luminance increments (Anstis \& Ho, 1998; Levelt, 1965),
+particularly against a dark background (Baker et al., 2012). Both
+structural and functional data therefore imply that binocular
+combination may differ between spatial and temporal contrast.
 
@@
 Experiment 1 we replicate the four key pedestal masking conditions of
-Meese et al. (2006) described above for achromatic grating stimuli, and
+Meese et al. (2006) described above for achromatic grating stimuli and
 extend this to both red/green and blue/yellow isoluminant chromatic
@@
 these stimuli. Experiment 3 repeats the achromatic condition from the
-first experiment, but using a temporally modulated disc rather than
+first experiment but using a temporally modulated disc rather than
 sine-wave gratings. We take a Bayesian approach to data analysis and
@@
 readings and the Stockman-Sharpe 2 degree cone fundamentals (Stockman \&
-Sharpe, 2000). The stimuli in Experiment 3 were temporal modulations of
-luminance applied to a disc made using the same raised cosine envelope
-as described above, but with no further spatial modulation. The stimuli
-counterphase flickered sinusoidally at 4Hz (see examples in the lower
-portion of Figure~\ref{fig-examplestim}). In all experiments, we
-displayed a binocular fusion lock, consisting of three concentric rings
-of small square elements with random colour. A black central fixation
-cross was also displayed throughout.
+Sharpe, 2000). The maximum displayable cone contrasts on our system were
+0.1 for L-M, and 0.88 for S-(L+M). The stimuli in Experiment 3 were
+temporal modulations of luminance applied to a disc made using the same
+raised cosine envelope as described above, but with no further spatial
+modulation. The stimuli counterphase flickered sinusoidally at 4Hz (see
+examples in the lower portion of Figure~\ref{fig-examplestim}). In all
+experiments, we displayed a binocular fusion lock, consisting of three
+concentric rings of small square elements with random colour. A black
+central fixation cross was also displayed throughout.
 
@@
 Insight, Florida), and used these measurements to convert between LMS
-(cone) space and the monitor RGB coordinates.
-
-For convenience, we express stimulus contrast as a percentage of the
-maximum possible contrast that could be displayed on our system. For
-achromatic stimuli, the maximum contrast is 1, so this is equivalent to
-the standard Michelson contrast expressed as a percentage. For the
-isoluminant chromatic stimuli, the maximum displayable L-M (red/green)
-cone contrast was 0.1, and the maximum displayable S-(L+M) (blue/yellow)
-cone contrast was 0.88. An L-M threshold of 50\% therefore corresponds
-to a cone contrast of \(0.5\times0.1 = 0.05\), and an S-(L+M) threshold
-of 50\% corresponds to a cone contrast of \(0.5\times0.88 = 0.44\). This
-means that the threshold values reported throughout can be converted to
-cone contrast by a straightforward multiplicative transform.
+(cone) space and the monitor RGB coordinates. We express contrast values
+in normalized units, relative to the monocular threshold for each
+stimulus type.
 
@@
 Experiments 1 and 2 completed an isoluminance adjustment task. Grating
-stimuli were presented that counterphase flickered at 5Hz, defined about
-either the L-M or S-(L+M) plane in cone space. Participants used a
-trackball to dynamically adjust the colour angle of the stimulus to
-minimise the percept of flicker. Each participant completed ten such
-trials for each colour plane, and the average angle across repetition
-was taken as the isoluminant point, and used to generate stimuli for the
-main experiment for that participant. Settings were very similar across
-participants for the S-(L+M) direction, and somewhat more heterogeneous
-for the L-M direction (see Figure~\ref{fig-isofig}).
+stimuli were presented that counterphase flickered at 5Hz, with contrast
+variations defined about either the L-M or S-(L+M) plane in cone space.
+Participants used a trackball to dynamically adjust the colour angle of
+the stimulus to minimise the percept of flicker. Each participant
+completed ten such trials for each colour plane, and the average angle
+across repetition was taken as the isoluminant point, and used to
+generate stimuli for the main experiment for that participant. Settings
+were very similar across participants for the S-(L+M) direction, and
+somewhat more heterogeneous for the L-M direction (see
+Figure~\ref{fig-isofig}).
 
@@
 an auditory beep, and participants made their responses using a
-two-button trackball. Correct responses were followed by a high pitched
-tone, and incorrect responses by a low pitched tone. Each block of the
-experiment tested a single pedestal contrast level, and lasted around 12
+two-button trackball. Correct responses were followed by a high-pitched
+tone, and incorrect responses by a low-pitched tone. Each block of the
+experiment tested a single pedestal contrast level and lasted around 12
 minutes. On each trial the target contrast level was determined by a
@@
 16 times their (monocular) detection threshold, based on the data from
-Experiment 1. As a percentage of the maximum displayable contrast, these
-were 16\% for achromatic stimuli, and 64\% for both of the chromatic
-stimuli. Each block of the experiment tested a single condition, and
+Experiment 1. The contrasts were 16\% Michelson contrast for the
+achromatic stimuli, 6.4\% cone contrast for L-M and 56\% cone contrast
+for S-(L+M). Each block of the experiment tested a single condition, and
 consisted of 200 trials. A high contrast example of the target stimulus
@@
 
-The two stage model of Meese et al. (2006) was fit to the threshold data
+The two-stage model of Meese et al. (2006) was fit to the threshold data
 from Experiments 1 and 3 using a simplex algorithm to minimise the error
-between the model and data. The model is defined by a series of
-equations:
+between the model and data. We normalized the thresholds and pedestal
+contrasts to the appropriate monocular threshold for each stimulus type.
+The model is defined by a series of equations:
 
@@
 
-where \(C_L\) and \(C_R\) are the contrasts displayed to the left and
-right eyes, and \(m\), \(S\), \(\omega\), \(p\), \(q\) and \(Z\) are
-free parameters in the model. A further free parameter, \(k\),
+where \(C_L\) and \(C_R\) are the (normalized) contrasts displayed to
+the left and right eyes, and \(m\), \(S\), \(\omega\), \(p\), \(q\) and
+\(Z\) are free parameters in the model. A further free parameter, \(k\),
 represents additive internal noise, and is used to convert the model
@@
 and the flickering disc data from Experiment 3 (i.e.~four fits in total,
-as for the simplex fitting). Prior distributions were Gaussian, with
-means determined from published values (see first row of
-Table~\ref{tbl-parametertable}). This modelling primarily focuses on
+as for the simplex fitting). Prior distributions for the parameters
+\emph{p}, \emph{q}, \emph{m} and \(\omega\) were Gaussian, with means
+determined from published values (see first row of
+Table~\ref{tbl-parametertable}). Priors for parameters \emph{S},
+\emph{Z} and \emph{k} were uniform. This modelling primarily focuses on
 examining posterior parameter distributions, rather than a model
@@
 pathways. To simplify the model, and avoid free parameters that are
-poorly constrained by the data, we fixed several parameters at the
-average values from the fits from Experiment 1
-(Table~\ref{tbl-parametertable}), such that \(p=7.82\), \(q=6.4\),
-\(m=1.21\), \(S=1.03\) and \(k=0.23\). We additionally fixed the
-within-mechanism weight of interocular suppression (\(\omega\)) at 1.
-This left 9 free parameters: a \(Z\) parameter for each mechanism, and
-six cross-mechanism weights of interocular suppression. These parameters
+poorly constrained by the data, we fixed several parameters (\emph{p},
+\emph{q}, \emph{m}, \emph{S}, \emph{k}, and \(\omega\) for the
+within-pathway suppression) at the values from the fits from Experiment
+1 (Table~\ref{tbl-parametertable}, lower rows). This left 9 free
+parameters: a \(Z\) parameter for each mechanism, and six
+cross-mechanism weights of interocular suppression. These parameters
 were again estimated within a Bayesian hierarchical framework, using the
@@
 function expressed in Weibull \(\beta\) units. Error bars give ±1SE
-across participants. Note that contrast values are expressed as a
-percentage of the maximum displayable contrast (see Procedures for
-details). Curves in panels (a-c) show the best fitting models, optimized
-using a simplex algorithm, and RMSE values give the root mean squared
-errors of the fits.}
+across participants. Note that all contrast values for both thresholds
+and pedestals are normalized to the monocular detection threshold in
+each panel. Curves in panels (a-c) show the best fitting models,
+optimized using a simplex algorithm, and RMSE values give the root mean
+squared errors of the fits.}
 
@@
 (note the large error bars), particularly when using adaptive
-staircases, which deploy the majority of trials close to threshold. Our
-second experiment therefore investigated the slope of the psychometric
-function in more detail for dichoptic masking using the method of
-constant stimuli, as well as exploring dichoptic interactions between
-chromatic channels.
+staircases, which deploy most trials close to threshold. Our second
+experiment therefore investigated the slope of the psychometric function
+in more detail for dichoptic masking using the method of constant
+stimuli, as well as exploring dichoptic interactions between chromatic
+channels.
 
@@
 geometric mean psychometric slope value for each masking condition in
-Weibull \(\beta\) units.}
+Weibull \(\beta\) units. Contrast values are expressed relative to the
+target only threshold for each stimulus type.}
 
@@
 Masking was weakest between achromatic masks/targets and chromatic
-masks/targets. Finally there was an intermediate level of masking
+masks/targets. Finally, there was an intermediate level of masking
 between red/green and blue/yellow stimuli. This is summarised in
@@
 Figure~\ref{fig-MCSfig}h, and also Figure~\ref{fig-dipperfig}d-f).
-However we did not see such markedly steep functions for any of the
+However, we did not see such markedly steep functions for any of the
 cross-chromaticity masking conditions (average \(\beta\) = 2.83 for the
@@
 \textbf{Simplex fits} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
-Achromatic gratings & 6.51 & 5.10 & 1.31 & 0.83 & 0.16 & 1.00 & 0.21 & 1.59 dB\\
-Red/green gratings & 19.42 & 1.10 & 1.03 & 0.37 & 1.49 & 1.00 & 0.29 & 1.43 dB\\
-Blue/yellow gratings & 9.47 & 6.21 & 1.14 & 1.89 & 0.26 & 1.00 & 0.34 & 1.38 dB\\
-Flickering discs & 6.13 & 4.93 & 1.24 & 0.84 & 0.27 & 0.89 & 0.13 & 1.06 dB\\
+Achromatic gratings & 5.96 & 4.69 & 1.34 & 0.87 & 0.13 & 1.00 & 0.20 & 1.59 dB\\
+Red/green gratings & 7.77 & 5.19 & 1.17 & 0.55 & 0.07 & 1.00 & 0.17 & 1.39 dB\\
+Blue/yellow gratings & 16.01 & 11.56 & 1.13 & 0.33 & 0.00 & 0.99 & 0.27 & 1.46 dB\\
+Flickering discs & 5.62 & 4.51 & 1.26 & 0.95 & 0.25 & 0.89 & 0.13 & 1.05 dB\\
 \midrule
 \textbf{Bayesian model} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
-Achromatic gratings & 7.78 & 6.37 & 1.29 & 0.88 & 0.12 & 0.99 & 0.25 & \\
-Red/green gratings & 7.88 & 6.46 & 1.21 & 1.10 & 0.46 & 0.95 & 0.21 & \\
-Blue/yellow gratings & 7.79 & 6.37 & 1.14 & 1.10 & 0.59 & 1.00 & 0.24 & \\
-Flickering discs & 7.72 & 6.32 & 1.26 & 0.83 & 0.22 & 0.90 & 0.23 & \\
+Achromatic gratings & 7.12 & 5.79 & 1.27 & 0.65 & 0.07 & 0.99 & 0.31 & \\
+Red/green gratings & 5.25 & 3.60 & 1.23 & 1.27 & 0.03 & 1.05 & 0.20 & \\
+Blue/yellow gratings & 6.78 & 5.17 & 1.24 & 0.58 & 0.01 & 0.96 & 0.36 & \\
+Flickering discs & 7.21 & 5.75 & 1.25 & 0.69 & 0.13 & 0.88 & 0.26 & \\
 \bottomrule
@@
 Figure~\ref{fig-dipperfig} and Figure~\ref{fig-discdata}, and provide an
-excellent description of the data, with RMS errors between 1.06 and
+excellent description of the data, with RMS errors between 1.05 and
 1.59dB. Best fitting parameters are shown in the `Simplex fits' section
 of Table~\ref{tbl-parametertable}. We note that in previous work, the
-weight of interocular suppression (\(\omega\) in the model) is
+weight of interocular suppression (\(\omega\) in the model) was
 implicitly fixed at 1. Here we allowed it to vary, but it still received
-a value of exactly 1 in all of our grating conditions, and slightly
+a value very close to 1 in all of our grating conditions, and slightly
 below 1 (0.89) for our flickering discs. The exponent values (\emph{p}
-and \emph{q}) for the red/green gratings are rather different from those
-of the other conditions. In previous work (Meese et al., 2006) the
+and \emph{q}) for the blue/yellow gratings are rather different from
+those of the other conditions. In previous work (Meese et al., 2006) the
 second stage gain control nonlinearity (Equation 4) does typically have
@@
 that results in contrast masking (the handle of the dipper). The high
-value of \emph{p} = 19.42 is therefore likely to be compensating for the
-low value of \emph{m} = 1.03 at stage one, but may well represent the
+value of \emph{p} = 16.01 is therefore likely to be compensating for the
+low value of \emph{m} = 1.13 at stage one, but may well represent the
 combination of several successive stages of nonlinearity, and perhaps
@@
 We additionally implemented a hierarchical Bayesian version of the model
-in order to estimate full posterior parameter distributions. This model
-was fit simultaneously to the full trial-by-trial data from all
-participants who participated in a given experiment (i.e.~the model was
-fitted separately to each of the four dipper data sets).
-Figure~\ref{fig-bayesianmodel}a-d summarises the model behaviour, which
-displays the same pattern of dipper functions as we found empirically.
-Mean posterior parameter values are given in the lower rows of
-Table~\ref{tbl-parametertable}. These correspond quite closely to the
-parameters from the simplex fitting and the original Meese et al. (2006)
-parameters (reproduced in the first row of the table for reference). The
-panels in the right and upper margins of Figure~\ref{fig-bayesianmodel}
-show posterior distributions for each model parameter. Note in
-particular that the posterior distribution for the weight of interocular
-suppression (\(\omega\), top right panel) overlaps 1 for each
-experiment, consistent with the strong dichoptic masking observed in the
-threshold data. We note that the distribution for \(\omega\) in the
-flickering disc condition is somewhat lower than for the other three
-data sets. However this difference is not meaningful according to widely
-accepted criteria such as comparing the 95\% intervals of the
-distribution to a value of \(\omega=1\).
+to estimate full posterior parameter distributions. This model was fit
+simultaneously to the full trial-by-trial data from all participants who
+participated in a given experiment (i.e.~the model was fitted separately
+to each of the four dipper data sets). Figure~\ref{fig-bayesianmodel}a-d
+summarises the model behaviour, which displays the same pattern of
+dipper functions as we found empirically. Modal posterior parameter
+values (maximum a posteriori (MAP) estimates) are given in the lower
+rows of Table~\ref{tbl-parametertable}. These correspond quite closely
+to the parameters from the simplex fitting and the original Meese et al.
+(2006) parameters (reproduced in the first row of the table for
+reference). The panels in the right and upper margins of
+Figure~\ref{fig-bayesianmodel} show posterior distributions for each
+model parameter. Note in particular that the posterior distribution for
+the weight of interocular suppression (\(\omega\), top right panel)
+overlaps 1 for each experiment, consistent with the strong dichoptic
+masking observed in the threshold data. We note that the distribution
+for \(\omega\) in the flickering disc condition is somewhat lower than
+for the other three data sets. However this difference is not meaningful
+according to widely accepted criteria such as comparing the 95\%
+intervals of the distribution to a value of \(\omega=1\).
 
@@
 parameters (top and right margin plots) for the hierarchical Bayesian
-model. Thick lines in panels (a-d) show curves generated from the mean
-posterior parameter estimates. The probability density functions in the
-margin plots are peak-normalized, and shown for each of the four data
-sets in different colours (see legend in upper left plot). Distributions
-were generated from 1000000 samples per data set, using a Markov Chain
-Monte Carlo sampling algorithm. Note the logarithmic x-axis for all
-posterior plots.}
+model. Curves in panels (a-d) show thresholds generated using the
+maximum a posteriori parameter estimates. The probability density
+functions in the margin plots are peak-normalized, and shown for each of
+the four data sets in different colours (see legend in upper left plot).
+Distributions were generated from 1000000 samples per data set, using a
+Markov Chain Monte Carlo sampling algorithm. Note the logarithmic x-axis
+for all posterior plots.}
 
@@
 interocular suppression in each combination of target and mask
-chromaticity. Although the weights might appear to indicate that
-(excluding within-mechanism effects) suppression is strongest between
-blue/yellow targets and achromatic masks (a weight of 0.56), this is
-somewhat complicated by the differences in mask contrast between
-conditions. We selected mask contrasts that were approximately equal
-multiples (\(16\times\)) of their own detection thresholds, based on the
-data of Experiment 1 (Figure~\ref{fig-dipperfig}a-c). However the
-modelling expressed these contrasts as a percentage of the maximum
-contrast that it was possible to display on the monitor (see
-Procedures). The values in brackets in Figure~\ref{fig-MCSmodel}d
-indicate the overall suppressive term on the denominator of the model at
-stage 1, calculated by multiplying the mask contrast by the fitted
-weight. These values indicate that the strongest suppression is instead
-between red/green targets and blue/yellow masks, consistent with the
-threshold elevation observed empirically (Figure~\ref{fig-MCSfig}g). In
-principle it would be possible to repeat this modelling using either
-cone contrast values, or contrast expressed relative to detection
-threshold, which would require re-fitting the model.
+chromaticity. The weakest suppression was between achromatic targets and
+masks and blue/yellow targets and masks, and the strongest suppression
+was between red/green targets and blue/yellow masks. Note that the
+weight parameter value of 1.21 for this condition is higher than that of
+the within-channel weights (values around 1), even though the
+within-channel conditions generate more threshold elevation. In the
+model, high thresholds for within-channel dichoptic masks occur because
+the target and mask are summed together, which causes additional masking
+(see Baker et al., 2013). There do not appear to be any other salient
+patterns in the suppressive weight estimates.
 
@@
 format as those in Figure 5. Panel (d) shows the fitted suppressive
-weights (\(\omega\) values), with values in brackets indicating the
-combined suppressive denominator term calculated by multiplying together
-the suppressive weight and the dichoptic mask contrast. Panel (e) shows
+weights (\(\omega\) values) estiamted by the model, and panel (e) shows
 the posterior distributions for each weight parameter. The lower right
@@
 cortex (Dougherty et al., 2019). Most cells in this layer are
-monocularly exciteable, in that their responses increase only by
+monocularly excitable, in that their responses increase only by
 stimulation of their preferred eye. However, simultaneous stimulation of
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Economides2011}{}}%
+Economides, J. R., Sincich, L. C., Adams, D. L., \& Horton, J. C.
+(2011). Orientation tuning of cytochrome oxidase patches in macaque
+primary visual cortex. \emph{Nat Neurosci}, \emph{14}(12), 1574--1580.
+\url{https://doi.org/10.1038/nn.2958}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Edwards1995}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Sharpe2011}{}}%
+Sharpe, L. T., Stockman, A., Jagla, W., \& Jägle, H. (2011). A luminous
+efficiency function, VD65* (λ), for daylight adaptation: A correction.
+\emph{Color Research \& Application}, \emph{36}(1), 42--46.
+https://doi.org/\url{https://doi.org/10.1002/col.20602}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Simmons2005}{}}%

### 2024-04-15 manuscript.qmd
Testing full build (no modelling)

@@
   mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-  title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-  title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+  title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+  title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
   title(main='(a) Flickering disc (thresholds)',cex.main=1.5)
@@
   mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-  title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+  title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
   title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
 title(main=paste0('(',letters[(3*(p-1)+1)],')  P',p,': Achromatic'),cex.main=2)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
 title(main=paste0('(',letters[(3*(p-1)+2)],')  P',p,': Red/Green'),cex.main=2)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
 title(main=paste0('(',letters[(3*(p-1)+3)],')  P',p,': Blue/Yellow'),cex.main=2)
@@
   mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-  title(xlab="Normalized target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+  title(xlab="Normalized target contrast", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
   title(ylab="Percent correct", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
 title(main=paste0('(',letters[p],')  P', pnos[p] ,': Flickering disc'),cex.main=2)

### 2024-04-16 manuscript.qmd
Fixed python again
Added axis breaks!

@@
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','parallel','doParallel','R.matlab','bayestestR','alphahull','kableExtra') # list of CRAN packages
+packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','parallel','doParallel','R.matlab','bayestestR','alphahull','kableExtra','plotrix') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
     ticklocsx <- seq(-24,30,6)
-    ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+    ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
     ticklocsy <- seq(-24,30,6)
@@
     title(main=paneltitles[expt],cex.main=2.5)
+    axis.break(axis=1,breakpos=-18)
 
@@
     ticklocsx <- seq(-24,30,6)
-    ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+    ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
 
@@
   ticklocsx <- seq(-24,30,6)
-  ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+  ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
   ticklocsy <- seq(-24,30,6)
@@
   title(main='(a) Flickering disc (thresholds)',cex.main=1.5)
+  axis.break(axis=1,breakpos=-18)
 
@@
   title(main='(b) Flickering disc (slopes)',cex.main=1.5)
+  axis.break(axis=1,breakpos=-18)
 
@@
   title(main=paneltitles[expt],cex.main=2)
-  # pedcontrasts <- seq(-12,30,6)
+  axis.break(axis=1,breakpos=-18)
 
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Normalized target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+title(xlab="Normalized target contrast", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
 title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
@@
 ticklocsx <- seq(-24,30,6)
-ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
+ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
 ticklocsy <- seq(-24,30,6)
@@
 title(main=paste0('(',letters[(3*(p-1)+1)],')  P',p,': Achromatic'),cex.main=2)
+axis.break(axis=1,breakpos=-18)
 
@@
 title(main=paste0('(',letters[(3*(p-1)+2)],')  P',p,': Red/Green'),cex.main=2)
+axis.break(axis=1,breakpos=-18)
 
@@
 title(main=paste0('(',letters[(3*(p-1)+3)],')  P',p,': Blue/Yellow'),cex.main=2)
+axis.break(axis=1,breakpos=-18)
 
@@
 title(main=paste0('(',letters[p],')  P', pnos[p] ,': Flickering disc'),cex.main=2)
+axis.break(axis=1,breakpos=-18)
 

### 2024-04-17 manuscript.qmd
Tweaks to example stimuli

@@
 title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+axis.break(axis=1,breakpos=-9)
 
@@
 
-t <- seq(0,1,length=9)
+# t <- seq(0,1,length=9)
+# manually adjust time points for example discs to compensate for monitor gamma
+t <- c(0,0.05,0.25,0.45,0.5,0.55,0.75,0.95,1)
 lummod <- sin(t*2*pi)
@@
 axis(1, at=seq(0,4,4/5), tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-mtext(text = seq(0,250,50), side = 1, at=seq(0,4,4/5), line=0)     
-title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+mtext(text = seq(0,250,50), side = 1, at=seq(0,4,4/5), line=0.25, cex=1.5)     
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=2)
 

### 2024-04-18 manuscript.qmd
Fixed python
Update to threshold criteria

@@
 if (processdata>0){
-  # install_python(version="3.6")
-  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
-
-  use_miniconda('r-reticulate')
+  install_python(version="3.6")
+  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
+
+  # use_miniconda('r-reticulate')
 
@@
 }
+
+# calculate d-prime at 75% correct threshold
+thdcriteria <- qnorm(0.75)*sqrt(2)
 
@@
 
-modelString = "
+modelString = paste0("
   data {
@@
 
-    dprime = (targresp-nullresp)/k[s[i]] ;
+    dprime = (targresp-nullresp)/(k[s[i]]/",thdcriteria,") ;
     if (is_nan(dprime)){
@@
   }  
-" # close quote for modelString
+") # close quote for modelString
 
@@
     nullresp = pow((Ln + Rn), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Ln + Rn), ",allstanparams[1,2],")) ;     
-    dprime = (targresp-nullresp)/",allstanparams[1,7]," ;
+    dprime = (targresp-nullresp)/(",allstanparams[1,7],"/",thdcriteria,") ;
 
@@
     nullresp = pow((Ln + Rn), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Ln + Rn), ",allstanparams[2,2],")) ;     
-    dprime = (targresp-nullresp)/",allstanparams[2,7]," ;
+    dprime = (targresp-nullresp)/(",allstanparams[2,7],"/",thdcriteria,") ;
 
@@
     nullresp = pow((Ln + Rn), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Ln + Rn), ",allstanparams[3,2],")) ;     
-    dprime = (targresp-nullresp)/",allstanparams[3,7]," ;
+    dprime = (targresp-nullresp)/(",allstanparams[3,7],"/",thdcriteria,") ;
 
@@
       nullresp = pow((Ln + Rn), ",allstanparams[1,1],") / (ZAc[s[i]] + pow((Ln + Rn), ",allstanparams[1,2],")) ;     
-      dprime = (targresp-nullresp)/",allstanparams[1,7]," ;
+      dprime = (targresp-nullresp)/(",allstanparams[1,7],"/",thdcriteria,") ;
 
@@
       nullresp = pow((Ln + Rn), ",allstanparams[2,1],") / (ZRg[s[i]] + pow((Ln + Rn), ",allstanparams[2,2],")) ;     
-      dprime = (targresp-nullresp)/",allstanparams[2,7]," ;
+      dprime = (targresp-nullresp)/(",allstanparams[2,7],"/",thdcriteria,") ;
     }
@@
       nullresp = pow((Ln + Rn), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Ln + Rn), ",allstanparams[3,2],")) ;     
-      dprime = (targresp-nullresp)/",allstanparams[3,7]," ;
+      dprime = (targresp-nullresp)/(",allstanparams[3,7],"/",thdcriteria,") ;
     }
@@
       nullresp = pow((Ln + Rn), ",allstanparams[3,1],") / (ZBy[s[i]] + pow((Ln + Rn), ",allstanparams[3,4],")) ;     
-      dprime = (targresp-nullresp)/",allstanparams[3,7]," ;
+      dprime = (targresp-nullresp)/(",allstanparams[3,7],"/",thdcriteria,") ;
     }
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[1,] - nr[1,])/p[1,7]
+  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[1,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[2,] - nr[2,])/p[2,7]
+  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[2,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[3,] - nr[3,])/p[3,7]
+  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[3,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[1,] - nr[1,])/p[1,7]
+  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[4,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[2,] - nr[2,])/p[2,7]
+  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[5,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[3,] - nr[3,])/p[3,7]
+  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[6,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
-  dprime <- (tr[1,] - nr[1,])/p[1,7]
+  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[7,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
-  dprime <- (tr[2,] - nr[2,])/p[2,7]
+  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[8,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
-  dprime <- (tr[3,] - nr[3,])/p[3,7]
+  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[9,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
-  dprime <- (tr[1,] - nr[1,])/p[1,7]
+  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[10,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
-  dprime <- (tr[2,] - nr[2,])/p[2,7]
+  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[11,] <- 100*pnorm(dprime/sqrt(2))
@@
   nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
-  dprime <- (tr[3,] - nr[3,])/p[3,7]
+  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
   pmfout[12,] <- 100*pnorm(dprime/sqrt(2))
@@
 
-\begin{equation}
-Stage1_L = \frac{C_L^m}{S + C_L + \omega C_R},
-\end{equation}
-
-\begin{equation}
-Stage1_R = \frac{C_R^m}{S + C_R + \omega C_L},
-\end{equation}
-
-\begin{equation}
-binsum = Stage1_L + Stage1_R,
-\end{equation}
-
-\begin{equation}
-Stage2 = \frac{binsum^p}{Z + binsum^q},
-\end{equation}
+$$\mathrm{Stage1}_L = \frac{C_L^m}{S + C_L + \omega C_R},$${#eq-s1l}
+
+$$\mathrm{Stage1}_R = \frac{C_R^m}{S + C_R + \omega C_L},$${#eq-s1r}
+
+$$\mathrm{binsum} = \mathrm{Stage1}_L + \mathrm{Stage1}_R,$${#eq-binsum}
+
+$$\mathrm{Stage2} = \frac{\mathrm{binsum}^p}{Z + \mathrm{binsum}^q},$${#eq-s2}
 
 where $C_L$ and $C_R$ are the (normalized) contrasts displayed to the left and right eyes, and $m$, $S$, $\omega$, $p$, $q$ and $Z$ are free parameters in the model.
-A further free parameter, $k$, represents additive internal noise, and is used to convert the model outputs to either d-prime or threshold values (note that in the original model specification [@Meese2006] this parameter was called $\sigma$, but we use the $k$ symbol here to avoid confusion with the standard deviation of the cumulative Gaussian used when fitting the psychometric functions to estimate thresholds).
+A further free parameter, $k$, is used to convert the model outputs to either d-prime or threshold values (note that in the original model specification [@Meese2006] this parameter was called $\sigma$, but we use the $k$ symbol here to avoid confusion with the standard deviation of the cumulative Gaussian used when fitting the psychometric functions to estimate thresholds).
 Thresholds are defined by iteratively adjusting the target contrast until the following equality is satisfied:
 
-\begin{equation}
-Stage2_{target+pedestal} - Stage2_{pedestal} = k,
-\end{equation}
-
-and d-prime for a single target level is defined as:
-
-\begin{equation}
-d' = \frac{Stage2_{target+pedestal} - Stage2_{pedestal}}{k}.
-\end{equation}
+$$\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}} = k,$${#eq-thd}
+
+and $d'$ (d-prime) for a single target level is defined as:
+
+$$d' = \frac{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}}}{k/\tau},$${#eq-dprime}
+
+where the parameter $\tau$ reflects the value of $d'$ at detection threshold.
+Defining threshold as the 75% correct point on the psychometric function (as here) yields a value of $\tau = \Phi^{-1}(0.75)\sqrt{2}$ = `r round(qnorm(0.75)*sqrt(2),digits=3)` (where $\Phi^{-1}$ is the inverse cumulative normal density function).
+The combined denominator term ($k/\tau$) therefore represents internal additive noise in the model.
 
@@
 
-\begin{equation}
-ACStage1_L = \frac{AC_L^m}{S + AC_L + \omega_A AC_R + \omega_R RG_R + \omega_B BY_R},
-\end{equation}
+$$^{AC}\mathrm{Stage1}_L = \frac{AC_L^m}{S + AC_L + \omega_A AC_R + \omega_R RG_R + \omega_B BY_R},$${#eq-s1multi}
 
@@
 The exponent values (*p* and *q*) for the blue/yellow gratings are rather different from those of the other conditions.
-In previous work [@Meese2006] the second stage gain control nonlinearity (Equation 4) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper).
+In previous work [@Meese2006] the second stage gain control nonlinearity (@eq-s2) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper).
 The high value of *p* = `r round(allp[3,1], digits=2)` is therefore likely to be compensating for the low value of *m* = `r round(allp[3,3], digits=2)` at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty [@Pelli1985].
@@
 Consistent with previous reports [@Simmons2005], summation was slightly higher for chromatic versus achromatic stimuli, but fell short of perfect linear summation (a ratio of 2).
-In our model, summation at threshold is determined by the exponent at the first gain control stage (the *m* parameter in Equations 1 & 2).
+In our model, summation at threshold is determined by the exponent at the first gain control stage (the *m* parameter in @eq-s1l and @eq-s1r).
 The summation ratio can be approximated by $2^{1/m}$ [see Figure 9 of @Baker2012], such that an exponent of $m=1$ produces a ratio of 2, and an exponent of $m = 2$ produces a ratio of $\sqrt{2}$.
@@
 
-The weight of interocular suppression is represented by the model parameter, $\omega$ (Equations 1 & 2).
+The weight of interocular suppression is represented by the model parameter, $\omega$ (@eq-s1l and @eq-s1r).
 Posterior distributions of this parameter overlapped 1 for all of our dipper function data sets (see top right panel in [@fig-bayesianmodel]), indicating strong interocular suppression regardless of post-retinal pathway.
@@
 Most cells in this layer are monocularly excitable, in that their responses increase only by stimulation of their preferred eye.
-However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed at stage 1 of the two-stage model (Equations 1 & 2).
+However, simultaneous stimulation of the non-preferred eye can modulate the response, usually in an inhibitory fashion, exactly as proposed at stage 1 of the two-stage model (@eq-s1l and @eq-s1r).
 In terms of perception, one consequence of this early suppression is to achieve 'ocularity invariance', whereby the perceived contrast of a stimulus viewed by one eye is equivalent to that of the same stimulus viewed by both eyes [@Baker2007].

### 2024-04-18 manuscript.tex
Update to threshold criteria

@@
 
-\begin{equation}
-Stage1_L = \frac{C_L^m}{S + C_L + \omega C_R},
-\end{equation}
-
-\begin{equation}
-Stage1_R = \frac{C_R^m}{S + C_R + \omega C_L},
-\end{equation}
-
-\begin{equation}
-binsum = Stage1_L + Stage1_R,
-\end{equation}
-
-\begin{equation}
-Stage2 = \frac{binsum^p}{Z + binsum^q},
-\end{equation}
+\begin{equation}\protect\hypertarget{eq-s1l}{}{\mathrm{Stage1}_L = \frac{C_L^m}{S + C_L + \omega C_R},}\label{eq-s1l}\end{equation}
+
+\begin{equation}\protect\hypertarget{eq-s1r}{}{\mathrm{Stage1}_R = \frac{C_R^m}{S + C_R + \omega C_L},}\label{eq-s1r}\end{equation}
+
+\begin{equation}\protect\hypertarget{eq-binsum}{}{\mathrm{binsum} = \mathrm{Stage1}_L + \mathrm{Stage1}_R,}\label{eq-binsum}\end{equation}
+
+\begin{equation}\protect\hypertarget{eq-s2}{}{\mathrm{Stage2} = \frac{\mathrm{binsum}^p}{Z + \mathrm{binsum}^q},}\label{eq-s2}\end{equation}
 
@@
 
-\begin{equation}
-Stage2_{target+pedestal} - Stage2_{pedestal} = k,
-\end{equation}
-
-and d-prime for a single target level is defined as:
-
-\begin{equation}
-d' = \frac{Stage2_{target+pedestal} - Stage2_{pedestal}}{k}.
-\end{equation}
+\begin{equation}\protect\hypertarget{eq-thd}{}{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}} = k,}\label{eq-thd}\end{equation}
+
+and \(d'\) (d-prime) for a single target level is defined as:
+
+\begin{equation}\protect\hypertarget{eq-dprime}{}{d' = \frac{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}}}{k/0.954},}\label{eq-dprime}\end{equation}
+
+where the constant 0.954 reflects the value of \(d'\) at the 75\%
+correct point on the psychometric function used to estimate threshold.
 
@@
 
-\begin{equation}
-ACStage1_L = \frac{AC_L^m}{S + AC_L + \omega_A AC_R + \omega_R RG_R + \omega_B BY_R},
-\end{equation}
+\begin{equation}\protect\hypertarget{eq-s1multi}{}{^{AC}\mathrm{Stage1}_L = \frac{AC_L^m}{S + AC_L + \omega_A AC_R + \omega_R RG_R + \omega_B BY_R},}\label{eq-s1multi}\end{equation}
 
@@
 \textbf{Bayesian model} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
-Achromatic gratings & 7.12 & 5.79 & 1.27 & 0.65 & 0.07 & 0.99 & 0.31 & \\
-Red/green gratings & 5.25 & 3.60 & 1.23 & 1.27 & 0.03 & 1.05 & 0.20 & \\
-Blue/yellow gratings & 6.78 & 5.17 & 1.24 & 0.58 & 0.01 & 0.96 & 0.36 & \\
-Flickering discs & 7.21 & 5.75 & 1.25 & 0.69 & 0.13 & 0.88 & 0.26 & \\
+Achromatic gratings & 7.06 & 5.63 & 1.27 & 0.63 & 0.08 & 0.98 & 0.30 & \\
+Red/green gratings & 5.11 & 3.63 & 1.24 & 1.22 & 0.03 & 1.05 & 0.19 & \\
+Blue/yellow gratings & 6.78 & 5.34 & 1.24 & 0.61 & 0.01 & 0.95 & 0.34 & \\
+Flickering discs & 7.16 & 5.76 & 1.25 & 0.65 & 0.13 & 0.87 & 0.24 & \\
 \bottomrule
@@
 those of the other conditions. In previous work (Meese et al., 2006) the
-second stage gain control nonlinearity (Equation 4) does typically have
-quite substantial exponent values, which balance the relatively mild
-nonlinearity at the first stage, and produce a compressive transducer
-that results in contrast masking (the handle of the dipper). The high
-value of \emph{p} = 16.01 is therefore likely to be compensating for the
-low value of \emph{m} = 1.13 at stage one, but may well represent the
-combination of several successive stages of nonlinearity, and perhaps
-also other phenomena such as uncertainty (Pelli, 1985).
+second stage gain control nonlinearity (Equation~\ref{eq-s2}) does
+typically have quite substantial exponent values, which balance the
+relatively mild nonlinearity at the first stage, and produce a
+compressive transducer that results in contrast masking (the handle of
+the dipper). The high value of \emph{p} = 16.01 is therefore likely to
+be compensating for the low value of \emph{m} = 1.13 at stage one, but
+may well represent the combination of several successive stages of
+nonlinearity, and perhaps also other phenomena such as uncertainty
+(Pelli, 1985).
 
@@
 determined by the exponent at the first gain control stage (the \emph{m}
-parameter in Equations 1 \& 2). The summation ratio can be approximated
-by \(2^{1/m}\) (see Figure 9 of Baker et al., 2012), such that an
-exponent of \(m=1\) produces a ratio of 2, and an exponent of \(m = 2\)
-produces a ratio of \(\sqrt{2}\). Both the simplex and Bayesian model
-fits (see Table~\ref{tbl-parametertable}) generated parameter estimates
-in the range \(1 < m < 1.4\), consistent with the high levels of
-summation observed empirically.
+parameter in Equation~\ref{eq-s1l} and Equation~\ref{eq-s1r}). The
+summation ratio can be approximated by \(2^{1/m}\) (see Figure 9 of
+Baker et al., 2012), such that an exponent of \(m=1\) produces a ratio
+of 2, and an exponent of \(m = 2\) produces a ratio of \(\sqrt{2}\).
+Both the simplex and Bayesian model fits (see
+Table~\ref{tbl-parametertable}) generated parameter estimates in the
+range \(1 < m < 1.4\), consistent with the high levels of summation
+observed empirically.
 
@@
 The weight of interocular suppression is represented by the model
-parameter, \(\omega\) (Equations 1 \& 2). Posterior distributions of
-this parameter overlapped 1 for all of our dipper function data sets
-(see top right panel in Figure~\ref{fig-bayesianmodel}), indicating
-strong interocular suppression regardless of post-retinal pathway. The
-flickering disc stimuli produced a slightly lower suppression estimate,
-with \(\omega \sim 0.9\). This may indicate slightly weaker suppression
+parameter, \(\omega\) (Equation~\ref{eq-s1l} and Equation~\ref{eq-s1r}).
+Posterior distributions of this parameter overlapped 1 for all of our
+dipper function data sets (see top right panel in
+Figure~\ref{fig-bayesianmodel}), indicating strong interocular
+suppression regardless of post-retinal pathway. The flickering disc
+stimuli produced a slightly lower suppression estimate, with
+\(\omega \sim 0.9\). This may indicate slightly weaker suppression
 between the eyes for temporal modulations, but it is much less extreme
@@
 inhibitory fashion, exactly as proposed at stage 1 of the two-stage
-model (Equations 1 \& 2). In terms of perception, one consequence of
-this early suppression is to achieve `ocularity invariance', whereby the
-perceived contrast of a stimulus viewed by one eye is equivalent to that
-of the same stimulus viewed by both eyes (Baker et al., 2007). Similar
-processes of response invariance have also been reported using fMRI
-(Moradi \& Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).
+model (Equation~\ref{eq-s1l} and Equation~\ref{eq-s1r}). In terms of
+perception, one consequence of this early suppression is to achieve
+`ocularity invariance', whereby the perceived contrast of a stimulus
+viewed by one eye is equivalent to that of the same stimulus viewed by
+both eyes (Baker et al., 2007). Similar processes of response invariance
+have also been reported using fMRI (Moradi \& Heeger, 2009) and
+steady-state EEG (Baker \& Wade, 2017).
 

### 2024-04-19 manuscript.qmd
Various edits and fixes

@@
     keep-tex: true
+#   docx
+# prefer-html: true
 header-includes: 
@@
 
-if (processdata>0){
-
-getmodelresp3inputs <- function(p,La,Ra,Lr,Rr,Lb,Rb){
-
-  maxlength <- max(length(La),length(Ra),length(Lr),length(Rr),length(Lb),length(Rb))
-  resp <- matrix(0,nrow=3,ncol=maxlength)
-
-  LrespA <- (La^p[1,3])/(p[1,4] + La + p[1,6]*Ra + p[1,8]*Rr + p[1,9]*Rb)
-  RrespA <- (Ra^p[1,3])/(p[1,4] + Ra + p[1,6]*La + p[1,8]*Lr + p[1,9]*Lb)
-  LrespR <- (Lr^p[2,3])/(p[2,4] + Lr + p[2,8]*Ra + p[2,6]*Rr + p[2,9]*Rb)
-  RrespR <- (Rr^p[2,3])/(p[2,4] + Rr + p[2,8]*La + p[2,6]*Lr + p[2,9]*Lb)
-  LrespB <- (Lb^p[3,3])/(p[3,4] + Lb + p[3,8]*Ra + p[3,9]*Rr + p[3,6]*Rb)
-  RrespB <- (Rb^p[3,3])/(p[3,4] + Rb + p[3,8]*La + p[3,9]*Lr + p[3,6]*Lb)
-
-  bs <- LrespA + RrespA
-  resp[1,] <- (bs^p[1,1])/(p[1,5] + bs^p[1,2])
-
-  bs <- LrespR + RrespR
-  resp[2,] <- (bs^p[2,1])/(p[2,5] + bs^p[2,2])
-
-  bs <- LrespB + RrespB
-  resp[3,] <- (bs^p[3,1])/(p[3,5] + bs^p[3,2])
-
-  return(resp)}
-
-predictpmfs <- function(p){
-
-  contrastsC <- 10^(targetcontsdB/20)
-  pmfout <- matrix(0,nrow=12,ncol=length(contrastsC))
-
-  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,0)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[1,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,0)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[2,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,0)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
-  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[3,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,contrastsC,16,0,0,0,0)
-  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[4,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,0,16,contrastsC,0,0,0)
-  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[5,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,0,16,0,0,contrastsC,0)
-  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
-  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[6,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,contrastsC,0,0,16,0,0)
-  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
-  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[7,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,0,0,contrastsC,16,0,0)
-  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
-  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[8,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,0,0,0,16,contrastsC,0)
-  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
-  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[9,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,16)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
-  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[10,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,16)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
-  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[11,] <- 100*pnorm(dprime/sqrt(2))
-
-  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,16)
-  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
-  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
-  pmfout[12,] <- 100*pnorm(dprime/sqrt(2))
-
-  return(pmfout)}
-
 load('local/MCSdata.RData')
@@
 
+if (processdata>0){
+
+getmodelresp3inputs <- function(p,La,Ra,Lr,Rr,Lb,Rb){
+
+  maxlength <- max(length(La),length(Ra),length(Lr),length(Rr),length(Lb),length(Rb))
+  resp <- matrix(0,nrow=3,ncol=maxlength)
+
+  LrespA <- (La^p[1,3])/(p[1,4] + La + p[1,6]*Ra + p[1,8]*Rr + p[1,9]*Rb)
+  RrespA <- (Ra^p[1,3])/(p[1,4] + Ra + p[1,6]*La + p[1,8]*Lr + p[1,9]*Lb)
+  LrespR <- (Lr^p[2,3])/(p[2,4] + Lr + p[2,8]*Ra + p[2,6]*Rr + p[2,9]*Rb)
+  RrespR <- (Rr^p[2,3])/(p[2,4] + Rr + p[2,8]*La + p[2,6]*Lr + p[2,9]*Lb)
+  LrespB <- (Lb^p[3,3])/(p[3,4] + Lb + p[3,8]*Ra + p[3,9]*Rr + p[3,6]*Rb)
+  RrespB <- (Rb^p[3,3])/(p[3,4] + Rb + p[3,8]*La + p[3,9]*Lr + p[3,6]*Lb)
+
+  bs <- LrespA + RrespA
+  resp[1,] <- (bs^p[1,1])/(p[1,5] + bs^p[1,2])
+
+  bs <- LrespR + RrespR
+  resp[2,] <- (bs^p[2,1])/(p[2,5] + bs^p[2,2])
+
+  bs <- LrespB + RrespB
+  resp[3,] <- (bs^p[3,1])/(p[3,5] + bs^p[3,2])
+
+  return(resp)}
+
+predictpmfs <- function(p){
+
+  contrastsC <- 10^(targetcontsdB/20)
+  pmfout <- matrix(0,nrow=12,ncol=length(contrastsC))
+
+  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
+  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[1,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
+  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[2,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,0)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
+  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[3,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,contrastsC,16,0,0,0,0)
+  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
+  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[4,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,16,contrastsC,0,0,0)
+  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
+  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[5,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,16,0,0,contrastsC,0)
+  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
+  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[6,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,contrastsC,0,0,16,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
+  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[7,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,contrastsC,16,0,0)
+  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
+  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[8,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,0,16,contrastsC,0)
+  nr <- getmodelresp3inputs(p,0,0,0,16,0,0)
+  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[9,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,16)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
+  dprime <- (tr[1,] - nr[1,])/(p[1,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[10,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,16)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
+  dprime <- (tr[2,] - nr[2,])/(p[2,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[11,] <- 100*pnorm(dprime/sqrt(2))
+
+  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,16)
+  nr <- getmodelresp3inputs(p,0,0,0,0,0,16)
+  dprime <- (tr[3,] - nr[3,])/(p[3,7]/(qnorm(0.75)*sqrt(2)))
+  pmfout[12,] <- 100*pnorm(dprime/sqrt(2))
+
+  return(pmfout)}
+
   propcorr <- apply(MCSpropcorr,2:3,mean)
@@
 Our second experiment measured dichoptic masking within and between pathways using the method of constant stimuli.
-Masking was strongest within-pathway, and weakest between chromatic and achromatic mechanisms.
+Masking was strongest within-pathway, and weakest between blue/yellow and achromatic mechanisms.
 Finally, we repeated the dipper experiment using temporal luminance modulations, which produced slightly weaker interocular suppression than for spatially modulated stimuli.
 We interpret our results in the context of a contemporary two-stage model of binocular contrast gain control, implemented here using a hierarchical Bayesian framework.
-Posterior distributions of the weight of interocular suppression overlapped with a value of 1 for all dipper data sets, and the model captured well the pattern of threshold and slope values from all three experiments.
+Posterior distributions of the weight of interocular suppression overlapped with a value of 1 for all dipper data sets, and the model captured well the pattern of thresholds from all three experiments.
 
@@
 Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast to be detectable [@Legge1979; @Maehara2005; @Baker2007b].
-The characteristic pattern of dipper functions is well-described by the gain control model of @Meese2006 for achromatic stimuli.
+The characteristic pattern of dipper functions (right panel of @fig-exampledips) is well-described by the gain control model of @Meese2006 for achromatic stimuli.
 
@@
 In primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981].
-The blob regions appear to be largely monocular [@Livingstone1984], suggesting that binocular combination for chromatic stimuli might occur later than for achromatic stimuli, and perhaps be subject to different constraints.
+The blob regions appear to be largely monocular [@Livingstone1984], suggesting that binocular combination for chromatic stimuli might occur separately than for achromatic stimuli, and perhaps be subject to different constraints.
 
@@
 Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement.
-This is very different from the 'ocularity invariance' (where binocular and monocular stimuli appear equal) that is well-established when using DC-balanced periodic stimuli such as sine-wave gratings, and implies strong interocular suppression [@Meese2006; @Baker2017; @Moradi2009].
+This is very different from the 'ocularity invariance' (where binocular and monocular stimuli appear equal) that is well-established when using spatially modulated stimuli such as sine-wave gratings, and implies strong interocular suppression [@Meese2006; @Baker2017; @Moradi2009].
 There is additional psychophysical evidence from matching studies that binocular combination can be close to linear for luminance increments [@Levelt1965; @Anstis1998], particularly against a dark background [@Baker2012].
@@
 We also measured the spectral output of each phosphor using a Jaz spectroradiometer (Ocean Insight, Florida), and used these measurements to convert between LMS (cone) space and the monitor RGB coordinates.
-We express contrast values in normalized units, relative to the monocular threshold for each stimulus type.
+We express threshold and pedestal contrasts in normalized units, relative to the monocular detection threshold for each stimulus type.
+A threshold value of 2 therefore means that, relative to monocular detection, twice as much contrast was required to reach the same level of performance.
 
@@
 Participants used a trackball to dynamically adjust the colour angle of the stimulus to minimise the percept of flicker.
-Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli for the main experiment for that participant.
+Each participant completed ten such trials for each colour plane, and the average angle across repetition was taken as the isoluminant point, and used to generate stimuli in the main experiment for that participant.
 Settings were very similar across participants for the S-(L+M) direction, and  somewhat more heterogeneous for the L-M direction (see @fig-isofig).
@@
 Each block of the experiment tested a single pedestal contrast level and lasted around 12 minutes.
-On each trial the target contrast level was determined by a 3-down-1-up staircase procedure.
+The pedestal contrasts were 0, 0.5, 1, 2, 4, 8, 16 and 32% Michelson contrast for the achromatic stimulus, and 0, 1, 2, 4, 8, 16, 32 and 64% of the maximum available contrast for each chromatic stimulus.
+On each trial the target contrast level was determined by a 3-down-1-up staircase procedure, moving in logarithmic (3dB) steps.
 There were 8 interleaved staircases in total; four stimulus arrangements (see @fig-exampledips) combined factorially with two target eye assignments.
@@
 This left 9 free parameters: a $Z$ parameter for each mechanism, and six cross-mechanism weights of interocular suppression.
-These parameters were again estimated within a Bayesian hierarchical framework, using the trial-wise data from Experiment 2.
+These parameters were again estimated within a Bayesian hierarchical framework, using the binomial proportion correct data from Experiment 2.
 Note that the model as specified does not currently include monocular suppression between different pathways, as we did not collect any data for these conditions.
@@
 
-Following @Meese2006, we also inspected the slope of the psychometric function for each condition (see [@fig-dipperfig]d-f).
+Following @Meese2006, we also inspected the slope of the psychometric function for each condition (see [@fig-dipperfig]d-f), as this provides information about the effective gradient of the underlying contrast response function.
 At detection threshold, slopes were relatively steep for all stimuli, with values around $\beta=4$.
@@
 Panel (g) shows the average threshold elevation factor for each combination of target and mask stimulus.
-Panel (h) shows the geometric mean psychometric slope value for each masking condition in Weibull $\beta$ units.
-Contrast values are expressed relative to the target only threshold for each stimulus type.](Figures/MCSdata.pdf){#fig-MCSfig}
+Panel (h) shows the geometric mean psychometric slope value for each masking condition, expressed in Weibull $\beta$ units.
+Contrast values are normalized to the target only threshold for each stimulus type.](Figures/MCSdata.pdf){#fig-MCSfig}
 
@@
 Modal posterior parameter values (maximum a posteriori (MAP) estimates) are given in the lower rows of @tbl-parametertable.
-These correspond quite closely to the parameters from the simplex fitting and the original @Meese2006 parameters (reproduced in the first row of the table for reference).
-The panels in the right and upper margins of [@fig-bayesianmodel] show posterior distributions for each model parameter.
+These are in a similar range to the parameters from the simplex fitting and the original @Meese2006 parameters (reproduced in the first row of the table for reference).
+The panels along the right and upper margins of [@fig-bayesianmodel] show posterior distributions for each model parameter.
 Note in particular that the posterior distribution for the weight of interocular suppression ($\omega$, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data.
@@
 
-Finally we fitted an extended model, that included interocular suppression between the different pathways, to the data of Experiment 2.
+Finally we fitted an extended model, that included interocular suppression between the different pathways (see @eq-s1multi), to the data of Experiment 2.
 [@fig-MCSmodel] shows the model curves (panels a-c), which correspond closely to the data in [@fig-MCSfig].
@@
 The weakest suppression was between achromatic targets and masks and blue/yellow targets and masks, and the strongest suppression was between red/green targets and blue/yellow masks.
-Note that the weight parameter value of 1.21 for this condition is higher than that of the within-channel weights (values around 1), even though the within-channel conditions generate more threshold elevation.
+Note that the weight parameter value of $\omega$ = `r round(wRgB,digits=2)` for this condition is slightly higher than that of the within-channel weights (values around 1), even though the within-channel conditions generate more threshold elevation.
 In the model, high thresholds for within-channel dichoptic masks occur because the target and mask are summed together, which causes additional masking [see @Baker2013].
+However it is clear that the posterior distribution of the weight parameter is quite broad and overlaps 1, so this difference may not be meaningful.
 There do not appear to be any other salient patterns in the suppressive weight estimates.
@@
 Panels (a-c) show model psychometric functions in the same format as those in Figure 5.
-Panel (d) shows the fitted suppressive weights ($\omega$ values) estiamted by the model, and panel (e) shows the posterior distributions for each weight parameter.
+Panel (d) shows the fitted suppressive weights ($\omega$ values) estimated by the model, and panel (e) shows the posterior distributions for each weight parameter.
 The lower right plot gives the legends for the upper row (top) and the posterior distributions in panel (e).](Figures/MCSmodel.pdf){#fig-MCSmodel}
@@
 - Binocular combination of isoluminant chromatic stimuli is similar to that for achromatic stimuli
-- Interocular suppression is strongest within a post-retinal pathway, and weakest between achromatic and chromatic pathways
+- Interocular suppression is strongest within a post-retinal pathway, and weakest between the achromatic and blue/yellow pathways
 - Binocular combination occurs similarly for spatial and temporal luminance modulations
@@
 Posterior distributions of this parameter overlapped 1 for all of our dipper function data sets (see top right panel in [@fig-bayesianmodel]), indicating strong interocular suppression regardless of post-retinal pathway.
-The flickering disc stimuli produced a slightly lower suppression estimate, with $\omega \sim 0.9$.
+The flickering disc stimuli produced a slightly lower suppression estimate, with $\omega < 0.9$.
 This may indicate slightly weaker suppression between the eyes for temporal modulations, but it is much less extreme than our recent estimates using EEG and matching paradigms [@Segala2023].
@@
 
-In V1, chromatic stimuli are processed in 'blob' regions that are largely monocular as they fall within ocular dominance columns [@Livingstone1984].
-Since our psychophysical results indicate that interocular suppression is equally strong within chromatic and achromatic pathways, it may be that blob regions include interocular suppression.
-Presumably binocular summation of signals occurs at a later stage of processing for chromatic stimuli, but this does not lead to different perceptual outcomes.
-This physiological arrangement might also be responsible for the pattern of between-pathway interocular suppression (see [@fig-MCSfig]g).
-If blobs process signals from both the L-M and S-(L+M) pathways, their close physical proximity might explain the stronger suppression between the two chromatic pathways than between the chromatic and (more distant) achromatic pathways.
+In V1, the classical view is that chromatic stimuli are processed in 'blob' regions that are largely monocular as they fall within ocular dominance columns [@Livingstone1984].
+However more recent work has shown chromatic processing outside of the blobs [@Sincich2005], especially for stimuli with spatial structure [@Chatterjee2021].
+Since our psychophysical results indicate that interocular suppression is equally strong within chromatic and achromatic pathways, it may be that psychophysical performance indexes a common population of (non-blob) neurons for all of our stimuli.
+On the other hand, if blob regions include a subset of monocular neurons subject to interocular suppression [e.g.
+@Dougherty2019], this might be followed by binocular summation at a later stage of processing for chromatic stimuli, and potentially also for very low spatial frequency luminance modulations also processed in blobs [@Economides2011].
 
@@
 Here we provide estimates of interocular suppression within and between the three primary post-retinal visual pathways.
-These results show that binocular signal combination is similar within each pathway, but that interocular suppression is relatively weak between pathways.
+These results show that binocular signal combination is similar within each pathway, but that interocular suppression is typically weaker between pathways.
 Our findings could be applied when building models to predict perception of binocular images and movies, for example those generated by virtual and augmented reality systems, or in 3D cinema and television.

### 2024-04-19 manuscript.tex
Various edits and fixes

@@
 constant stimuli. Masking was strongest within-pathway, and weakest
-between chromatic and achromatic mechanisms. Finally, we repeated the
+between blue/yellow and achromatic mechanisms. Finally, we repeated the
 dipper experiment using temporal luminance modulations, which produced
@@
 weight of interocular suppression overlapped with a value of 1 for all
-dipper data sets, and the model captured well the pattern of threshold
-and slope values from all three experiments.
+dipper data sets, and the model captured well the pattern of thresholds
+from all three experiments.
 
@@
 contrast to be detectable (Baker \& Meese, 2007; Legge, 1979; Maehara \&
-Goryo, 2005). The characteristic pattern of dipper functions is
-well-described by the gain control model of Meese et al. (2006) for
-achromatic stimuli.
+Goryo, 2005). The characteristic pattern of dipper functions (right
+panel of Figure~\ref{fig-exampledips}) is well-described by the gain
+control model of Meese et al. (2006) for achromatic stimuli.
 
@@
 1984), suggesting that binocular combination for chromatic stimuli might
-occur later than for achromatic stimuli, and perhaps be subject to
+occur separately than for achromatic stimuli, and perhaps be subject to
 different constraints.
@@
 monocular stimuli appear equal) that is well-established when using
-DC-balanced periodic stimuli such as sine-wave gratings, and implies
+spatially modulated stimuli such as sine-wave gratings, and implies
 strong interocular suppression (Baker \& Wade, 2017; Meese et al., 2006;
@@
 Insight, Florida), and used these measurements to convert between LMS
-(cone) space and the monitor RGB coordinates. We express contrast values
-in normalized units, relative to the monocular threshold for each
-stimulus type.
+(cone) space and the monitor RGB coordinates. We express threshold and
+pedestal contrasts in normalized units, relative to the monocular
+detection threshold for each stimulus type. A threshold value of 2
+therefore means that, relative to monocular detection, twice as much
+contrast was required to reach the same level of performance.
 
@@
 across repetition was taken as the isoluminant point, and used to
-generate stimuli for the main experiment for that participant. Settings
+generate stimuli in the main experiment for that participant. Settings
 were very similar across participants for the S-(L+M) direction, and
@@
 experiment tested a single pedestal contrast level and lasted around 12
-minutes. On each trial the target contrast level was determined by a
-3-down-1-up staircase procedure. There were 8 interleaved staircases in
-total; four stimulus arrangements (see Figure~\ref{fig-exampledips})
-combined factorially with two target eye assignments. Each pedestal
-contrast was repeated 3 times by each participant, and the block order
-was randomised. The experiment lasted around 4 hours per participant for
-each chromatic condition, and took place over the course of several
-weeks. In total, the experiment consisted of 67978 trials (pooled across
-participants).
+minutes. The pedestal contrasts were 0, 0.5, 1, 2, 4, 8, 16 and 32\%
+Michelson contrast for the achromatic stimulus, and 0, 1, 2, 4, 8, 16,
+32 and 64\% of the maximum available contrast for each chromatic
+stimulus. On each trial the target contrast level was determined by a
+3-down-1-up staircase procedure, moving in logarithmic (3dB) steps.
+There were 8 interleaved staircases in total; four stimulus arrangements
+(see Figure~\ref{fig-exampledips}) combined factorially with two target
+eye assignments. Each pedestal contrast was repeated 3 times by each
+participant, and the block order was randomised. The experiment lasted
+around 4 hours per participant for each chromatic condition, and took
+place over the course of several weeks. In total, the experiment
+consisted of 67978 trials (pooled across participants).
 
@@
 \(Z\) are free parameters in the model. A further free parameter, \(k\),
-represents additive internal noise, and is used to convert the model
-outputs to either d-prime or threshold values (note that in the original
-model specification (Meese et al., 2006) this parameter was called
-\(\sigma\), but we use the \(k\) symbol here to avoid confusion with the
-standard deviation of the cumulative Gaussian used when fitting the
-psychometric functions to estimate thresholds). Thresholds are defined
-by iteratively adjusting the target contrast until the following
-equality is satisfied:
+is used to convert the model outputs to either d-prime or threshold
+values (note that in the original model specification (Meese et al.,
+2006) this parameter was called \(\sigma\), but we use the \(k\) symbol
+here to avoid confusion with the standard deviation of the cumulative
+Gaussian used when fitting the psychometric functions to estimate
+thresholds). Thresholds are defined by iteratively adjusting the target
+contrast until the following equality is satisfied:
 
@@
 
-\begin{equation}\protect\hypertarget{eq-dprime}{}{d' = \frac{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}}}{k/0.954},}\label{eq-dprime}\end{equation}
-
-where the constant 0.954 reflects the value of \(d'\) at the 75\%
-correct point on the psychometric function used to estimate threshold.
+\begin{equation}\protect\hypertarget{eq-dprime}{}{d' = \frac{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}}}{k/\tau},}\label{eq-dprime}\end{equation}
+
+where the parameter \(\tau\) reflects the value of \(d'\) at detection
+threshold. Defining threshold as the 75\% correct point on the
+psychometric function (as here) yields a value of
+\(\tau = \Phi^{-1}(0.75)\sqrt{2}\) = 0.954 (where \(\Phi^{-1}\) is the
+inverse cumulative normal density function). The combined denominator
+term (\(k/\tau\)) therefore represents internal additive noise in the
+model.
 
@@
 were again estimated within a Bayesian hierarchical framework, using the
-trial-wise data from Experiment 2. Note that the model as specified does
-not currently include monocular suppression between different pathways,
-as we did not collect any data for these conditions. Previous work (Chen
-et al., 2000) has measured such interactions, and they could in
-principle be incorporated into the denominator of either stage 1 or
-stage 2 in the model.
+binomial proportion correct data from Experiment 2. Note that the model
+as specified does not currently include monocular suppression between
+different pathways, as we did not collect any data for these conditions.
+Previous work (Chen et al., 2000) has measured such interactions, and
+they could in principle be incorporated into the denominator of either
+stage 1 or stage 2 in the model.
 
@@
 psychometric function for each condition (see
-Figure~\ref{fig-dipperfig}d-f). At detection threshold, slopes were
-relatively steep for all stimuli, with values around \(\beta=4\). As
-pedestal contrasts increased, slopes linearized and reduced to around
-\(\beta=1.3\) (Foley \& Legge, 1981; Meese et al., 2006), and remained
-shallow at high pedestal contrasts. The exception to this was the
-dichoptic condition, where slopes became extremely steep at high
-dichoptic mask contrasts, consistent with previous observations (Baker
-et al., 2013; Meese et al., 2006). This was clear for all three data
-sets, with slope values in the range \(4 < \beta < 8\). However, we
-observe that slope estimates are more variable than threshold estimates
-(note the large error bars), particularly when using adaptive
-staircases, which deploy most trials close to threshold. Our second
-experiment therefore investigated the slope of the psychometric function
-in more detail for dichoptic masking using the method of constant
-stimuli, as well as exploring dichoptic interactions between chromatic
-channels.
+Figure~\ref{fig-dipperfig}d-f), as this provides information about the
+effective gradient of the underlying contrast response function. At
+detection threshold, slopes were relatively steep for all stimuli, with
+values around \(\beta=4\). As pedestal contrasts increased, slopes
+linearized and reduced to around \(\beta=1.3\) (Foley \& Legge, 1981;
+Meese et al., 2006), and remained shallow at high pedestal contrasts.
+The exception to this was the dichoptic condition, where slopes became
+extremely steep at high dichoptic mask contrasts, consistent with
+previous observations (Baker et al., 2013; Meese et al., 2006). This was
+clear for all three data sets, with slope values in the range
+\(4 < \beta < 8\). However, we observe that slope estimates are more
+variable than threshold estimates (note the large error bars),
+particularly when using adaptive staircases, which deploy most trials
+close to threshold. Our second experiment therefore investigated the
+slope of the psychometric function in more detail for dichoptic masking
+using the method of constant stimuli, as well as exploring dichoptic
+interactions between chromatic channels.
 
@@
 for each combination of target and mask stimulus. Panel (h) shows the
-geometric mean psychometric slope value for each masking condition in
-Weibull \(\beta\) units. Contrast values are expressed relative to the
-target only threshold for each stimulus type.}
+geometric mean psychometric slope value for each masking condition,
+expressed in Weibull \(\beta\) units. Contrast values are normalized to
+the target only threshold for each stimulus type.}
 
@@
 values (maximum a posteriori (MAP) estimates) are given in the lower
-rows of Table~\ref{tbl-parametertable}. These correspond quite closely
-to the parameters from the simplex fitting and the original Meese et al.
+rows of Table~\ref{tbl-parametertable}. These are in a similar range to
+the parameters from the simplex fitting and the original Meese et al.
 (2006) parameters (reproduced in the first row of the table for
-reference). The panels in the right and upper margins of
+reference). The panels along the right and upper margins of
 Figure~\ref{fig-bayesianmodel} show posterior distributions for each
@@
 Finally we fitted an extended model, that included interocular
-suppression between the different pathways, to the data of Experiment 2.
+suppression between the different pathways (see
+Equation~\ref{eq-s1multi}), to the data of Experiment 2.
 Figure~\ref{fig-MCSmodel} shows the model curves (panels a-c), which
@@
 was between red/green targets and blue/yellow masks. Note that the
-weight parameter value of 1.21 for this condition is higher than that of
-the within-channel weights (values around 1), even though the
-within-channel conditions generate more threshold elevation. In the
-model, high thresholds for within-channel dichoptic masks occur because
-the target and mask are summed together, which causes additional masking
-(see Baker et al., 2013). There do not appear to be any other salient
-patterns in the suppressive weight estimates.
+weight parameter value of \(\omega\) = 1.11 for this condition is
+slightly higher than that of the within-channel weights (values around
+1), even though the within-channel conditions generate more threshold
+elevation. In the model, high thresholds for within-channel dichoptic
+masks occur because the target and mask are summed together, which
+causes additional masking (see Baker et al., 2013). However it is clear
+that the posterior distribution of the weight parameter is quite broad
+and overlaps 1, so this difference may not be meaningful. There do not
+appear to be any other salient patterns in the suppressive weight
+estimates.
 
@@
 format as those in Figure 5. Panel (d) shows the fitted suppressive
-weights (\(\omega\) values) estiamted by the model, and panel (e) shows
+weights (\(\omega\) values) estimated by the model, and panel (e) shows
 the posterior distributions for each weight parameter. The lower right
@@
   Interocular suppression is strongest within a post-retinal pathway,
-  and weakest between achromatic and chromatic pathways
+  and weakest between the achromatic and blue/yellow pathways
 \item
@@
 stimuli produced a slightly lower suppression estimate, with
-\(\omega \sim 0.9\). This may indicate slightly weaker suppression
-between the eyes for temporal modulations, but it is much less extreme
-than our recent estimates using EEG and matching paradigms (Segala et
-al., 2023). One difference between these studies is the luminance of the
-background, which was set to black for the experiments of Segala et al.
-(2023), but here was set at the mean luminance. Other studies using
-static luminance increments have also reported differences in the
-character of binocular combination that are attributable to background
-luminance (Baker et al., 2012), so this may explain the differences
-between studies. We also note that the weaker interocular suppression
-for flickering disc stimuli appears to be largely due to one participant
-(see Figure~\ref{fig-individualdiscs}c), so individual differences might
-also play a role. Future work should manipulate the background luminance
+\(\omega < 0.9\). This may indicate slightly weaker suppression between
+the eyes for temporal modulations, but it is much less extreme than our
+recent estimates using EEG and matching paradigms (Segala et al., 2023).
+One difference between these studies is the luminance of the background,
+which was set to black for the experiments of Segala et al. (2023), but
+here was set at the mean luminance. Other studies using static luminance
+increments have also reported differences in the character of binocular
+combination that are attributable to background luminance (Baker et al.,
+2012), so this may explain the differences between studies. We also note
+that the weaker interocular suppression for flickering disc stimuli
+appears to be largely due to one participant (see
+Figure~\ref{fig-individualdiscs}c), so individual differences might also
+play a role. Future work should manipulate the background luminance
 systematically to better understand how this modulates interocular
@@
 
-In V1, chromatic stimuli are processed in `blob' regions that are
-largely monocular as they fall within ocular dominance columns
-(Livingstone \& Hubel, 1984). Since our psychophysical results indicate
-that interocular suppression is equally strong within chromatic and
-achromatic pathways, it may be that blob regions include interocular
-suppression. Presumably binocular summation of signals occurs at a later
-stage of processing for chromatic stimuli, but this does not lead to
-different perceptual outcomes. This physiological arrangement might also
-be responsible for the pattern of between-pathway interocular
-suppression (see Figure~\ref{fig-MCSfig}g). If blobs process signals
-from both the L-M and S-(L+M) pathways, their close physical proximity
-might explain the stronger suppression between the two chromatic
-pathways than between the chromatic and (more distant) achromatic
-pathways.
+In V1, the classical view is that chromatic stimuli are processed in
+`blob' regions that are largely monocular as they fall within ocular
+dominance columns (Livingstone \& Hubel, 1984). However more recent work
+has shown chromatic processing outside of the blobs (Sincich \& Horton,
+2005), especially for stimuli with spatial structure (Chatterjee et al.,
+2021). Since our psychophysical results indicate that interocular
+suppression is equally strong within chromatic and achromatic pathways,
+it may be that psychophysical performance indexes a common population of
+(non-blob) neurons for all of our stimuli. On the other hand, if blob
+regions include a subset of monocular neurons subject to interocular
+suppression (e.g. Dougherty et al., 2019), this might be followed by
+binocular summation at a later stage of processing for chromatic
+stimuli, and potentially also for very low spatial frequency luminance
+modulations also processed in blobs (Economides et al., 2011).
 
@@
 binocular signal combination is similar within each pathway, but that
-interocular suppression is relatively weak between pathways. Our
+interocular suppression is typically weaker between pathways. Our
 findings could be applied when building models to predict perception of
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Chatterjee2021}{}}%
+Chatterjee, S., Ohki, K., \& Reid, R. C. (2021). Chromatic micromaps in
+primary visual cortex. \emph{Nat Commun}, \emph{12}(1), 2315.
+\url{https://doi.org/10.1038/s41467-021-22488-3}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Chen2000}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Sincich2005}{}}%
+Sincich, L. C., \& Horton, J. C. (2005). The circuitry of V1 and V2:
+Integration of color, form, and motion. \emph{Annu Rev Neurosci},
+\emph{28}, 303--326.
+\url{https://doi.org/10.1146/annurev.neuro.28.061604.135731}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%

### 2024-04-20 manuscript.qmd
Testing kbl instead of kable for table production

@@
 
-knitr::kable(tableparams, align='lrrrrrrrr', booktabs = TRUE, linesep='',escape = FALSE) %>%
+kableExtra::kbl(tableparams, align='lrrrrrrrr', booktabs = TRUE, linesep='',escape = FALSE) %>%
 row_spec(c(1,6),hline_after=T) %>% row_spec(0,italic=T) %>% row_spec(c(0,2,7),bold=T)

### 2024-07-16 manuscript.qmd
Revised in line with reviewer comments

@@
 header-includes: 
+  \usepackage{lineno} \linenumbers
   \usepackage{float} \floatplacement{figure}{H} 
@@
 if (processdata>0){
-  install_python(version="3.6")
-  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
-
-  # use_miniconda('r-reticulate')
+  # install_python(version="3.6")
+  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
+
+  use_miniconda('r-reticulate')
 
@@
 mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
-title(xlab="L", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(xlab=expression(paste(Delta,"L/L")), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab=expression(paste(Delta,"M/M")), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
 title(main='(a) L-M gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=2)
@@
 mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
-title(xlab="L+M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
-title(ylab="S", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(xlab=expression(paste(Delta,"L/L + ",Delta,"M/M")), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
+title(ylab=expression(paste(Delta,"S/S")), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
 title(main='(b) S-(L+M) gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=2)
@@
 
-  paneltitles <- c('(a) Achromatic thresholds','(b) Red/Green thresholds','(c) Blue/Yellow thresholds')
+  paneltitles <- c('(a) Achromatic thresholds','(b) L-M thresholds','(c) S-(L+M) thresholds')
   par(mfrow=c(2,3))
@@
 
-  paneltitles <- c('(d) Achromatic slopes','(e) Red/Green slopes','(f) Blue/Yellow slopes')
+  paneltitles <- c('(d) Achromatic slopes','(e) L-M slopes','(f) S-(L+M) slopes')
 
@@
   if (param==1){
-    legend(0,1,c('Achromatic','Red/green','Blue/yellow','Flicker'),fill=addalpha(concols1,alpha=0.25),border=concols2,box.lwd=2,cex=0.95)
-  }
-
-}
-
-paneltitles <- c('(a) Achromatic grating','(b) Red/green grating','(c) Blue/yellow grating','(d) Flickering disc')
+    legend(0,1,c('Achromatic','L-M','S-(L+M)','Flicker'),fill=addalpha(concols1,alpha=0.25),border=concols2,box.lwd=2,cex=0.95)
+  }
+
+}
+
+paneltitles <- c('(a) Achromatic grating','(b) L-M grating','(c) S-(L+M) grating','(d) Flickering disc')
 collist <- c('red','blue','orange','darkgreen')
@@
 
-titlelist <- c('(a) Achromatic target','(b) R/G target','(c) B/Y target','(d) Achromatic densities','(e) R/G densities','(f) B/Y densities','(g) Threshold elevation','(h) Psychometric slope')
+titlelist <- c('(a) Achromatic target','(b) L-M target','(c) S-(L+M) target','(d) Achromatic densities','(e) L-M densities','(f) S-(L+M) densities','(g) Threshold elevation','(h) Psychometric slope')
 
@@
 
-  legend(-2,40,c('Target only','Achromatic mask','R/G mask','B/Y mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)
+  legend(-2,40,c('Target only','Achromatic mask','L-M mask','S-(L+M) mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)
 
@@
 ticklocs <- seq(1,3)    # locations of tick marks on x axis
-ticklabels <- c('ACH','R/G','B/Y')
+ticklabels <- c('ACH','L-M','S-(L+M)')
 plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
@@
 mtext(text = ticklabels, side = 2, at=ticklocs, line=0.2, las=1) 
-title(xlab="Target", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
-title(ylab="Mask", col.lab=rgb(0,0,0), line=2.5, cex.lab=1.5)
+title(xlab="Target", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+title(ylab="Mask", col.lab=rgb(0,0,0), line=3, cex.lab=1.5)
 title(main=titlelist[7],cex.main=2)
@@
 mtext(text = ticklabels, side = 2, at=ticklocs, line=0.2, las=1) 
-title(xlab="Target", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
-title(ylab="Mask", col.lab=rgb(0,0,0), line=2.5, cex.lab=1.5)
+title(xlab="Target", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
+title(ylab="Mask", col.lab=rgb(0,0,0), line=3, cex.lab=1.5)
 title(main=titlelist[8],cex.main=2)
@@
 
-    if (c[i]==2) { // red/green detection condition
+    if (c[i]==2) { // L-M detection condition
     Lt = pow(TargetContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + (TargetContrast[i])) ;
@@
 
-    if (c[i]==3) { // blue/yellow detection condition
+    if (c[i]==3) { // S-(L+M) detection condition
     Lt = pow(TargetContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4],"  + (TargetContrast[i])) ;
@@
 
-    if (c[i]==5) { // red/green target, achromatic mask
+    if (c[i]==5) { // L-M target, achromatic mask
       Lt = pow(TargetContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + TargetContrast[i] + wRgA[s[i]]*PedestalContrast[i]) ;
@@
 
-    if (c[i]==6) { // blue/yellow target, achromatic mask
+    if (c[i]==6) { // S-(L+M) target, achromatic mask
       Lt = pow(TargetContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4]," + TargetContrast[i] + wByA[s[i]]*PedestalContrast[i]) ;
@@
 
-    if (c[i]==7) { // achromatic target, red/green mask
+    if (c[i]==7) { // achromatic target, L-M mask
       Lt = pow(TargetContrast[i],",allstanparams[1,3],") / (",allstanparams[1,4]," + TargetContrast[i] + wAcR[s[i]]*PedestalContrast[i]) ;
@@
 
-    if (c[i]==8) { // red/green target, red/green mask
+    if (c[i]==8) { // L-M target, L-M mask
       Lt = pow(TargetContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + TargetContrast[i] + ",allstanparams[2,6],"*PedestalContrast[i]) ;
@@
 
-    if (c[i]==9) { // blue/yellow target, red/green mask
+    if (c[i]==9) { // S-(L+M) target, L-M mask
       Lt = pow(TargetContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4]," + TargetContrast[i] + wByR[s[i]]*PedestalContrast[i]) ;
@@
 
-     if (c[i]==10) { // achromatic target, blue/yellow mask
+     if (c[i]==10) { // achromatic target, S-(L+M) mask
       Lt = pow(TargetContrast[i],",allstanparams[1,3],") / (",allstanparams[1,4]," + TargetContrast[i] + wAcB[s[i]]*PedestalContrast[i]) ;
@@
 
-    if (c[i]==11) { // red/green target, blue/yellow mask
+    if (c[i]==11) { // L-M target, S-(L+M) mask
       Lt = pow(TargetContrast[i],",allstanparams[2,3],") / (",allstanparams[2,4]," + TargetContrast[i] + wRgB[s[i]]*PedestalContrast[i]) ;
@@
 
-    if (c[i]==12) { // blue/yellow target, blue/yellow mask
+    if (c[i]==12) { // S-(L+M) target, S-(L+M) mask
       Lt = pow(TargetContrast[i],",allstanparams[3,3],") / (",allstanparams[3,4]," + TargetContrast[i] + ",allstanparams[3,6],"*PedestalContrast[i]) ;
@@
 
-  titlelist <- c('(a) Achromatic target','(b) R/G target','(c) B/Y target')
+  titlelist <- c('(a) Achromatic target','(b) L-M target','(c) S-(L+M) target')
 
@@
 
-    # legend(-2,40,c('Target only','Achromatic mask','R/G mask','B/Y mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)
+    # legend(-2,40,c('Target only','Achromatic mask','L-M mask','S-(L+M) mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)
 
@@
   ticklocs <- seq(1,3)    # locations of tick marks on x axis
-  ticklabels <- c('ACH','R/G','B/Y')
+  ticklabels <- c('ACH','L-M','S-(L+M)')
   plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
@@
 
-  legend(0,1,c('Target only','Achromatic mask','R/G mask','B/Y mask'), lwd=3, col=c('black','black','red','cornflowerblue'),cex=1.9,box.lwd=2)
-
-  legend(0,1,c('Target only','Achromatic mask','R/G mask','B/Y mask'), lty=2, lwd=3, col=c('black','white','green','gold'),cex=1.9,box.lwd=2)
-
-  legend(0.05,0.5,c('Ach target, R/G mask','Ach target, B/Y mask','R/G target, Ach mask','R/G target, B/Y mask','B/Y target, Ach mask','B/Y target, R/G mask'), lwd=3, pch=22, col=c('black','black','red','red','cornflowerblue','cornflowerblue'),pt.bg=addalpha(c('red','cornflowerblue','black','cornflowerblue','black','red'),alpha=0.5),lty=NA,pt.cex=2,cex=1.5,box.lwd=2)
+  legend(0,1,c('Target only','Achromatic mask','L-M mask','S-(L+M) mask'), lwd=3, col=c('black','black','red','cornflowerblue'),cex=1.9,box.lwd=2)
+
+  legend(0,1,c('Target only','Achromatic mask','L-M mask','S-(L+M) mask'), lty=2, lwd=3, col=c('black','white','green','gold'),cex=1.9,box.lwd=2)
+
+  legend(0.05,0.5,c('Ach target, L-M mask','Ach target, S-(L+M) mask','L-M target, Ach mask','L-M target, S-(L+M) mask','S-(L+M) target, Ach mask','S-(L+M) target, L-M mask'), lwd=3, pch=22, col=c('black','black','red','red','cornflowerblue','cornflowerblue'),pt.bg=addalpha(c('red','cornflowerblue','black','cornflowerblue','black','red'),alpha=0.5),lty=NA,pt.cex=2,cex=1.5,box.lwd=2)
 
@@
 text(0.5,2.8,'Achromatic grating',adj=0.5,cex=1.5)
-text(2,2.8,'Red/green grating',adj=0.5,cex=1.5)
-text(3.5,2.8,'Blue/yellow grating',adj=0.5,cex=1.5)
+text(2,2.8,'L-M grating',adj=0.5,cex=1.5)
+text(3.5,2.8,'S-(L+M) grating',adj=0.5,cex=1.5)
 text(3,1.8,'Flickering disc (4Hz)',adj=0.5,cex=1.5)
@@
 title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
-title(main=paste0('(',letters[(3*(p-1)+2)],')  P',p,': Red/Green'),cex.main=2)
+title(main=paste0('(',letters[(3*(p-1)+2)],')  P',p,': L-M'),cex.main=2)
 axis.break(axis=1,breakpos=-18)
@@
 title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
-title(main=paste0('(',letters[(3*(p-1)+3)],')  P',p,': Blue/Yellow'),cex.main=2)
+title(main=paste0('(',letters[(3*(p-1)+3)],')  P',p,': S-(L+M)'),cex.main=2)
 axis.break(axis=1,breakpos=-18)
@@
 
-titlelist <- c('(a)  P1: Achromatic target','(b)  P1: R/G target','(c)  P1: B/Y target','(d)  P4: Achromatic target','(e)  P4: R/G target','(f)  P4: B/Y target','(g)  P5: Achromatic target','(h)  P5: R/G target','(i)  P5: B/Y target')
+titlelist <- c('(a)  P1: Achromatic target','(b)  P1: L-M target','(c)  P1: S-(L+M) target','(d)  P4: Achromatic target','(e)  P4: L-M target','(f)  P4: S-(L+M) target','(g)  P5: Achromatic target','(h)  P5: L-M target','(i)  P5: S-(L+M) target')
 
@@
 
-if (p==1 & cond==1){legend(-2,40,c('Target only','Achromatic mask','R/G mask','B/Y mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)}
+if (p==1 & cond==1){legend(-2,40,c('Target only','Achromatic mask','L-M mask','S-(L+M) mask'), pch=21, col=c('black','black','red','cornflowerblue'),pt.cex=2,cex=1.5,pt.lwd=3,pt.bg=c('black','white','green','gold'),box.lwd=2)}
 
@@
 However, most of this work has involved achromatic (black and white) stimuli, and it is not clear if the same processes apply in colour-sensitive pathways.
-In our first experiment, we measured contrast discrimination ('dipper') functions for four key ocular configurations (monocular, binocular, half-binocular and dichoptic), for achromatic, isoluminant red/green and isoluminant blue/yellow sine-wave grating stimuli.
+In our first experiment, we measured contrast discrimination ('dipper') functions for four key ocular configurations (monocular, binocular, half-binocular and dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M) sine-wave grating stimuli.
 We find a similar pattern of results across stimuli, implying equivalently strong interocular suppression within each pathway.
 Our second experiment measured dichoptic masking within and between pathways using the method of constant stimuli.
-Masking was strongest within-pathway, and weakest between blue/yellow and achromatic mechanisms.
+Masking was strongest within-pathway, and weakest between S-(L+M) and achromatic mechanisms.
 Finally, we repeated the dipper experiment using temporal luminance modulations, which produced slightly weaker interocular suppression than for spatially modulated stimuli.
@@
 
-The process by which the brain combines independent inputs is of fundamental importance for understanding sensory perception.
-Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains typically combine the inputs from the left and right eyes to provide binocular single vision.
+The process by which the brain combines independent inputs is of fundamental importance for understanding sensory perception [@Ernst2002; @Baker2017].
+Binocular vision is a useful test-case for determining the general principles involved in neural signal combination, as our brains typically combine the inputs from the left and right eyes to provide binocular single vision [@Read2021].
 In recent years our understanding has been facilitated by the development of binocular gain control models that provide a framework to interpret empirical data from multiple experimental paradigms and techniques, including psychophysics [@Meese2006], EEG [@Baker2017], fMRI [@Moradi2009] and pupillometry [@Segala2023].
@@
 In the monocular condition, participants must discriminate between stimuli of two contrasts (a 'pedestal', and a 'pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance.
-Threshold is defined as the minimum target contrast required to make this judgement with 75% accuracy.
+Threshold is defined as the minimum target contrast required to make this judgement with 75% accuracy; this reduces at pedestal contrasts around threshold (facilitation), and increases at high pedestal contrasts (masking).
 The binocular condition is the same, except that the stimuli are shown to both eyes.
@@
 The pedestal is always binocular in this condition, whereas the target increment is monocular, and thresholds are consistently higher than in the binocular condition across the full range of pedestal contrasts.
-This demonstrates that binocular summation occurs across the full contrast range, when the pedestal ocularity is appropriately controlled.
+This demonstrates that binocular summation occurs across the entire contrast range, when the pedestal ocularity is appropriately controlled.
 Finally, the dichoptic condition produces extremely strong masking of the target, such that when the pedestal is visible, the target must equal or exceed its contrast to be detectable [@Legge1979; @Maehara2005; @Baker2007b].
@@
 At isoluminance, where (L+M) is held constant, this channel is driven purely by the S-cone outputs.
-
-There has not yet been a detailed investigation of binocular contrast discrimination in either of these chromatic pathways, however there is reason to believe they may differ from the achromatic pathway.
+Within each chromatic pathway, contrast discrimination functions are similar to those for achromatic vision, showing evidence of facilitation at low pedestal contrasts and masking at high pedestal contrasts [@Switkes1988; @Chen2000].
+There are also interactions between luminance and colour mechanisms, which are able to mask each other [@Switkes1988; @Mullen1994; @Chen2000], and under some circumstances also show cross-pathway facilitation [@Switkes1988; @Cole1990; @Mullen1994; @Shooner2020].
+
+There has not yet been a detailed investigation of binocular contrast interactions in either chromatic pathway, however there are reasons to believe they may differ from the achromatic pathway.
 At detection threshold, binocular summation is greater for chromatic versus achromatic stimuli [@Simmons2005], implying a more linear initial stage of processing.
-For cross-orientation masking, there are differences in the magnitude of masking between chromatic (red/green) and achromatic stimuli [@Kim2013; @Medina2009], as well as differences in their temporal dynamics [@Kim2015].
-There are also interactions between chromatic and achromatic pathways both within [@Chen2000] and between [@Mullen2014; @Kingdom2015] the eyes, yet these have not been fully explored for arrangements where the target and mask have the same orientation.
-Finally, the neurophysiological underpinnings of colour vision are distinct from those of the achromatic system.
-In primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981].
-The blob regions appear to be largely monocular [@Livingstone1984], suggesting that binocular combination for chromatic stimuli might occur separately than for achromatic stimuli, and perhaps be subject to different constraints.
-
-A further property of 'blob' regions is that they are less strongly orientation-tuned than other regions of V1 [@Horton1981; @Livingstone1984], and biased towards low spatial frequencies [@Edwards1995; @Tootell1988; though see @Economides2011].
+For cross-orientation masking, there are differences in the magnitude of masking between chromatic (L-M) and achromatic stimuli [@Kim2013; @Medina2009], as well as differences in their temporal dynamics [@Kim2015].
+There are also binocular interactions between chromatic and achromatic pathways [@Mullen2014; @Kingdom2015], yet these have not been fully explored for arrangements where the target and mask have the same orientation.
+Finally, the neurophysiological underpinnings of colour vision may be distinct from those of the achromatic system.
+The classical view is that in primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981], and are largely monocular [@Livingstone1984].
+However subsequent work has revealed a more complex arrangement, making such a clear-cut phyisological distinction unlikely [for a review, see @Shapley2011].
+Nevertheless, the physiological segregation between pathways at the output of the retina could still lead to differences in the way signals are combined across the eyes.
+
+The spatiotemporal profile of stimuli also appears to impact their binocular combination.
+For example, matching studies indicate that binocular combination can be close to linear for luminance increments [@Levelt1965; @Anstis1998], particularly against a dark background [@Baker2012].
+This is quite different from the 'ocularity invariance' (where binocular and monocular stimuli appear equal) that is well-established when using spatially modulated stimuli such as sine-wave gratings, and implies strong interocular suppression [@Meese2006; @Baker2017; @Moradi2009].
 Our recent work [@Segala2023] has investigated binocular combination for flickering discs of luminance, which are DC-balanced across time (i.e.
 the time-averaged luminance is equal to the background).
-Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement.
-This is very different from the 'ocularity invariance' (where binocular and monocular stimuli appear equal) that is well-established when using spatially modulated stimuli such as sine-wave gratings, and implies strong interocular suppression [@Meese2006; @Baker2017; @Moradi2009].
-There is additional psychophysical evidence from matching studies that binocular combination can be close to linear for luminance increments [@Levelt1965; @Anstis1998], particularly against a dark background [@Baker2012].
-Both structural and functional data therefore imply that binocular combination may differ between spatial and temporal contrast.
+Steady-state EEG responses from early visual cortex and psychophysical contrast matching data were both consistent with weak interocular suppression when using this stimulus arrangement, but it is currently unclear whether this has implications for contrast discrimination performance.
 
@@
 We therefore preregistered a series of psychophysical experiments (see: [https://osf.io/3vdga/](https://osf.io/3vdga/)).
-In Experiment 1 we replicate the four key pedestal masking conditions of @Meese2006 described above for achromatic grating stimuli and extend this to both red/green and blue/yellow isoluminant chromatic stimuli.
+In Experiment 1 we replicate the four key pedestal masking conditions of @Meese2006 described above for achromatic grating stimuli and extend this to both L-M and S-(L+M) isoluminant chromatic stimuli.
 In Experiment 2 we explore dichoptic masking within and between these stimuli.
@@
 Written informed consent was obtained before data collection began, and all procedures were approved by the ethics committee of the Department of Psychology at the University of York (ID number 2202).
+The study conformed to the tenets of the Declaration of Helsinki.
 
@@
 In the achromatic conditions, the sine-wave modulated all three monitor colour channels equally (red, green and blue).
-In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant.
-In the S-(L+M) condition, the isoluminant stimuli maximised S-cone contrast.
+In the L-M condition, we generated isoluminant stimuli for each participant (see Procedures) designed to maximise contrast between L and M cones, whilst keeping S cone activity constant [more accurately, this is a $\Delta L/L - \Delta M/M$ condition, see @Cole1993].
+In the S-(L+M) condition (or more accurately the $\Delta S/S - (\Delta L/L + \Delta M/M)$ condition), the isoluminant stimuli maximised S-cone contrast.
 Stimuli were converted from cone space to monitor RGB coordinates using the monitor spectral readings and the Stockman-Sharpe 2 degree cone fundamentals [@Stockman2000].
@@
 ![Isoluminance settings from all participants in Experiments 1 and 2.
-Panel (a) shows red/green and panel (b) shows blue/yellow settings that were subsequently used to generate stimuli in the main experiments.
+Panel (a) shows L-M and panel (b) shows S-(L+M) settings that were subsequently used to generate stimuli in the main experiments.
 Within each panel, solid lines show the mean settings for each participant, and black curves show the range of possible stimuli displayed during the adjustment task.](Figures/isosettings.pdf){#fig-isofig}
@@
 The stimuli and trial protocol were the same as for Experiment 1, except that the target contrast was chosen from a set of 10 possible values, determined in advance based on the data of Experiment 1.
-There were 12 possible conditions: baseline detection thresholds for achromatic, red/green and blue/yellow stimuli, and the nine possible factorial pairings obtained by assigning these conditions to be target and dichoptic mask stimuli.
+There were 12 possible conditions: baseline detection thresholds for achromatic, L-M and S-(L+M) stimuli, and the nine possible factorial pairings obtained by assigning these conditions to be target and dichoptic mask stimuli.
 Mask contrasts were chosen to be approximately 16 times their (monocular) detection threshold, based on the data from Experiment 1.
@@
 
-We also implemented a Bayesian hierarchical version of the model using the Stan language [@Carpenter2017].
+We also implemented a Bayesian hierarchical version of the model using the Stan probabilistic programming language [@Carpenter2017].
 This used a binomial generator function to model the proportion correct data at each target level, and was fit simultaneously to all participants for a given experiment, but separately for each chromatic condition of Experiment 1, and the flickering disc data from Experiment 3 (i.e.
@@
 
-Finally, we adapted the two stage model to include parallel pathways to process achromatic, red/green and blue/yellow stimuli, that mutually suppress each other.
+Finally, we adapted the two stage model to include parallel pathways to process achromatic, L-M and S-(L+M) stimuli, that mutually suppress each other.
 We added additional suppressive terms at the first (monocular) stage of the model, for example:
@@
 
-where *AC* represents the achromatic contrast, *RG* represents the red/green contrast, *BY* represents the blue/yellow contrast, and $\omega_A$, $\omega_R$ and $\omega_B$ are the accompanying weights of interocular suppression.
+where *AC* represents the achromatic contrast, *RG* represents the L-M contrast, *BY* represents the S-(L+M) contrast, and $\omega_A$, $\omega_R$ and $\omega_B$ are the accompanying weights of interocular suppression.
 There is an equivalent expression for the right eye, and for each of the two isoluminant chromatic pathways.
@@
 Note that the model as specified does not currently include monocular suppression between different pathways, as we did not collect any data for these conditions.
-Previous work [@Chen2000] has measured such interactions, and they could in principle be incorporated into the denominator of either stage 1 or stage 2 in the model.
+Previous work [e.g.
+@Chen2000; @Mullen1994] has measured such interactions, and they could in principle be incorporated into the denominator of either stage 1 or stage 2 in the model.
 
@@
 All experimental code, raw data and analysis scripts are available at: https://osf.io/3vdga/.
-The linked GitHub repository also contains a fully reproducible version of the manuscript.
+The linked GitHub repository also contains a fully computationally reproducible version of the manuscript.
 Note that we deviated slightly from the planned preregistration, in that we did not collect data for chromatic flickering discs, or for the cross-pathway dichoptic experiment using disc stimuli.
@@
 
-A similar pattern of results was observed for both the red/green and blue/yellow isoluminant stimuli (see [@fig-dipperfig]b,c).
-Summation at threshold was a factor of `r round(10^(summation[2]/20),digits=2)` (`r round(summation[2],digits=2)`dB) for the red/green targets, and a factor of `r round(10^(summation[3]/20),digits=2)` (`r round(summation[3],digits=2)`dB) for the blue/yellow targets, and so was marginally higher than for achromatic stimuli.
-The general character of the dipper functions was largely consistent with the achromatic results, though we observed shallower facilitation and weaker masking, especially for the blue/yellow stimuli.
-For example, the strongest facilitation in the binocular condition for achromatic stimuli was a factor of `r round(10^((meanthresh[1,2,1]-meanthresh[1,2,3])/20),digits=2)`, whereas it reduced to a factor of `r round(10^((meanthresh[2,2,1]-meanthresh[2,2,3])/20),digits=2)` for red/green stimuli and `r round(10^((meanthresh[3,2,1]-meanthresh[3,2,3])/20),digits=2)` for blue/yellow stimuli.
-The slope of the binocular dipper handle was `r round(binregACH$coefficients[2], digits=2)` for achromatic stimuli, `r round(binregRG$coefficients[2], digits=2)` for red/green stimuli, and `r round(binregBY$coefficients[2], digits=2)` for blue/yellow stimuli.
-Dichoptic masking remained as strong for the chromatic conditions as for the achromatic stimuli (regression slopes of `r round(dichregRG$coefficients[2], digits=2)` for red/green and `r round(dichregBY$coefficients[2], digits=2)` for blue/yellow).
+A similar pattern of results was observed for both the L-M and S-(L+M) isoluminant stimuli (see [@fig-dipperfig]b,c).
+Summation at threshold was a factor of `r round(10^(summation[2]/20),digits=2)` (`r round(summation[2],digits=2)`dB) for the L-M targets, and a factor of `r round(10^(summation[3]/20),digits=2)` (`r round(summation[3],digits=2)`dB) for the S-(L+M) targets, and so was marginally higher than for achromatic stimuli.
+The general character of the dipper functions was largely consistent with the achromatic results, though we observed shallower facilitation and weaker masking, especially for the S-(L+M) stimuli.
+For example, the strongest facilitation in the binocular condition for achromatic stimuli was a factor of `r round(10^((meanthresh[1,2,1]-meanthresh[1,2,3])/20),digits=2)`, whereas it reduced to a factor of `r round(10^((meanthresh[2,2,1]-meanthresh[2,2,3])/20),digits=2)` for L-M stimuli and `r round(10^((meanthresh[3,2,1]-meanthresh[3,2,3])/20),digits=2)` for S-(L+M) stimuli.
+The slope of the binocular dipper handle was `r round(binregACH$coefficients[2], digits=2)` for achromatic stimuli, `r round(binregRG$coefficients[2], digits=2)` for L-M stimuli, and `r round(binregBY$coefficients[2], digits=2)` for S-(L+M) stimuli.
+Dichoptic masking remained as strong for the chromatic conditions as for the achromatic stimuli (regression slopes of `r round(dichregRG$coefficients[2], digits=2)` for L-M and `r round(dichregBY$coefficients[2], digits=2)` for S-(L+M)).
 The pattern of results for individual participants was consistent with the group averages, as shown in [@fig-individualdippers].
@@
 
-Threshold elevation was greatest when the target and mask had the same chromaticity - notice that the psychometric function is shifted furthest to the right for the achromatic target with an achromatic mask (white and black circles in [@fig-MCSfig]a), for the red/green target with a red/green mask (red and green circles in [@fig-MCSfig]b), and for the blue/yellow target with a blue/yellow mask (blue and yellow circles in [@fig-MCSfig]c).
+Threshold elevation was greatest when the target and mask had the same chromaticity - notice that the psychometric function is shifted furthest to the right for the achromatic target with an achromatic mask (white and black circles in [@fig-MCSfig]a), for the L-M target with an L-M mask (red and green circles in [@fig-MCSfig]b), and for the S-(L+M) target with a S-(L+M) mask (blue and yellow circles in [@fig-MCSfig]c).
 Masking was weakest between achromatic masks/targets and chromatic masks/targets.
-Finally, there was an intermediate level of masking between red/green and blue/yellow stimuli.
+Finally, there was an intermediate level of masking between L-M and S-(L+M) stimuli.
 This is summarised in [@fig-MCSfig]g, which represents threshold elevation for each combination of target and mask chromaticity.
@@
 tableparams$Model <- c('Meese et al.
-(2006)','Simplex fits','Achromatic gratings','Red/green gratings','Blue/yellow gratings','Flickering discs','Bayesian model','Achromatic gratings','Red/green gratings','Blue/yellow gratings','Flickering discs')
+(2006)','Simplex fits','Achromatic gratings','L-M gratings','S-(L+M) gratings','Flickering discs','Bayesian model','Achromatic gratings','L-M gratings','S-(L+M) gratings','Flickering discs')
 
@@
 Here we allowed it to vary, but it still received a value very close to 1 in all of our grating conditions, and slightly below 1 (`r round(allp[4,6],digits=2)`) for our flickering discs.
-The exponent values (*p* and *q*) for the blue/yellow gratings are rather different from those of the other conditions.
+The exponent values (*p* and *q*) for the S-(L+M) gratings are rather different from those of the other conditions.
 In previous work [@Meese2006] the second stage gain control nonlinearity (@eq-s2) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper).
@@
 [@fig-MCSmodel]d,e shows the model estimates for the weight of interocular suppression in each combination of target and mask chromaticity.
-The weakest suppression was between achromatic targets and masks and blue/yellow targets and masks, and the strongest suppression was between red/green targets and blue/yellow masks.
+The weakest suppression was between achromatic targets and masks and S-(L+M) targets and masks, and the strongest suppression was between L-M targets and S-(L+M) masks.
 Note that the weight parameter value of $\omega$ = `r round(wRgB,digits=2)` for this condition is slightly higher than that of the within-channel weights (values around 1), even though the within-channel conditions generate more threshold elevation.
@@
 - Binocular combination of isoluminant chromatic stimuli is similar to that for achromatic stimuli
-- Interocular suppression is strongest within a post-retinal pathway, and weakest between the achromatic and blue/yellow pathways
+- Interocular suppression is strongest within a post-retinal pathway, and weakest between the achromatic and S-(L+M) pathways
 - Binocular combination occurs similarly for spatial and temporal luminance modulations
@@
 Both the simplex and Bayesian model fits (see @tbl-parametertable) generated parameter estimates in the range $1 < m < 1.4$, consistent with the high levels of summation observed empirically.
+Note that the exponents at stage 2 ($p$ and $q$) have no effect on binocular summation at threshold, because they impact after the signals have been combined.
+The differences in these parameter values between chromatic conditions (see @tbl-parametertable) primarily reflects differences in the slope of the dipper handle (chromatic conditions are shallower), and are of incidental interest for our main questions.
 
@@
 
+Strong interocular suppression is responsible for the convergence of monocular and binocular dipper handles [e.g.
+@Legge1984] at high pedestal contrasts (see @fig-dipperfig).
+In the model, monocular stimuli avoid the impact of interocular suppression, because the unstimulated eye sees a blank screen, and so contributes a contrast of zero to the denominator of the stimulated eye.
+Binocular stimuli receive strong suppression, which acts to approximately halve the excitation when contrasts in the two eyes are equal [see @Georgeson2016; @Meese2006].
+This normalization leads to very similar responses for monocular and binocular stimulation.
+In the auditory system, binaural combination of amplitude modulated signals involves much weaker suppression between channels, and the monaural and binaural dipper handles do not converge at high contrasts [@Baker2020].
+
+One phenomenon that often occurs with conflicting dichoptic stimuli is binocular rivalry, and it is worth considering how this might impact the results of Experiment 2, where the two eyes often saw stimuli of different chromaticities.
+However rivalry typically only ‘kicks in’ at presentation durations longer than the 200ms used here [see e.g.
+@Wolfe1983], and certainly rivalry alternations need much longer presentations to be clearly observed.
+In a dichoptic masking paradigm it is often difficult to distinguish dichoptic fusion from dominance of one eye over the other; indeed, interocular suppression of sufficient strength would render the weaker stimulus invisible.
+On the other hand, if the stimuli appear fused, we might expect dichoptic colour mixing to occur [@Kingdom2015; @Kingdom2015b], whereas if one eye dominates the colour percept would be equivalent to monocular presentation of the dominant stimulus.
+Here we used a performance task (2AFC detection/discrimination), and did not explicitly ask participants about the stimulus appearance.
+Future studies could use matching and adjustment tasks to investigate this further.
+
 ## Psychometric slopes

### 2024-07-16 manuscript.tex
Testing kbl instead of kable for table production
Revised in line with reviewer comments

@@
 \makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \KOMAoption{captions}{tableheading}
-\usepackage{float} \floatplacement{figure}{H} \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
-\makeatletter
-\makeatother
-\makeatletter
-\makeatother
+\usepackage{lineno} \linenumbers \usepackage{float} \floatplacement{figure}{H} \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
 \makeatletter
@@
 \makeatletter
+\makeatother
+\makeatletter
 \@ifpackageloaded{caption}{}{\usepackage{caption}}
 \@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\makeatletter
 \makeatother
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
+
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \maketitle
+
 \(^1\)Department of Psychology, University of York, UK\\
@@
 
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
+\section{Abstract}\label{abstract}
 
@@
 ocular configurations (monocular, binocular, half-binocular and
-dichoptic), for achromatic, isoluminant red/green and isoluminant
-blue/yellow sine-wave grating stimuli. We find a similar pattern of
-results across stimuli, implying equivalently strong interocular
-suppression within each pathway. Our second experiment measured
-dichoptic masking within and between pathways using the method of
-constant stimuli. Masking was strongest within-pathway, and weakest
-between blue/yellow and achromatic mechanisms. Finally, we repeated the
-dipper experiment using temporal luminance modulations, which produced
-slightly weaker interocular suppression than for spatially modulated
-stimuli. We interpret our results in the context of a contemporary
-two-stage model of binocular contrast gain control, implemented here
-using a hierarchical Bayesian framework. Posterior distributions of the
-weight of interocular suppression overlapped with a value of 1 for all
-dipper data sets, and the model captured well the pattern of thresholds
-from all three experiments.
+dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M)
+sine-wave grating stimuli. We find a similar pattern of results across
+stimuli, implying equivalently strong interocular suppression within
+each pathway. Our second experiment measured dichoptic masking within
+and between pathways using the method of constant stimuli. Masking was
+strongest within-pathway, and weakest between S-(L+M) and achromatic
+mechanisms. Finally, we repeated the dipper experiment using temporal
+luminance modulations, which produced slightly weaker interocular
+suppression than for spatially modulated stimuli. We interpret our
+results in the context of a contemporary two-stage model of binocular
+contrast gain control, implemented here using a hierarchical Bayesian
+framework. Posterior distributions of the weight of interocular
+suppression overlapped with a value of 1 for all dipper data sets, and
+the model captured well the pattern of thresholds from all three
+experiments.
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
 The process by which the brain combines independent inputs is of
-fundamental importance for understanding sensory perception. Binocular
-vision is a useful test-case for determining the general principles
-involved in neural signal combination, as our brains typically combine
-the inputs from the left and right eyes to provide binocular single
-vision. In recent years our understanding has been facilitated by the
-development of binocular gain control models that provide a framework to
-interpret empirical data from multiple experimental paradigms and
-techniques, including psychophysics (Meese et al., 2006), EEG (Baker \&
-Wade, 2017), fMRI (Moradi \& Heeger, 2009) and pupillometry (Segala et
-al., 2023). However, most of this work has used achromatic (black and
-white) stimuli; we know comparatively little about how chromatic signals
-are combined binocularly, or about how signals in different ocular and
+fundamental importance for understanding sensory perception (Baker \&
+Wade, 2017; Ernst \& Banks, 2002). Binocular vision is a useful
+test-case for determining the general principles involved in neural
+signal combination, as our brains typically combine the inputs from the
+left and right eyes to provide binocular single vision (Read, 2021). In
+recent years our understanding has been facilitated by the development
+of binocular gain control models that provide a framework to interpret
+empirical data from multiple experimental paradigms and techniques,
+including psychophysics (Meese et al., 2006), EEG (Baker \& Wade, 2017),
+fMRI (Moradi \& Heeger, 2009) and pupillometry (Segala et al., 2023).
+However, most of this work has used achromatic (black and white)
+stimuli; we know comparatively little about how chromatic signals are
+combined binocularly, or about how signals in different ocular and
 chromatic channels interact. In this study we use psychophysical
@@
 the minimum target contrast required to make this judgement with 75\%
-accuracy. The binocular condition is the same, except that the stimuli
-are shown to both eyes. In the half-binocular condition the pedestal is
-shown to both eyes, but the target increment is shown only to one eye.
-Finally, the dichoptic condition involves presenting the pedestal to one
-eye, and the target increment to the other eye.
+accuracy; this reduces at pedestal contrasts around threshold
+(facilitation), and increases at high pedestal contrasts (masking). The
+binocular condition is the same, except that the stimuli are shown to
+both eyes. In the half-binocular condition the pedestal is shown to both
+eyes, but the target increment is shown only to one eye. Finally, the
+dichoptic condition involves presenting the pedestal to one eye, and the
+target increment to the other eye.
 
@@
 
-{\centering \includegraphics{Figures/exampledips.pdf}
+\centering{
+
+\includegraphics{Figures/exampledips.pdf}
 
@@
 
-\end{figure}
+\end{figure}%
 
@@
 across the full range of pedestal contrasts. This demonstrates that
-binocular summation occurs across the full contrast range, when the
+binocular summation occurs across the entire contrast range, when the
 pedestal ocularity is appropriately controlled. Finally, the dichoptic
@@
 blue/yellow axis. At isoluminance, where (L+M) is held constant, this
-channel is driven purely by the S-cone outputs.
+channel is driven purely by the S-cone outputs. Within each chromatic
+pathway, contrast discrimination functions are similar to those for
+achromatic vision, showing evidence of facilitation at low pedestal
+contrasts and masking at high pedestal contrasts (Chen et al., 2000;
+Switkes et al., 1988). There are also interactions between luminance and
+colour mechanisms, which are able to mask each other (Chen et al., 2000;
+Mullen \& Losada, 1994; Switkes et al., 1988), and under some
+circumstances also show cross-pathway facilitation (Cole et al., 1990;
+Mullen \& Losada, 1994; Shooner \& Mullen, 2020; Switkes et al., 1988).
 
 There has not yet been a detailed investigation of binocular contrast
-discrimination in either of these chromatic pathways, however there is
-reason to believe they may differ from the achromatic pathway. At
-detection threshold, binocular summation is greater for chromatic versus
+interactions in either chromatic pathway, however there are reasons to
+believe they may differ from the achromatic pathway. At detection
+threshold, binocular summation is greater for chromatic versus
 achromatic stimuli (Simmons, 2005), implying a more linear initial stage
 of processing. For cross-orientation masking, there are differences in
-the magnitude of masking between chromatic (red/green) and achromatic
-stimuli (Kim et al., 2013; Medina \& Mullen, 2009), as well as
-differences in their temporal dynamics (Kim \& Mullen, 2015). There are
-also interactions between chromatic and achromatic pathways both within
-(Chen et al., 2000) and between (Kingdom \& Libenson, 2015; Mullen et
-al., 2014) the eyes, yet these have not been fully explored for
-arrangements where the target and mask have the same orientation.
-Finally, the neurophysiological underpinnings of colour vision are
-distinct from those of the achromatic system. In primary visual cortex
-(V1), chromatic signals are processed in `blob' regions that are
-revealed by cytochrome oxidase staining (Horton \& Hubel, 1981). The
-blob regions appear to be largely monocular (Livingstone \& Hubel,
-1984), suggesting that binocular combination for chromatic stimuli might
-occur separately than for achromatic stimuli, and perhaps be subject to
-different constraints.
-
-A further property of `blob' regions is that they are less strongly
-orientation-tuned than other regions of V1 (Horton \& Hubel, 1981;
-Livingstone \& Hubel, 1984), and biased towards low spatial frequencies
-(Edwards et al., 1995; Tootell et al., 1988; though see Economides et
-al., 2011). Our recent work (Segala et al., 2023) has investigated
-binocular combination for flickering discs of luminance, which are
-DC-balanced across time (i.e.~the time-averaged luminance is equal to
-the background). Steady-state EEG responses from early visual cortex and
-psychophysical contrast matching data were both consistent with weak
-interocular suppression when using this stimulus arrangement. This is
-very different from the `ocularity invariance' (where binocular and
-monocular stimuli appear equal) that is well-established when using
-spatially modulated stimuli such as sine-wave gratings, and implies
-strong interocular suppression (Baker \& Wade, 2017; Meese et al., 2006;
-Moradi \& Heeger, 2009). There is additional psychophysical evidence
-from matching studies that binocular combination can be close to linear
-for luminance increments (Anstis \& Ho, 1998; Levelt, 1965),
-particularly against a dark background (Baker et al., 2012). Both
-structural and functional data therefore imply that binocular
-combination may differ between spatial and temporal contrast.
+the magnitude of masking between chromatic (L-M) and achromatic stimuli
+(Kim et al., 2013; Medina \& Mullen, 2009), as well as differences in
+their temporal dynamics (Kim \& Mullen, 2015). There are also binocular
+interactions between chromatic and achromatic pathways (Kingdom \&
+Libenson, 2015; Mullen et al., 2014), yet these have not been fully
+explored for arrangements where the target and mask have the same
+orientation. Finally, the neurophysiological underpinnings of colour
+vision may be distinct from those of the achromatic system. The
+classical view is that in primary visual cortex (V1), chromatic signals
+are processed in `blob' regions that are revealed by cytochrome oxidase
+staining (Horton \& Hubel, 1981), and are largely monocular (Livingstone
+\& Hubel, 1984). However subsequent work has revealed a more complex
+arrangement, making such a clear-cut phyisological distinction unlikely
+(for a review, see Shapley \& Hawken, 2011). Nevertheless, the
+physiological segregation between pathways at the output of the retina
+could still lead to differences in the way signals are combined across
+the eyes.
+
+The spatiotemporal profile of stimuli also appears to impact their
+binocular combination. For example, matching studies indicate that
+binocular combination can be close to linear for luminance increments
+(Anstis \& Ho, 1998; Levelt, 1965), particularly against a dark
+background (Baker et al., 2012). This is quite different from the
+`ocularity invariance' (where binocular and monocular stimuli appear
+equal) that is well-established when using spatially modulated stimuli
+such as sine-wave gratings, and implies strong interocular suppression
+(Baker \& Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009). Our
+recent work (Segala et al., 2023) has investigated binocular combination
+for flickering discs of luminance, which are DC-balanced across time
+(i.e.~the time-averaged luminance is equal to the background).
+Steady-state EEG responses from early visual cortex and psychophysical
+contrast matching data were both consistent with weak interocular
+suppression when using this stimulus arrangement, but it is currently
+unclear whether this has implications for contrast discrimination
+performance.
 
@@
 Meese et al. (2006) described above for achromatic grating stimuli and
-extend this to both red/green and blue/yellow isoluminant chromatic
-stimuli. In Experiment 2 we explore dichoptic masking within and between
-these stimuli. Experiment 3 repeats the achromatic condition from the
-first experiment but using a temporally modulated disc rather than
-sine-wave gratings. We take a Bayesian approach to data analysis and
-modelling; by fitting a hierarchical version of the two-stage gain
-control model (Meese et al., 2006) we compare posterior parameter
-distributions to understand how model parameters such as the weight of
-interocular suppression vary across visual pathways.
-
-\hypertarget{materials-methods}{%
-\section{Materials \& Methods}\label{materials-methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+extend this to both L-M and S-(L+M) isoluminant chromatic stimuli. In
+Experiment 2 we explore dichoptic masking within and between these
+stimuli. Experiment 3 repeats the achromatic condition from the first
+experiment but using a temporally modulated disc rather than sine-wave
+gratings. We take a Bayesian approach to data analysis and modelling; by
+fitting a hierarchical version of the two-stage gain control model
+(Meese et al., 2006) we compare posterior parameter distributions to
+understand how model parameters such as the weight of interocular
+suppression vary across visual pathways.
+
+\section{Materials \& Methods}\label{materials-methods}
+
+\subsection{Participants}\label{participants}
 
@@
 procedures were approved by the ethics committee of the Department of
-Psychology at the University of York (ID number 2202).
-
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+Psychology at the University of York (ID number 2202). The study
+conformed to the tenets of the Declaration of Helsinki.
+
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}
 
@@
 (see Procedures) designed to maximise contrast between L and M cones,
-whilst keeping S cone activity constant. In the S-(L+M) condition, the
-isoluminant stimuli maximised S-cone contrast. Stimuli were converted
-from cone space to monitor RGB coordinates using the monitor spectral
-readings and the Stockman-Sharpe 2 degree cone fundamentals (Stockman \&
-Sharpe, 2000). The maximum displayable cone contrasts on our system were
-0.1 for L-M, and 0.88 for S-(L+M). The stimuli in Experiment 3 were
-temporal modulations of luminance applied to a disc made using the same
-raised cosine envelope as described above, but with no further spatial
+whilst keeping S cone activity constant (more accurately, this is a
+\(\Delta L/L - \Delta M/M\) condition, see Cole et al., 1993). In the
+S-(L+M) condition (or more accurately the
+\(\Delta S/S - (\Delta L/L + \Delta M/M)\) condition), the isoluminant
+stimuli maximised S-cone contrast. Stimuli were converted from cone
+space to monitor RGB coordinates using the monitor spectral readings and
+the Stockman-Sharpe 2 degree cone fundamentals (Stockman \& Sharpe,
+2000). The maximum displayable cone contrasts on our system were 0.1 for
+L-M, and 0.88 for S-(L+M). The stimuli in Experiment 3 were temporal
+modulations of luminance applied to a disc made using the same raised
+cosine envelope as described above, but with no further spatial
 modulation. The stimuli counterphase flickered sinusoidally at 4Hz (see
@@
 
-{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{Figures/examplestim.pdf}
+\centering{
+
+\includegraphics[width=0.5\textwidth,height=\textheight]{Figures/examplestim.pdf}
 
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
@@
 
-{\centering \includegraphics{Figures/isosettings.pdf}
+\centering{
+
+\includegraphics{Figures/isosettings.pdf}
 
@@
 \caption{\label{fig-isofig}Isoluminance settings from all participants
-in Experiments 1 and 2. Panel (a) shows red/green and panel (b) shows
-blue/yellow settings that were subsequently used to generate stimuli in
-the main experiments. Within each panel, solid lines show the mean
-settings for each participant, and black curves show the range of
-possible stimuli displayed during the adjustment task.}
-
-\end{figure}
+in Experiments 1 and 2. Panel (a) shows L-M and panel (b) shows S-(L+M)
+settings that were subsequently used to generate stimuli in the main
+experiments. Within each panel, solid lines show the mean settings for
+each participant, and black curves show the range of possible stimuli
+displayed during the adjustment task.}
+
+\end{figure}%
 
@@
 determined in advance based on the data of Experiment 1. There were 12
-possible conditions: baseline detection thresholds for achromatic,
-red/green and blue/yellow stimuli, and the nine possible factorial
-pairings obtained by assigning these conditions to be target and
-dichoptic mask stimuli. Mask contrasts were chosen to be approximately
-16 times their (monocular) detection threshold, based on the data from
-Experiment 1. The contrasts were 16\% Michelson contrast for the
-achromatic stimuli, 6.4\% cone contrast for L-M and 56\% cone contrast
-for S-(L+M). Each block of the experiment tested a single condition, and
-consisted of 200 trials. A high contrast example of the target stimulus
-was displayed at the foot of the screen throughout, so that there was no
-ambiguity about the target identity on a given block. Participants
-completed 10 repetitions of each condition (120 blocks of
-\textasciitilde6 minutes each), lasting around 12 hours, for a total of
-72000 trials (pooled across participants).
+possible conditions: baseline detection thresholds for achromatic, L-M
+and S-(L+M) stimuli, and the nine possible factorial pairings obtained
+by assigning these conditions to be target and dichoptic mask stimuli.
+Mask contrasts were chosen to be approximately 16 times their
+(monocular) detection threshold, based on the data from Experiment 1.
+The contrasts were 16\% Michelson contrast for the achromatic stimuli,
+6.4\% cone contrast for L-M and 56\% cone contrast for S-(L+M). Each
+block of the experiment tested a single condition, and consisted of 200
+trials. A high contrast example of the target stimulus was displayed at
+the foot of the screen throughout, so that there was no ambiguity about
+the target identity on a given block. Participants completed 10
+repetitions of each condition (120 blocks of \textasciitilde6 minutes
+each), lasting around 12 hours, for a total of 72000 trials (pooled
+across participants).
 
@@
 
-\hypertarget{data-analysis-and-computational-modelling}{%
 \subsection{Data analysis and computational
-modelling}\label{data-analysis-and-computational-modelling}}
+modelling}\label{data-analysis-and-computational-modelling}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-s1l}{}{\mathrm{Stage1}_L = \frac{C_L^m}{S + C_L + \omega C_R},}\label{eq-s1l}\end{equation}
-
-\begin{equation}\protect\hypertarget{eq-s1r}{}{\mathrm{Stage1}_R = \frac{C_R^m}{S + C_R + \omega C_L},}\label{eq-s1r}\end{equation}
-
-\begin{equation}\protect\hypertarget{eq-binsum}{}{\mathrm{binsum} = \mathrm{Stage1}_L + \mathrm{Stage1}_R,}\label{eq-binsum}\end{equation}
-
-\begin{equation}\protect\hypertarget{eq-s2}{}{\mathrm{Stage2} = \frac{\mathrm{binsum}^p}{Z + \mathrm{binsum}^q},}\label{eq-s2}\end{equation}
+\begin{equation}\phantomsection\label{eq-s1l}{\mathrm{Stage1}_L = \frac{C_L^m}{S + C_L + \omega C_R},}\end{equation}
+
+\begin{equation}\phantomsection\label{eq-s1r}{\mathrm{Stage1}_R = \frac{C_R^m}{S + C_R + \omega C_L},}\end{equation}
+
+\begin{equation}\phantomsection\label{eq-binsum}{\mathrm{binsum} = \mathrm{Stage1}_L + \mathrm{Stage1}_R,}\end{equation}
+
+\begin{equation}\phantomsection\label{eq-s2}{\mathrm{Stage2} = \frac{\mathrm{binsum}^p}{Z + \mathrm{binsum}^q},}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-thd}{}{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}} = k,}\label{eq-thd}\end{equation}
+\begin{equation}\phantomsection\label{eq-thd}{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}} = k,}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-dprime}{}{d' = \frac{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}}}{k/\tau},}\label{eq-dprime}\end{equation}
+\begin{equation}\phantomsection\label{eq-dprime}{d' = \frac{\mathrm{Stage2}_{\mathrm{target+pedestal}} - \mathrm{Stage2}_{\mathrm{pedestal}}}{k/\tau},}\end{equation}
 
@@
 We also implemented a Bayesian hierarchical version of the model using
-the Stan language (Carpenter et al., 2017). This used a binomial
-generator function to model the proportion correct data at each target
-level, and was fit simultaneously to all participants for a given
-experiment, but separately for each chromatic condition of Experiment 1,
-and the flickering disc data from Experiment 3 (i.e.~four fits in total,
-as for the simplex fitting). Prior distributions for the parameters
-\emph{p}, \emph{q}, \emph{m} and \(\omega\) were Gaussian, with means
-determined from published values (see first row of
-Table~\ref{tbl-parametertable}). Priors for parameters \emph{S},
-\emph{Z} and \emph{k} were uniform. This modelling primarily focuses on
-examining posterior parameter distributions, rather than a model
-comparison approach. We generated over 1 million posterior samples for
-the model, and retained 10\% of them for plotting.
+the Stan probabilistic programming language (Carpenter et al., 2017).
+This used a binomial generator function to model the proportion correct
+data at each target level, and was fit simultaneously to all
+participants for a given experiment, but separately for each chromatic
+condition of Experiment 1, and the flickering disc data from Experiment
+3 (i.e.~four fits in total, as for the simplex fitting). Prior
+distributions for the parameters \emph{p}, \emph{q}, \emph{m} and
+\(\omega\) were Gaussian, with means determined from published values
+(see first row of Table~\ref{tbl-parametertable}). Priors for parameters
+\emph{S}, \emph{Z} and \emph{k} were uniform. This modelling primarily
+focuses on examining posterior parameter distributions, rather than a
+model comparison approach. We generated over 1 million posterior samples
+for the model, and retained 10\% of them for plotting.
 
 Finally, we adapted the two stage model to include parallel pathways to
-process achromatic, red/green and blue/yellow stimuli, that mutually
-suppress each other. We added additional suppressive terms at the first
-(monocular) stage of the model, for example:
-
-\begin{equation}\protect\hypertarget{eq-s1multi}{}{^{AC}\mathrm{Stage1}_L = \frac{AC_L^m}{S + AC_L + \omega_A AC_R + \omega_R RG_R + \omega_B BY_R},}\label{eq-s1multi}\end{equation}
+process achromatic, L-M and S-(L+M) stimuli, that mutually suppress each
+other. We added additional suppressive terms at the first (monocular)
+stage of the model, for example:
+
+\begin{equation}\phantomsection\label{eq-s1multi}{^{AC}\mathrm{Stage1}_L = \frac{AC_L^m}{S + AC_L + \omega_A AC_R + \omega_R RG_R + \omega_B BY_R},}\end{equation}
 
 where \emph{AC} represents the achromatic contrast, \emph{RG} represents
-the red/green contrast, \emph{BY} represents the blue/yellow contrast,
-and \(\omega_A\), \(\omega_R\) and \(\omega_B\) are the accompanying
-weights of interocular suppression. There is an equivalent expression
-for the right eye, and for each of the two isoluminant chromatic
-pathways. To simplify the model, and avoid free parameters that are
-poorly constrained by the data, we fixed several parameters (\emph{p},
+the L-M contrast, \emph{BY} represents the S-(L+M) contrast, and
+\(\omega_A\), \(\omega_R\) and \(\omega_B\) are the accompanying weights
+of interocular suppression. There is an equivalent expression for the
+right eye, and for each of the two isoluminant chromatic pathways. To
+simplify the model, and avoid free parameters that are poorly
+constrained by the data, we fixed several parameters (\emph{p},
 \emph{q}, \emph{m}, \emph{S}, \emph{k}, and \(\omega\) for the
@@
 different pathways, as we did not collect any data for these conditions.
-Previous work (Chen et al., 2000) has measured such interactions, and
-they could in principle be incorporated into the denominator of either
-stage 1 or stage 2 in the model.
-
-\hypertarget{open-science-practices}{%
-\subsection{Open science practices}\label{open-science-practices}}
+Previous work (e.g. Chen et al., 2000; Mullen \& Losada, 1994) has
+measured such interactions, and they could in principle be incorporated
+into the denominator of either stage 1 or stage 2 in the model.
+
+\subsection{Open science practices}\label{open-science-practices}
 
@@
 https://osf.io/3vdga/. The linked GitHub repository also contains a
-fully reproducible version of the manuscript. Note that we deviated
-slightly from the planned preregistration, in that we did not collect
-data for chromatic flickering discs, or for the cross-pathway dichoptic
-experiment using disc stimuli. This is because the grating data from
-Experiments 1 and 2, and the achromatic disc data from Experiment 3,
-were sufficient to address the questions we had hoped to answer from
-these experiments.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{experiment-1}{%
-\subsection{Experiment 1}\label{experiment-1}}
+fully computationally reproducible version of the manuscript. Note that
+we deviated slightly from the planned preregistration, in that we did
+not collect data for chromatic flickering discs, or for the
+cross-pathway dichoptic experiment using disc stimuli. This is because
+the grating data from Experiments 1 and 2, and the achromatic disc data
+from Experiment 3, were sufficient to address the questions we had hoped
+to answer from these experiments.
+
+\section{Results}\label{results}
+
+\subsection{Experiment 1}\label{experiment-1}
 
@@
 
-{\centering \includegraphics{Figures/dipperssimplex.pdf}
+\centering{
+
+\includegraphics{Figures/dipperssimplex.pdf}
 
@@
 
-\end{figure}
-
-A similar pattern of results was observed for both the red/green and
-blue/yellow isoluminant stimuli (see Figure~\ref{fig-dipperfig}b,c).
-Summation at threshold was a factor of 1.71 (4.66dB) for the red/green
-targets, and a factor of 1.73 (4.77dB) for the blue/yellow targets, and
-so was marginally higher than for achromatic stimuli. The general
-character of the dipper functions was largely consistent with the
-achromatic results, though we observed shallower facilitation and weaker
-masking, especially for the blue/yellow stimuli. For example, the
-strongest facilitation in the binocular condition for achromatic stimuli
-was a factor of 2.63, whereas it reduced to a factor of 2.35 for
-red/green stimuli and 1.57 for blue/yellow stimuli. The slope of the
-binocular dipper handle was 0.52 for achromatic stimuli, 0.58 for
-red/green stimuli, and 0.34 for blue/yellow stimuli. Dichoptic masking
-remained as strong for the chromatic conditions as for the achromatic
-stimuli (regression slopes of 1.3 for red/green and 1.21 for
-blue/yellow). The pattern of results for individual participants was
+\end{figure}%
+
+A similar pattern of results was observed for both the L-M and S-(L+M)
+isoluminant stimuli (see Figure~\ref{fig-dipperfig}b,c). Summation at
+threshold was a factor of 1.71 (4.66dB) for the L-M targets, and a
+factor of 1.73 (4.77dB) for the S-(L+M) targets, and so was marginally
+higher than for achromatic stimuli. The general character of the dipper
+functions was largely consistent with the achromatic results, though we
+observed shallower facilitation and weaker masking, especially for the
+S-(L+M) stimuli. For example, the strongest facilitation in the
+binocular condition for achromatic stimuli was a factor of 2.63, whereas
+it reduced to a factor of 2.35 for L-M stimuli and 1.57 for S-(L+M)
+stimuli. The slope of the binocular dipper handle was 0.52 for
+achromatic stimuli, 0.58 for L-M stimuli, and 0.34 for S-(L+M) stimuli.
+Dichoptic masking remained as strong for the chromatic conditions as for
+the achromatic stimuli (regression slopes of 1.3 for L-M and 1.21 for
+S-(L+M)). The pattern of results for individual participants was
 consistent with the group averages, as shown in
@@
 
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
+\subsection{Experiment 2}\label{experiment-2}
 
@@
 
-{\centering \includegraphics{Figures/MCSdata.pdf}
+\centering{
+
+\includegraphics{Figures/MCSdata.pdf}
 
@@
 to the right for the achromatic target with an achromatic mask (white
-and black circles in Figure~\ref{fig-MCSfig}a), for the red/green target
-with a red/green mask (red and green circles in
-Figure~\ref{fig-MCSfig}b), and for the blue/yellow target with a
-blue/yellow mask (blue and yellow circles in Figure~\ref{fig-MCSfig}c).
-Masking was weakest between achromatic masks/targets and chromatic
-masks/targets. Finally, there was an intermediate level of masking
-between red/green and blue/yellow stimuli. This is summarised in
-Figure~\ref{fig-MCSfig}g, which represents threshold elevation for each
-combination of target and mask chromaticity. Note that the positive
-diagonal exhibits the highest values, and represents threshold elevation
-between targets and masks of the same chromaticity.
+and black circles in Figure~\ref{fig-MCSfig}a), for the L-M target with
+an L-M mask (red and green circles in Figure~\ref{fig-MCSfig}b), and for
+the S-(L+M) target with a S-(L+M) mask (blue and yellow circles in
+Figure~\ref{fig-MCSfig}c). Masking was weakest between achromatic
+masks/targets and chromatic masks/targets. Finally, there was an
+intermediate level of masking between L-M and S-(L+M) stimuli. This is
+summarised in Figure~\ref{fig-MCSfig}g, which represents threshold
+elevation for each combination of target and mask chromaticity. Note
+that the positive diagonal exhibits the highest values, and represents
+threshold elevation between targets and masks of the same chromaticity.
 
@@
 
-\hypertarget{experiment-3}{%
-\subsection{Experiment 3}\label{experiment-3}}
+\subsection{Experiment 3}\label{experiment-3}
 
@@
 
-{\centering \includegraphics[width=0.8\textwidth,height=\textheight]{Figures/discdata.pdf}
+\centering{
+
+\includegraphics[width=0.8\textwidth,height=\textheight]{Figures/discdata.pdf}
 
@@
 
-\end{figure}
-
-\hypertarget{computational-modelling}{%
-\subsection{Computational modelling}\label{computational-modelling}}
-
-\hypertarget{tbl-parametertable}{}
+\end{figure}%
+
+\subsection{Computational modelling}\label{computational-modelling}
+
 \begin{table}
-\caption{\label{tbl-parametertable}Summary of fitted model parameters. The top row gives the best fitting
-parameters from the study of Meese et al. (2006). The second section
-shows the best fitting parameters from simplex fits to the averaged
-thresholds for each experiment. The final rows show the posterior
-parameter estimates from the Bayesian model, fitted to each data set
-from Experiments 1 and 3. }\tabularnewline
-
-\centering
-\begin{tabular}{lrrrrrrrr}
+
+\caption{\label{tbl-parametertable}Summary of fitted model parameters.
+The top row gives the best fitting parameters from the study of Meese et
+al.~(2006). The second section shows the best fitting parameters from
+simplex fits to the averaged thresholds for each experiment. The final
+rows show the posterior parameter estimates from the Bayesian model,
+fitted to each data set from Experiments 1 and 3.}
+
+\centering{
+
+\begin{tabular}[t]{lrrrrrrrr}
 \toprule
@@
 Achromatic gratings & 5.96 & 4.69 & 1.34 & 0.87 & 0.13 & 1.00 & 0.20 & 1.59 dB\\
-Red/green gratings & 7.77 & 5.19 & 1.17 & 0.55 & 0.07 & 1.00 & 0.17 & 1.39 dB\\
-Blue/yellow gratings & 16.01 & 11.56 & 1.13 & 0.33 & 0.00 & 0.99 & 0.27 & 1.46 dB\\
+L-M gratings & 7.77 & 5.19 & 1.17 & 0.55 & 0.07 & 1.00 & 0.17 & 1.39 dB\\
+S-(L+M) gratings & 16.01 & 11.56 & 1.13 & 0.33 & 0.00 & 0.99 & 0.27 & 1.46 dB\\
 Flickering discs & 5.62 & 4.51 & 1.26 & 0.95 & 0.25 & 0.89 & 0.13 & 1.05 dB\\
@@
 Achromatic gratings & 7.06 & 5.63 & 1.27 & 0.63 & 0.08 & 0.98 & 0.30 & \\
-Red/green gratings & 5.11 & 3.63 & 1.24 & 1.22 & 0.03 & 1.05 & 0.19 & \\
-Blue/yellow gratings & 6.78 & 5.34 & 1.24 & 0.61 & 0.01 & 0.95 & 0.34 & \\
+L-M gratings & 5.11 & 3.63 & 1.24 & 1.22 & 0.03 & 1.05 & 0.19 & \\
+S-(L+M) gratings & 6.78 & 5.34 & 1.24 & 0.61 & 0.01 & 0.95 & 0.34 & \\
 Flickering discs & 7.16 & 5.76 & 1.25 & 0.65 & 0.13 & 0.87 & 0.24 & \\
@@
 \end{tabular}
-\end{table}
+
+}
+
+\end{table}%
 
@@
 below 1 (0.89) for our flickering discs. The exponent values (\emph{p}
-and \emph{q}) for the blue/yellow gratings are rather different from
-those of the other conditions. In previous work (Meese et al., 2006) the
+and \emph{q}) for the S-(L+M) gratings are rather different from those
+of the other conditions. In previous work (Meese et al., 2006) the
 second stage gain control nonlinearity (Equation~\ref{eq-s2}) does
@@
 
-{\centering \includegraphics{Figures/stanoutput.pdf}
+\centering{
+
+\includegraphics{Figures/stanoutput.pdf}
 
@@
 chromaticity. The weakest suppression was between achromatic targets and
-masks and blue/yellow targets and masks, and the strongest suppression
-was between red/green targets and blue/yellow masks. Note that the
-weight parameter value of \(\omega\) = 1.11 for this condition is
-slightly higher than that of the within-channel weights (values around
-1), even though the within-channel conditions generate more threshold
-elevation. In the model, high thresholds for within-channel dichoptic
-masks occur because the target and mask are summed together, which
-causes additional masking (see Baker et al., 2013). However it is clear
-that the posterior distribution of the weight parameter is quite broad
-and overlaps 1, so this difference may not be meaningful. There do not
-appear to be any other salient patterns in the suppressive weight
-estimates.
+masks and S-(L+M) targets and masks, and the strongest suppression was
+between L-M targets and S-(L+M) masks. Note that the weight parameter
+value of \(\omega\) = 1.11 for this condition is slightly higher than
+that of the within-channel weights (values around 1), even though the
+within-channel conditions generate more threshold elevation. In the
+model, high thresholds for within-channel dichoptic masks occur because
+the target and mask are summed together, which causes additional masking
+(see Baker et al., 2013). However it is clear that the posterior
+distribution of the weight parameter is quite broad and overlaps 1, so
+this difference may not be meaningful. There do not appear to be any
+other salient patterns in the suppressive weight estimates.
 
@@
 
-{\centering \includegraphics{Figures/MCSmodel.pdf}
+\centering{
+
+\includegraphics{Figures/MCSmodel.pdf}
 
@@
 
-\end{figure}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\end{figure}%
+
+\section{Discussion}\label{discussion}
 
@@
   Interocular suppression is strongest within a post-retinal pathway,
-  and weakest between the achromatic and blue/yellow pathways
+  and weakest between the achromatic and S-(L+M) pathways
 \item
@@
 
-\hypertarget{summation-at-threshold}{%
-\subsection{Summation at threshold}\label{summation-at-threshold}}
+\subsection{Summation at threshold}\label{summation-at-threshold}
 
@@
 range \(1 < m < 1.4\), consistent with the high levels of summation
-observed empirically.
-
-\hypertarget{interocular-suppression}{%
-\subsection{Interocular suppression}\label{interocular-suppression}}
+observed empirically. Note that the exponents at stage 2 (\(p\) and
+\(q\)) have no effect on binocular summation at threshold, because they
+impact after the signals have been combined. The differences in these
+parameter values between chromatic conditions (see
+Table~\ref{tbl-parametertable}) primarily reflects differences in the
+slope of the dipper handle (chromatic conditions are shallower), and are
+of incidental interest for our main questions.
+
+\subsection{Interocular suppression}\label{interocular-suppression}
 
@@
 
-\hypertarget{psychometric-slopes}{%
-\subsection{Psychometric slopes}\label{psychometric-slopes}}
+Strong interocular suppression is responsible for the convergence of
+monocular and binocular dipper handles (e.g. Legge, 1984) at high
+pedestal contrasts (see Figure~\ref{fig-dipperfig}). In the model,
+monocular stimuli avoid the impact of interocular suppression, because
+the unstimulated eye sees a blank screen, and so contributes a contrast
+of zero to the denominator of the stimulated eye. Binocular stimuli
+receive strong suppression, which acts to approximately halve the
+excitation when contrasts in the two eyes are equal (see Georgeson et
+al., 2016; Meese et al., 2006). This normalization leads to very similar
+responses for monocular and binocular stimulation. In the auditory
+system, binaural combination of amplitude modulated signals involves
+much weaker suppression between channels, and the monaural and binaural
+dipper handles do not converge at high contrasts (Baker et al., 2020).
+
+One phenomenon that often occurs with conflicting dichoptic stimuli is
+binocular rivalry, and it is worth considering how this might impact the
+results of Experiment 2, where the two eyes often saw stimuli of
+different chromaticities. However rivalry typically only `kicks in' at
+presentation durations longer than the 200ms used here (see e.g. Wolfe,
+1983), and certainly rivalry alternations need much longer presentations
+to be clearly observed. In a dichoptic masking paradigm it is often
+difficult to distinguish dichoptic fusion from dominance of one eye over
+the other; indeed, interocular suppression of sufficient strength would
+render the weaker stimulus invisible. On the other hand, if the stimuli
+appear fused, we might expect dichoptic colour mixing to occur (Kingdom
+\& Libenson, 2015; Kingdom \& Wang, 2015), whereas if one eye dominates
+the colour percept would be equivalent to monocular presentation of the
+dominant stimulus. Here we used a performance task (2AFC
+detection/discrimination), and did not explicitly ask participants about
+the stimulus appearance. Future studies could use matching and
+adjustment tasks to investigate this further.
+
+\subsection{Psychometric slopes}\label{psychometric-slopes}
 
@@
 
-\hypertarget{physiological-substrates}{%
-\subsection{Physiological substrates}\label{physiological-substrates}}
+\subsection{Physiological substrates}\label{physiological-substrates}
 
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+\section{Conclusions}\label{conclusions}
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
+\section{Acknowledgements}\label{acknowledgements}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
+\section{References}\label{references}
+
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Anstis1998}{}}%
+\bibitem[\citeproctext]{ref-Anstis1998}
 Anstis, S., \& Ho, A. (1998). Nonlinear combination of luminance
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
+\bibitem[\citeproctext]{ref-Baker2018}
 Baker, D. H., Lygo, F. A., Meese, T. S., \& Georgeson, M. A. (2018).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2007b}{}}%
+\bibitem[\citeproctext]{ref-Baker2007b}
 Baker, D. H., \& Meese, T. S. (2007). Binocular contrast interactions:
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2012b}{}}%
+\bibitem[\citeproctext]{ref-Baker2012b}
 Baker, D. H., \& Meese, T. S. (2012). Zero-dimensional noise: The best
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
+\bibitem[\citeproctext]{ref-Baker2007}
 Baker, D. H., Meese, T. S., \& Georgeson, M. A. (2007). Binocular
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2013}{}}%
+\bibitem[\citeproctext]{ref-Baker2013}
 Baker, D. H., Meese, T. S., \& Georgeson, M. A. (2013). Paradoxical
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
+\bibitem[\citeproctext]{ref-Baker2020}
+Baker, D. H., Vilidaite, G., McClarnon, E., Valkova, E., Bruno, A., \&
+Millman, R. E. (2020). Binaural summation of amplitude modulation
+involves weak interaural suppression. \emph{Sci Rep}, \emph{10}(1),
+3560. \url{https://doi.org/10.1038/s41598-020-60602-5}
+
+\bibitem[\citeproctext]{ref-Baker2017}
 Baker, D. H., \& Wade, A. R. (2017). Evidence for an optimal algorithm
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2012}{}}%
+\bibitem[\citeproctext]{ref-Baker2012}
 Baker, D. H., Wallis, S. A., Georgeson, M. A., \& Meese, T. S. (2012).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
+\bibitem[\citeproctext]{ref-Campbell1965}
 Campbell, F. W., \& Green, D. G. (1965). Monocular versus binocular
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
+\bibitem[\citeproctext]{ref-Carpenter2017}
 Carpenter, B., Gelman, A., Hoffman, M. D., Lee, D., Goodrich, B.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Chatterjee2021}{}}%
+\bibitem[\citeproctext]{ref-Chatterjee2021}
 Chatterjee, S., Ohki, K., \& Reid, R. C. (2021). Chromatic micromaps in
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Chen2000}{}}%
+\bibitem[\citeproctext]{ref-Chen2000}
 Chen, C., Foley, J. M., \& Brainard, D. H. (2000). Detection of
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dougherty2019}{}}%
+\bibitem[\citeproctext]{ref-Cole1993}
+Cole, G. R., Hine, T., \& McIlhagga, W. (1993). Detection mechanisms in
+l-, m-, and s-cone contrast space. \emph{J Opt Soc Am A}, \emph{10}(1),
+38--51. \url{https://doi.org/10.1364/josaa.10.000038}
+
+\bibitem[\citeproctext]{ref-Cole1990}
+Cole, G. R., Stromeyer, C. F., 3rd, \& Kronauer, R. E. (1990). Visual
+interactions with luminance and chromatic stimuli. \emph{J Opt Soc Am
+A}, \emph{7}(1), 128--140. \url{https://doi.org/10.1364/josaa.7.000128}
+
+\bibitem[\citeproctext]{ref-Dougherty2019}
 Dougherty, K., Cox, M. A., Westerberg, J. A., \& Maier, A. (2019).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Economides2011}{}}%
+\bibitem[\citeproctext]{ref-Economides2011}
 Economides, J. R., Sincich, L. C., Adams, D. L., \& Horton, J. C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Edwards1995}{}}%
-Edwards, D. P., Purpura, K. P., \& Kaplan, E. (1995). Contrast
-sensitivity and spatial frequency response of primate cortical neurons
-in and around the cytochrome oxidase blobs. \emph{Vision Res},
-\emph{35}(11), 1501--1523.
-\url{https://doi.org/10.1016/0042-6989(94)00253-i}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Foley1981}{}}%
+\bibitem[\citeproctext]{ref-Ernst2002}
+Ernst, M. O., \& Banks, M. S. (2002). Humans integrate visual and haptic
+information in a statistically optimal fashion. \emph{Nature},
+\emph{415}(6870), 429--433. \url{https://doi.org/10.1038/415429a}
+
+\bibitem[\citeproctext]{ref-Foley1981}
 Foley, J. M., \& Legge, G. E. (1981). Contrast detection and
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Georgeson2016}{}}%
+\bibitem[\citeproctext]{ref-Georgeson2016}
 Georgeson, M. A., Wallis, S. A., Meese, T. S., \& Baker, D. H. (2016).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Horton1981}{}}%
+\bibitem[\citeproctext]{ref-Horton1981}
 Horton, J. C., \& Hubel, D. H. (1981). Regular patchy distribution of
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kim2013}{}}%
+\bibitem[\citeproctext]{ref-Kim2013}
 Kim, Y. J., Gheiratmand, M., \& Mullen, K. T. (2013). Cross-orientation
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kim2015}{}}%
+\bibitem[\citeproctext]{ref-Kim2015}
 Kim, Y. J., \& Mullen, K. T. (2015). The dynamics of cross-orientation
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
+\bibitem[\citeproctext]{ref-Kingdom2015}
 Kingdom, F. A. A., \& Libenson, L. (2015). Dichoptic color saturation
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1979}{}}%
+\bibitem[\citeproctext]{ref-Kingdom2015b}
+Kingdom, F. A. A., \& Wang, D. (2015). Dichoptic colour-saturation
+masking is unmasked by binocular luminance contrast. \emph{Vision Res},
+\emph{116}(Pt A), 45--52.
+\url{https://doi.org/10.1016/j.visres.2015.08.016}
+
+\bibitem[\citeproctext]{ref-Legge1979}
 Legge, G. E. (1979). Spatial frequency masking in human vision:
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
+\bibitem[\citeproctext]{ref-Legge1984}
 Legge, G. E. (1984). Binocular contrast summation--II. Quadratic
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Levelt1965}{}}%
+\bibitem[\citeproctext]{ref-Levelt1965}
 Levelt, W. J. (1965). Binocular brightness averaging and contour
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Livingstone1984}{}}%
+\bibitem[\citeproctext]{ref-Livingstone1984}
 Livingstone, M. S., \& Hubel, D. H. (1984). Anatomy and physiology of a
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lu2008}{}}%
+\bibitem[\citeproctext]{ref-Lu2008}
 Lu, Z.-L., \& Dosher, B. A. (2008). Characterizing observers using
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Maehara2005}{}}%
+\bibitem[\citeproctext]{ref-Maehara2005}
 Maehara, G., \& Goryo, K. (2005). Binocular, monocular and dichoptic
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Medina2009}{}}%
+\bibitem[\citeproctext]{ref-Medina2009}
 Medina, J. M., \& Mullen, K. T. (2009). Cross-orientation masking in
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2009}{}}%
+\bibitem[\citeproctext]{ref-Meese2009}
 Meese, T. S., \& Baker, D. H. (2009). Cross-orientation masking is speed
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
+\bibitem[\citeproctext]{ref-Meese2006}
 Meese, T. S., Georgeson, M. A., \& Baker, D. H. (2006). Binocular
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+\bibitem[\citeproctext]{ref-Moradi2009}
 Moradi, F., \& Heeger, D. J. (2009). Inter-ocular contrast normalization
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mullen2014}{}}%
+\bibitem[\citeproctext]{ref-Mullen2014}
 Mullen, K. T., Kim, Y. J., \& Gheiratmand, M. (2014). Contrast
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pelli1985}{}}%
+\bibitem[\citeproctext]{ref-Mullen1994}
+Mullen, K. T., \& Losada, M. A. (1994). Evidence for separate pathways
+for color and luminance detection mechanisms. \emph{J Opt Soc Am A Opt
+Image Sci Vis}, \emph{11}(12), 3136--3151.
+\url{https://doi.org/10.1364/josaa.11.003136}
+
+\bibitem[\citeproctext]{ref-Pelli1985}
 Pelli, D. G. (1985). Uncertainty explains many aspects of visual
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schutt2016}{}}%
+\bibitem[\citeproctext]{ref-Read2021}
+Read, J. C. A. (2021). Binocular vision and stereopsis across the animal
+kingdom. \emph{Annu Rev Vis Sci}, \emph{7}, 389--415.
+\url{https://doi.org/10.1146/annurev-vision-093019-113212}
+
+\bibitem[\citeproctext]{ref-Schutt2016}
 Schütt, H. H., Harmeling, S., Macke, J. H., \& Wichmann, F. A. (2016).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
+\bibitem[\citeproctext]{ref-Segala2023}
 Segala, F. G., Bruno, A., Martin, J. T., Aung, M. T., Wade, A. R., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sharpe2011}{}}%
+\bibitem[\citeproctext]{ref-Shapley2011}
+Shapley, R., \& Hawken, M. J. (2011). Color in the cortex: Single- and
+double-opponent cells. \emph{Vision Res}, \emph{51}(7), 701--717.
+\url{https://doi.org/10.1016/j.visres.2011.02.012}
+
+\bibitem[\citeproctext]{ref-Sharpe2011}
 Sharpe, L. T., Stockman, A., Jagla, W., \& Jägle, H. (2011). A luminous
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Simmons2005}{}}%
+\bibitem[\citeproctext]{ref-Shooner2020}
+Shooner, C., \& Mullen, K. T. (2020). Enhanced luminance sensitivity on
+color and luminance pedestals: Threshold measurements and a model of
+parvocellular luminance processing. \emph{J Vis}, \emph{20}(6), 12.
+\url{https://doi.org/10.1167/jov.20.6.12}
+
+\bibitem[\citeproctext]{ref-Simmons2005}
 Simmons, D. R. (2005). The binocular combination of chromatic contrast.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sincich2005}{}}%
+\bibitem[\citeproctext]{ref-Sincich2005}
 Sincich, L. C., \& Horton, J. C. (2005). The circuitry of V1 and V2:
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
+\bibitem[\citeproctext]{ref-Stockman2000}
 Stockman, A., \& Sharpe, L. T. (2000). The spectral sensitivities of the
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tootell1988}{}}%
-Tootell, R. B., Silverman, M. S., Hamilton, S. L., De Valois, R. L., \&
-Switkes, E. (1988). Functional anatomy of macaque striate cortex. III.
-color. \emph{J Neurosci}, \emph{8}(5), 1569--1593.
-\url{https://doi.org/10.1523/JNEUROSCI.08-05-01569.1988}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wallis2013}{}}%
+\bibitem[\citeproctext]{ref-Switkes1988}
+Switkes, E., Bradley, A., \& De Valois, K. K. (1988). Contrast
+dependence and mechanisms of masking interactions among chromatic and
+luminance gratings. \emph{J Opt Soc Am A}, \emph{5}(7), 1149--1162.
+\url{https://doi.org/10.1364/josaa.5.001149}
+
+\bibitem[\citeproctext]{ref-Wallis2013}
 Wallis, S. A., Baker, D. H., Meese, T. S., \& Georgeson, M. A. (2013).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Yu2002}{}}%
+\bibitem[\citeproctext]{ref-Wolfe1983}
+Wolfe, J. M. (1983). Influence of spatial frequency, luminance, and
+duration on binocular rivalry and abnormal fusion of briefly presented
+dichoptic stimuli. \emph{Perception}, \emph{12}(4), 447--456.
+\url{https://doi.org/10.1068/p120447}
+
+\bibitem[\citeproctext]{ref-Yu2002}
 Yu, C., Klein, S. A., \& Levi, D. M. (2002). Facilitation of contrast
@@
 
-\hypertarget{appendices}{%
-\section{Appendices}\label{appendices}}
+\section{Appendices}\label{appendices}
 
@@
 
-{\centering \includegraphics{Figures/individualdippers.pdf}
+\centering{
+
+\includegraphics{Figures/individualdippers.pdf}
 
@@
 
-{\centering \includegraphics{Figures/individualMCS.pdf}
+\centering{
+
+\includegraphics{Figures/individualMCS.pdf}
 
@@
 
-{\centering \includegraphics{Figures/individualdiscs.pdf}
+\centering{
+
+\includegraphics{Figures/individualdiscs.pdf}
 

### 2024-09-15 manuscript.qmd
Implemented further reviewer suggestions

@@
   - name: Federico G. Segala$^1$
-  - name: Annie Y. Morsi$^1$
+  - name: Anisa Y. Morsi$^1$
   - name: Rowan J. Huxley$^{1,3}$
@@
 csl: journal-of-vision.csl
+# prefer-html: true
 format:
@@
   # docx
-# prefer-html: true
 header-includes: 
@@
 However, most of this work has involved achromatic (black and white) stimuli, and it is not clear if the same processes apply in colour-sensitive pathways.
-In our first experiment, we measured contrast discrimination ('dipper') functions for four key ocular configurations (monocular, binocular, half-binocular and dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M) sine-wave grating stimuli.
+In our first experiment, we measured contrast discrimination ('dipper') functions for four key ocular configurations (monocular, binocular, half-binocular and dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M) sine-wave grating stimuli (L: long-, M: medium-, S: short-wavelength).
 We find a similar pattern of results across stimuli, implying equivalently strong interocular suppression within each pathway.
@@
 At the output of the human retina, cone responses are split into three distinct pathways.
-The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information [see @Sharpe2011], and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
+The sum of long- (L) and medium- (M) wavelength cone outputs (L+M) transmits luminance information [see @Sharpe2011], and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above).
 The difference of long- and medium-wavelength cone outputs (L-M) is responsive to chromatic stimuli modulating along a red/green axis in colour space.
-Finally the opponent (S-(L+M)) channel codes chromatic stimuli modulating along a blue/yellow axis.
+Finally the opponent short-wavelength (S) channel codes chromatic stimuli modulating along a blue/yellow axis (S-(L+M)).
 At isoluminance, where (L+M) is held constant, this channel is driven purely by the S-cone outputs.
-Within each chromatic pathway, contrast discrimination functions are similar to those for achromatic vision, showing evidence of facilitation at low pedestal contrasts and masking at high pedestal contrasts [@Switkes1988; @Chen2000].
+Note that we use these shorthand terms throughout to refer to chromatic mechanisms, but acknowledge that in reality the photoreceptor outputs are weighted, for example S-0.5(L+M), and 3L+M.
+Within each chromatic pathway, contrast discrimination functions (which plot discrimination thresholds against pedestal contrast; sometimes referred to as TvC functions) are similar to those for achromatic vision, showing evidence of facilitation at low pedestal contrasts and masking at high pedestal contrasts [@Switkes1988; @Chen2000].
 There are also interactions between luminance and colour mechanisms, which are able to mask each other [@Switkes1988; @Mullen1994; @Chen2000], and under some circumstances also show cross-pathway facilitation [@Switkes1988; @Cole1990; @Mullen1994; @Shooner2020].
@@
 Finally, the neurophysiological underpinnings of colour vision may be distinct from those of the achromatic system.
-The classical view is that in primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981], and are largely monocular [@Livingstone1984].
-However subsequent work has revealed a more complex arrangement, making such a clear-cut phyisological distinction unlikely [for a review, see @Shapley2011].
+The classical view was that in primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981], and are largely monocular [@Livingstone1984].
+However subsequent work has revealed a large population of colour-luminance neurons with a subset of colour-only ones, making such a clear-cut physiological distinction unlikely [for a review, see @Shapley2011].
 Nevertheless, the physiological segregation between pathways at the output of the retina could still lead to differences in the way signals are combined across the eyes.
@@
 We additionally implemented a hierarchical Bayesian version of the model to estimate full posterior parameter distributions.
-This model was fit simultaneously to the full trial-by-trial data from all participants who participated in a given experiment (i.e.
+This model was fit simultaneously to the full trial-by-trial data from all participants who completed a given experiment (i.e.
 the model was fitted separately to each of the four dipper data sets).
@@
 
-In V1, the classical view is that chromatic stimuli are processed in 'blob' regions that are largely monocular as they fall within ocular dominance columns [@Livingstone1984].
+In V1, the classical view was that chromatic stimuli are processed in 'blob' regions that are largely monocular as they fall within ocular dominance columns [@Livingstone1984].
 However more recent work has shown chromatic processing outside of the blobs [@Sincich2005], especially for stimuli with spatial structure [@Chatterjee2021].

### 2024-09-15 manuscript.tex
Implemented further reviewer suggestions

@@
 Hansford\^{}1; Federico G.
-Segala\^{}1; Annie Y.
+Segala\^{}1; Anisa Y.
 Morsi\^{}1; Rowan J.
@@
 \author{Daniel H. Baker\(^{1,2,*}\) \and Kirralise J.
-Hansford\(^1\) \and Federico G. Segala\(^1\) \and Annie Y.
+Hansford\(^1\) \and Federico G. Segala\(^1\) \and Anisa Y.
 Morsi\(^1\) \and Rowan J. Huxley\(^{1,3}\) \and Joel T.
@@
 dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M)
-sine-wave grating stimuli. We find a similar pattern of results across
-stimuli, implying equivalently strong interocular suppression within
-each pathway. Our second experiment measured dichoptic masking within
-and between pathways using the method of constant stimuli. Masking was
-strongest within-pathway, and weakest between S-(L+M) and achromatic
-mechanisms. Finally, we repeated the dipper experiment using temporal
-luminance modulations, which produced slightly weaker interocular
-suppression than for spatially modulated stimuli. We interpret our
-results in the context of a contemporary two-stage model of binocular
-contrast gain control, implemented here using a hierarchical Bayesian
-framework. Posterior distributions of the weight of interocular
-suppression overlapped with a value of 1 for all dipper data sets, and
-the model captured well the pattern of thresholds from all three
-experiments.
+sine-wave grating stimuli (L: long-, M: medium-, S: short-wavelength).
+We find a similar pattern of results across stimuli, implying
+equivalently strong interocular suppression within each pathway. Our
+second experiment measured dichoptic masking within and between pathways
+using the method of constant stimuli. Masking was strongest
+within-pathway, and weakest between S-(L+M) and achromatic mechanisms.
+Finally, we repeated the dipper experiment using temporal luminance
+modulations, which produced slightly weaker interocular suppression than
+for spatially modulated stimuli. We interpret our results in the context
+of a contemporary two-stage model of binocular contrast gain control,
+implemented here using a hierarchical Bayesian framework. Posterior
+distributions of the weight of interocular suppression overlapped with a
+value of 1 for all dipper data sets, and the model captured well the
+pattern of thresholds from all three experiments.
 
@@
 At the output of the human retina, cone responses are split into three
-distinct pathways. The sum of long- and medium-wavelength cone outputs
-(L+M) transmits luminance information (see Sharpe et al., 2011), and is
-likely responsible for the binocular combination effects previously
-studied using achromatic stimuli (see above). The difference of long-
-and medium-wavelength cone outputs (L-M) is responsive to chromatic
-stimuli modulating along a red/green axis in colour space. Finally the
-opponent (S-(L+M)) channel codes chromatic stimuli modulating along a
-blue/yellow axis. At isoluminance, where (L+M) is held constant, this
-channel is driven purely by the S-cone outputs. Within each chromatic
-pathway, contrast discrimination functions are similar to those for
-achromatic vision, showing evidence of facilitation at low pedestal
-contrasts and masking at high pedestal contrasts (Chen et al., 2000;
-Switkes et al., 1988). There are also interactions between luminance and
-colour mechanisms, which are able to mask each other (Chen et al., 2000;
-Mullen \& Losada, 1994; Switkes et al., 1988), and under some
-circumstances also show cross-pathway facilitation (Cole et al., 1990;
-Mullen \& Losada, 1994; Shooner \& Mullen, 2020; Switkes et al., 1988).
+distinct pathways. The sum of long- (L) and medium- (M) wavelength cone
+outputs (L+M) transmits luminance information (see Sharpe et al., 2011),
+and is likely responsible for the binocular combination effects
+previously studied using achromatic stimuli (see above). The difference
+of long- and medium-wavelength cone outputs (L-M) is responsive to
+chromatic stimuli modulating along a red/green axis in colour space.
+Finally the opponent short-wavelength (S) channel codes chromatic
+stimuli modulating along a blue/yellow axis (S-(L+M)). At isoluminance,
+where (L+M) is held constant, this channel is driven purely by the
+S-cone outputs. Note that we use these shorthand terms throughout to
+refer to chromatic mechanisms, but acknowledge that in reality the
+photoreceptor outputs are weighted, for example S-0.5(L+M), and 3L+M.
+Within each chromatic pathway, contrast discrimination functions (which
+plot discrimination thresholds against pedestal contrast; sometimes
+referred to as TvC functions) are similar to those for achromatic
+vision, showing evidence of facilitation at low pedestal contrasts and
+masking at high pedestal contrasts (Chen et al., 2000; Switkes et al.,
+1988). There are also interactions between luminance and colour
+mechanisms, which are able to mask each other (Chen et al., 2000; Mullen
+\& Losada, 1994; Switkes et al., 1988), and under some circumstances
+also show cross-pathway facilitation (Cole et al., 1990; Mullen \&
+Losada, 1994; Shooner \& Mullen, 2020; Switkes et al., 1988).
 
@@
 vision may be distinct from those of the achromatic system. The
-classical view is that in primary visual cortex (V1), chromatic signals
+classical view was that in primary visual cortex (V1), chromatic signals
 are processed in `blob' regions that are revealed by cytochrome oxidase
 staining (Horton \& Hubel, 1981), and are largely monocular (Livingstone
-\& Hubel, 1984). However subsequent work has revealed a more complex
-arrangement, making such a clear-cut phyisological distinction unlikely
-(for a review, see Shapley \& Hawken, 2011). Nevertheless, the
-physiological segregation between pathways at the output of the retina
-could still lead to differences in the way signals are combined across
-the eyes.
+\& Hubel, 1984). However subsequent work has revealed a large population
+of colour-luminance neurons with a subset of colour-only ones, making
+such a clear-cut physiological distinction unlikely (for a review, see
+Shapley \& Hawken, 2011). Nevertheless, the physiological segregation
+between pathways at the output of the retina could still lead to
+differences in the way signals are combined across the eyes.
 
@@
 simultaneously to the full trial-by-trial data from all participants who
-participated in a given experiment (i.e.~the model was fitted separately
-to each of the four dipper data sets). Figure~\ref{fig-bayesianmodel}a-d
+completed a given experiment (i.e.~the model was fitted separately to
+each of the four dipper data sets). Figure~\ref{fig-bayesianmodel}a-d
 summarises the model behaviour, which displays the same pattern of
@@
 
-In V1, the classical view is that chromatic stimuli are processed in
+In V1, the classical view was that chromatic stimuli are processed in
 `blob' regions that are largely monocular as they fall within ocular
